### 2015-11-19 contextual combinatorial cascading bandits.tex
add ICML 2015 template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2015 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2015,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2015} with
% \usepackage[nohyperref]{icml2015} above.
\usepackage{hyperref}

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{bm}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2015}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2015}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Contextual Combinatorial Cascading Bandits}

\begin{document}

\twocolumn[
\icmltitle{Contextual Combinatorial Cascading Bandits}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2015
% package.
\icmlauthor{Your Name}{email@yourdomain.edu}
\icmladdress{Your Fantastic Institute,
            314159 Pi St., Palo Alto, CA 94306 USA}
\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
\icmladdress{Their Fantastic Institute,
            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

\vskip 0.3in
]

\begin{abstract} 
The purpose of this document is to provide both the basic paper template and
submission guidelines.
\end{abstract}

\section{Introduction}

\section{Related Works}

\section{Contextual Combinatorial Cascading Bandits}

\subsection{Setting}

We model our problem as a contextual combinatorial cascading bandit. Suppose we have $E=\{1,...,L\}$ a finite set of $L$ ground items. Let $\prod^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. Let $\cS \subset \prod^{\leq K}(E)$ consist of feasible actions with length no more than $K$.

At time $t$, the learning agent is revealed with feature vectors $X_{t,a} \in \RR^d$ for every basic arm $a \in E$, where we have $\norm{X_{t,a}}_2 \leq 1$; this feature vector combines both information of the user and the corresponding basic arm. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$, which is called weight for arm $a$ at time $t$, to indicate whether the user on round $t$ will click on the item $a$ or not. Assume $\bw_{t,a}$ are mutually independent and satisfy
\begin{equation}
	\label{eq:expectation}
	\EE[\bw_{t,a} | X_{t,a}] = \theta_*^{\top} X_{t,a}
\end{equation}
where $\theta_*$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_*}_2 \leq 1$ and $0 < \theta_*^{\top} x_{t,a} < 1$ for all $t, a$. At time $t$, the learning agent chooses a solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ based on its past observations. The user then checks from the first item and stops if she has checked all items or click on one interesting. Suppose we add position discount $1 \geq\gamma_1 \geq \gamma_2\geq \cdots \geq \gamma_K>0$. If the user clicks on the $k$-th item of $\bA_t$, the reward we receive is $\gamma_k$. At the end of time $t$, the agent observes $\bO_t$ items in $\bA_t$ and receive the reward
$$
\br_t = \max_{1 \leq k \leq \abs{\bA_t}} \gamma_k \bw_t(\ba_k^t) = \bigvee_{k=1}^{\abs{A_t}} \gamma_k \bw_t(\ba_k^t),
$$
where we use the notation that $\bigvee_{1\leq i\leq n}a_i = \max_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed $\bw_t(\ba_k^t), 1\leq k\leq\bO_t$.

If we define a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
\begin{align*}
	& f : \cS \times [0,1]^E \to [0,1]\\
	& f(A,w) = \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1}(1 -w(a_i)))w(a_k),
\end{align*}
then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[r_t]=f(\bA_t,\theta_*^{\top}X_t)$ where $X_t=(X_{t,1} \cdots X_{t,L})\in\RR^{d\times L}$. Let 
$$
A_t^* = \argmax_{A\in \cS} f(A,\theta_*^{\top}X_t).
$$ 
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE[\sum_{t=1}^T f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)].
$$
In the rest of this paper, we denote $\Delta_{t,\bA_t} = f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)$ and $R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}]$.

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k X_{s,\ba_k^s})$. By ridge regression of data 
$$
\{(\gamma_k X_{s,\ba_k^s}, \gamma_k\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t
\end{equation}
where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma^{2k-2}X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.
\subsection{Algorithm}

\begin{theorem}[Theorem 2 in \cite{abbasi2011improved}]
	\label{thm:theta_estimate}
	Let 
	$$
		\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}.
	$$
	Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
	\begin{equation}
	\norm{\hat{\theta}_t - \theta_*}_{\bV_{t}} \leq \beta_{t}(\delta).
	\end{equation}
\end{theorem}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
\begin{equation}
	\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}
By theorem \ref{thm:theta_estimate}, it holds that
\begin{lemma}
	For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
	$$
		0 \leq \bU_t(a) - \theta_*^{\top}X_{t,a} \leq 2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	\begin{align*}
	\abs{\hat{\theta}_{t-1}^{\top}X_{t,a} - \theta_*^{\top}X_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{X_{t,a}}_{\bV_{t-1}^{-1}} \\
	&\leq \beta_{t}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
\end{proof}

\begin{algorithm}
	\caption{ConComCascade}
	\label{alg:ConComCascade}
	\begin{algorithmic}
		\STATE {//Initialization}
		\STATE {Parameters: $\delta > 0, \lambda >0, 1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$}
		\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 0, \bV_0 = \lambda I$}
		\STATE{}

		\FORALL {t=1,2,...}
			\STATE {//Compute UCBs}
			\STATE {$\forall a\in E: $}
			\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
			\STATE {}

			\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
			\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
			\STATE {Observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
			\STATE {}

			\STATE {//Update statistics}
			\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 X_{t, \ba_k^t}X_{t, \ba_k^t}^{\top}$}
			\STATE {$X^t \leftarrow (X^{t-1, \top}, \gamma_1 X_{t, \ba_1^t},  ..., \gamma_{\bO_t} X_{t, \ba_{\bO_t}^t})^{\top}$}
			\STATE {$Y^t \leftarrow (Y^{t-1,\top}, \gamma_1 \bw(\ba_1^t),  ..., \gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t))^{\top}$}
			\STATE {$\hat{\theta}_t \leftarrow (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t$}
			\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}

		\ENDFOR {~~t}
	\end{algorithmic}
\end{algorithm}

Let
\begin{equation}
	C_\gamma = \sum_{k=1}^{K} \gamma_k^2.
\end{equation}

\begin{theorem}
	For any $\delta > 0$, with probability at least $1 - \delta$, we have
	\begin{equation}
		R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
	\end{equation}
\end{theorem}
\begin{proof}
	With probability at least $1-\delta$,
	\begin{equation}
	\begin{split}
	&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
	&\leq \sum_{t=1}^{T} \frac{8}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\\
	&\leq \frac{8}{f^*}\beta_T(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
	&\leq \frac{8}{f^*}\beta_T(\delta) \sqrt{(\sum_{t=1}^T\bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\gamma^{2k-2}\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
	&\leq O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{TK})
	\end{split}
	\end{equation}
\end{proof}

\begin{lemma}
	$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$, then for any $A$,
	$$
		f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	It suffices to prove when $A = \{1,...,m\}, m\leq K$. First, 
	\begin{align*}
		& f(A, w)=\sum_{k=1}^m \gamma_k\prod_{i=1}^{k-1}(1-w_i)w_k\\
		&\geq f(K,w_1,...,w_{K-1},w_K'). 
	\end{align*}
	For $f(K, w_1,...,w_k,w_{k+1}',...,w_K')\geq f(K;w_1,...,w_k',...,w_K')$, it is equivalent to prove that $(w_k-w_k')(1-\gamma(w_{k+1}'+(1-w_{k+1}')w_{k+2}'+...))>0$.
\end{proof}

\begin{lemma}
	$\sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-(a_i+c_i))(a_k + c_k) \leq \sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-a_i)a_k + \sum_{k=1}^K \gamma^{k-1}c_k$.
\end{lemma}
This lemma can be proved by induction. Need to change definition of Ut to min(Ut,1). So similarly, we can have

\begin{lemma}
	$E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
\end{lemma}

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{cascade_reference}
\bibliographystyle{icml2015}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was
% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
% slightly modified from the 2009 version by Kiri Wagstaff and 
% Sam Roweis's 2008 version, which is slightly modified from 
% Prasad Tadepalli's 2007 version which is a lightly 
% changed version of the previous year's version by Andrew Moore, 
% which was in turn edited from those of Kristian Kersting and 
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2015-11-19 contextual combinatorial cascading bandits.tex
update main theorem and several useful lemmas

@@
 	\begin{lemma}
+		\label{lem:estimateU}
 		For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
@@
 
+	\section{Analysis}
 	Let
@@
 	\end{equation}
+
+	\begin{lemma}
+		\label{lem:increasing} 
+		$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
+		$$
+		f(A, w) \leq f(A, w').
+		$$
+	\end{lemma}
+	\begin{proof}
+		Because for $1 \leq k \leq m$,
+		\begin{align*}
+		&~~\gamma_k - \sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
+		&\geq \gamma_k (1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1-w_j)w_i) \\
+		&=\gamma_k \prod_{i=k+1}^{m}(1-w_i)\geq 0,
+		\end{align*}
+		then
+		\begin{align*}
+		&~~\gamma_k w_k + (1-w_k)\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
+		& \leq \gamma_k w_k' + (1-w_k')\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i.
+		\end{align*}
+		Therefore, 
+		\begin{align*}
+		& f(A; w_1',...,w_{k-1}',w_k,w_{k+1},...,w_m)\\
+		&=\sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k \\
+		&\qquad +(1-w_k)\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
+		&\leq \sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k' \\
+		&\qquad +(1-w_k')\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
+		&=f(A; w_1',...,w_{k-1}',w_{k}',w_{k+1},...,w_m).
+		\end{align*}
+		Then we obtain the result.
+	\end{proof}
+
+	\begin{lemma}
+		\label{lem:estimateTech}
+		Let $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Then
+		\begin{align*}
+		&~~\sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
+		& \leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k.
+		\end{align*}
+	\end{lemma}
+	\begin{proof}
+		We prove this by induction. It holds obviously for $K=1$.
+		\begin{align*}
+		&~~\sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
+		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\}\\
+		&+\gamma_{K+1}\prod_{i=1}^{K}(1-\min\{p_i+u_i, 1\})\min\{p_{K+1}+u_{K+1}, 1\}\\
+		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k\\
+		&+\gamma_{K+1}\prod_{i=1}^{K}(1-p_i)(p_{K+1}+u_{K+1})\\
+		&\leq \sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^{K+1} \gamma_k u_k
+		\end{align*}
+	\end{proof}
+
+	\begin{lemma}
+		With high probability $1-\delta$, $E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
+	\end{lemma}
+	\begin{proof}
+		Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t)$, then
+		\begin{align*}
+		&\sum_{k=1}^{\abs{A_t^*}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(a_{t,i}^*)))\bU_t(a_{t,k}^*) \\
+		\leq &\sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(\ba_i^t)))\bU_t(\ba_k^t) 
+		\end{align*}
+		By lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
+		\begin{align*}
+		&~~f(A_t^*, \theta_*^{\top}X_t) \\
+		&\leq f(\bA_t, \min\{\theta_*^{\top}X_{t,a}+2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}},1\}).
+		\end{align*}
+		Therefore by lemma \ref{lem:estimateTech},
+		\begin{align*}
+		&~~f(A_t^*, \theta_*^{\top}X_t) \\
+		&\leq  \sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\theta_*^{\top}X_{t,a_{t,i}^*})\theta_*^{\top}X_{t,a_{t,k}^*} \\
+		&~~ + 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}\\
+		&=f(\bA_t, \theta_*^{\top}X_t) + 2\beta_{t-1}(\delta)\sum_{k=1}^{\abs{\bA_t}}\gamma_k\norm{X_{t,a}}_{\bV_{t-1}^{-1}},
+		\end{align*}
+		which is equivalent to 
+		$$
+		\Delta_{\bA_t} \leq 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
+		$$
+	\end{proof}
 
@@
 
-\begin{lemma}
-	$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$, then for any $A$,
-	$$
-		f(A, w) \leq f(A, w').
-	$$
-\end{lemma}
-\begin{proof}
-	It suffices to prove when $A = \{1,...,m\}, m\leq K$. First, 
-	\begin{align*}
-		& f(A, w)=\sum_{k=1}^m \gamma_k\prod_{i=1}^{k-1}(1-w_i)w_k\\
-		&\geq f(K,w_1,...,w_{K-1},w_K'). 
-	\end{align*}
-	For $f(K, w_1,...,w_k,w_{k+1}',...,w_K')\geq f(K;w_1,...,w_k',...,w_K')$, it is equivalent to prove that $(w_k-w_k')(1-\gamma(w_{k+1}'+(1-w_{k+1}')w_{k+2}'+...))>0$.
-\end{proof}
-
-\begin{lemma}
-	$\sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-(a_i+c_i))(a_k + c_k) \leq \sum_{k=1}^K \gamma^{k-1}\prod_{i=1}^{k-1}(1-a_i)a_k + \sum_{k=1}^K \gamma^{k-1}c_k$.
-\end{lemma}
-This lemma can be proved by induction. Need to change definition of Ut to min(Ut,1). So similarly, we can have
-
-\begin{lemma}
-	$E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
-\end{lemma}
-
 	% In the unusual situation where you want a paper to appear in the

### 2015-11-20 contextual combinatorial cascading bandits.tex
update basics for 'and' case

@@
 \icmlauthor{Your Name}{email@yourdomain.edu}
-	\icmladdress{Your Fantastic Institute,
-		314159 Pi St., Palo Alto, CA 94306 USA}
+\icmladdress{Your Fantastic Institute, 314159 Pi St., Palo Alto, CA 94306 USA}
 \icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
-	\icmladdress{Their Fantastic Institute,
-		27182 Exp St., Toronto, ON M6H 2T1 CANADA}
+\icmladdress{Their Fantastic Institute, 27182 Exp St., Toronto, ON M6H 2T1 CANADA}
 
@@
 The user then checks from the first item and stops if she has checked all items or click on one interesting.
-Suppose we add position discount $1 \geq\gamma_1 \geq \gamma_2\geq \cdots \geq \gamma_K>0$.
-If the user clicks on the $k$-th item of $\bA_t$, the reward we receive is $\gamma_k$.
+Suppose we add position discount $0 \leq \gamma_1,...,\gamma_K\leq \gamma_0 \leq 1$.
+If the $k$-th item of $\bA_t$ appears blocking, the reward we receive is $\gamma_k$.
+And if the whole path of $\bA_t$ is unblocked, the received reward is $\gamma_0$.
 At the end of time $t$, the agent observes $\bO_t$ items in $\bA_t$ and receive the reward
-	$$
-	\br_t = \max_{1 \leq k \leq \abs{\bA_t}} \gamma_k \bw_t(\ba_k^t) = \bigvee_{k=1}^{\abs{A_t}} \gamma_k \bw_t(\ba_k^t),
-	$$
-	where we use the notation that $\bigvee_{1\leq i\leq n}a_i = \max_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed $\bw_t(\ba_k^t), 1\leq k\leq\bO_t$.
+\begin{align*}
+\br_t &= \min_{1 \leq k \leq \abs{\bA_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)] \\
+&= \bigwedge_{k=1}^{\abs{A_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)],
+\end{align*}
+where we use the notation that $\bigwedge_{1\leq i\leq n}a_i = \min_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed $\bw_t(\ba_k^t), 1\leq k\leq\bO_t$.
 
@@
 \begin{align*}
-	& f : \cS \times [0,1]^E \to [0,1]\\
-	& f(A,w) = \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1}(1 -w(a_i)))w(a_k),
+f : \cS \times [0,1]^E \to [0,1]&~\\
+f(A,w;\gamma_1,...,\gamma_K,\gamma_0) =& \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) \\
+\qquad \qquad &~+ \gamma_0 \prod_{i=1}^{\abs{A}}w(a_i),
 \end{align*}
-	then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[r_t]=f(\bA_t,\theta_*^{\top}X_t)$ where $X_t=(X_{t,1} \cdots X_{t,L})\in\RR^{d\times L}$. Let 
+then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}X_t)$ where $X_t=(X_{t,1} \cdots X_{t,L})\in\RR^{d\times L}$. Let 
 $$
@@
 \label{lem:increasing} 
-		$1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$. If we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
+If $1 \leq \gamma_1 \leq ... \leq \gamma_K \leq \gamma_0 \leq 1$ and we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
 $$
@@
 \begin{proof}
-		Because for $1 \leq k \leq m$,
+	It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
 	\begin{align*}
-		&~~\gamma_k - \sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
-		&\geq \gamma_k (1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1-w_j)w_i) \\
-		&=\gamma_k \prod_{i=k+1}^{m}(1-w_i)\geq 0,
+		&~~-\gamma_k + \sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0\prod_{j=k+1}^{m}w_j'\\
+		&\geq \gamma_k (-1 + \sum_{i=k+1}^m (1- w_i')\prod_{j=k+1}^{i-1}w_j' +  \prod_{j=k+1}^{m}w_j')\\
+		&=\gamma_k \cdot 0 = 0,
 	\end{align*}
@@
 	\begin{align*}
-		&~~\gamma_k w_k + (1-w_k)\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i\\
-		& \leq \gamma_k w_k' + (1-w_k')\sum_{i=k+1}^m \gamma_i\prod_{j=k+1}^{i-1}(1-w_j)w_i.
+		&~~\gamma_k (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
+		&\qquad \qquad + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
+		& \leq \gamma_k (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
+		&\qquad \qquad + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'.
 	\end{align*}
@@
 	\begin{align*}
-		& f(A; w_1',...,w_{k-1}',w_k,w_{k+1},...,w_m)\\
-		&=\sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k \\
-		&\qquad +(1-w_k)\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
-		&\leq \sum_{i=1}^{k-1} \gamma_i\prod_{j=1}^{i-1}(1-w_j')w_i' + \prod_{j=1}^{k-1}(1-w_j')[\gamma_k w_k' \\
-		&\qquad +(1-w_k')\sum_{i=k+1}^{m}\gamma_{i}\prod_{j=k+1}^{i-1}(1-w_j)w_i]\\
-		&=f(A; w_1',...,w_{k-1}',w_{k}',w_{k+1},...,w_m).
+		& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
+		&=\sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k) \\
+		&\qquad + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
+		&\leq \sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k') \\
+		&\qquad + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'\\
+		&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
 	\end{align*}
@@
 
+Let $p_A$ denote the probability that all of items in $A$ are observed. Then $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$.
+
 \begin{lemma}
+
+\end{lemma}
+
+\begin{proposition}
 	With high probability $1-\delta$, $E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
-	\end{lemma}
+\end{proposition}
 \begin{proof}
@@
 
+\begin{lemma} % det(V_t)
+	$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
+\end{lemma}
+\begin{proof}
+	We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$ and
+	\begin{align*}
+	\trace(\bV_t) &= \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\
+	& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \norm{X_{s,\ba_k^s}}_2^2\\
+	& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma^{2k-2}=d\lambda + tC_\gamma.
+	\end{align*}
+\end{proof}
+
+\begin{lemma} % technical lemma for det
+	Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
+	$$
+	\det(I + \sum_{i=1}^n x_i x_i^{\top}) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
+	$$
+\end{lemma}
+\begin{proof}
+	Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
+	\begin{align*}
+	\det(I + \sum_{i=1}^n x_i x_i^{\top}) &= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
+	&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
+	&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
+	\end{align*}
+\end{proof}
+
+\begin{lemma}
+	If $\lambda \geq C_\gamma$, it holds that
+	$$
+	\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\gamma^{2k-2}\norm{X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\frac{\det(\bV_t)}{\det(\lambda I)}).
+	$$
+\end{lemma}
+\begin{proof}
+	\begin{align*}
+	\det(\bV_t) &= \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
+	&=\det(\bV_{t-1})\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
+	&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
+	&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
+	\end{align*}
+	Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$ and 
+	$$
+	0 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma^{2k-2}/\lambda,
+	$$
+	we get
+	\begin{align*}
+	\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 &\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+	&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I)))
+	\end{align*}
+\end{proof}
+
 	% In the unusual situation where you want a paper to appear in the

### 2015-11-20 contextual combinatorial cascading bandits.tex
complete proof for the 'and' case with discount

@@
 \begin{abstract} 
-		The purpose of this document is to provide both the basic paper template and
-		submission guidelines.
+The purpose of this document is to provide both the basic paper template and submission guidelines.
 \end{abstract}
@@
 Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
-By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k X_{s,\ba_k^s})$.
+By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' X_{s,\ba_k^s})$.
 By ridge regression of data
 $$
-\{(\gamma_k X_{s,\ba_k^s}, \gamma_k\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
+\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
 $$
+where $\gamma_k' = \begin{cases}
+\gamma_0, ~~k=1\\
+\gamma_0-\gamma_k, ~~k\geq 2,
+\end{cases}$
 let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
@@
 \end{equation}
-	where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
+where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
 Let
 $$
-	\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma^{2k-2}X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
+\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
 $$
 Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.
+
 \subsection{Algorithm}
@@
 \begin{equation}
-	C_\gamma = \sum_{k=1}^{K} \gamma_k^2.
+C_\gamma = \sum_{k=1}^{K} \gamma_k'^2.
 \end{equation}
@@
 \label{lem:estimateTech}
-		Let $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Then
+Suppose $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}$. Then
 \begin{align*}
-		&~~\sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
-		& \leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k.
+&~~f(K, w) \leq f(K, p) + \sum_{k=1}^{K} \gamma_k' u_k
 \end{align*}
@@
 \begin{align*}
-		&~~\sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\} \\
-		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-\min\{p_i+u_i, 1\})\min\{p_k+u_k, 1\}\\
-		&+\gamma_{K+1}\prod_{i=1}^{K}(1-\min\{p_i+u_i, 1\})\min\{p_{K+1}+u_{K+1}, 1\}\\
-		&\leq \sum_{k=1}^K \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^K \gamma_k u_k\\
-		&+\gamma_{K+1}\prod_{i=1}^{K}(1-p_i)(p_{K+1}+u_{K+1})\\
-		&\leq \sum_{k=1}^{K+1} \gamma_k\prod_{i=1}^{k-1}(1-p_i)p_k + \sum_{k=1}^{K+1} \gamma_k u_k
+&~~f(K+1, w)\\
+&= f(K, w) -\gamma_0 \prod_{k=1}^{K} w_k + \gamma_{K+1} (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
+&~~ + \gamma_0 \prod_{k=1}^{K+1} w_k\\
+&= f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
+&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} p_k\\
+&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1} - u_{K+1}) \prod_{k=1}^{K} p_k\\
+&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1}) \prod_{k=1}^{K} p_k\\
+&~~ + (\gamma_0 - \gamma_{K+1}) u_{K+1}\\
+&\leq f(K+1, p) + \sum_{k=1}^{K+1} \gamma_k' u_k
 \end{align*}
@@
 \begin{lemma}
-
+Suppose $A = (a_1, ..., a_{\abs{A}})$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then we have the following properties.
+\begin{itemize}
+\item[(1)] $f(A, w) \leq \gamma_0 p_A + \gamma_{\abs{A}}$;
+\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
+\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
+\item[(4)] $f(B_k, w) \leq \gamma_0 p_{B_{k+1}} + \gamma_{k+1}$.
+\end{itemize}	
 \end{lemma}
 
+\begin{proof}
+It suffices to prove these properties when $A = [m]$.
+\begin{itemize}
+\item[(1)]
+$f(A, w) \leq \gamma_m(1 - p_A w_m) + \gamma_0 p_A w_m \leq \gamma_m + \gamma_0 p_A$
+
+\item[(2)]
+\begin{align*}
+&f(B_k, w) - f(B_{k+1}, w)\\
+&=\gamma_0 w_1 \cdots w_k - \gamma_{k+1} w_1 \cdots w_k (1 - w_{k+1})\\
+&~~ - \gamma_0 w_1 \cdots w_{k} w_{k+1}\\
+&=(\gamma_0 - \gamma_{k+1}) w_1 \cdots w_k (1 - w_{k+1}) \geq 0.
+\end{align*}
+
+\item[(3)]
+Obvious.
+
+\item[(4)]
+$f(B_k, w) \leq \gamma_k (1 - p_{B_{k+1}}) + \gamma_0 p_{B_{k+1}}\leq \gamma_0 p_{B_{k+1}} + \gamma_{k}$
+\end{itemize}
+\end{proof}
+
 \begin{proposition}
-	With high probability $1-\delta$, $E[\Delta_{\bA_t}|\cH_t] \leq \frac{2}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$
+Suppose $A = (a_1, ..., a_{\abs{A}})$. Then there exists a prefix $B$ of $A$, such that 
+$$
+p_{B} \geq \frac{\frac{1}{2}f^* - \gamma_{B}}{\gamma_0}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
+$$ 
 \end{proposition}
 \begin{proof}
-	Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t)$, then
-	\begin{align*}
-		&\sum_{k=1}^{\abs{A_t^*}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(a_{t,i}^*)))\bU_t(a_{t,k}^*) \\
-		\leq &\sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\bU_t(\ba_i^t)))\bU_t(\ba_k^t) 
-	\end{align*}
-		By lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
-		\begin{align*}
-		&~~f(A_t^*, \theta_*^{\top}X_t) \\
-		&\leq f(\bA_t, \min\{\theta_*^{\top}X_{t,a}+2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}},1\}).
-		\end{align*}
-		Therefore by lemma \ref{lem:estimateTech},
-		\begin{align*}
-		&~~f(A_t^*, \theta_*^{\top}X_t) \\
-		&\leq  \sum_{k=1}^{\abs{\bA_t}}\gamma_k (\prod_{i=1}^{k-1}(1 -\theta_*^{\top}X_{t,a_{t,i}^*})\theta_*^{\top}X_{t,a_{t,k}^*} \\
-		&~~ + 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}\\
-		&=f(\bA_t, \theta_*^{\top}X_t) + 2\beta_{t-1}(\delta)\sum_{k=1}^{\abs{\bA_t}}\gamma_k\norm{X_{t,a}}_{\bV_{t-1}^{-1}},
-		\end{align*}
-		which is equivalent to 
+	Notice that $f^* \leq \gamma_0$. By above lemma, we have $[f(A,w), \gamma_0] \subset \bigcup [f(B_k,w), \gamma_0 p_{B_k} + \gamma_k]$.
+\end{proof}
+
+\begin{proposition}
+Suppose $\gamma_K \leq \frac{1}{4} f_t^*$. With high probability $1-\delta$, 
 $$
-		\Delta_{\bA_t} \leq 2\sum_{k=1}^{\abs{\bA_t}}\gamma_k\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
+E[\Delta_{\bA_t}|\cH_t] \leq \frac{4}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+\end{proposition}
+\begin{proof}
+By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}\frac{f_t^*}{\gamma_0}$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
+$$
+\EE[\Delta_{\bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{\bB_t} \bOne\{\Delta_{\bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+$$
+Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$ and lemma \ref{lem:estimateU}, \ref{lem:increasing}, it holds that
+$$
+f(\bA_t^*, \theta_*^{\top}X_t) \leq f(\bB_t,\bU_t).
+$$
+Then by lemma \ref{lem:estimateTech}
+$$
+f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}X_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+Therefore,
+$$
+\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
 \end{proof}
+
+\begin{corollary}
+With high probability $1-\delta$, 
+$$
+E[\Delta_{\bA_t}|\cH_t] \leq 4\sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}.
+$$
+\end{corollary}
 
@@
 &R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
-		&\leq \sum_{t=1}^{T} \frac{8}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\\
-		&\leq \frac{8}{f^*}\beta_T(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-		&\leq \frac{8}{f^*}\beta_T(\delta) \sqrt{(\sum_{t=1}^T\bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\gamma^{2k-2}\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
-		&\leq O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{TK})
+&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
+&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
+&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
 \end{split}
@@
 \begin{align*}
-	\trace(\bV_t) &= \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\
-	& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma^{2k-2} \norm{X_{s,\ba_k^s}}_2^2\\
-	& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma^{2k-2}=d\lambda + tC_\gamma.
+&\trace(\bV_t)\\
+& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\	
+& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \norm{X_{s,\ba_k^s}}_2^2\\
+& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k'^2=d\lambda + tC_\gamma.
 \end{align*}
@@
 \begin{align*}
-	\det(I + \sum_{i=1}^n x_i x_i^{\top}) &= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
+&\det(I + \sum_{i=1}^n x_i x_i^{\top})\\
+&= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
 &=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
@@
 \begin{align*}
-	\det(\bV_t) &= \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
-	&=\det(\bV_{t-1})\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
+&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
+&=\det(\bV_{t-1})\\
+&~~~~\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
 &\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
@@
 Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$ and 
-	$$
-	0 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma^{2k-2}/\lambda,
-	$$
+\begin{align*}
+\norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 &\leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1})\\
+& \leq \gamma^{2k-2}/\lambda
+\end{align*}
 we get
 \begin{align*}
-	\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 &\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+&\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
+&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
 &\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I)))

### 2015-11-20 contextual combinatorial cascading bandits.tex
update first half of 'Problem Formulation' part

@@
 \usepackage{multirow}
+\newcommand{\EE}{\mathbb{E}}
+\newcommand{\II}{\mathbb{I}}
+\newcommand{\PP}{\mathbb{P}}
+\newcommand{\RR}{\mathbb{R}}
 \newcommand{\bT}{\mathbb{T}}
@@
 \newcommand{\cS}{\mathcal{S}}
-\newcommand{\EE}{\mathbb{E}}
-\newcommand{\II}{\mathbb{I}}
-\newcommand{\PP}{\mathbb{P}}
-\newcommand{\RR}{\mathbb{R}}
 \newcommand{\argmax}{\mathrm{argmax}}
@@
 
-\section{Contextual Combinatorial Cascading Bandits}
-
-\subsection{Setting}
+\section{Problem Formulation}
 
@@
 
-At time $t$, the learning agent is revealed with feature vectors $X_{t,a} \in \RR^d$ for every basic arm $a \in E$, where we have $\norm{X_{t,a}}_2 \leq 1$; this feature vector combines both information of the user and the corresponding basic arm.
-We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$, which is called weight for arm $a$ at time $t$, to indicate whether the user on round $t$ will click on the item $a$ or not.
+At time $t$, the learning agent is revealed with feature vectors $x_{t,a} \in \RR^{d \times 1}$ for every basic arm $a \in E$, where we have $\norm{x_{t,a}}_2 \leq 1$; this feature vector combines both information of the user and the corresponding basic arm.
+We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$, which is called {\it weight} for arm $a$ at time $t$, to indicate the output of the item $a$ at time $t$.
 Assume $\bw_{t,a}$ are mutually independent and satisfy
@@
 \label{eq:expectation}
-\EE[\bw_{t,a} | X_{t,a}] = \theta_*^{\top} X_{t,a}
+\EE[\bw_{t,a} | x_{t,a}] = \theta_*^{\top} x_{t,a}
 \end{equation}
-where $\theta_*$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_*}_2 \leq 1$ and $0 < \theta_*^{\top} x_{t,a} < 1$ for all $t, a$.
+where $\theta_*$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_*}_2 \leq 1$ and $0 \leq \theta_*^{\top} x_{t,a} \leq 1$ for all $t, a$.
 At time $t$, the learning agent chooses a solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ based on its past observations.
-The user then checks from the first item and stops if she has checked all items or click on one interesting.
-Suppose we add position discount $0 \leq \gamma_1,...,\gamma_K\leq \gamma_0 \leq 1$.
-If the $k$-th item of $\bA_t$ appears blocking, the reward we receive is $\gamma_k$.
-And if the whole path of $\bA_t$ is unblocked, the received reward is $\gamma_0$.
-At the end of time $t$, the agent observes $\bO_t$ items in $\bA_t$ and receive the reward
+At the end of every time $t$, the agent observes weights of the first $\bO_t$ items of $\bA_t$ where
+$$
+\bO_t \leq \abs{\bA_t}, \bw_t(\ba_k^t) = 1, \forall k < \bO_t, \bw_t(\ba_{\bO_t}^t) = 0
+$$ 
+or 
+$$
+\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 1, \forall k \leq \abs{\bA_t}.
+$$
+We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
+
+The agent receives reward $1$ if all items in $\bA_t$ are observed and have weights $1$.
+Suppose we consider partial reward, $0 \leq \gamma_1 \leq \ldots \leq \gamma_{K-1} \leq 1$, for partial number of observed items with weight $1$: If $\bO_t = 1 < \abs{\bA_t}$, then the agent only observes the weight of the first item of $\bw_t(\ba_1^t)$ and receives zero reward; if $1 < \bO_t < \abs{\bA_t}$, then the agent observes weights of first $\bO_t$ items among which $\bO_t - 1$ items have weights 1 and receives reward $\gamma_{\bO_t - 1}$; if $\bO_t = \abs{\bA_t}$ and $\bw_{\ba_{\abs{\bA_t}}^t} = 0$, then the agent observes $\abs{\bA_t} - 1$ items with weights $1$ and receives reward $\gamma_{\abs{\bA_t} - 1}$.
+Note that the order of $\bA_t$ affects both the feedback and the reward.
+In the analysis part, we will show how the order affects the reward.
+
+At the end of time $t$, the agent observes $\bO_t, \bw_t(\ba_k^t), 1\leq k\leq\bO_t$ and receives the reward
 \begin{align*}
@@
 \end{align*}
-where we use the notation that $\bigwedge_{1\leq i\leq n}a_i = \min_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed $\bw_t(\ba_k^t), 1\leq k\leq\bO_t$.
+where we use the notation that $\bigwedge_{1\leq i\leq n}a_i = \min_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed.
 
@@
 In the rest of this paper, we denote $\Delta_{t,\bA_t} = f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)$ and $R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}]$.
+
+\section{Algorithms and Results}
+
+\subsection{Algorithm}
 
@@
 Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.
-
-\subsection{Algorithm}
 
@@
 
-\FORALL {t=1,2,...}
+\FORALL {$t=1,2,\ldots$}
+\STATE {Obtain context $X_{t,a}$ for all $a\in E$}
+\STATE{}
+
 \STATE {//Compute UCBs}
@@
 \STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
-\STATE {Observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
+\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
 \STATE {}
@@
 \STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 X_{t, \ba_k^t}X_{t, \ba_k^t}^{\top}$}
-\STATE {$X^t \leftarrow (X^{t-1, \top}, \gamma_1 X_{t, \ba_1^t},  ..., \gamma_{\bO_t} X_{t, \ba_{\bO_t}^t})^{\top}$}
-\STATE {$Y^t \leftarrow (Y^{t-1,\top}, \gamma_1 \bw(\ba_1^t),  ..., \gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t))^{\top}$}
-\STATE {$\hat{\theta}_t \leftarrow (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t$}
+\STATE {$X^t \leftarrow ((X^{t-1})^\top, \gamma_1 X_{t, \ba_1^t},  ..., \gamma_{\bO_t} X_{t, \ba_{\bO_t}^t})^{\top}$}
+\STATE {$Y^t \leftarrow ((Y^{t-1})^\top, \gamma_1 \bw(\ba_1^t),  ..., \gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t))^{\top}$}
+\STATE {$\hat{\theta}_t \leftarrow ((X^{t})^\top X^{t} + \lambda I)^{-1} (X^{t})^\top \bY^t$}
 \STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}
 
-\ENDFOR {~~t}
+\ENDFOR {~~$t$}
 \end{algorithmic}
@@
 
-\section{Analysis}
+\subsection{Results}
+
+\begin{theorem}
+For any $\delta > 0$, with probability at least $1 - \delta$, we have
+\begin{equation}
+R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
+\end{equation}
+\end{theorem}
+\begin{proof}
+With probability at least $1-\delta$,
+\begin{equation}
+\begin{split}
+&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
+&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
+&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
+&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
+\end{split}
+\end{equation}
+\end{proof}
+
 Let
@@
 
-\begin{theorem}
-For any $\delta > 0$, with probability at least $1 - \delta$, we have
-\begin{equation}
-R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
-\end{equation}
-\end{theorem}
-\begin{proof}
-With probability at least $1-\delta$,
-\begin{equation}
-\begin{split}
-&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
-&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
-&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
-&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
-\end{split}
-\end{equation}
-\end{proof}
-
 \begin{lemma} % det(V_t)

### 2015-11-20 agent.py
contextual draft

@@ -52,12 +52,10 @@ def ucb(candidates, K=8, T=150000, verbose=False):
             logger.debug('Reward={0}'.format(reward))
             logger.debug('Score={0}/{1}'.format(score, t))
             if t % 10000 == 0:
-                logger.info('Reward={0}'.format(reward))
                 logger.info('Score={0}/{1}'.format(score, t))
             for k in range(min(c, K)):
                 ob[recc[k]] += 1
                 w[recc[k]] = ((ob[recc[k]] - 1) * w[recc[k]] + (c == k)) / ob[recc[k]]
-        logger.info('Reward={0}'.format(reward))
         logger.info('Score={0}/{1}'.format(score, t))
         print(sorted(u.items()))
         print(sorted(ob.items()))
@@ -75,17 +73,15 @@ def monkey(candidates, K=8, T=150000, verbose=False):
             reward = int(isinstance(c, int))
             score += reward
             if verbose:
-                print('Agent: Reward={0}'.format(reward))
                 print('Agent: Score={0}/{1}'.format(score, t))
             else:
                 if t % 10000 == 0:
-                    print('Agent: Reward={0}'.format(reward))
                     print('Agent: Score={0}/{1}'.format(score, t))
     return agent
 
 from environment import movielens
 candidates = movies_mix_cld_adt()
-environment = movielens(candidates[0] + candidates[1], 5)
+environment = movielens(candidates[0] + candidates[1], 1)
 agent = ucb(candidates)
 agent(environment)
 agent = monkey(candidates)

### 2015-11-20 context.py

@@ -1,0 +1,65 @@
+import csv
+import time
+import random
+from itertools import chain
+
+import logging
+logger = logging.getLogger('Contextual')
+
+from scipy import sparse
+from scipy.sparse.linalg import svds
+import numpy as np
+
+def movielens_load():
+    fpr = open('ratings.csv')
+    fpt = open('tags.csv')
+    gr = csv.reader(fpr, delimiter=',', quotechar='"')
+    gt = csv.reader(fpt, delimiter=',', quotechar='"')
+    gr.__next__()
+    gt.__next__()
+    return chain(gr, gt)
+
+portion = 0.5
+d = 30
+gamma = 0.95
+cox = []
+coy = []
+records = {}
+for idx, (user, movie, rate, timestamp) in enumerate(movielens_load()):
+    user = int(user) - 1
+    movie = int(movie) - 1
+    if random.uniform(0,1) < portion:
+        cox.append(user)
+        coy.append(movie)
+    else:
+        if user in records:
+            records[user].append(movie)
+        else:
+            records[user] = [movie]
+
+cox = np.array(cox)
+coy = np.array(coy)
+A = sparse.coo_matrix((np.ones(cox.shape), (cox, coy)), shape=(cox.max() + 1, coy.max() + 1), dtype=np.float32)
+U, S, VT = svds(A, d)
+for i in range(U.shape[0]):
+    U[i] = U[i] / np.linalg.norm(U[i])
+
+eligable_users = set(records.keys())
+logger.info('#Total eligabli users = {0}'.format(len(eligable_users)))
+logger.info('#Users participated ea/round = {0}'.format(1))
+user = [random.sample(eligable_users, 1)[0]]
+def environment(*arg):
+    if len(arg) == 0:
+        user[0] = random.sample(eligable_users, 1)[0]
+        logger.debug('Random user {0}'.format(user))
+        return U[user[0]]
+    else:
+        recommend = arg[0]
+        movies = records[user[0]]
+        logger.debug('Received recommendation {0}'.format(recommend))
+        logger.debug('User ctr history {0}'.format(movies))
+        for idx, movie in enumerate(recommend):
+            if movie in movies:
+                return idx, gamma ** idx
+        return float('Inf'), 0
+logger.info('Initializing environment "Movielens" done')

### 2015-11-20 environment.py

@@ -9,8 +9,52 @@ logger = logging.getLogger('Environment')
 
 from functools import reduce
 
-def movielens_chrono():
+def movielens(candidates, userno=1):
+    logger.info('Initializing environment "Movielens"')
+    records = {}
+    with open('ratings.csv') as fp:
+        r = csv.reader(fp, delimiter=',', quotechar='"')
+        for idx, tpl in enumerate(r):
+            if idx == 0:
+                continue
+            user, movie, rate, _ = tpl
+            if not int(movie) in candidates:
+                continue 
+            try:
+                records[int(user)].append(int(movie))
+            except:
+                records[int(user)] = [int(movie)]
+    with open('tags.csv') as fp:
+        r = csv.reader(fp, delimiter=',', quotechar='"')
+        for idx, tpl in enumerate(r):
+            if idx == 0:
+                continue
+            user, movie, tag, _ = tpl
+            if not int(movie) in candidates:
+                continue
+            try:
+                records[int(user)].append(int(movie))
+            except:
+                records[int(user)] = [(int(movie))]
 
+    total = len(records)
+    # leave those who have viewed at least one candidates
+    eligable_users = set(records.keys())
+    logger.info('#Total eligabli users = {0}'.format(len(eligable_users)))
+    logger.info('#Users participated ea/round = {0}'.format(userno))
+    def environment(recommend):
+        users = random.sample(eligable_users, userno)
+        movies = reduce(set.union, [set(records[user]) for user in users])
+        logger.debug('Received recommendation {0}'.format(recommend))
+        logger.debug('User ctr history {0}'.format(movies))
+        for idx, movie in enumerate(recommend):
+            if movie in movies:
+                return idx
+        return float('Inf')
+    logger.info('Initializing environment "Movielens" done')
+    return environment
+
+def movielens_chrono():
     print('Initializing environment "Movielens-chrono"')
     records = {}
     tts = []
@@ -62,49 +106,4 @@ def movielens_chrono():
                 return idx
         return float('Inf')
     print('Initializing environment "Movielens-chrono" done')
-    return environment
-
-def movielens(candidates, userno=1):
-    logger.info('Initializing environment "Movielens"')
-    records = {}
-    with open('ratings.csv') as fp:
-        r = csv.reader(fp, delimiter=',', quotechar='"')
-        for idx, tpl in enumerate(r):
-            if idx == 0:
-                continue
-            user, movie, rate, _ = tpl
-            if not int(movie) in candidates:
-                continue 
[…]

### 2015-11-21 experiment.tex
add documents (draft)

\documentclass[a4paper,11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{tikz}

\begin{document}

C3UCB Draft \hfill Fall 2015

\vspace*{\baselineskip}

\begin{center}
  \textbf{Contextual Combinatorial Cascading Bandit Experiment}
\end{center}

\vspace*{2\baselineskip}

\section{Synthetic dataset}

Let $I=\{e_1,e_2,\dots,e_L\}$ be a set of arms, each associated with a $d$-dimensional vector $x_i$ randomly drawn from $\{x\in R^d : \|x\|_2=1\}$. The expected payoff of an superarm $A\subseteq I$, denoted as $r_A$, will be $\sum_{i:e_i\in A, i\leq O_t}{(\theta_\ast^Tx_i + \epsilon_{i,t})\gamma^i z_i}$, where $\theta_\ast$ s.t. $\|\theta_\ast\|_2=1$ is randomly initiated and holds throughout the experiment, and $\epsilon_{i,t}\sim N(\mu_i,\sigma_i)$ i.i.d. be the fluctuation. In this experiment, the set of avaiable superarms $S$ is $\{A\subseteq I:|A|=k\}$.

The following approaches are served as baselines:

\begin{enumerate}

  \item The monkey who randomly select $A\in S$ at each round.

  \item Combinatorial Cascading UCB which maintains its upper confidence bound purely by the historical payoff of the superarms selected. The contextual information $x_{i,t}$ is totally ignored so it can only catch the $\epsilon$ part while suffers a lot from noisy. The performance of Combinatorial Cascading UCB will mainly depends on the magnitude of $\mu$.

  \item Contextual Combinatorial UCB which takes full feedback instead of cascading feedback, which is sureal in some settings in real world. It's expected to perform better than C3UCB, but as long as their regret being comparable, the result is acceptable.

\end{enumerate}

\section{Movielens}

let $Y$ be a matrix in which each entry $y_{ij}\in \{0,1\}$ records the clickthrough history between user $i$ and movie $j$. We split $Y$ into training set and test set $Y=Y_{\text{train}}+Y_{\text{test}}$ by categorizing each entry randomly with probability $\delta$. Let $USV^T=Y_{\text{train}}$ be the SVD decomposition of $Y_{\text{train}}$, the context corresponding to user $i$ and movie $j$ is defined as $U_i^T(V_j, G_j)$, where $G_i$ records the binary indicators of genres.

Upon received a super arm $A\in S$, the reward $\sum_{i:e_i\in I, i\leq O_t}{Y_{\text{test},ij}\gamma^i z_i}$ is returned as well as the terminal of cascade. The result is compared with the same baselines as in the above synthetic dateset experiment.

\end{document}

### 2015-11-23 contextual combinatorial cascading bandits.tex
update and rearrange structure
update second half part of 'Problem Formulation' section

@@
 \begin{align*}
-\br_t &= \min_{1 \leq k \leq \abs{\bA_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)] \\
-&= \bigwedge_{k=1}^{\abs{A_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)],
+\br_t &= \begin{cases}
+\gamma_{\bO_t - 1}  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0\\
+1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
+\end{cases}\\
+&=\begin{cases}
+\gamma_{k - 1}  &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq k-1, \bw_t(\ba_{k}^t) = 0, k\leq \abs{\bA_t}\\
+1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t},
+\end{cases}
 \end{align*}
-where we use the notation that $\bigwedge_{1\leq i\leq n}a_i = \min_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed.
+where we use the notation of $\gamma_0 = 0$.
 
-If we define a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
+Given partial reward parameters $0 \leq \gamma_1 \leq \ldots \leq \gamma_{K-1} \leq 1$, we introduce a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
 \begin{align*}
-f : \cS \times [0,1]^E \to [0,1]&~\\
-f(A,w;\gamma_1,...,\gamma_K,\gamma_0) =& \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) \\
-\qquad \qquad &~+ \gamma_0 \prod_{i=1}^{\abs{A}}w(a_i),
+&f : \cS \times [0,1]^E \to [0,1]\\
+&f(A,w) = \sum_{k=2}^{\abs{A}}\gamma_{k-1} (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \end{align*}
-then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}X_t)$ where $X_t=(X_{t,1} \cdots X_{t,L})\in\RR^{d\times L}$. Let 
-$$
-A_t^* = \argmax_{A\in \cS} f(A,\theta_*^{\top}X_t).
-$$ 
+then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}x_t)$ where $x_t=(x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+\begin{align*}
+A_t^* &= \argmax_{A\in \cS} f(A,\theta_*^{\top}x_t),\\
+f_t^* &= f(A_t^*, \theta_*^{\top}x_t).
+\end{align*}
 The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
 $$
-R(T) = \EE[\sum_{t=1}^T f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)].
+R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}].
 $$
-In the rest of this paper, we denote $\Delta_{t,\bA_t} = f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)$ and $R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}]$.
+where $\Delta_{t,\bA_t} = f_t^* - f(\bA_t, \theta_*^{\top}x_t)$.
 
@@
 
-Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
-By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' X_{s,\ba_k^s})$.
+Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
+Let
+$$
+\gamma_k' = 1 - \gamma_{k-1}, ~~~1 \leq k \leq K.
+$$
+By equation (\ref{eq:expectation}), we have 
+$$
+\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' x_{s,\ba_k^s}).
+$$
 By ridge regression of data 
@@
 $$
-where $\gamma_k' = \begin{cases}
-\gamma_0, ~~k=1\\
-\gamma_0-\gamma_k, ~~k\geq 2,
-\end{cases}$
+where
 let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
 \begin{equation}
-\hat{\theta}_t = (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t
+\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t
 \end{equation}
-where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
+where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
 Let
 $$
-\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
+\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
 $$
@@
 \begin{equation}
-\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
+\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
 \end{equation}
@@
 $$
-0 \leq \bU_t(a) - \theta_*^{\top}X_{t,a} \leq 2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
+0 \leq \bU_t(a) - \theta_*^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 $$
@@
 \begin{align*}
-\abs{\hat{\theta}_{t-1}^{\top}X_{t,a} - \theta_*^{\top}X_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{X_{t,a}}_{\bV_{t-1}^{-1}} \\
-&\leq \beta_{t}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
+\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_*^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
+&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 \end{align*}
@@
 \label{alg:ConComCascade}
-\begin{algorithmic}
+\begin{algorithmic}[1]
 \STATE {//Initialization}
-\STATE {Parameters: $\delta > 0, \lambda >0, 1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$}
-\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 0, \bV_0 = \lambda I$}
+\STATE {Parameters: $\delta > 0, \lambda >0, 0 = \gamma_0 \leq \gamma_1 \leq \cdots \leq \gamma_{K-1} \leq 1$}
+\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I$}
 \STATE{}
@@
 \FORALL {$t=1,2,\ldots$}
-\STATE {Obtain context $X_{t,a}$ for all $a\in E$}
+\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
 \STATE{}
@@
 \STATE {$\forall a\in E: $}
-\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
+\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
 \STATE {}
@@
 \STATE {//Update statistics}
-\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 X_{t, \ba_k^t}X_{t, \ba_k^t}^{\top}$}
-\STATE {$X^t \leftarrow ((X^{t-1})^\top, \gamma_1 X_{t, \ba_1^t},  ..., \gamma_{\bO_t} X_{t, \ba_{\bO_t}^t})^{\top}$}
-\STATE {$Y^t \leftarrow ((Y^{t-1})^\top, \gamma_1 \bw(\ba_1^t),  ..., \gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t))^{\top}$}
-\STATE {$\hat{\theta}_t \leftarrow ((X^{t})^\top X^{t} + \lambda I)^{-1} (X^{t})^\top \bY^t$}
+\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
+\STATE {$\bX_t \leftarrow [\bX_{t-1}^\top; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
+\STATE {$\bY_t \leftarrow [\bY_{t-1}^\top; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)^{\top}]$}
+\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
 \STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}
@@
 \begin{split}
-&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
-&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
-&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
-&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
+&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
+&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
+&\leq 4 \beta_T(\Delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(d\log(C_\gamma T)\sqrt{TK})
 \end{split}
@@
 \label{lem:increasing} 
-If $1 \leq \gamma_1 \leq ... \leq \gamma_K \leq \gamma_0 \leq 1$ and we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
+If $0= \gamma_0 \leq \gamma_1 \leq ... \leq \gamma_{K-1} \leq 1$ and we have $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A\in\cS$,
 $$
@@
 \begin{align*}
-&~~-\gamma_k + \sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0\prod_{j=k+1}^{m}w_j'\\
-&\geq \gamma_k (-1 + \sum_{i=k+1}^m (1- w_i')\prod_{j=k+1}^{i-1}w_j' +  \prod_{j=k+1}^{m}w_j')\\
-&=\gamma_k \cdot 0 = 0,
+&~~-\gamma_{k-1} + \sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + \prod_{j=k+1}^{m}w_j'\\
+&\geq \gamma_{k-1} (-1 + \sum_{i=k+1}^m (\prod_{j=k+1}^{i-1}w_j')(1- w_i') +  \prod_{j=k+1}^{m}w_j')\\
+&=\gamma_{k-1} \cdot 0 = 0,
 \end{align*}
@@
 \begin{align*}
-&~~\gamma_k (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
-&\qquad \qquad + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
-& \leq \gamma_k (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
-&\qquad \qquad + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'.
+&~~\gamma_{k-1} (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
+&\qquad \qquad + w_k\prod_{j=k+1}^{m}w_j'\\
+& \leq \gamma_{k-1} (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
+&\qquad \qquad + w_k'\prod_{j=k+1}^{m}w_j'.
 \end{align*}
@@
 & f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
-&=\sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k) \\
-&\qquad + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
-&\leq \sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k') \\
-&\qquad + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'\\
+&=\sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j)(1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k) \\
+&\qquad + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k\prod_{j=k+1}^{m}w_j']\\
+&\leq \sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j) (1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k') \\
+&\qquad + w_k'\sum_{i=k+1}^m \gamma_{i-1} (\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k'\prod_{j=k+1}^{m}w_j']\\
 &=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
@@
 \label{lem:estimateTech}
-Suppose $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}$. Then
-\begin{align*}
-&~~f(K, w) \leq f(K, p) + \sum_{k=1}^{K} \gamma_k' u_k
-\end{align*}
+Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+$$
+f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
+$$
+where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
 \end{lemma}
 \begin{proof}
-We prove this by induction. It holds obviously for $K=1$.
+We prove this by induction. It holds obviously for $m=1$.
 \begin{align*}
-&~~f(K+1, w)\\
-&= f(K, w) -\gamma_0 \prod_{k=1}^{K} w_k + \gamma_{K+1} (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
-&~~ + \gamma_0 \prod_{k=1}^{K+1} w_k\\
-&= f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
-&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} p_k\\
-&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1} - u_{K+1}) \prod_{k=1}^{K} p_k\\
-&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1}) \prod_{k=1}^{K} p_k\\
-&~~ + (\gamma_0 - \gamma_{K+1}) u_{K+1}\\
-&\leq f(K+1, p) + \sum_{k=1}^{K+1} \gamma_k' u_k
+&~~f(m+1, w)\\
+&= f(m, w) -\prod_{k=1}^{m} w_k + \gamma_{m}  (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
+&= f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
+&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
+&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
+&\leq f(m, p) +  \sum_{k=1}^{m} \gamma_k' u_k + (\gamma_{m} - 1) (1 - p_{m+1}) \prod_{k=1}^{m} p_k\\
+&~~ + (1 - \gamma_{m}) u_{m+1}\\
+&\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
 \end{align*}
@@
 \begin{itemize}
-\item[(1)] $f(A, w) \leq \gamma_0 p_A + \gamma_{\abs{A}}$;
+\item[(1)] $f(A, w) \leq p_A + \gamma_{\abs{A} - 1}$;
 \item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
 \item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
-\item[(4)] $f(B_k, w) \leq \gamma_0 p_{B_{k+1}} + \gamma_{k+1}$.
+\item[(4)] $f(B_k, w) \leq p_{B_{k+1}} + \gamma_{k}$.
 \end{itemize}	
@@
 \begin{proof}
-It suffices to prove these properties when $A = [m]$.
+It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$.
 \begin{itemize}
 \item[(1)]
-$f(A, w) \leq \gamma_m(1 - p_A w_m) + \gamma_0 p_A w_m \leq \gamma_m + \gamma_0 p_A$
+$f(A, w) \leq \gamma_{m-1}(1 - p_A w_m) + p_A w_m \leq \gamma_{m-1} + p_A$;
 
@@
 &f(B_k, w) - f(B_{k+1}, w)\\
-&=\gamma_0 w_1 \cdots w_k - \gamma_{k+1} w_1 \cdots w_k (1 - w_{k+1})\\
-&~~ - \gamma_0 w_1 \cdots w_{k} w_{k+1}\\
-&=(\gamma_0 - \gamma_{k+1}) w_1 \cdots w_k (1 - w_{k+1}) \geq 0.
+&=\prod_{i=1}^{k}w_i - \gamma_{k} (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
+&=(1 - \gamma_{k}) (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0.
 \end{align*}
@@
 \item[(4)]
-$f(B_k, w) \leq \gamma_k (1 - p_{B_{k+1}}) + \gamma_0 p_{B_{k+1}}\leq \gamma_0 p_{B_{k+1}} + \gamma_{k}$
+$$
+f(B_k, w) \leq \gamma_{k-1} (1 - p_{B_{k+1}}) + p_{B_{k+1}}\leq p_{B_{k+1}} + \gamma_{k}
+$$
 \end{itemize}
@@
 $$
-p_{B} \geq \frac{\frac{1}{2}f^* - \gamma_{B}}{\gamma_0}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
+p_{B} \geq \frac{1}{2}f^* - \gamma_{\abs{B}-1}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
 $$ 
@@
 \begin{proof}
-	Notice that $f^* \leq \gamma_0$. By above lemma, we have $[f(A,w), \gamma_0] \subset \bigcup [f(B_k,w), \gamma_0 p_{B_k} + \gamma_k]$.
+	Notice that $f^* \leq 1$. By above lemma, we have $[f(A,w), 1] \subset \bigcup [f(B_k,w), p_{B_k} + \gamma_{k-1}]$.
 \end{proof}
@@
 \begin{proposition}
-Suppose $\gamma_K \leq \frac{1}{4} f_t^*$. With high probability $1-\delta$, 
+Suppose $\gamma_{K-1} \leq \frac{1}{4} f^*$. With high probability $1-\delta$, 
 $$
-E[\Delta_{\bA_t}|\cH_t] \leq \frac{4}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{4}{f^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
@@
 \begin{proof}
-By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}\frac{f_t^*}{\gamma_0}$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
+By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}f_t^*$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
 $$
-\EE[\Delta_{\bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{\bB_t} \bOne\{\Delta_{\bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+\EE[\Delta_{t, \bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{t, \bB_t} \bOne\{\Delta_{t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
 $$
@@
 $$
-f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}X_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
-\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
 \end{proof}
-
-\begin{corollary}
-With high probability $1-\delta$, 
-$$
-E[\Delta_{\bA_t}|\cH_t] \leq 4\sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}.
-$$
-\end{corollary}
 
@@
 &\trace(\bV_t)\\
-& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \trace(X_{s,\ba_k^s} X_{s,\ba_k^s}^{\top})\\	
-& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \norm{X_{s,\ba_k^s}}_2^2\\
+& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
+& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \norm{x_{s,\ba_k^s}}_2^2\\
 & \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k'^2=d\lambda + tC_\gamma.
@@
 $$
-\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\gamma^{2k-2}\norm{X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\frac{\det(\bV_t)}{\det(\lambda I)}).
+\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma_k' x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\det(\bV_t)).
 $$
@@
 \begin{align*}
-&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}X_{t,\ba_k^{t}}X_{t, \ba_k^{t}}^{\top})\\
+&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k' X_{t,\ba_k^{t}})(\gamma_k' X_{t, \ba_k^{t}}^{\top}))\\
 &=\det(\bV_{t-1})\\
-&~~~~\det(I + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \gamma^{2k-2}\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}} (\bV_{t-1}^{-1/2}X_{t,\ba_{k}^{t}})^{\top})\\
-&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\min\{\bO_t, \abs{\bA_t}\}} \norm{\gamma^{k-1}X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
-&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
+&~~~~\det(I + \sum_{k=1}^{\bO_t} \gamma_k'\bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k' \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
+&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma^{k-1}x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
+&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma^{k-1}x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
 \end{align*}
-Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$ and 
+Because
+$$
+\norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k' x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k'^2 /\lambda,
+$$
+we have 
+$$
+\sum_{k=1}^{\bO_s} \norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k'^2 = C_\gamma /\lambda \leq 1
+$$
+Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$, we get
 \begin{align*}
-\norm{\gamma^{k-1}X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 &\leq \norm{\gamma^{k-1}X_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1})\\
-& \leq \gamma^{2k-2}/\lambda
-\end{align*}
-we get
-\begin{align*}
-&\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}}\norm{\gamma^{k-1}X_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{X_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
-&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I)))
+&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k' x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
+&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I))) < 2\log(\det(\bV_t))
 \end{align*}

### 2015-11-26 contextual combinatorial cascading bandits.tex
update 'Algorithm' section and main theorem

@@
 
-Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
+Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
+Here we abuse the notation $\abs{\bA_s}$ to denote the number of elements in the list $\bA_s$.
 Let
@@
 $$
-\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
+\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
 $$
-where
-let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
+we get a $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
 \begin{equation}
-\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t
+\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
 \end{equation}
@@
 
-\begin{theorem}[Theorem 2 in \cite{abbasi2011improved}]
+Next we build on a good estimate of differences between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.
+
+\begin{theorem}[\cite{abbasi2011improved}]
 \label{thm:theta_estimate}
@@
 \begin{equation}
+\label{eq:estimateTheta}
 \norm{\hat{\theta}_t - \theta_*}_{\bV_{t}} \leq \beta_{t}(\delta).
@@
 
-Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}.
-First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$.
-The UCB of item $a$ at time $t$ is defined as:
+This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm.
+Building on this, we can define an upper confidence bound of the expected weight of item $a$ by
 \begin{equation}
@@
 \end{equation}
-By theorem \ref{thm:theta_estimate}, it holds that
+
+The fact that $\bU_t(a)$ is an upper confidence bound of $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
 \begin{lemma}
 \label{lem:estimateU}
-For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
+When (\ref{eq:estimateTheta}) holds for time $t$, we have
 $$
@@
 \end{proof}
+
+Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}.
+First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$.
+Second, it recommends the output $\bA_t$ by the offline oracle with estimated weights $\bU_t$.
+Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), 1 \leq k \leq \bO_t$, where $\bw_t(\ba_{\bO_t}^t) = 0, \bw_t(\ba_k^t) = 1, 1 \leq k < \bO_t$ or $\bw_t(\ba_k^t) = 1, 1 \leq k \leq \bO_t = \abs{\bA_t}$.
+Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
+In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.
 
@@
 
+Here is our main theorem.
 \begin{theorem}
-For any $\delta > 0$, with probability at least $1 - \delta$, we have
+Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq 1$ and regularization parameter $\lambda \geq C_\gamma$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
 \begin{equation}
-R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
+R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT}),
 \end{equation}
+where
+\begin{align*}
+f^* &= \min_{1 \leq t \leq T} f_t^*\\
+C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
+\end{align*}
 \end{theorem}
@@
 &\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
-&\leq 4 \beta_T(\Delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
 &\leq O(d\log(C_\gamma T)\sqrt{TK})
@@
 \end{proof}
-
-Let
-\begin{equation}
-C_\gamma = \sum_{k=1}^{K} \gamma_k'^2.
-\end{equation}
 

### 2015-11-26 contextual combinatorial cascading bandits.tex
write an outline proof under main theorem

@@
 \begin{theorem}
-Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq 1$ and regularization parameter $\lambda \geq C_\gamma$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
+Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq c f^*$ and regularization parameter $\lambda \geq C_\gamma$ for some constant $\frac{1}{2} < c < 1$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
 \begin{equation}
@@
 \end{theorem}
-\begin{proof}
-With probability at least $1-\delta$,
-\begin{equation}
-\begin{split}
-&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
-&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
-&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(d\log(C_\gamma T)\sqrt{TK})
-\end{split}
-\end{equation}
-\end{proof}
+
+To prove this theorem, we want to estimate $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$.
+If the chosen action $\bA_t$ is not suboptimal, which is equivalent to $\Delta_{t, \bA_t} > 0$, then we must have
+$$
+f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
+$$
+From the above relation, we need the following two lemmas to derive an estimate of $\Delta_{t, \bA_t}$ in terms of all elements in $\bA_t$.
 
@@
 \label{lem:increasing} 
-If $0= \gamma_0 \leq \gamma_1 \leq ... \leq \gamma_{K-1} \leq 1$ and we have $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A\in\cS$,
+Given parameters $0= \gamma_0 \leq \gamma_1 \leq ...
+\leq \gamma_{K-1} \leq 1$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A\in\cS$,
 $$
@@
 \end{lemma}
-\begin{proof}
+
+\begin{lemma}
+\label{lem:estimateTech}
+Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+$$
+f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
+$$
+where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
+\end{lemma}
+
+From lemma \ref{lem:increasing} and $\theta_*^{\top}x_t \leq \bU_t$ by lemma \ref{lem:estimateU}, we can deduce 
+\begin{equation}
+\label{eq:fIncrease}
+f(A_t^*, \theta_*^{\top}x_t) \leq f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
+\end{equation}
+Further from lemma \ref{lem:estimateTech}, we can deduce
+\begin{equation}
+\label{eq:fTech}
+f(\bA_t, \bU_t) \leq f(\bA_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k
+\end{equation}
+where $u_k = \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}$. Combining equation (\ref{eq:fIncrease})) and (\ref{eq:fTech})), we can conclude that
+$$
+\Delta_{t, \bA_t} = f(A_t^*, \theta_*^{\top}x_t) - f(\bA_t, \theta_*^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k.
+$$
+
+However, this estimate involves all elements of $\bA_t$. Only when the learning agent has observed all elements of $\bA_t$, we can use such an estimate, which means we are able to estimate
+$$
+\EE[\Delta_{t, \bA_t}] = \EE[\Delta_{t, \bA_t}(1/p_{\bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}].
+$$
+Problem might happen if $p_{\bA_t}$ is small. Thus we need the following lemma to find a good substitution of $\bA_t$.
+
+\begin{lemma}
+\label{lem:prefixExist}
+Suppose the weights for items in $E$ are $w = (w_a)_{a \in E}$.
+Let $A = (a_1, ..., a_{\abs{A}})$ be a list and let $p_A$ denote the probability that all of items in $A$ are observed; equivalently, $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$.
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$.
+Then for any given constant $\frac{1}{2} < c < 1$, there exists a prefix $B$ of $A$ such that
+$$
+p_B \geq c f^* - \gamma_{\abs{B}}, \qquad \Delta_B \geq \frac{1}{2} \Delta_A,
+$$
+where
+$$
+f^* = \max_{A'} f(A', w), \qquad \Delta_{A'} = f^* - f(A', w).
+$$
+\end{lemma}
+
+From this lemma, we can find a prefix $\bB_t$ of $\bA_t$ such that $p_{B_t}$ is large enough and $\Delta_{\bB_t}$ will not be too small.
+Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$, we can get an estimate of $R(T)$.
+We leave all details in the next subsection.
+
+\subsection{Proofs}
+
+\begin{proof}[ of lemma \ref{lem:increasing}]
 It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
@@
 
-\begin{lemma}
-\label{lem:estimateTech}
-Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
-$$
-f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
-$$
-where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
-\end{lemma}
-\begin{proof}
+\begin{proof}[ of lemma \ref{lem:estimateTech}]
 We prove this by induction. It holds obviously for $m=1$.
@@
 
-Let $p_A$ denote the probability that all of items in $A$ are observed. Then $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$.
+\begin{proof}
+With probability at least $1-\delta$,
+\begin{equation}
+\begin{split}
+&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
+&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
+&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(d\log(C_\gamma T)\sqrt{TK})
+\end{split}
+\end{equation}
+\end{proof}
 
@@
 % references without citing it in the main text, use \nocite
-\nocite{langley00}
+%\nocite{langley00}
 

### 2015-11-27 contextual combinatorial cascading bandits.tex
update proof outline

@@
 \STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
-\STATE {$\bX_t \leftarrow [\bX_{t-1}^\top; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
-\STATE {$\bY_t \leftarrow [\bY_{t-1}^\top; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)^{\top}]$}
+\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
+\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)]$}
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
@@
 \begin{theorem}
+\label{thm:main}
 Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq c f^*$ and regularization parameter $\lambda \geq C_\gamma$ for some constant $\frac{1}{2} < c < 1$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
 \begin{equation}
-R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT}),
+R(T) = O(d^{3/4}\log^{3/4}(C_\gamma T)\sqrt{KT}),
 \end{equation}
@@
 
-To prove this theorem, we want to estimate $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$.
-If the chosen action $\bA_t$ is not suboptimal, which is equivalent to $\Delta_{t, \bA_t} > 0$, then we must have
+To prove this theorem, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+\begin{lemma}
+\label{lem:DeltaEstimate}
+For any time $t$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$ where $A = (a_1, \ldots, a_{\abs{A}})$, then we have
+$$
+\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k' \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+$$
+\end{lemma}
+
+Then if the chosen action $\bA_t$ is not suboptimal, which means
 $$
@@
 $$
-From the above relation, we need the following two lemmas to derive an estimate of $\Delta_{t, \bA_t}$ in terms of all elements in $\bA_t$.
-
-\begin{lemma}
-\label{lem:increasing} 
-Given parameters $0= \gamma_0 \leq \gamma_1 \leq ...
-\leq \gamma_{K-1} \leq 1$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A\in\cS$,
-$$
-f(A, w) \leq f(A, w').
-$$
-\end{lemma}
-
-\begin{lemma}
-\label{lem:estimateTech}
-Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
-$$
-f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
-$$
-where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
-\end{lemma}
-
-From lemma \ref{lem:increasing} and $\theta_*^{\top}x_t \leq \bU_t$ by lemma \ref{lem:estimateU}, we can deduce 
-\begin{equation}
-\label{eq:fIncrease}
-f(A_t^*, \theta_*^{\top}x_t) \leq f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
-\end{equation}
-Further from lemma \ref{lem:estimateTech}, we can deduce
-\begin{equation}
-\label{eq:fTech}
-f(\bA_t, \bU_t) \leq f(\bA_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k
-\end{equation}
-where $u_k = \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}$. Combining equation (\ref{eq:fIncrease})) and (\ref{eq:fTech})), we can conclude that
-$$
-\Delta_{t, \bA_t} = f(A_t^*, \theta_*^{\top}x_t) - f(\bA_t, \theta_*^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k.
-$$
+Then we can derive an estimate of $\Delta_{t, \bA_t}$, however, in terms of all elements in $\bA_t$.
 
@@
 Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$, we can get an estimate of $R(T)$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bete_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$.
 We leave all details in the next subsection.
@@
 
-\begin{proof}[ of lemma \ref{lem:increasing}]
+\begin{lemma}
+\label{lem:increasing} 
+Given parameters $0= \gamma_0 \leq \gamma_1 \leq ...
+\leq \gamma_{K-1} \leq 1$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A\in\cS$,
+$$
+f(A, w) \leq f(A, w').
+$$
+\end{lemma}
+\begin{proof}
 It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
@@
 
-\begin{proof}[ of lemma \ref{lem:estimateTech}]
+\begin{lemma}
+\label{lem:estimateTech}
+Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+$$
+f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
+$$
+where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
+\end{lemma}
+\begin{proof}
 We prove this by induction. It holds obviously for $m=1$.
@@
 
-\begin{proof}
-With probability at least $1-\delta$,
+\begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
+From lemma \ref{lem:increasing} and $\theta_*^{\top}x_t \leq \bU_t$ by lemma \ref{lem:estimateU}, we can deduce 
 \begin{equation}
-\begin{split}
-&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
-&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
-&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(d\log(C_\gamma T)\sqrt{TK})
-\end{split}
+\label{eq:fIncrease}
+f(A_t^*, \theta_*^{\top}x_t) \leq f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
 \end{equation}
+Further from lemma \ref{lem:estimateTech}, we can deduce
+\begin{equation}
+\label{eq:fTech}
+f(\bA_t, \bU_t) \leq f(\bA_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k
+\end{equation}
+where $u_k = \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}$. Combining equation (\ref{eq:fIncrease})) and (\ref{eq:fTech})), we can conclude that
+$$
+\Delta_{t, \bA_t} = f(A_t^*, \theta_*^{\top}x_t) - f(\bA_t, \theta_*^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k.
+$$
 \end{proof}
@@
 
+\begin{proof}[ of theorem \ref{thm:main}]
+With probability at least $1-\delta$,
+\begin{equation}
+\begin{split}
+&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
+&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
+&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(d\log(C_\gamma T)\sqrt{TK})
+\end{split}
+\end{equation}
+\end{proof}
+
 % In the unusual situation where you want a paper to appear in the

### 2015-11-27 contextual combinatorial cascading bandits.tex

@@
 Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bete_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$.
 We leave all details in the next subsection.

### 2015-11-27 environment.py
tmp

@@ -9,6 +9,23 @@ logger = logging.getLogger('Environment')
 
 from functools import reduce
 
+class ucb_settings:
+    def __init__():
+        pass
+
+def monkey_context(L=20, K=4, d=10, gamma=0.95, ):
+    logger.info('Initializing environment "Monkey Contextual"')
+    arms = [idx for idx in range(L)]
+    theta = {arm:np.random.uniform(0, 1, d) for arm in arms}
+
+    arm = [0]
+    def environment(recommend=None):
+        if recommend == None:
+            arm = [np.random.choice(arms)]
+            return arm[0], theta[arm[0]]
+    
+
+
 def movielens(candidates, userno=1):
     logger.info('Initializing environment "Movielens"')
     records = {}

### 2015-11-27 environment.py
minor on gitignore; fix architecture for synthetic experiment

@@ -13,16 +13,19 @@ class ucb_settings:
     def __init__():
         pass
 
-def monkey_context(L=20, K=4, d=10, gamma=0.95, ):
+def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3):
     logger.info('Initializing environment "Monkey Contextual"')
     arms = [idx for idx in range(L)]
-    theta = {arm:np.random.uniform(0, 1, d) for arm in arms}
+    x = {arm:np.random.uniform(0, 1, d) for arm in arms}
+    theta = np.random.uniform(0, 1, d)
 
-    arm = [0]
+    xt = {arm:x[arm] for arm in x}
     def environment(recommend=None):
         if recommend == None:
-            arm = [np.random.choice(arms)]
-            return arm[0], theta[arm[0]]
+            xt = {arm:x[arm] + np.random.uniform(-v, v, d) for arm in x}
+            return xt
+        else:
+            p = [theta.dot(xt[arm]) for arm in recommend]
     
 
 

### 2015-11-29 contextual combinatorial cascading bandits.tex
update part of 'or' case

@@
 
-To prove this theorem, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+Suppose the reward function is disjunctive.
+At every time $t$, the forecaster recommends a list $\bA_t$.
+Then the user checks from the first item to the end.
+The weight $\bw_t(a)$ denote whether the user click on item $a$ or not.
+The user stops if she clicks on one item of $\bA_t$ or she has checked all items of $\bA_t$.
+If the user clicks on the first item, then the learning agent receives reward $1$.
+If the user clicks on the $k$-th reward of $\bA_t$, then the reward is $\gamma_k$.
+If the user doesn't click on any item, then the reward is $0$.
+Here we further assume $\gamma_2 \geq \gamma_3 \geq \ldots \geq \gamma_K$.
+If we define a function $f_{\vee}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS$ and $w = (w(1), \ldots, w(L))$ by
+\begin{align*}
+&f_{\vee} : \cS \times [0,1]^E \to [0,1]\\
+&f_{\vee}(A,w) = \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
+\end{align*}
+Here we use notation that $\gamma_1 = 1$. Then the expected reward of $\bA_t$ is $f_{\vee}(\bA_t, \theta_*^{\top}x_t)$.
+
+Then we have a relationship between $f$ and $f_{\vee}$
+\begin{equation}
+\label{eq:relation}
+\begin{split}
+&f_{\vee}(A, w; 1, \gamma_2, \ldots, \gamma_K) \\
+&~~= 1 - f(A, 1 - w; 0, 1-\gamma_2, \ldots, 1-\gamma_K)
+\end{split}
+\end{equation}
+If $\gamma$ is decreasing, then $1 - \gamma$ is increasing. Thus we have $1 - \gamma$ a feasible parameters for $f$. Then we could have a similar result for disjunctive case.
+\begin{theorem}
+Disjunctive case
+\end{theorem}
+
+To prove theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
 \begin{lemma}
@@
 \Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k' \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+$$
+If $f_{\vee}(A_t^*, \bU_t) \leq f_{\vee}(A, \bU_t)$ where $A = (a_1, \ldots, a_{\abs{A}})$, then we have
+$$
+\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
+By relation (\ref{eq:relation}), it also holds that
+$$
+f_{\vee}(A, w) \leq f_{\vee}(A, w').
+$$
 \end{lemma}
@@
 $$
-where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
+where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$, $\gamma$ is increasing. It also holds that
+$$
+f_{\vee}(A^{(m)}, w) \leq f_{\vee}(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k,
+$$
+for any positive sequence $\gamma$.
 \end{lemma}
@@
 &\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
+\end{align*}
+\begin{align*}
+&~~f_{\vee}(A^{(m+1)}, w) = f_{\vee}(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
+&= f_{\vee}(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})
 \end{align*}
@@
 \end{itemize}
+It also holds that $p_{A} \geq \gamma_{\abs{A}} - f_{\vee}(A, w)$.
 \end{lemma}

### 2015-11-29 environment.py
finished synthetic env

@@ -10,10 +10,10 @@ logger = logging.getLogger('Environment')
 from functools import reduce
 
 class ucb_settings:
-    def __init__():
-        pass
+    def __init__(**s):
+        self.__dict__ = s
 
-def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3):
+def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3, eps=0.1, disj=False):
     logger.info('Initializing environment "Monkey Contextual"')
     arms = [idx for idx in range(L)]
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
@@ -25,8 +25,13 @@ def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3):
             xt = {arm:x[arm] + np.random.uniform(-v, v, d) for arm in x}
             return xt
         else:
-            p = [theta.dot(xt[arm]) for arm in recommend]
-    
+            for C, arm in enumerate(recomend): 
+                p = theta.dot(xt[arm]) + np.random.normal(0, eps)
+                if (np.random.uniform(0, 1) < p) ^ disj:
+                    return gamma ^ C * int(not disj), C
+            return int(not disj), np.inf
+
+    return environment, ucb_setting(arms=arms, K=K, d=d, gamma=gamma)
 
 
 def movielens(candidates, userno=1):

### 2015-11-30 contextual combinatorial cascading bandits.tex
add problem formulation for 'or' case

@@
 
-At time $t$, the learning agent is revealed with feature vectors $x_{t,a} \in \RR^{d \times 1}$ for every basic arm $a \in E$, where we have $\norm{x_{t,a}}_2 \leq 1$; this feature vector combines both information of the user and the corresponding basic arm.
-We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$, which is called {\it weight} for arm $a$ at time $t$, to indicate the output of the item $a$ at time $t$.
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every basic arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding basic arm.
+Then the learning agent recommends a feasible solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
+Starting from the first item, the user checks the items one by one.
+The checking process stops if the user clicks on one item or has checked all items without clicking anyone.
+We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate whether the user has clicked on item $a$ or not at time $t$.
+
 Assume $\bw_{t,a}$ are mutually independent and satisfy
@@
 \label{eq:expectation}
-\EE[\bw_{t,a} | x_{t,a}] = \theta_*^{\top} x_{t,a}
+\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a}
 \end{equation}
-where $\theta_*$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_*}_2 \leq 1$ and $0 \leq \theta_*^{\top} x_{t,a} \leq 1$ for all $t, a$.
-At time $t$, the learning agent chooses a solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ based on its past observations.
-At the end of every time $t$, the agent observes weights of the first $\bO_t$ items of $\bA_t$ where
+where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$ where
 $$
-\bO_t \leq \abs{\bA_t}, \bw_t(\ba_k^t) = 1, \forall k < \bO_t, \bw_t(\ba_{\bO_t}^t) = 0
+\bO_t \leq \abs{\bA_t}, \bw_t(\ba_k^t) = \begin{cases} 0, ~~k < \bO_t \\ 1, ~~k = \bO_t \end{cases}
 $$ 
@@
 $$
-\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 1, \forall k \leq \abs{\bA_t}.
+\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 0, ~~ k \leq \abs{\bA_t}.
 $$
@@
 
-The agent receives reward $1$ if all items in $\bA_t$ are observed and have weights $1$.
-Suppose we consider partial reward, $0 \leq \gamma_1 \leq \ldots \leq \gamma_{K-1} \leq 1$, for partial number of observed items with weight $1$: If $\bO_t = 1 < \abs{\bA_t}$, then the agent only observes the weight of the first item of $\bw_t(\ba_1^t)$ and receives zero reward; if $1 < \bO_t < \abs{\bA_t}$, then the agent observes weights of first $\bO_t$ items among which $\bO_t - 1$ items have weights 1 and receives reward $\gamma_{\bO_t - 1}$; if $\bO_t = \abs{\bA_t}$ and $\bw_{\ba_{\abs{\bA_t}}^t} = 0$, then the agent observes $\abs{\bA_t} - 1$ items with weights $1$ and receives reward $\gamma_{\abs{\bA_t} - 1}$.
-Note that the order of $\bA_t$ affects both the feedback and the reward.
-In the analysis part, we will show how the order affects the reward.
+The agent receives some reward if the user clicks on some item.
+Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
+Usually the importance of the positions is decreasing: the first position is most important.
+So it is a reasonable assumption that
+$$
+1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
+$$
+At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+$$
+\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
+$$
+where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
 
-At the end of time $t$, the agent observes $\bO_t, \bw_t(\ba_k^t), 1\leq k\leq\bO_t$ and receives the reward
+Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
 \begin{align*}
-\br_t &= \begin{cases}
-\gamma_{\bO_t - 1}  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0\\
+&f : \cS \times [0,1]^E \to [0,1]\\
+&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
+\end{align*}
+then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+\begin{align*}
+A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
+\end{align*}
+The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+$$
+R(T) = \EE[\sum_{t=1}^T R(t, \bA_t)].
+$$
+where $R(t, \bA_t) = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t)$.
+
+Similarly, we could also consider the case of conjunctive objective.
+We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the {\it weight} of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})).
+The learning agent observes all items until the first one with weight $0$.
+Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
+The more items, the more reward the learning agent should receive.
+It is reasonable to assume that
+$$
+0 = \gamma_1 \leq \gamma_2 \leq \cdots \leq \gamma_K \leq 1.
+$$
+At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+\begin{align*}
+\br_{\wedge, t} &= \begin{cases}
+\gamma_{\bO_t - 1}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
 1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
@@
 &=\begin{cases}
-\gamma_{k - 1}  &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq k-1, \bw_t(\ba_{k}^t) = 0, k\leq \abs{\bA_t}\\
-1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t},
+\gamma_{k - 1}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
+1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
 \end{cases}
 \end{align*}
-where we use the notation of $\gamma_0 = 0$.
 
-Given partial reward parameters $0 \leq \gamma_1 \leq \ldots \leq \gamma_{K-1} \leq 1$, we introduce a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
+If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
 \begin{align*}
-&f : \cS \times [0,1]^E \to [0,1]\\
-&f(A,w) = \sum_{k=2}^{\abs{A}}\gamma_{k-1} (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+&f_{\wedge} : \cS \times [0,1]^E \to [0,1]\\
+&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' (\prod_{i = 1}^{k - 1} w(a_i))(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \end{align*}
-then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}x_t)$ where $x_t=(x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
+To simplify notations, we assume
+$$
+\gamma_k' = 1 - \gamma_k.
+$$
+Then it holds that
+\begin{equation}
+\label{eq:ConDisRelation}
+f_{\wedge}(A, w) = 1 - f(A, 1 - w).
+\end{equation}
+Let 
 \begin{align*}
-A_t^* &= \argmax_{A\in \cS} f(A,\theta_*^{\top}x_t),\\
-f_t^* &= f(A_t^*, \theta_*^{\top}x_t).
+A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
 \end{align*}
-The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
 $$
-R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}].
+R_{\wedge}(T) = \EE[\sum_{t=1}^T R_{\wedge}(t, \bA_t)].
 $$
-where $\Delta_{t,\bA_t} = f_t^* - f(\bA_t, \theta_*^{\top}x_t)$.
+where $R_{\wedge}(t, \bA_t) = f_{\wedge, t}^{\ast} - f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$.
 

### 2015-12-01 contextual combinatorial cascading bandits.tex
update proof for 'or' case

@@
 
-Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
+Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
 Here we abuse the notation $\abs{\bA_s}$ to denote the number of elements in the list $\bA_s$.
-Let
-$$
-\gamma_k' = 1 - \gamma_{k-1}, ~~~1 \leq k \leq K.
-$$
 By equation (\ref{eq:expectation}), we have
 $$
-\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' x_{s,\ba_k^s}).
+\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
 $$
-By ridge regression of data 
+Using the ridge regression of data 
 $$
-\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
+\{(\gamma_k X_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
 $$
@@
 \end{equation}
-where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
+where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
 Let
 $$
-\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
+\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
 $$
-Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.
+Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. The above notifications hold for both disjunctive and conjunctive objectives.
 
@@
 \label{eq:estimateTheta}
-\norm{\hat{\theta}_t - \theta_*}_{\bV_{t}} \leq \beta_{t}(\delta).
+\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \beta_{t}(\delta).
 \end{equation}
@@
 $$
-0 \leq \bU_t(a) - \theta_*^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 $$
@@
 \begin{align*}
-\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_*^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
+\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
 &\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
@@
 Second, it recommends the output $\bA_t$ by the offline oracle with estimated weights $\bU_t$.
-Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), 1 \leq k \leq \bO_t$, where $\bw_t(\ba_{\bO_t}^t) = 0, \bw_t(\ba_k^t) = 1, 1 \leq k < \bO_t$ or $\bw_t(\ba_k^t) = 1, 1 \leq k \leq \bO_t = \abs{\bA_t}$.
+Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), k \in [\bO_t]$, where
+$$
+\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
+$$ 
+or
+$$
+\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
+$$
 Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
@@
 \STATE {//Initialization}
-\STATE {Parameters: $\delta > 0, \lambda >0, 0 = \gamma_0 \leq \gamma_1 \leq \cdots \leq \gamma_{K-1} \leq 1$}
+\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma$}
+\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
 \STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I$}
@@
 \label{lem:DeltaEstimate}
-For any time $t$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$ where $A = (a_1, \ldots, a_{\abs{A}})$, then we have
+For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
 $$
-\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k' \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
 $$
-If $f_{\vee}(A_t^*, \bU_t) \leq f_{\vee}(A, \bU_t)$ where $A = (a_1, \ldots, a_{\abs{A}})$, then we have
+if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
 $$
@@
 
-Then if the chosen action $\bA_t$ is not suboptimal, which means
+So if the chosen action $\bA_t$ is not suboptimal, which means
 $$
@@
 \label{lem:increasing} 
-Given parameters $0= \gamma_0 \leq \gamma_1 \leq ...
-\leq \gamma_{K-1} \leq 1$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A\in\cS$,
+Given $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A \in \prod^{\leq K}(E)$,
 $$
@@
 $$
-By relation (\ref{eq:relation}), it also holds that
+By relation (\ref{eq:ConDisRelation}), it also holds that
 $$
-f_{\vee}(A, w) \leq f_{\vee}(A, w').
+f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
 $$
@@
 \begin{proof}
-It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
+It suffices to prove when $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
 \begin{align*}
-&~~-\gamma_{k-1} + \sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + \prod_{j=k+1}^{m}w_j'\\
-&\geq \gamma_{k-1} (-1 + \sum_{i=k+1}^m (\prod_{j=k+1}^{i-1}w_j')(1- w_i') +  \prod_{j=k+1}^{m}w_j')\\
-&=\gamma_{k-1} \cdot 0 = 0,
+&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
+\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+\geq &~\gamma_{k-1} \cdot 0 = 0,
 \end{align*}
@@
 \begin{align*}
-&~~\gamma_{k-1} (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
-&\qquad \qquad + w_k\prod_{j=k+1}^{m}w_j'\\
-& \leq \gamma_{k-1} (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
-&\qquad \qquad + w_k'\prod_{j=k+1}^{m}w_j'.
+&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
+\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
 \end{align*}
@@
 \begin{align*}
-& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
-&=\sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j)(1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k) \\
-&\qquad + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k\prod_{j=k+1}^{m}w_j']\\
-&\leq \sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j) (1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k') \\
-&\qquad + w_k'\sum_{i=k+1}^m \gamma_{i-1} (\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k'\prod_{j=k+1}^{m}w_j']\\
-&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
+& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
+&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
 \end{align*}
-Then we obtain the result.
 \end{proof}
@@
 \label{lem:estimateTech}
-Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
-$$
-f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
-$$
-where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$, $\gamma$ is increasing. It also holds that
-$$
-f_{\vee}(A^{(m)}, w) \leq f_{\vee}(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k,
-$$
-for any positive sequence $\gamma$.
+Suppose $0 \leq p_1, \ldots, p_m \leq 1$ and $u_1, \ldots, u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+\begin{align*}
+f(A^{(m)}, w) &\leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
+f_{\wedge}(A^{(m)}, w) &\leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,
+\end{align*}
+for any positive $\gamma_k, \gamma_k'$ with $\gamma_k' = 1 - \gamma_k$, where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
+Notice that the parameters involved in the conclusions are $\gamma_k, k \in [m]$ while the parameters used in the definition of $f_{\wedge}$ are $\gamma_k', k \in [m]$.
 \end{lemma}
 \begin{proof}
-We prove this by induction. It holds obviously for $m=1$.
+We prove this by induction. It holds obviously for $m = 1$.
 \begin{align*}
-&~~f(m+1, w)\\
-&= f(m, w) -\prod_{k=1}^{m} w_k + \gamma_{m}  (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
-&= f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
-&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
-&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
-&\leq f(m, p) +  \sum_{k=1}^{m} \gamma_k' u_k + (\gamma_{m} - 1) (1 - p_{m+1}) \prod_{k=1}^{m} p_k\\
-&~~ + (1 - \gamma_{m}) u_{m+1}\\
-&\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
+&~~f(A^{(m+1)}, w)\\
+&= f(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
+&\leq f(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})\\
+&\leq f(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k \\
+&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - p_k) p_{m+1} + \gamma_{m+1} u_{m+1}\\
+&= f(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
 \end{align*}
 \begin{align*}
-&~~f_{\vee}(A^{(m+1)}, w) = f_{\vee}(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
-&= f_{\vee}(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})
+&~~f_{\wedge}(A^{(m+1)}, w) \\
+&= f_{\wedge}(A^{(m)}, w) -\prod_{k=1}^{m} w_k \\
+&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
+&= f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} \gamma_k u_k \\
+&\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
+&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
 \end{align*}
@@
 \begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
-From lemma \ref{lem:increasing} and $\theta_*^{\top}x_t \leq \bU_t$ by lemma \ref{lem:estimateU}, we can deduce 
-\begin{equation}
-\label{eq:fIncrease}
-f(A_t^*, \theta_*^{\top}x_t) \leq f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
-\end{equation}
-Further from lemma \ref{lem:estimateTech}, we can deduce
-\begin{equation}
-\label{eq:fTech}
-f(\bA_t, \bU_t) \leq f(\bA_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k
-\end{equation}
-where $u_k = \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}$. Combining equation (\ref{eq:fIncrease})) and (\ref{eq:fTech})), we can conclude that
+Using lemma \ref{lem:increasing} and lemma \ref{lem:estimateU}, we can deduce 
 $$
-\Delta_{t, \bA_t} = f(A_t^*, \theta_*^{\top}x_t) - f(\bA_t, \theta_*^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k.
+f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
 $$
+Using lemma \ref{lem:estimateU} and lemma \ref{lem:estimateTech}, we can deduce
+$$
+f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+Combining the above two inequalities with $f(A_t^{\ast}, \bU_t) \leq f(\bA_t, \bU_t)$, we can conclude that
+$$
+\Delta_{t, \bA_t} = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+The result for the disjunctive objective is similar.
 \end{proof}
@@
 \begin{lemma}
-Suppose $A = (a_1, ..., a_{\abs{A}})$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then we have the following properties.
+\label{lem:prefixRelation}
+Suppose $A = (a_1, ..., a_{\abs{A}})$. For the conjunctive objective, it holds that
+$$
+p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
+$$
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the disjunctive objective, we have the following properties.
 \begin{itemize}
-\item[(1)] $f(A, w) \leq p_A + \gamma_{\abs{A} - 1}$;
-\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
-\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
-\item[(4)] $f(B_k, w) \leq p_{B_{k+1}} + \gamma_{k}$.
+\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
+\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
+\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
+\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}, ~k < \abs{A}$,
 \end{itemize}
-It also holds that $p_{A} \geq \gamma_{\abs{A}} - f_{\vee}(A, w)$.
+where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$ and $0 = \gamma_1' \leq \gamma_2' \leq \cdots \leq \gamma_K' \leq 1$.
 \end{lemma}
@@
 \begin{proof}
-It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$.
+It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
+$$
+f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
+$$
+Then for the disjunctive objective,
 \begin{itemize}
 \item[(1)]
-$f(A, w) \leq \gamma_{m-1}(1 - p_A w_m) + p_A w_m \leq \gamma_{m-1} + p_A$;
+\begin{align*}
+f_{\wedge}(A, w) &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
+&\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
+\end{align*}
 
@@
 &f(B_k, w) - f(B_{k+1}, w)\\
-&=\prod_{i=1}^{k}w_i - \gamma_{k} (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
-&=(1 - \gamma_{k}) (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0.
+&=\prod_{i=1}^{k}w_i - \gamma_{k+1}' (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
+&=(1 - \gamma_{k+1}') (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0;
 \end{align*}
@@
 \item[(3)]
-Obvious.
+obvious;
 
 \item[(4)]
-$$
-f(B_k, w) \leq \gamma_{k-1} (1 - p_{B_{k+1}}) + p_{B_{k+1}}\leq p_{B_{k+1}} + \gamma_{k}
-$$
+\begin{align*}
+f_{\wedge}(B_k, w) &\leq \gamma_{k}' (1 - p_{B_{k+1}}) + p_{B_{k+1}}\\
+&\leq \gamma_{k+1}' (1 - p_{B_{k+1}}) + p_{B_{k+1}} \\
+&= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}
+\end{align*}
 \end{itemize}
@@
 
-\begin{proposition}
-Suppose $A = (a_1, ..., a_{\abs{A}})$. Then there exists a prefix $B$ of $A$, such that 
+\begin{lemma}
+Suppose $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the disjunctive objective, there exists a prefix $B$ of $A$ such that 
 $$
-p_{B} \geq \frac{1}{2}f^* - \gamma_{\abs{B}-1}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
+p_{B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
 $$ 
-\end{proposition}
+\end{lemma}
 \begin{proof}
-	Notice that $f^* \leq 1$. By above lemma, we have $[f(A,w), 1] \subset \bigcup [f(B_k,w), p_{B_k} + \gamma_{k-1}]$.
+Notice that $f_{\wedge, t}^{\ast} \leq 1$. If $p_{A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'$, then the lemma is proved.
+
+Suppose this does not hold.
+By lemma \ref{lem:prefixRelation}, we have $[f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}]$ is an interval and the intersection between interval $[f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}]$ and interval $[f_{\wedge}(B_{k+1},w), \gamma_{k+1}' + (1 - \gamma_{k+1}')p_{B_{k+1}}]$ in not empty.
+Notice when $k=\abs{A}$, $f_{\wedge}(B_k,w) = f_{\wedge}(A, w)$ and when $k = 1$, $\gamma_k' + (1 - \gamma_k')p_{B_k} = 1$.
+So we have
+$$
+[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} [f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}].
+$$
+Then there exists a $k$ such that $f(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{B_k}$. Therefore, the results are derived.
 \end{proof}
@@
 \begin{proposition}
-Suppose $\gamma_{K-1} \leq \frac{1}{4} f^*$. With high probability $1-\delta$, 
+Suppose the equation (\ref{eq:estimateTheta}) holds for any time $t$ and $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0, \gamma_k' = 1 - \gamma_k$. If we have
 $$
-E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{4}{f^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+\gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad \gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast}
 $$
+for some positive integer $n_0$, then
+\begin{align*}
+&E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
+&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
+\end{align*}
+where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
 \end{proposition}
 \begin{proof}
-By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}f_t^*$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
+The conjunctive case can be derived directly.
+For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}f_t^*$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$.
+Then we have
 $$
-\EE[\Delta_{t, \bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{t, \bB_t} \bOne\{\Delta_{t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+\EE[\Delta_{\wedge, t, \bA_t} | \cH_{t-1}] \leq \frac{8}{f_t^*} \EE[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
 $$
-Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$ and lemma \ref{lem:estimateU}, \ref{lem:increasing}, it holds that
+Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$, lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
 $$

### 2015-12-02 contextual combinatorial cascading bandits.tex

@@
 \usepackage{multirow}
+\usepackage{ifthen}
+\usepackage[usenames]{color}
+\usepackage[usenames,dvipsnames]{xcolor}
+
 \newcommand{\EE}{\mathbb{E}}
@@
 
+\newcommand{\compilehidecomments}{false}
+
+% Macro for comments:
+\ifthenelse{ \equal{\compilehidecomments}{true} }{%
+	\newcommand{\wei}[1]{}
+	\newcommand{\yang}[1]{}
+	\newcommand{\yajun}[1]{}
+}{
+\newcommand{\wei}[1]{{\color{blue!50!black}  [\text{Wei:} #1]}}
+\newcommand{\shuai}[1]{{\color{brown!60!black} [\text{Shuai:} #1]}}
+\newcommand{\shengyu}[1]{{\color{green!50!black} [\text{Shengyu:} #1]}}
+}
+
 % Employ the following version of the ``usepackage'' statement for
@@
 % the note in the first column to ``Under review.  Do not distribute.''
-\usepackage{icml2015}
+%\usepackage{icml2015}
 
@@
 % note in the first column to ``Proceedings of the...''
-%\usepackage[accepted]{icml2015}
+\usepackage[accepted]{icml2015}
 
@@
 
-We model our problem as a contextual combinatorial cascading bandit.
-Suppose we have $E=\{1,...,L\}$ a finite set of $L$ ground items.
+We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set of $L$ ground items,  $E=\{1,...,L\}$, also referred to as {\em base arms}. 
 Let $\prod^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
-Let $\cS \subset \prod^{\leq K}(E)$ consist of feasible actions with length no more than $K$.
+We also refer to each of such tuples as an {\em action}.
+Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$.
 
+\wei{We should unify terms, such as agent, user, player, etc. Also I suggest to refer to the agent as she, her.
+Also for base arms, should we call them base arms, or items? their outcome as weights, or reward? It is fine to use up to two
+terms interchangibly, but if so, we need to say it clearly at the first time the term is referred to.
+Otherwise, we stick to one term.}
 At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every basic arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding basic arm.
 Then the learning agent recommends a feasible solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
+\wei{Why using $\ba_{1}^t$, not $a_1^t$?}
 Starting from the first item, the user checks the items one by one.
@@
 
-Assume $\bw_{t,a}$ are mutually independent and satisfy
+Assume $\bw_{t,a}$'s are mutually independent and satisfy
 \begin{equation}
 \label{eq:expectation}
-\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a}
+\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a},
 \end{equation}
@@
 $$ 
+\wei{The above definition of $\bO_t$ looks indirect to me. What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$
+	if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.}
 or 
 $$
-\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 0, ~~ k \leq \abs{\bA_t}.
+\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 0, ~~ \forall\, k \leq \abs{\bA_t}.
 $$
@@
 &f : \cS \times [0,1]^E \to [0,1]\\
-&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
+&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
 \end{align*}
-then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
 \begin{align*}
@@
 
+The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm
+	at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
 Similarly, we could also consider the case of conjunctive objective.
@@
 Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
-The more items, the more reward the learning agent should receive.
+The more items the learning agent reveals, the more reward the agent should receive.
 It is reasonable to assume that
 $$
-0 = \gamma_1 \leq \gamma_2 \leq \cdots \leq \gamma_K \leq 1.
+0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
 $$
 At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of
+	$\gamma_{\bO_t}'$ and $\gamma_{k}'$. It is inconsistent with the above description, and I think the latter makes sense.}
 \begin{align*}

### 2015-12-02 contextual combinatorial cascading bandits.tex
update proofs and use of language

@@
 Otherwise, we stick to one term.}
-At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every basic arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding basic arm.
-Then the learning agent recommends a feasible solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
-\wei{Why using $\ba_{1}^t$, not $a_1^t$?}
+\shuai{I have unified all terms by {\em base arms}, {\em actions} and {\em the learning agent}}
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
+Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
+\wei{Why using $\ba_{1}^t$, not $a_1^t$?} \shuai{I think $a_1^t$ is a random variable because $\bA_t$ is random. Is it making sense?}
 Starting from the first item, the user checks the items one by one.
 The checking process stops if the user clicks on one item or has checked all items without clicking anyone.
-We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate whether the user has clicked on item $a$ or not at time $t$.
+We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$ to indicate whether the user has clicked on $a$ or not.
 
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
-At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$ where
+\wei{The above definition of $\bO_t$ looks indirect to me.
+What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$, if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.} \shuai{I have modified accordingly.} For some $k=1,2,\ldots, \abs{\bA_t}$,
 $$
-\bO_t \leq \abs{\bA_t}, \bw_t(\ba_k^t) = \begin{cases} 0, ~~k < \bO_t \\ 1, ~~k = \bO_t \end{cases}
+\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
 $$
-\wei{The above definition of $\bO_t$ looks indirect to me. What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$
-	if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.}
 or 
 $$
-\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 0, ~~ \forall\, k \leq \abs{\bA_t}.
+\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
 $$
-We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
+At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
 
@@
 
-The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm
-	at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
 Similarly, we could also consider the case of conjunctive objective.
-We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the {\it weight} of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})).
+We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})).
 The learning agent observes all items until the first one with weight $0$.
@@
 At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
-\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of
-	$\gamma_{\bO_t}'$ and $\gamma_{k}'$. It is inconsistent with the above description, and I think the latter makes sense.}
+\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of $\gamma_{\bO_t}'$ and $\gamma_{k}'$.
+It is inconsistent with the above description, and I think the latter makes sense.}
+\shuai{This is an earlier version. I have modified it and all others.}
 \begin{align*}
 \br_{\wedge, t} &= \begin{cases}
-\gamma_{\bO_t - 1}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
+\gamma_{\bO_t}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
 1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
@@
 &=\begin{cases}
-\gamma_{k - 1}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
+\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
 1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
@@
 Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
-Here we abuse the notation $\abs{\bA_s}$ to denote the number of elements in the list $\bA_s$.
+Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$.
 By equation (\ref{eq:expectation}), we have
@@
 $$
-we get a $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
+we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
 \begin{equation}
@@
 This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm.
-Building on this, we can define an upper confidence bound of the expected weight of item $a$ by
+Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
 \begin{equation}
@@
 
-The fact that $\bU_t(a)$ is an upper confidence bound of $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
+The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
 \begin{lemma}
@@
 Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}.
-First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$.
-Second, it recommends the output $\bA_t$ by the offline oracle with estimated weights $\bU_t$.
-Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), k \in [\bO_t]$, where
+First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$.
+Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$.
+Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where
 $$
@@
 \label{thm:main}
-Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq c f^*$ and regularization parameter $\lambda \geq C_\gamma$ for some constant $\frac{1}{2} < c < 1$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
-\begin{equation}
-R(T) = O(d^{3/4}\log^{3/4}(C_\gamma T)\sqrt{KT}),
-\end{equation}
+Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \gamma_{K} \geq c f^*$ for some constant $c > 1$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$.
+Let regularization parameter satisfy $\lambda \geq C_\gamma$.
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
+\begin{align}
+&R(T) = O(\frac{d}{c-1} \log(C_\gamma T) \sqrt{KT}),\\
+&R_{\wedge}(T) = O(\frac{d}{f_{\wedge}^{\ast}} \log(C_\gamma T) \sqrt{KT}).
+\end{align}
 where
@@
 \end{align*}
-\end{theorem}
-
-Suppose the reward function is disjunctive.
-At every time $t$, the forecaster recommends a list $\bA_t$.
-Then the user checks from the first item to the end.
-The weight $\bw_t(a)$ denote whether the user click on item $a$ or not.
-The user stops if she clicks on one item of $\bA_t$ or she has checked all items of $\bA_t$.
-If the user clicks on the first item, then the learning agent receives reward $1$.
-If the user clicks on the $k$-th reward of $\bA_t$, then the reward is $\gamma_k$.
-If the user doesn't click on any item, then the reward is $0$.
-Here we further assume $\gamma_2 \geq \gamma_3 \geq \ldots \geq \gamma_K$.
-If we define a function $f_{\vee}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS$ and $w = (w(1), \ldots, w(L))$ by
-\begin{align*}
-&f_{\vee} : \cS \times [0,1]^E \to [0,1]\\
-&f_{\vee}(A,w) = \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
-\end{align*}
-Here we use notation that $\gamma_1 = 1$. Then the expected reward of $\bA_t$ is $f_{\vee}(\bA_t, \theta_*^{\top}x_t)$.
-
-Then we have a relationship between $f$ and $f_{\vee}$
-\begin{equation}
-\label{eq:relation}
-\begin{split}
-&f_{\vee}(A, w; 1, \gamma_2, \ldots, \gamma_K) \\
-&~~= 1 - f(A, 1 - w; 0, 1-\gamma_2, \ldots, 1-\gamma_K)
-\end{split}
-\end{equation}
-If $\gamma$ is decreasing, then $1 - \gamma$ is increasing. Thus we have $1 - \gamma$ a feasible parameters for $f$. Then we could have a similar result for disjunctive case.
-\begin{theorem}
-Disjunctive case
 \end{theorem}
@@
 \label{lem:increasing} 
-Given $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A \in \prod^{\leq K}(E)$,
+Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$.
+Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; equivalently, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}(E)$, it holds that
 $$
-f(A, w) \leq f(A, w').
-$$
-By relation (\ref{eq:ConDisRelation}), it also holds that
-$$
-f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
+f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
 $$
@@
 \geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-\geq &~\gamma_{k-1} \cdot 0 = 0,
+\geq &~\gamma_{k} \cdot 0 = 0,
 \end{align*}
@@
 \end{align*}
+By letting $\gamma_k = 1 - \gamma_k'$ and the relation (\ref{eq:ConDisRelation}), the increasing property of $f_{\wedge}$ is obtained directly.
 \end{proof}
@@
 \label{lem:estimateTech}
-Suppose $0 \leq p_1, \ldots, p_m \leq 1$ and $u_1, \ldots, u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq p_1, \ldots, p_m \leq 1$, $u_1, \ldots, u_m \geq 0$ and $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
 \begin{align*}
-f(A^{(m)}, w) &\leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
-f_{\wedge}(A^{(m)}, w) &\leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,
+&f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
+&f_{\wedge}(A^{(m)}, w) \leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} (1 - \gamma_k') u_k,
 \end{align*}
-for any positive $\gamma_k, \gamma_k'$ with $\gamma_k' = 1 - \gamma_k$, where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
-Notice that the parameters involved in the conclusions are $\gamma_k, k \in [m]$ while the parameters used in the definition of $f_{\wedge}$ are $\gamma_k', k \in [m]$.
+where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
 \end{lemma}
@@
 &\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} \gamma_k u_k \\
+&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} (1 - \gamma_k') u_k \\
 &\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
-&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
+&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} (1 - \gamma_k') u_k
 \end{align*}
@@
 \begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
-Using lemma \ref{lem:increasing} and lemma \ref{lem:estimateU}, we can deduce 
+By lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by lemma \ref{lem:increasing},
 $$
@@
 $$
-Using lemma \ref{lem:estimateU} and lemma \ref{lem:estimateTech}, we can deduce
+By lemma \ref{lem:estimateTech} and the definition of $\bU_t$ (\ref{eq:defU}),
 $$
-f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
 $$
-Combining the above two inequalities with $f(A_t^{\ast}, \bU_t) \leq f(\bA_t, \bU_t)$, we can conclude that
+Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
 $$
-\Delta_{t, \bA_t} = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
 $$
-The result for the disjunctive objective is similar.
+Therefore,
+$$
+\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+The result for the disjunctive case can be deduced similarly.
 \end{proof}
@@
 \label{lem:prefixRelation}
-Suppose $A = (a_1, ..., a_{\abs{A}})$. For the conjunctive objective, it holds that
+Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the conjunctive case, it holds that
 $$
@@
 $$
-Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the disjunctive objective, we have the following properties.
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the disjunctive case and $k < \abs{A}$, we have the following properties:
 \begin{itemize}
@@
 \item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
-\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}, ~k < \abs{A}$,
+\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
 \end{itemize}
-where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$ and $0 = \gamma_1' \leq \gamma_2' \leq \cdots \leq \gamma_K' \leq 1$.
 \end{lemma}
@@
 \begin{align*}
-&f(B_k, w) - f(B_{k+1}, w)\\
+&f_{\wedge}(B_k, w) - f_{\wedge}(B_{k+1}, w)\\
 &=\prod_{i=1}^{k}w_i - \gamma_{k+1}' (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
@@
 \item[(3)]
-obvious;
+$p_{\wedge, B_{k+1}} = \prod_{i=1}^{k} w_i \leq \prod_{i=1}^{k-1} w_i = p_{\wedge, B_k}$;
 
@@
 \begin{lemma}
-Suppose $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the disjunctive objective, there exists a prefix $B$ of $A$ such that 
+Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the disjunctive objective, there exists a prefix $B$ of $A$ such that 
 $$
-p_{B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
+p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
 $$ 
@@
 \begin{proof}
-Notice that $f_{\wedge, t}^{\ast} \leq 1$. If $p_{A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'$, then the lemma is proved.
+If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by lemma \ref{lem:prefixRelation},
+$$
+p_{A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
+$$
 
-Suppose this does not hold.
-By lemma \ref{lem:prefixRelation}, we have $[f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}]$ is an interval and the intersection between interval $[f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}]$ and interval $[f_{\wedge}(B_{k+1},w), \gamma_{k+1}' + (1 - \gamma_{k+1}')p_{B_{k+1}}]$ in not empty.
-Notice when $k=\abs{A}$, $f_{\wedge}(B_k,w) = f_{\wedge}(A, w)$ and when $k = 1$, $\gamma_k' + (1 - \gamma_k')p_{B_k} = 1$.
-So we have
+Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
 $$
-[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} [f_{\wedge}(B_k,w), \gamma_k' + (1 - \gamma_k')p_{B_k}].
+x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
 $$
-Then there exists a $k$ such that $f(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{B_k}$. Therefore, the results are derived.
+Then by lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$.
+Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$.
+Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$.
+Thus
+$$
+[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
+$$
+Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
+$$
+f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}
+$$
+Therefore, the results are derived.
 \end{proof}
@@
 \begin{proposition}
-Suppose the equation (\ref{eq:estimateTheta}) holds for any time $t$ and $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0, \gamma_k' = 1 - \gamma_k$. If we have
+Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for any time $t$. If we have
 $$
@@
 \begin{proof}
-The conjunctive case can be derived directly.
-For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}f_t^*$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$.
+For the conjunctive case, $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
+
+For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$.
 Then we have
 $$
-\EE[\Delta_{\wedge, t, \bA_t} | \cH_{t-1}] \leq \frac{8}{f_t^*} \EE[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+\EE[\Delta_{\wedge, t, \bA_t} | \cH_{t-1}] \leq \frac{8}{f_{\wedge, t}^*} \EE[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
 $$
-Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$, lemma \ref{lem:estimateU} and lemma \ref{lem:increasing}, it holds that
+Because 
 $$
-f(\bA_t^*, \theta_*^{\top}X_t) \leq f(\bB_t,\bU_t).
+f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
 $$
-Then by lemma \ref{lem:estimateTech}
+by lemma \ref{lem:increasing} and
 $$
-f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
-Therefore,
+by lemma \ref{lem:estimateTech}, we have
 $$
@@
 &\trace(\bV_t)\\
-& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
-& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s,\abs{\bA_s}\}} \gamma_k'^2 \norm{x_{s,\ba_k^s}}_2^2\\
-& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k'^2=d\lambda + tC_\gamma.
+& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
+& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
+& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
 \end{align*}
@@
 \begin{align*}
-&\det(I + \sum_{i=1}^n x_i x_i^{\top})\\
-&= \prod_{j=1}^d (1 + \alpha_j)\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
+&\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
+&\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
 &=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
@@
 \begin{lemma}
-If $\lambda \geq C_\gamma$, it holds that
+If $\lambda \geq C_\gamma$, then
 $$
-\sum_{s=1}^t \sum_{k=1}^{\min\{\bO_s, \abs{\bA_s}\}} \norm{\gamma_k' x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\det(\bV_t)).
+\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\det(\bV_t)).
 $$
@@
 \begin{align*}
-&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k' X_{t,\ba_k^{t}})(\gamma_k' X_{t, \ba_k^{t}}^{\top}))\\
+&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
 &=\det(\bV_{t-1})\\
-&~~~~\det(I + \sum_{k=1}^{\bO_t} \gamma_k'\bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k' \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
-&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma^{k-1}x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
-&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma^{k-1}x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
+&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
+&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
+&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
 \end{align*}
@@
 $$
-\norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k' x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k'^2 /\lambda,
+\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
 $$
@@
 $$
-\sum_{k=1}^{\bO_s} \norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k'^2 = C_\gamma /\lambda \leq 1
+\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
 $$
@@
 \begin{align*}
-&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k' x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k' x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
+&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
 &\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I))) < 2\log(\det(\bV_t))
@@
 \begin{proof}[ of theorem \ref{thm:main}]
-With probability at least $1-\delta$,
+Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.
+
+For the conjunctive case,
 \begin{equation}
 \begin{split}
-&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
-&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
-&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(d\log(C_\gamma T)\sqrt{TK})
+&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
+&\leq \sum_{t=1}^{T} (n_0 + 1) \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq (n_0 + 1) \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
+&\leq O(n_0 d \log(C_\gamma T)\sqrt{TK}).
+\end{split}
+\end{equation}
+
+For the disjunctive case, 
+\begin{equation}
+\begin{split}
+&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
+&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
+&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sqrt{(\sum_{t=1}^{T} \bO_t) (\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)}]\\
+&\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).
 \end{split}

### 2015-12-02 agent.py
cccucb draft

@@ -7,12 +7,11 @@ import matplotlib.pyplot as plt
 
 import time
 import random
-seed = time.time()
-random.seed(seed)
+
 import logging
 logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.INFO)
 logger = logging.getLogger('Agent')
-logger.info('Random seed = {0}'.format(seed))
+
 
 def movies_mix_cld_adt(L=200):
     children, adults = set(), set()
@@ -79,11 +78,22 @@ def monkey(candidates, K=8, T=150000, verbose=False):
                     print('Agent: Score={0}/{1}'.format(score, t))
     return agent
 
-from environment import movielens
-candidates = movies_mix_cld_adt()
-environment = movielens(candidates[0] + candidates[1], 1)
-agent = ucb(candidates)
-agent(environment)
-agent = monkey(candidates)
-agent(environment)
+from environment import monkey_context
+e, s = monkey_context()
+delta = 
+lamb = 
+theta = np.zeros(s.d)
+beta = 0
+V = lamb * np.eye(s.d)
+X = np.zeros
+for i in range (100):
+    c = e()
+    U = {min(arm:theta.dot(c[arm]) + beta * c[arm].T.dot(np.linalg.inv(V)).dot(c[arm]), 1) fro arm in s.arms}
+    recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in arms])]
+    r, C = e(recc)
+    if np.isinf(C):
+    
+    V += sum([s.gamma ** (2*k) * c[recc[k]].dot(c[recc[k]].T) for k in range(C+1)])
+    X = np.concatenate([gamma ** k * c[recc[k]] for k in range(C+1)])
+    print(r, C)
 

### 2015-12-02 environment.py

@@ -7,32 +7,43 @@ import random
 import logging
 logger = logging.getLogger('Environment')
 
+seed = int(time.time())
+np.random.seed(seed)
+logger.info('Numpy Random seed = {0}'.format(seed))
+
 from functools import reduce
 
-class ucb_settings:
-    def __init__(**s):
-        self.__dict__ = s
+def uni(x):
+    return x/np.sqrt((x*x).sum())
 
-def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3, eps=0.1, disj=False):
+class ucb_settings:
+    def __init__(self, **s):
+        self.__dict__ = s
+        
+    def __str__(self):
+        return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
+
+def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3, eps=0.1, v=0.35, disj=False):
     logger.info('Initializing environment "Monkey Contextual"')
     arms = [idx for idx in range(L)]
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
-    theta = np.random.uniform(0, 1, d)
-
+    theta = v * uni(np.random.uniform(0, 1, d))
     xt = {arm:x[arm] for arm in x}
     def environment(recommend=None):
         if recommend == None:
-            xt = {arm:x[arm] + np.random.uniform(-v, v, d) for arm in x}
+            for arm in xt:
+                xt[arm] = uni(x[arm] + np.random.uniform(-v, v, d))
             return xt
         else:
-            for C, arm in enumerate(recomend): 
+            assert(len(recommend) <= K)
+            for C, arm in enumerate(recommend): 
                 p = theta.dot(xt[arm]) + np.random.normal(0, eps)
+                print('proba', p)
                 if (np.random.uniform(0, 1) < p) ^ disj:
-                    return gamma ^ C * int(not disj), C
-            return int(not disj), np.inf
-
-    return environment, ucb_setting(arms=arms, K=K, d=d, gamma=gamma)
-
+                    return gamma ** C * int(not disj), C
+            return int(disj), np.inf
+    logger.info('Initialized environment "Monkey Contextual"')
+    return environment, ucb_settings(arms=arms, K=K, d=d, gamma=gamma)
 
 def movielens(candidates, userno=1):
     logger.info('Initializing environment "Movielens"')

### 2015-12-02 contextual combinatorial cascading bandits.tex
update main theorem and unify items

@@
 $$
-At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward
 \wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of $\gamma_{\bO_t}'$ and $\gamma_{k}'$.
@@
 \br_{\wedge, t} &= \begin{cases}
-\gamma_{\bO_t}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
-1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
+\gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
+1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
 \end{cases}\\
@@
 $$
-Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. The above notifications hold for both disjunctive and conjunctive objectives.
+Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. In the following, we will mainly use notations for disjunctive objective when the two cases are similar.
 
@@
 \label{thm:main}
-Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \gamma_{K} \geq c f^*$ for some constant $c > 1$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$.
+Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$.
 Let regularization parameter satisfy $\lambda \geq C_\gamma$.
@@
 \begin{align}
-&R(T) = O(\frac{d}{c-1} \log(C_\gamma T) \sqrt{KT}),\\
+&R(T) = O(\frac{d}{p^*} \log(C_\gamma T) \sqrt{KT}),\\
 &R_{\wedge}(T) = O(\frac{d}{f_{\wedge}^{\ast}} \log(C_\gamma T) \sqrt{KT}).
@@
 \begin{align*}
-f^* &= \min_{1 \leq t \leq T} f_t^*\\
-C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
+&f^* = \min_{1 \leq t \leq T} f_t^{\ast},\\
+&f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},\\
+&C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K-1} (1 - \gamma_k')^2 = O(K),
+\end{align*}
+and $p_{t, \bA_t}$ and $p_{\wedge, t, \bA_t}$ are probabilities that all base arms of $\bA_t$ have been observed
+\begin{align*}
+&p_{t, \bA_t} = \PP(\bO_t \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (1 - \theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
+&p_{\wedge, t, \bA_t} = \PP(\bO_{\wedge, t} \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (\theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
+&p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}.
 \end{align*}
@@
 $$
-\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+\Delta_{\wedge, t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
-f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
+f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
 $$
-Then we can derive an estimate of $\Delta_{t, \bA_t}$, however, in terms of all elements in $\bA_t$.
+Then we can derive an estimate of $\Delta_{t, \bA_t}$ and $\Delta_{\wedge, t, \bA_t}$, however, in terms of all base arms in $\bA_t$.
+Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
+\begin{align*}
+&~~\EE_t[\Delta_{t, \bA_t}] \\
+&= \EE[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
+&~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
+&= \EE[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
+\end{align*}
 
-However, this estimate involves all elements of $\bA_t$. Only when the learning agent has observed all elements of $\bA_t$, we can use such an estimate, which means we are able to estimate
-$$
-\EE[\Delta_{t, \bA_t}] = \EE[\Delta_{t, \bA_t}(1/p_{\bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}].
-$$
-Problem might happen if $p_{\bA_t}$ is small. Thus we need the following lemma to find a good substitution of $\bA_t$.
+In real problems involved with recommendations, the click rate is a very small number.
+Thus for the problem with disjunctive objective, $p^*$ is relatively high and can be regarded as a constant.
+So we have $p_{t, \bA_t} \geq p^*$.
+For the problem with conjunctive objective, $p_{\wedge, t, \bA_t}$ might be small.
+Thus we need the following lemma to find a good substitution of $\bA_t$.
 
@@
 \label{lem:prefixExist}
-Suppose the weights for items in $E$ are $w = (w_a)_{a \in E}$.
-Let $A = (a_1, ..., a_{\abs{A}})$ be a list and let $p_A$ denote the probability that all of items in $A$ are observed; equivalently, $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$.
-Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$.
-Then for any given constant $\frac{1}{2} < c < 1$, there exists a prefix $B$ of $A$ such that
+Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
 $$
-p_B \geq c f^* - \gamma_{\abs{B}}, \qquad \Delta_B \geq \frac{1}{2} \Delta_A,
-$$
-where
-$$
-f^* = \max_{A'} f(A', w), \qquad \Delta_{A'} = f^* - f(A', w).
+p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad \Delta_{\wedge, t, \bB_t} \geq \frac{1}{2} \Delta_{\wedge, t, \bA_t}.
 $$
 \end{lemma}
-
-From this lemma, we can find a prefix $\bB_t$ of $\bA_t$ such that $p_{B_t}$ is large enough and $\Delta_{\bB_t}$ will not be too small.
-Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$.
+From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $\Delta_{\wedge, t, \bB_t}$ will not be too small.
+Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
 We leave all details in the next subsection.

### 2015-12-03 contextual combinatorial cascading bandits.tex

@@
 \usepackage{hyperref}
+\hypersetup{
+	colorlinks   = true, %Colours links instead of ugly boxes
+	urlcolor     = blue, %Colour for external hyperlinks
+	linkcolor    = blue, %Colour of internal links
+	citecolor   = blue %Colour of citations
+}
 
@@
 \usepackage{amssymb,amsfonts,amsmath,bbm}
-\usepackage{hyperref}
 \usepackage{mathrsfs}
@@
 
-\wei{We should unify terms, such as agent, user, player, etc. Also I suggest to refer to the agent as she, her.
-Also for base arms, should we call them base arms, or items? their outcome as weights, or reward? It is fine to use up to two
-terms interchangibly, but if so, we need to say it clearly at the first time the term is referred to.
-Otherwise, we stick to one term.}
-\shuai{I have unified all terms by {\em base arms}, {\em actions} and {\em the learning agent}}
 At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
@@
 Assume $\bw_{t,a}$'s are mutually independent and satisfy
+\wei{Is this given $x_{t,a}$ accurate? $x_{t,a}$  is not a probabilistic event. Also, are we assuming $\bw_{t,a}$'s are
+		also independent of all other events, such as the event before time $t$? We should make it clear.
+Perhaps we should put the history definition here?}
 \begin{equation}
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
-\wei{The above definition of $\bO_t$ looks indirect to me.
-What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$, if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.} \shuai{I have modified accordingly.} For some $k=1,2,\ldots, \abs{\bA_t}$,
+We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is,
+	for some $k=1,2,\ldots, \abs{\bA_t}$, 
 $$
@@
 Similarly, we could also consider the case of conjunctive objective.
-We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})).
+We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}).
 The learning agent observes all items until the first one with weight $0$.
@@
 At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward
-\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of $\gamma_{\bO_t}'$ and $\gamma_{k}'$.
-It is inconsistent with the above description, and I think the latter makes sense.}
-\shuai{This is an earlier version. I have modified it and all others.}
+	$\br_{\wedge, t}$:
 \begin{align*}
@@
 Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$.
-By equation (\ref{eq:expectation}), we have
+By Equation \eqref{eq:expectation}, we have
 $$

### 2015-12-03 contextual combinatorial cascading bandits.tex
update notation of history and conditional expectation

@@
 We also refer to each of such tuples as an {\em action}.
-Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$.
+Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$. As a convention, we use boldface symbols to represent all random variables.
 
@@
 
-Assume $\bw_{t,a}$'s are mutually independent and satisfy
+Let $\cH_t$ denote all history before the learning agent chooses action at time $t$; $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
+Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
 \wei{Is this given $x_{t,a}$ accurate? $x_{t,a}$  is not a probabilistic event. Also, are we assuming $\bw_{t,a}$'s are
@@
 \label{eq:expectation}
-\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a},
+\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
 \end{equation}
@@
 
-Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
+Because $\cH_t$ denotes all history before time $t$ and context information of time $t$, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s<t, x_t \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
 Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$.
@@
 $$
-\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
+\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
 $$
@@
 $$
-\{(\gamma_k X_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
+\{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
 $$
@@
 &~~\EE_t[\Delta_{t, \bA_t}] \\
-&= \EE[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
+&= \EE_t[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
 &~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
-&= \EE[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
+&= \EE_t[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
 \end{align*}
@@
 \label{lem:prefixRelation}
-Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the conjunctive case, it holds that
-$$
-p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
-$$
-Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the disjunctive case and $k < \abs{A}$, we have the following properties:
+Suppose 
+% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
+$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
+% For the conjunctive case, it holds that
+% $$
+% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
+% $$
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with disjunctive objective and $k < \abs{A}$, we have the following properties:
 \begin{itemize}
@@
 \begin{proof}
-It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
-$$
-f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
-$$
-Then for the disjunctive objective,
+% It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
+% $$
+% f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
+% $$
+% Then for the disjunctive objective,
 \begin{itemize}
@@
 \begin{proposition}
-Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for any time $t$. If we have
+Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
 $$
-\gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad \gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast}
+E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
 $$
-for some positive integer $n_0$, then
+If we have
+% $$
+% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
+% $$
+$$
+\gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast},
+$$
+then
 \begin{align*}
-&E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
+% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
 &E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
@@
 \begin{proof}
-For the conjunctive case, $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
+For the conjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
+% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
 
@@
 $$
-\EE[\Delta_{\wedge, t, \bA_t} | \cH_{t-1}] \leq \frac{8}{f_{\wedge, t}^*} \EE[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
 $$
@@
 $$
-\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
-&\leq \sum_{t=1}^{T} (n_0 + 1) \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq (n_0 + 1) \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
-&\leq O(n_0 d \log(C_\gamma T)\sqrt{TK}).
+&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
+&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
+&\leq O(\frac{d}{p^*} \log(C_\gamma T)\sqrt{TK}).
 \end{split}
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
-&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
-&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sqrt{(\sum_{t=1}^{T} \bO_t) (\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)}]\\
+&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
+&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
 &\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).

### 2015-12-03 agent.py
synthetic: sherry beats monkey

@@ -3,6 +3,7 @@ import csv
 import heapq
 
 import numpy as np
+from scipy.spatial.distance import cosine
 import matplotlib.pyplot as plt
 
 import time
@@ -11,7 +12,6 @@ import random
 import logging
 logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.INFO)
 logger = logging.getLogger('Agent')
-
 
 def movies_mix_cld_adt(L=200):
     children, adults = set(), set()
@@ -78,22 +78,44 @@ def monkey(candidates, K=8, T=150000, verbose=False):
                     print('Agent: Score={0}/{1}'.format(score, t))
     return agent
 
-from environment import monkey_context
-e, s = monkey_context()
-delta = 
-lamb = 
-theta = np.zeros(s.d)
-beta = 0
-V = lamb * np.eye(s.d)
-X = np.zeros
-for i in range (100):
-    c = e()
-    U = {min(arm:theta.dot(c[arm]) + beta * c[arm].T.dot(np.linalg.inv(V)).dot(c[arm]), 1) fro arm in s.arms}
-    recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in arms])]
-    r, C = e(recc)
-    if np.isinf(C):
-    
-    V += sum([s.gamma ** (2*k) * c[recc[k]].dot(c[recc[k]].T) for k in range(C+1)])
-    X = np.concatenate([gamma ** k * c[recc[k]] for k in range(C+1)])
-    print(r, C)
+def contextual_cascading_monkey(T=100000):
+    def agent(environment):
+        e, s = environment
+        score = 0
+        for t in range(1, T):
+            recc = random.sample(s.arms, s.K)
+            r, _ = e(recc)
+            score += r
+            if t % 10000 == 0:
+                print('Agent: Score={0}/{1}'.format(score, t))
+    return agent
+        
+def contextual_cascading_sherry(environment, T=100000):
+    e, s = environment()
+    delta = 0.9
+    lamb = 0.1
+    theta = np.zeros(s.d)
+    beta = 0
+    V = lamb * np.eye(s.d)
+    ldV = np.log(np.linalg.det(V))
+    X = np.zeros((1, s.d))
+    Y = np.zeros(1)
+    score = [0]
+    for i in range (1, T):
+        x = e()
[…]

### 2015-12-03 environment.py

@@ -13,6 +13,12 @@ logger.info('Numpy Random seed = {0}'.format(seed))
 
 from functools import reduce
 
+import colorama
+colorama.init()
+
+def red(s):
+    return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
+
 def uni(x):
     return x/np.sqrt((x*x).sum())
 
@@ -23,7 +29,7 @@ class ucb_settings:
     def __str__(self):
         return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
 
-def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3, eps=0.1, v=0.35, disj=False):
+def contextual_cascading_monkey(L=20, K=4, d=10, gamma=0.95, eps=0.1, v=0.35, disj=False):
     logger.info('Initializing environment "Monkey Contextual"')
     arms = [idx for idx in range(L)]
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
@@ -36,14 +42,15 @@ def monkey_context(L=20, K=4, d=10, gamma=0.95, v=0.3, eps=0.1, v=0.35, disj=Fal
             return xt
         else:
             assert(len(recommend) <= K)
-            for C, arm in enumerate(recommend): 
+            print(sorted([theta.dot(xt[arm]) for arm in arms])[::-1])
+            print(red([theta.dot(xt[arm]) for arm in recommend]))
+            for c, arm in enumerate(recommend): 
                 p = theta.dot(xt[arm]) + np.random.normal(0, eps)
-                print('proba', p)
                 if (np.random.uniform(0, 1) < p) ^ disj:
-                    return gamma ** C * int(not disj), C
-            return int(disj), np.inf
+                    return gamma ** c * int(not disj), c
+            return int(disj), len(recommend)
     logger.info('Initialized environment "Monkey Contextual"')
-    return environment, ucb_settings(arms=arms, K=K, d=d, gamma=gamma)
+    return environment, ucb_settings(arms=arms, K=K, d=d, gamma=gamma, theta=theta)
 
 def movielens(candidates, userno=1):
     logger.info('Initializing environment "Movielens"')

### 2015-12-04 agent.py
arch refine

@@ -78,20 +78,16 @@ def monkey(candidates, K=8, T=150000, verbose=False):
                     print('Agent: Score={0}/{1}'.format(score, t))
     return agent
 
-def contextual_cascading_monkey(T=100000):
-    def agent(environment):
-        e, s = environment
-        score = 0
-        for t in range(1, T):
-            recc = random.sample(s.arms, s.K)
-            r, _ = e(recc)
-            score += r
-            if t % 10000 == 0:
-                print('Agent: Score={0}/{1}'.format(score, t))
-    return agent
-        
-def contextual_cascading_sherry(environment, T=100000):
-    e, s = environment()
+def contextual_cascading_monkey(e, s, T=10000):
+    score = [0]
+    for t in range(1, T):
+        _ = e()
+        recc = random.sample(s.arms, s.K)
+        r, _ = e(recc)
+        score.append(score[-1] + r)
+    return score, 0
+
+def contextual_cascading_sherry(e, s, T=10000):
     delta = 0.9
     lamb = 0.1
     theta = np.zeros(s.d)
@@ -103,7 +99,7 @@ def contextual_cascading_sherry(environment, T=100000):
     score = [0]
     for i in range (1, T):
         x = e()
-        U = {arm:min(theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]), 1) for arm in s.arms}
+        U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in s.arms}
         recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
         r, c = e(recc)
         V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(s.K, c+1))])
@@ -112,10 +108,15 @@ def contextual_cascading_sherry(environment, T=100000):
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.log(np.linalg.det(V))- ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
-    return score, cosine(s.theta, theta) 
+    return score, 1 - cosine(s.theta, theta) 
 
-from environment import contextual_cascading_monkey
-environment = contextual_cascading_monkey
-agent = contextual_cascading_sherry
[…]

### 2015-12-04 environment.py

@@ -20,7 +20,7 @@ def red(s):
     return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
 
 def uni(x):
-    return x/np.sqrt((x*x).sum())
+    return x/np.sqrt(x.dot(x))
 
 class ucb_settings:
     def __init__(self, **s):
@@ -29,28 +29,31 @@ class ucb_settings:
     def __str__(self):
         return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
 
-def contextual_cascading_monkey(L=20, K=4, d=10, gamma=0.95, eps=0.1, v=0.35, disj=False):
-    logger.info('Initializing environment "Monkey Contextual"')
-    arms = [idx for idx in range(L)]
+def contextual_monkey_rng(L=20, d=10, v=0.35):
+    arms = list(range(L))
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
     theta = v * uni(np.random.uniform(0, 1, d))
-    xt = {arm:x[arm] for arm in x}
+    return ucb_settings(arms=arms, x=x, theta=theta, d=d)
+
+def contextual_cascading_monkey(s=contextual_monkey_rng(), K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
+    logger.info('Initializing environment "Monkey Contextual"')
+    xt = {arm:s.x[arm] for arm in s.x}
     def environment(recommend=None):
         if recommend == None:
             for arm in xt:
-                xt[arm] = uni(x[arm] + np.random.uniform(-v, v, d))
+                xt[arm] = uni(s.x[arm] + np.random.uniform(-v, v, s.d))
             return xt
         else:
             assert(len(recommend) <= K)
-            print(sorted([theta.dot(xt[arm]) for arm in arms])[::-1])
-            print(red([theta.dot(xt[arm]) for arm in recommend]))
+            #print(sorted([s.theta.dot(xt[arm]) for arm in s.arms])[::-1])
+            #print(red([s.theta.dot(xt[arm]) for arm in recommend]))
             for c, arm in enumerate(recommend): 
-                p = theta.dot(xt[arm]) + np.random.normal(0, eps)
+                p = s.theta.dot(xt[arm]) + np.random.normal(0, eps)
                 if (np.random.uniform(0, 1) < p) ^ disj:
                     return gamma ** c * int(not disj), c
             return int(disj), len(recommend)
[…]

### 2015-12-04 contextual combinatorial cascading bandits.tex

@@
 We also refer to each of such tuples as an {\em action}.
-Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$. As a convention, we use boldface symbols to represent all random variables.
+Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$. 
+As a convention, we always use boldface symbols to represent random variables.
 
@@
 Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
-\wei{Why using $\ba_{1}^t$, not $a_1^t$?} \shuai{I think $a_1^t$ is a random variable because $\bA_t$ is random. Is it making sense?}
 Starting from the first item, the user checks the items one by one.
@@
 
-Let $\cH_t$ denote all history before the learning agent chooses action at time $t$; $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
-Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
-\wei{Is this given $x_{t,a}$ accurate? $x_{t,a}$  is not a probabilistic event. Also, are we assuming $\bw_{t,a}$'s are
-		also independent of all other events, such as the event before time $t$? We should make it clear.
-Perhaps we should put the history definition here?}
+Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
+Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
 \begin{equation}
@@
 At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t 
+	\mid  k \in[\bO_s], 1 \le s<t \}$.
 
@@
 
-Because $\cH_t$ denotes all history before time $t$ and context information of time $t$, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s<t, x_t \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$.
-Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$.
+At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent
+	chooses her action. 
 By Equation \eqref{eq:expectation}, we have 
@@
 $$
-Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. In the following, we will mainly use notations for disjunctive objective when the two cases are similar.
+Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. 
+%In the following, we will mainly use notations for disjunctive objective when the two cases are similar.
 
@@
 $$
-\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}.
+\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
 $$

### 2015-12-04 contextual combinatorial cascading bandits.tex

@@
 \label{lem:estimateU}
-When (\ref{eq:estimateTheta}) holds for time $t$, we have
+When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
 $$
@@
 \abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
-&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+&\leq \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 \end{align*}
@@
 Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
-In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.
+In this part, we use the notation $[A; B]$ to denote the matrix obtained by stack A and B vertically like
+ $\begin{pmatrix} A\\ B\end{pmatrix}$.
 
@@
 \STATE {//Initialization}
-\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma$}
 \STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
-\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I$}
-\STATE{}
+\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
+\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
+%\STATE{}
 
@@
 \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
-\STATE{}
+%\STATE{}
 
@@
 \STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
-\STATE {}
+%\STATE {}
 
@@
 \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
-\STATE {}
+%\STATE {}
 

### 2015-12-04 contextual combinatorial cascading bandits.tex

@@
 
-The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
 Similarly, we could also consider the case of conjunctive objective.
@@
 Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. 
-%In the following, we will mainly use notations for disjunctive objective when the two cases are similar.
+In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
 
@@
 Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. 
-First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$.
-Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$.
-Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where
+First, the learning agent 
+	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
+Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
+Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
 $$
@@
 $$
-\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
+\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
 $$
-Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
-In this part, we use the notation $[A; B]$ to denote the matrix obtained by stack A and B vertically like
+Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
+In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
  $\begin{pmatrix} A\\ B\end{pmatrix}$.
@@
 \STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
-\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
-\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)]$}
+\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
+\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}

### 2015-12-04 contextual combinatorial cascading bandits.tex
reorganize main theorem

@@
 \begin{equation}
+\label{eq:defU}
 \bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
@@
 \STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
+\STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
 \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
@@
 
+To state our main theorem, we need some definitions. Let
+$$
+f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
+$$
+denote the best expected reward in all time under the conjunctive objective and let $p_{t, \bA_t}$ (resp., $p_{\wedge, t, \bA_t}$) are probabilities that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under disjunctive objective(resp., conjunctive), that is
+\begin{align*}
+&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
+&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
+\end{align*}
+We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under disjunctive case.
 Here is our main theorem.
@@
 \label{thm:main}
-Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$.
+Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
+$$
+\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}.
+$$
 Let regularization parameter satisfy $\lambda \geq C_\gamma$.
 Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
-\begin{align}
-&R(T) = O(\frac{d}{p^*} \log(C_\gamma T) \sqrt{KT}),\\
-&R_{\wedge}(T) = O(\frac{d}{f_{\wedge}^{\ast}} \log(C_\gamma T) \sqrt{KT}).
-\end{align}
+\begin{equation}
+\begin{split}
+&R(T) = \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
+&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)},
+\end{split}
+\end{equation}
+\begin{equation}
+\begin{split}
+&R_{\wedge}(T) = \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)}.
+\end{split}
+\end{equation}
 where
 \begin{align*}
-&f^* = \min_{1 \leq t \leq T} f_t^{\ast},\\
-&f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},\\
-&C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K-1} (1 - \gamma_k')^2 = O(K),
-\end{align*}
-and $p_{t, \bA_t}$ and $p_{\wedge, t, \bA_t}$ are probabilities that all base arms of $\bA_t$ have been observed
-\begin{align*}
-&p_{t, \bA_t} = \PP(\bO_t \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (1 - \theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
-&p_{\wedge, t, \bA_t} = \PP(\bO_{\wedge, t} \geq \abs{\bA_t}) = \prod_{k=1}^{\abs{\bA_t}-1} (\theta_{\ast}^{\top} x_{t, \ba_k^t}),\\
-&p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}.
+C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
 \end{align*}
@@
 
-To prove theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+To prove Theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
 \begin{lemma}
@@
 
-\begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
-By lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by lemma \ref{lem:increasing},
+\begin{proof}[ of Lemma \ref{lem:DeltaEstimate}]
+By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
 $$
@@
 $$
-By lemma \ref{lem:estimateTech} and the definition of $\bU_t$ (\ref{eq:defU}),
+By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ \eqref{eq:defU},
 $$
@@
 % $$
-Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with disjunctive objective and $k < \abs{A}$, we have the following properties:
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
 \begin{itemize}
@@
 \begin{lemma}
-Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the disjunctive objective, there exists a prefix $B$ of $A$ such that 
+Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
 $$
@@
 \begin{proof}
-If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by lemma \ref{lem:prefixRelation},
+If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
 $$
-p_{A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
+p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
 $$
@@
 $$
-Then by lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$.
+Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$.
 Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$.
@@
 \begin{proof}
-For the conjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
+For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
 % $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
 
-For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$.
+For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$.
 Then we have
@@
 $$
-by lemma \ref{lem:increasing} and
+by Lemma \ref{lem:increasing} and
 $$
@@
 $$
-by lemma \ref{lem:estimateTech}, we have
+by Lemma \ref{lem:estimateTech}, we have
 $$
@@
 
-\begin{proof}[ of theorem \ref{thm:main}]
+\begin{proof}[ of Theorem \ref{thm:main}]
 Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.
@@
 &\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
-&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
-&\leq O(\frac{d}{p^*} \log(C_\gamma T)\sqrt{TK}).
+&\leq \EE[\frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
+&\leq \EE[\frac{1}{p^*} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
+&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
+&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
 \end{split}
@@
 &\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
-&\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).
+&\leq \EE[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
+&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
 \end{split}

### 2015-12-04 agent.py
synthetic: sherry ties lijing for both conj/disj

@@ -13,6 +13,10 @@ import logging
 logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.INFO)
 logger = logging.getLogger('Agent')
 
+from environment import contextual_cascading_monkey as contextual_cascading_monkey_environment
+from environment import contextual_full_monkey as contextual_full_monkey_environment
+from environment import contextual_monkey_rng
+
 def movies_mix_cld_adt(L=200):
     children, adults = set(), set()
     with open('movies.csv') as fp:
@@ -85,7 +89,10 @@ def contextual_cascading_monkey(e, s, T=10000):
         recc = random.sample(s.arms, s.K)
         r, _ = e(recc)
         score.append(score[-1] + r)
+    logger.info('Monkey play score {0}/{1}'.format(score[-1], T))
     return score, 0
+
+contextual_full_monkey = contextual_cascading_monkey
 
 def contextual_cascading_sherry(e, s, T=10000):
     delta = 0.9
@@ -97,26 +104,54 @@ def contextual_cascading_sherry(e, s, T=10000):
     X = np.zeros((1, s.d))
     Y = np.zeros(1)
     score = [0]
-    for i in range (1, T):
+    for t in range (1, T):
         x = e()
         U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in s.arms}
         recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
         r, c = e(recc)
         V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(s.K, c+1))])
         X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(s.K, c+1))])
-        Y = np.concatenate([Y] + [s.gamma ** k * (k == c) * np.ones(1) for k in range(min(s.K, c+1))])
+        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) ^ s.disj) * np.ones(1) for k in range(min(s.K, c+1))])
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.log(np.linalg.det(V))- ldV - 2 * np.log(delta)) + np.sqrt(lamb)
[…]

### 2015-12-04 environment.py

@@ -7,7 +7,7 @@ import random
 import logging
 logger = logging.getLogger('Environment')
 
-seed = int(time.time())
+seed = int(time.time() * 100) % 339
 np.random.seed(seed)
 logger.info('Numpy Random seed = {0}'.format(seed))
 
@@ -22,6 +22,12 @@ def red(s):
 def uni(x):
     return x/np.sqrt(x.dot(x))
 
+def reward(ctr, gamma, disj):
+    for c, click in enumerate(ctr):
+        if click ^ disj:
+            return int(disj) + gamma ** c * (int(not disj) - int(disj)), c
+    return int(disj), len(ctr)
+
 class ucb_settings:
     def __init__(self, **s):
         self.__dict__ = s
@@ -29,31 +35,41 @@ class ucb_settings:
     def __str__(self):
         return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
 
-def contextual_monkey_rng(L=20, d=10, v=0.35):
+def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
     arms = list(range(L))
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
-    theta = v * uni(np.random.uniform(0, 1, d))
-    return ucb_settings(arms=arms, x=x, theta=theta, d=d)
+    theta = h * uni(np.random.uniform(0, 1, d))
+    return ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, disj=disj)
 
-def contextual_cascading_monkey(s=contextual_monkey_rng(), K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
-    logger.info('Initializing environment "Monkey Contextual"')
+def contextual_cascading_monkey(s=contextual_monkey_rng()):
+    logger.info('Initializing environment "Contextual Cascading Monkey"')
     xt = {arm:s.x[arm] for arm in s.x}
     def environment(recommend=None):
         if recommend == None:
             for arm in xt:
-                xt[arm] = uni(s.x[arm] + np.random.uniform(-v, v, s.d))
+                xt[arm] = uni(s.x[arm] + np.random.uniform(-s.v, s.v, s.d))
             return xt
         else:
-            assert(len(recommend) <= K)
-            #print(sorted([s.theta.dot(xt[arm]) for arm in s.arms])[::-1])
[…]

### 2015-12-04 agent.py
synthetic sherry beats absolute; synthetic complete

@@ -82,7 +82,7 @@ def monkey(candidates, K=8, T=150000, verbose=False):
                     print('Agent: Score={0}/{1}'.format(score, t))
     return agent
 
-def contextual_cascading_monkey(e, s, T=10000):
+def contextual_cascading_monkey(e, s, T):
     score = [0]
     for t in range(1, T):
         _ = e()
@@ -94,7 +94,23 @@ def contextual_cascading_monkey(e, s, T=10000):
 
 contextual_full_monkey = contextual_cascading_monkey
 
-def contextual_cascading_sherry(e, s, T=10000):
+def absolute_cascading_ucb(e, s, T):
+    score = [0]
+    W = {arm:0.5 for arm in s.arms}
+    b = {arm:1 for arm in s.arms}
+    for t in range(1, T):
+        _ = e()
+        U = {arm:W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
+        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
+        r, c = e(recc)
+        for k in range(min(s.K, c+1)):
+            W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + ((k == c) ^ s.disj)) / (b[recc[k]] + 1)
+            b[recc[k]] += 1
+        score.append(score[-1] + r)
+    logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
+    return score, 0
+
+def contextual_cascading_sherry(e, s, T):
     delta = 0.9
     lamb = 0.1
     theta = np.zeros(s.d)
@@ -119,7 +135,7 @@ def contextual_cascading_sherry(e, s, T=10000):
     logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
     return score, 1 - cosine(s.theta, theta)
 
-def contextual_full_lijing(e, s, T=10000):
+def contextual_full_lijing(e, s, T):
     delta = 0.9
     lamb = 0.1
     theta = np.zeros(s.d)
@@ -148,8 +164,9 @@ def flowtest():
     exploit2, explore2 = contextual_cascading_monkey(*contextual_cascading_monkey_environment(s), T=T)
     exploit3, explore3 = contextual_full_monkey(*contextual_full_monkey_environment(s), T=T)
     exploit4, explore4 = contextual_full_lijing(*contextual_full_monkey_environment(s), T=T)
[…]

### 2015-12-04 context.py
movielens draft

@@ -1,65 +1,0 @@
-import csv
-import time
-import random
-from itertools import chain
-
-import logging
-logger = logging.getLogger('Contextual')
-
-from scipy import sparse
-from scipy.sparse.linalg import svds
-import numpy as np
-
-def movielens_load():
-    fpr = open('ratings.csv')
-    fpt = open('tags.csv')
-    gr = csv.reader(fpr, delimiter=',', quotechar='"')
-    gt = csv.reader(fpt, delimiter=',', quotechar='"')
-    gr.__next__()
-    gt.__next__()
-    return chain(gr, gt)
-
-portion = 0.5
-d = 30
-gamma = 0.95
-cox = []
-coy = []
-records = {}
-for idx, (user, movie, rate, timestamp) in enumerate(movielens_load()):
-    user = int(user) - 1
-    movie = int(movie) - 1
-    if random.uniform(0,1) < portion:
-        cox.append(user)
-        coy.append(movie)
-    else:
-        if user in records:
-            records[user].append(movie)
-        else:
-            records[user] = [movie]
-
-cox = np.array(cox)
-coy = np.array(coy)
-A = sparse.coo_matrix((np.ones(cox.shape), (cox, coy)), shape=(cox.max() + 1, coy.max() + 1), dtype=np.float32)
-U, S, VT = svds(A, d)
-for i in range(U.shape[0]):
-    U[i] = U[i] / np.linalg.norm(U[i])
-
-eligable_users = set(records.keys())
-logger.info('#Total eligabli users = {0}'.format(len(eligable_users)))
-logger.info('#Users participated ea/round = {0}'.format(1))
-user = [random.sample(eligable_users, 1)[0]]
-def environment(*arg):
-    if len(arg) == 0:
-        user[0] = random.sample(eligable_users, 1)[0]
-        logger.debug('Random user {0}'.format(user))
-        return U[user[0]]
-    else:
-        recommend = arg[0]
-        movies = records[user[0]]
-        logger.debug('Received recommendation {0}'.format(recommend))
-        logger.debug('User ctr history {0}'.format(movies))
-        for idx, movie in enumerate(recommend):
-            if movie in movies:
-                return idx, gamma ** idx
-        return float('Inf'), 0
-logger.info('Initializing environment "Movielens" done')

### 2015-12-04 environment.py

@@ -16,6 +16,8 @@ from functools import reduce
 import colorama
 colorama.init()
 
+from movielens import contextual_movielens_rng
+
 def red(s):
     return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
 
@@ -71,7 +73,10 @@ def contextual_full_monkey(s=contextual_monkey_rng()):
     logger.info('Initializing environment "Contextual Full Monkey" complete')
     return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d, gamma=s.gamma, theta=s.theta)
 
-def movielens(candidates, userno=1):
+def contextual_cascading_movielens(s=contextual_movielens_rng()):
+    pass
+
+def movielens_dep(candidates, userno=1):
     logger.info('Initializing environment "Movielens"')
     records = {}
     with open('ratings.csv') as fp:

### 2015-12-04 movielens.py

@@ -1,0 +1,72 @@
+import csv
+import time
+import random
+from itertools import chain
+
+import logging
+
+import numpy as np
+from scipy import sparse
+from scipy.sparse.linalg import svds
+
+def movielens_data():
+    fpr = open('ratings.csv')
+    fpt = open('tags.csv')
+    gr = csv.reader(fpr, delimiter=',', quotechar='"')
+    gt = csv.reader(fpt, delimiter=',', quotechar='"')
+    gr.__next__()
+    gt.__next__()
+    return chain(gr, gt)
+
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, gamma=0.95, disj=False):
+    cox = []
+    coy = []
+    history = {}
+    movies = {}
+    for idx, (user, movie, rate, timestamp) in enumerate(movielens_load()):
+        user = int(user) - 1
+        movie = int(movie) - 1
+        if movie in movies
+            movies[movie] += 1
+        else:
+            movies[movie] = 1
+        if random.uniform(0,1) < portion:
+            cox.append(user)
+            coy.append(movie)
+        else:
+            if user in history:
+                history[user].append(movie)
+            else:
+                history[user] = [movie]
+    cox = np.array(cox)
+    coy = np.array(coy)
+    A = sparse.coo_matrix((np.ones(cox.shape), (cox, coy)), shape=(cox.max() + 1, coy.max() + 1), dtype=np.float32)
+    U, S, VT = svds(A, d)
+    for i in range(U.shape[0]):
+        U[i] = U[i] / np.linalg.norm(U[i])
+    V = VT.T
+    for i in range(V.shape[0]):
+        V[i] = V[i] / np.linalg.norm(V[i])
+    
+    if L is None:
+        L = len(movies)
+    selected_movies = [x[1] for x in sorted[(movies[movie], movie) for movie in movies][-L:]]
+    eligable_users = set(history.keys())
+print('#Total eligabli users = {0}'.format(len(eligable_users)))
+print('#Users participated ea/round = {0}'.format(1))
+user = random.sample(eligable_users, 1)
+def environment(*arg):
+    if len(arg) == 0:
+        user[0] = random.sample(eligable_users, 1)[0]
+        logger.debug('Random user {0}'.format(user))
+        return U[user[0]]
+    else:
+        recommend = arg[0]
+        movies = history[user[0]]
+        logger.debug('Received recommendation {0}'.format(recommend))
+        logger.debug('User ctr history {0}'.format(movies))
[…]

### 2015-12-05 contextual combinatorial cascading bandits.tex

@@
 
-Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. 
+Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
 First, the learning agent 
@@
 \begin{algorithm}
-\caption{ConComCascade}
+\caption{C$^3$-UCB}
 \label{alg:ConComCascade}
@@
 $$
-denote the best expected reward in all time under the conjunctive objective and let $p_{t, \bA_t}$ (resp., $p_{\wedge, t, \bA_t}$) are probabilities that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under disjunctive objective(resp., conjunctive), that is
+denote the best expected reward of all time under the conjunctive objective.
+Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
 \begin{align*}
@@
 \end{align*}
-We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under disjunctive case.
-Here is our main theorem.
+We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under the 
+disjunctive objective. The following is the main theorem on the regret achieved by
+	our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
 \begin{theorem}
@@
 Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
-$$
-\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}.
-$$
-Let regularization parameter satisfy $\lambda \geq C_\gamma$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
+$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
+Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$,
+	where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
 \begin{equation}
 \begin{split}
-&R(T) = \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
-&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)},
+&R(T) \le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \\
+&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right),
 \end{split}
@@
 \begin{split}
-&R_{\wedge}(T) = \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
-&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)}.
+&R_{\wedge}(T) \le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \\
+&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right).
 \end{split}
 \end{equation}
-where
-\begin{align*}
-C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
-\end{align*}
+%where
+%\begin{align*}
+%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
+%\end{align*}
 \end{theorem}

### 2015-12-05 contextual combinatorial cascading bandits.tex
add big O bound

@@
 \label{eq:defU}
-\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
+\bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
 \end{equation}
@@
 \end{align*}
-We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under the 
+We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time 
+	that an action could have all base arms observed under the 
 disjunctive objective. The following is the main theorem on the regret achieved by
@@
 Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
-\begin{equation}
-\begin{split}
-&R(T) \le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \\
-&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right),
-\end{split}
-\end{equation}
-\begin{equation}
-\begin{split}
-&R_{\wedge}(T) \le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \\
-&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right).
-\end{split}
-\end{equation}
+\begin{align}
+R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \nonumber \\
+&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&=O\left(\frac{d}{p^*} \sqrt{TK} \log T\right),
+\end{align}
+\begin{align}
+R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \nonumber \\
+&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \log T\right).
+\end{align}
 %where
@@
 
+\wei{Is the $\log$ in the above theorem with base $2$? 
+	Other UCB regret bounds usually has $\ln$. Please double check if here
+	indeed we use $\log$ of base 2. }
 To prove Theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+\wei{I did not see $\Delta_{t,\bA_t}$ defined before.}
 \begin{lemma}
@@
 $$
-\gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast},
+\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast},
 $$

### 2015-12-05 contextual combinatorial cascading bandits.tex
log ->ln, \Delta->R

@@
 $$
-\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
+\beta_{t}(\delta) = \sqrt{\ln(\frac{\det(\bV_{t})}{\det(\lambda I)}) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
 $$
@@
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}
+\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})) + 2 \ln(\frac{1}{\delta})} + \sqrt{\lambda}$}
 
@@
 \end{align*}
-We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time 
-	that an action could have all base arms observed under the 
-disjunctive objective. The following is the main theorem on the regret achieved by
-	our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
+We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective.
+The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
 \begin{theorem}
@@
 $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
-Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$,
-	where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
+Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$.
 Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
 \begin{align}
-R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \nonumber \\
-&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{p^*} \sqrt{TK} \log T\right),
+R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
+&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
 \end{align}
 \begin{align}
-R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \nonumber \\
-&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \log T\right).
+R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
+&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
 \end{align}
@@
 	indeed we use $\log$ of base 2. }
-To prove Theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+\shuai{The all $\log$'s have base e. I have changed them to be $\ln$.}
+To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
 \wei{I did not see $\Delta_{t,\bA_t}$ defined before.}
+\shuai{Sorry. It should be $R(t, \bA_t)$ here. I have revised them all.}
 \begin{lemma}
@@
 $$
-\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
+R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
 $$
@@
 $$
-\Delta_{\wedge, t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
-Then we can derive an estimate of $\Delta_{t, \bA_t}$ and $\Delta_{\wedge, t, \bA_t}$, however, in terms of all base arms in $\bA_t$.
+Then we can derive an estimate of $R(t, \bA_t)$ and $R_{\wedge}(t, \bA_t)$, however, in terms of all base arms in $\bA_t$.
 Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
 \begin{align*}
-&~~\EE_t[\Delta_{t, \bA_t}] \\
-&= \EE_t[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
-&~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
-&= \EE_t[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
+&~~\EE_t[R(t, \bA_t)] \\
+&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
+&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
+&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
 \end{align*}
@@
 $$
-p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad \Delta_{\wedge, t, \bB_t} \geq \frac{1}{2} \Delta_{\wedge, t, \bA_t}.
+p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
 $$
 \end{lemma}
-From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $\Delta_{\wedge, t, \bB_t}$ will not be too small.
-Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
+From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small.
+Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
 We leave all details in the next subsection.
@@
 $$
-\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
-p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
+p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
 $$ 
@@
 $$
-E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
+E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
 $$
@@
 % &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
-&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
+&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
 \end{align*}
@@
 
-For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$.
+For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
 Then we have
 $$
-\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
+\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}
 $$
@@
 $$
-\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
@@
 $$
-\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\det(\bV_t)).
+\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)}).
 $$
@@
 $$
-Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$, we get
+Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
 \begin{align*}
 &\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
-&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I))) < 2\log(\det(\bV_t))
+&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
+&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
 \end{align*}
@@
 \begin{split}
-&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
+&R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
 &\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
 &\leq \EE[\frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
-&\leq \EE[\frac{1}{p^*} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
-&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
-&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
-&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
+&\leq \EE[\frac{1}{p^*} (\sqrt{\ln(\frac{\det(\bV_t)}{\det(\lambda I)}) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda}) \\
+&\qquad \qquad \cdot \sqrt{TK \cdot 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)})} ]\\
+&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
 \end{split}
@@
 \begin{split}
-&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
+&R(T) =\sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \\
 &\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
@@
 &\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
-&\leq \EE[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{\log(\det(\bV_t)) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
-&\qquad \qquad \cdot \sqrt{TK \cdot 2\log(\det(\bV_t))} ]\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
-&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)} ]
+&\leq \EE[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{\ln(\frac{\det(\bV_t)}{\det(\lambda I)}) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda}) \\
+&\qquad \qquad \cdot \sqrt{TK \cdot 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)})} ]\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
 \end{split}

### 2015-12-06 contextual combinatorial cascading bandits.tex

@@
 $$
-\beta_{t}(\delta) = \sqrt{\ln(\frac{\det(\bV_{t})}{\det(\lambda I)}) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
+\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
+$$
+\wei{I thought the following is simpler. Should we use the following?}
+$$
+\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
 $$
@@
 
-\wei{Is the $\log$ in the above theorem with base $2$? 
-	Other UCB regret bounds usually has $\ln$. Please double check if here
-	indeed we use $\log$ of base 2. }
-\shuai{The all $\log$'s have base e. I have changed them to be $\ln$.}
-To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
-\wei{I did not see $\Delta_{t,\bA_t}$ defined before.}
-\shuai{Sorry. It should be $R(t, \bA_t)$ here. I have revised them all.}
+To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
 \begin{lemma}

### 2015-12-06 contextual combinatorial cascading bandits.tex

@@
 We also refer to each of such tuples as an {\em action}.
-Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$. 
+Let $\prod^{\leq K}= \cup_{k=1}^K \prod^{k}$ denote set of all actions with length
+	at most $K$, and let $\cS \subseteq \prod^{\leq K}$ be the set of feasible actions with length no more than $K$.
+
 As a convention, we always use boldface symbols to represent random variables.
@@
 Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
-\begin{align*}
-&f : \cS \times [0,1]^E \to [0,1]\\
+\begin{align}
+&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
 &f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
-\end{align*}
+	\label{eq:functionf}
+\end{align}
 Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
@@
 If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
-\begin{align*}
-&f_{\wedge} : \cS \times [0,1]^E \to [0,1]\\
-&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' (\prod_{i = 1}^{k - 1} w(a_i))(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
-\end{align*}
+\begin{align}
+&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
+&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
+ (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+ \label{eq:functionfstar}
+\end{align}
 then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
@@
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})) + 2 \ln(\frac{1}{\delta})} + \sqrt{\lambda}$}
-
+\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})) + 2 \ln(\frac{1}{\delta})} + \sqrt{\lambda}$ \wei{This $\beta$ is different from what is defined in Theorem 4.1.}}
 \ENDFOR {~~$t$}
@@
 
+\wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
+	they should all be moved to Section 4.3}
+
 To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
@@
 Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
+
+\wei{I do not understand the above paragraph and the formula below.}
 \begin{align*}
@@
 
+We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined
+in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
 \begin{lemma}
@@
 Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$.
-Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; equivalently, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}(E)$, it holds that
+Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
 $$
@@
 \begin{proof}
-It suffices to prove when $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
+Without the loss of generality, we prove for the case
+	of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. 
+First, for $1 \leq k \leq m$, we have
 \begin{align*}
@@
 \end{align*}
-then
+Then it implies that
 \begin{align*}
@@
 \end{align*}
-By letting $\gamma_k = 1 - \gamma_k'$ and the relation (\ref{eq:ConDisRelation}), the increasing property of $f_{\wedge}$ is obtained directly.
+By letting $\gamma_k = 1 - \gamma_k'$ and using the relation
+	in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
 \end{proof}
 
+The following lemma provides the relationship between an estimated mean vector and its
+	upper bound, in terms of their $f$ function values.
+\wei{The symbol here may need to be changed. $w_i$ coincides with weight $w_i$ before, 
+		and $p$ coincides with many related probability definition using $p$.
+	$w_i$ can be replaced with $u_i$ (standing for upper bound), 
+	$u_i$ can be replaced with $r_i$ (standing for radius), but not sure yet
+	about $p_i$.}
 \begin{lemma}

### 2015-12-06 contextual combinatorial cascading bandits.tex
add comment

@@
 	they should all be moved to Section 4.3}
+\shuai{I think Section 4.3 will probably be put in the appendix. So I sketch a proof of main theorem here. If all the proofs will be kept, then we don't need Lemma 4.4 and 4.5 here.}
 
@@
 \wei{I do not understand the above paragraph and the formula below.}
+\shuai{If we choose action of $\bA_t$ instead of $A_t^{\ast}$, then we can know the differece between their expected reward.
+But the regret is bounded by all base arms in $\bA_t$.
+Only the observed base arms can be estimated together.
+So we can only estimate the following formula.
+I rewrite the following formula and can explain to you later.}
 \begin{align*}
 &~~\EE_t[R(t, \bA_t)] \\
+&= \EE[R(t, \bA_t) \bOne\{R(t, \bA_t) > 0\} \EE[(1/p_{t, \bA_t}) \bOne\{\bO_t \geq \abs{\bA_t}\}|\bA_t] | \cH_t]\\
 &= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
@@
 	about $p_i$.}
+\shuai{Maybe we can replace $p_i$ by $w_i$ like the lemma above. I have changed accordingly.}
 \begin{lemma}
 \label{lem:estimateTech}
-Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq p_1, \ldots, p_m \leq 1$, $u_1, \ldots, u_m \geq 0$ and $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
+Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
 \begin{align*}
-&f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
-&f_{\wedge}(A^{(m)}, w) \leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} (1 - \gamma_k') u_k,
+&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
+&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
 \end{align*}
-where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
+where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
 \end{lemma}
@@
 \begin{align*}
-&~~f(A^{(m+1)}, w)\\
-&= f(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
-&\leq f(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})\\
-&\leq f(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k \\
-&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - p_k) p_{m+1} + \gamma_{m+1} u_{m+1}\\
-&= f(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
+&~~f(A^{(m+1)}, u)\\
+&= f(A^{(m)}, u) + \gamma_{m+1}\prod_{k=1}^m(1 - u_k) u_{m+1}\\
+&\leq f(A^{(m)}, u) +  \gamma_{m+1} \prod_{k=1}^m(1 - w_k) (w_{m+1} + r_{m+1})\\
+&\leq f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k r_k \\
+&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w_k) w_{m+1} + \gamma_{m+1} r_{m+1}\\
+&= f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k r_k
 \end{align*}
 \begin{align*}
-&~~f_{\wedge}(A^{(m+1)}, w) \\
-&= f_{\wedge}(A^{(m)}, w) -\prod_{k=1}^{m} w_k \\
-&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
-&= f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} (1 - \gamma_k') u_k \\
-&\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
-&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} (1 - \gamma_k') u_k
+&~~f_{\wedge}(A^{(m+1)}, u) \\
+&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
+&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} u_k) (1 - u_{K+1})+ \prod_{k=1}^{K+1} u_k\\
+&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
+&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
+&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
 \end{align*}

### 2015-12-06 agent.py
add context movielens to evnironment; reworked project arch; next to test ucb/sherry/lijing/monkey on movielens; doc outdated, update soon;

@@ -1,21 +1,11 @@
-import math
-import csv
 import heapq
-
 import numpy as np
 from scipy.spatial.distance import cosine
 import matplotlib.pyplot as plt
 
-import time
 import random
-
 import logging
-logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.INFO)
 logger = logging.getLogger('Agent')
-
-from environment import contextual_cascading_monkey as contextual_cascading_monkey_environment
-from environment import contextual_full_monkey as contextual_full_monkey_environment
-from environment import contextual_monkey_rng
 
 def movies_mix_cld_adt(L=200):
     children, adults = set(), set()
@@ -131,6 +121,7 @@ def contextual_cascading_sherry(e, s, T):
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.log(np.linalg.det(V))- ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
+        logger.info('Sherry play score {0}/{1}'.format(score[-1], t))
     logger.info('Sherry play score {0}/{1}'.format(score[-1], T))
     logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
     return score, 1 - cosine(s.theta, theta)
@@ -156,19 +147,3 @@ def contextual_full_lijing(e, s, T):
     logger.info('Lijing play score {0}/{1}'.format(score[-1], T))
     logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
     return score, 1 - cosine(s.theta, theta)
-
-def flowtest():
-    T = 10000
-    s = contextual_monkey_rng(L=20, d=10, h=0.75, K=4, gamma=0.95, eps=0.1, v=0.35, disj=True)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_cascading_monkey_environment(s), T=T)
-    exploit2, explore2 = contextual_cascading_monkey(*contextual_cascading_monkey_environment(s), T=T)
-    exploit3, explore3 = contextual_full_monkey(*contextual_full_monkey_environment(s), T=T)
-    exploit4, explore4 = contextual_full_lijing(*contextual_full_monkey_environment(s), T=T)
[…]

### 2015-12-06 environment.py

@@ -1,49 +1,24 @@
-import sys
-import csv
 import numpy as np
-import matplotlib.pyplot as plt
-import time
 import random
 import logging
 logger = logging.getLogger('Environment')
 
-seed = int(time.time() * 100) % 339
-np.random.seed(seed)
-logger.info('Numpy Random seed = {0}'.format(seed))
-
 from functools import reduce
 
-import colorama
-colorama.init()
-
+from utils import red
+from utils import uni
+from utils import reward
+from utils import ucb_settings
 from movielens import contextual_movielens_rng
-
-def red(s):
-    return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
-
-def uni(x):
-    return x/np.sqrt(x.dot(x))
-
-def reward(ctr, gamma, disj):
-    for c, click in enumerate(ctr):
-        if click ^ disj:
-            return int(disj) + gamma ** c * (int(not disj) - int(disj)), c
-    return int(disj), len(ctr)
-
-class ucb_settings:
-    def __init__(self, **s):
-        self.__dict__ = s
-        
-    def __str__(self):
-        return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
 
 def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
     arms = list(range(L))
     x = {arm:np.random.uniform(0, 1, d) for arm in arms}
     theta = h * uni(np.random.uniform(0, 1, d))
+    logger.info('Initializing random settings "Contextual Monkey" complete')
     return ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, disj=disj)
 
-def contextual_cascading_monkey(s=contextual_monkey_rng()):
+def contextual_cascading_monkey(s):
     logger.info('Initializing environment "Contextual Cascading Monkey"')
     xt = {arm:s.x[arm] for arm in s.x}
     def environment(recommend=None):
@@ -58,7 +33,7 @@ def contextual_cascading_monkey(s=contextual_monkey_rng()):
     logger.info('Initializing environment "Contextual Cascading Monkey" complete')
     return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d, gamma=s.gamma, theta=s.theta, disj=s.disj)
 
-def contextual_full_monkey(s=contextual_monkey_rng()):
+def contextual_full_monkey(s):
[…]

### 2015-12-06 main.py

@@ -1,0 +1,49 @@
+import logging
+logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.INFO)
+logger = logging.getLogger('Main')
+
+import time
+seed = int(time.time() * 100) % 339
+import numpy as np
+np.random.seed(seed)
+import random
+random.seed(seed)
+logger.info('Numpy/Python random seed = {0}'.format(seed))
+
+import matplotlib.pyplot as plt
+
+from agent import contextual_cascading_sherry
+from agent import contextual_cascading_monkey
+from agent import contextual_full_monkey
+from agent import contextual_full_lijing
+from agent import absolute_cascading_ucb
+from environment import contextual_monkey_rng
+from environment import contextual_cascading_monkey as contextual_cascading_monkey_environment
+from environment import contextual_full_monkey as contextual_full_monkey_environment
+from movielens import contextual_movielens_rng
+from environment import contextual_cascading_movielens
+
+def flowtest_monkey_disj():
+    T = 10000
+    s = contextual_monkey_rng(L=20, d=10, h=0.75, K=4, gamma=0.95, eps=0.1, v=0.35, disj=True)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_cascading_monkey_environment(s), T=T)
+    exploit2, explore2 = contextual_cascading_monkey(*contextual_cascading_monkey_environment(s), T=T)
+    exploit3, explore3 = contextual_full_monkey(*contextual_full_monkey_environment(s), T=T)
+    exploit4, explore4 = contextual_full_lijing(*contextual_full_monkey_environment(s), T=T)
+    exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_monkey_environment(s), T=T)
+    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
+
+def flowtest_monkey_conj():
+    T = 10000
+    s = contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_cascading_monkey_environment(s), T=T)
+    exploit2, explore2 = contextual_cascading_monkey(*contextual_cascading_monkey_environment(s), T=T)
[…]

### 2015-12-06 movielens.py

@@ -1,13 +1,16 @@
 import csv
-import time
 import random
 from itertools import chain
 
 import logging
+logger = logging.getLogger('Movielens')
 
 import numpy as np
 from scipy import sparse
 from scipy.sparse.linalg import svds
+
+from utils import ucb_settings
+from utils import overlap
 
 def movielens_data():
     fpr = open('ratings.csv')
@@ -18,19 +21,19 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, gamma=0.95, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=13500, gamma=0.95, disj=False):
     cox = []
     coy = []
     history = {}
     movies = {}
-    for idx, (user, movie, rate, timestamp) in enumerate(movielens_load()):
+    for idx, (user, movie, rate, timestamp) in enumerate(movielens_data()):
         user = int(user) - 1
         movie = int(movie) - 1
-        if movie in movies
+        if movie in movies:
             movies[movie] += 1
         else:
             movies[movie] = 1
-        if random.uniform(0,1) < portion:
+        if np.random.uniform(0,1) < portion:
             cox.append(user)
             coy.append(movie)
         else:
@@ -47,26 +50,10 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, gamma=0.95, disj=Fa
     V = VT.T
     for i in range(V.shape[0]):
         V[i] = V[i] / np.linalg.norm(V[i])
-    
+
     if L is None:
         L = len(movies)
-    selected_movies = [x[1] for x in sorted[(movies[movie], movie) for movie in movies][-L:]]
-    eligable_users = set(history.keys())
-print('#Total eligabli users = {0}'.format(len(eligable_users)))
-print('#Users participated ea/round = {0}'.format(1))
-user = random.sample(eligable_users, 1)
-def environment(*arg):
-    if len(arg) == 0:
-        user[0] = random.sample(eligable_users, 1)[0]
-        logger.debug('Random user {0}'.format(user))
-        return U[user[0]]
-    else:
-        recommend = arg[0]
-        movies = history[user[0]]
-        logger.debug('Received recommendation {0}'.format(recommend))
-        logger.debug('User ctr history {0}'.format(movies))
-        for idx, movie in enumerate(recommend):
-            if movie in movies:
[…]

### 2015-12-06 utils.py

@@ -1,0 +1,25 @@
+import numpy as np
+import colorama
+colorama.init()
+
+def red(s):
+    return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
+
+def uni(x):
+    return x/np.sqrt(x.dot(x))
+
+def reward(ctr, gamma, disj):
+    for c, click in enumerate(ctr):
+        if click ^ disj:
+            return int(disj) + gamma ** c * (int(not disj) - int(disj)), c
+    return int(disj), len(ctr)
+
+def overlap(l1, l2):
+    return len(set(l1) & l2)
+
+class ucb_settings:
+    def __init__(self, **s):
+        self.__dict__ = s
+        
+    def __str__(self):
+        return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])

### 2015-12-07 contextual combinatorial cascading bandits.tex

@@
 $$
-Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. 
+Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. 
+For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any
+	vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on
+	$V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
 In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
@@
 Let 
-$$
-\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
-$$
-\wei{I thought the following is simpler. Should we use the following?}
+%$$
+%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
+%$$
+%\wei{I thought the following is simpler. Should we use the following?}
 $$
@@
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})) + 2 \ln(\frac{1}{\delta})} + \sqrt{\lambda}$ \wei{This $\beta$ is different from what is defined in Theorem 4.1.}}
+\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
 \ENDFOR {~~$t$}
@@
 
-\subsection{Proofs}
+\subsection{Proof of Theorem~\ref{thm:main}}
 
@@
 
-The following lemma provides the relationship between an estimated mean vector and its
-	upper bound, in terms of their $f$ function values.
-\wei{The symbol here may need to be changed. $w_i$ coincides with weight $w_i$ before, 
-		and $p$ coincides with many related probability definition using $p$.
-	$w_i$ can be replaced with $u_i$ (standing for upper bound), 
-	$u_i$ can be replaced with $r_i$ (standing for radius), but not sure yet
-	about $p_i$.}
-\shuai{Maybe we can replace $p_i$ by $w_i$ like the lemma above. I have changed accordingly.}
+The following lemma provides the relationship between an estimated mean vector $w$
+	and its upper bound vector $u$, in terms of their $f$ function values.
 \begin{lemma}
@@
 &= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
-&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} u_k) (1 - u_{K+1})+ \prod_{k=1}^{K+1} u_k\\
+&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{m} u_k) (1 - u_{m+1})+ \prod_{k=1}^{m+1} u_k\\
 &= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
@@
 
-\begin{proof}[ of Lemma \ref{lem:DeltaEstimate}]
+The following lemma provides the important result on the regret at each time $t$
+	in terms of feature vectors of base arms in the round.
+\begin{lemma}
+	\label{lem:DeltaEstimate}
+	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
+	$$
+	R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
+	$$
+	if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
+	$$
+	R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+	$$
+\end{lemma}
+\begin{proof}
 By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},

### 2015-12-07 agent.py
sherry beats monkey; bug fixes;

@@ -121,10 +121,13 @@ def contextual_cascading_sherry(e, s, T):
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.log(np.linalg.det(V))- ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
-        logger.info('Sherry play score {0}/{1}'.format(score[-1], t))
+        #logger.info('Sherry play score {0}/{1}'.format(score[-1], t))
     logger.info('Sherry play score {0}/{1}'.format(score[-1], T))
-    logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
-    return score, 1 - cosine(s.theta, theta)
+    if 'theta' in s.__dict__:
+        logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
+        return score, 1 - cosine(s.theta, theta)
+    else:
+        return score, 0
 
 def contextual_full_lijing(e, s, T):
     delta = 0.9
@@ -145,5 +148,8 @@ def contextual_full_lijing(e, s, T):
         beta = np.sqrt(s.d * np.log((1 + t*s.L) / delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
     logger.info('Lijing play score {0}/{1}'.format(score[-1], T))
-    logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
-    return score, 1 - cosine(s.theta, theta)
+    if 'theta' in s.__dict__:
+        logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))
+        return score, 1 - cosine(s.theta, theta)
+    else:
+        return score, 0

### 2015-12-07 environment.py

@@ -49,7 +49,7 @@ def contextual_full_monkey(s):
     return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d, gamma=s.gamma, theta=s.theta)
 
 def contextual_cascading_movielens(s):
-    logger.info('Initializing environment "Movielens"')
+    logger.info('Initializing environment "Contextual Cascading Movielens"')
     user = random.sample(s.users, 1)
     def environment(recommend=None):
         if recommend is None:
@@ -61,7 +61,23 @@ def contextual_cascading_movielens(s):
             logger.debug('User ctr history {0}'.format(s.ctrh[user[0]]))
             r, c = reward(ctr, s.gamma, s.disj)
             return r, c
-    logger.info('Initializing environment "Movielens" done')
+    logger.info('Initializing environment "Contextual Cascading Movielens" done')
+    return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d ** 2, gamma=s.gamma, disj=s.disj)
+
+def contextual_full_movielens(s):
+    logger.info('Initializing environment "Contextual Full Movielens"')
+    user = random.sample(s.users, 1)
+    def environment(recommend=None):
+        if recommend is None:
+            user[0] = random.sample(s.users, 1)[0]
+            return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms}
+        else:
+            ctr = [arm in s.ctrh[user[0]] for arm in recommend]
+            logger.debug('Received recommendation {0}'.format(recommend))
+            logger.debug('User ctr history {0}'.format(s.ctrh[user[0]]))
+            r, _ = reward(ctr, s.gamma, s.disj)
+            return r, [int(click) for click in ctr]
+    logger.info('Initializing environment "Contextual Full Movielens" done')
     return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d ** 2, gamma=s.gamma, disj=s.disj)
 
 def movielens_dep(candidates, userno=1):

### 2015-12-07 main.py

@@ -21,7 +21,8 @@ from environment import contextual_monkey_rng
 from environment import contextual_cascading_monkey as contextual_cascading_monkey_environment
 from environment import contextual_full_monkey as contextual_full_monkey_environment
 from movielens import contextual_movielens_rng
-from environment import contextual_cascading_movielens
+from environment import contextual_cascading_movielens as contextual_cascading_movielens_environment
+from environment import contextual_full_movielens as contextual_full_movielens_environment
 
 def flowtest_monkey_disj():
     T = 10000
@@ -43,7 +44,14 @@ def flowtest_monkey_conj():
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_monkey_environment(s), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
 
-T = 10000
-s = contextual_movielens_rng(L=None, portion=0.5, d=15, K=8, h=13500, gamma=0.95, disj=False)
-exploit1, explore1 = contextual_cascading_monkey(*contextual_cascading_movielens(s), T=T)
-exploit2, explore2 = contextual_cascading_sherry(*contextual_cascading_movielens(s), T=T)
+def flowtest_movielens_conj():
+    T = 10000
+    s = contextual_movielens_rng(L=400, portion=0.2, d=5, K=8, h=None, gamma=0.95, disj=False)
+    exploit1, explore1 = contextual_cascading_monkey(*contextual_cascading_movielens_environment(s), T=T)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_cascading_movielens_environment(s), T=T)
+    exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)
+    exploit4, explore4 = contextual_full_lijing(*contextual_full_movielens_environment(s), T=T)
+    exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_movielens_environment(s), T=T)
+    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
+
+flowtest_movielens_conj()

### 2015-12-07 movielens.py

@@ -21,7 +21,7 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=13500, gamma=0.95, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, disj=False):
     cox = []
     coy = []
     history = {}
@@ -33,7 +33,7 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=13500, gamma=0.95
             movies[movie] += 1
         else:
             movies[movie] = 1
-        if np.random.uniform(0,1) < portion:
+        if np.random.uniform(0,1) > portion:
             cox.append(user)
             coy.append(movie)
         else:
@@ -53,6 +53,8 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=13500, gamma=0.95
 
     if L is None:
         L = len(movies)
+    if h is None:
+        h = len(history)
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')

### 2015-12-07 contextual combinatorial cascading bandits.tex

@@
 \newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}
+
+\newcommand{\hidetext}[1]{}
 
@@
 denote the best expected reward of all time under the conjunctive objective.
-Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
+Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
+	observation of $A$, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
 \begin{align*}
@@
 
+\wei{I hided some paragraphs trying to explain the proof here.
+	We will re-write a proof outline after revising the proofs.}
+\hidetext{
 \wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
@@
 
-\begin{lemma}
-\label{lem:prefixExist}
-Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
-$$
-p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
-$$
-\end{lemma}
+%\begin{lemma}
+%\label{lem:prefixExist}
+%Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
+%$$
+%p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
+%$$
+%\end{lemma}
 From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small.
@@
 We leave all details in the next subsection.
+}
 
@@
 The following lemma provides the important result on the regret at each time $t$
-	in terms of feature vectors of base arms in the round.
+	in terms of feature vectors of base arms at the time.
 \begin{lemma}
@@
 $$
-By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ \eqref{eq:defU},
+By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
 $$
@@
 $$
-Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
+By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
 $$
@@
 $$
-The result for the disjunctive case can be deduced similarly.
+The result for the conjunctive case can be deduced in a similar way.
 \end{proof}
 
+The next lemma provides some properties about a prefix of action $A$
+	in the conjunctive case, 
+	which leads to the finding of a prefix $B$ of $A$ with similar regret
+	and probability of full observation as those of $A$, as given
+	in Lemma~\ref{lem:prefixexists}.
 \begin{lemma}
@@
 Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
+\wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
+	I guess you are using $w$ vector to be the mean vectors for $A$. Please define
+	this clearly.}
 \begin{itemize}
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:prefixexists}
 Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
@@
 
-\begin{proposition}
+\begin{lemma}
 Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
@@
 where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
-\end{proposition}
+\end{lemma}
 \begin{proof}

### 2015-12-07 contextual combinatorial cascading bandits.tex
update symbols
update proof details

@@
 $$
-f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
+f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
 $$
@@
 Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
-	observation of $A$, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
+	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
 \begin{align*}
@@
 \geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-\geq &~\gamma_{k} \cdot 0 = 0,
+\geq &~\gamma_{k} \cdot 0 = 0.
 \end{align*}
@@
 &\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
-\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
+\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
 \end{align*}
@@
 % $$
-Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
 \wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
@@
 	this clearly.}
+\shuai{I have modified this part.}
+Suppose we have weights $w$.
+Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
+$$
+p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
+$$
+Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
 \begin{itemize}
@@
 $$
-p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
+p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
 $$ 
@@
 $$
-p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
+p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
 $$
@@
 $$
-f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}
+f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
 $$
@@
 $$
-E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
+E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ].
 $$
@@
 $$
-\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast},
+\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
 $$
@@
 % &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
-&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
+&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}].
 \end{align*}
-where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
 \end{lemma}
@@
 $$
-\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}
+\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}]
 $$
@@
 $$
+Therefore
+\begin{align*}
+\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
+&\leq \EE[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ]
+\end{align*}
 \end{proof}
@@
 $$
-\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)}).
+\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\lambda^d}).
 $$

### 2015-12-08 contextual combinatorial cascading bandits.tex

@@
 $$
-R(T) = \EE[\sum_{t=1}^T R(t, \bA_t)].
+R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
 $$
@@
 $$
-R_{\wedge}(T) = \EE[\sum_{t=1}^T R_{\wedge}(t, \bA_t)].
+R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
 $$
@@
 Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
-\wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
-	I guess you are using $w$ vector to be the mean vectors for $A$. Please define
-	this clearly.}
-\shuai{I have modified this part.}
-Suppose we have weights $w$.
+Suppose we have expected weights $w$ for the base arms of action $A$. 
 Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
@@
 \item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
-\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
+\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}$.
 \end{itemize}
@@
 % Then for the disjunctive objective,
+Let $m = |A|$.
+By the definition of $f_{\wedge}(A,w)$ in Eq.~\eqref{eq:functionfstar}, we have
 \begin{itemize}
@@
 \begin{align*}
-f_{\wedge}(A, w) &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
+	f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
+	(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
+ &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
 &\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
@@
 \begin{align*}
-f_{\wedge}(B_k, w) &\leq \gamma_{k}' (1 - p_{B_{k+1}}) + p_{B_{k+1}}\\
-&\leq \gamma_{k+1}' (1 - p_{B_{k+1}}) + p_{B_{k+1}} \\
-&= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}
+f_{\wedge}(B_k, w) & \leq \gamma_{k}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}}\\
+&\leq \gamma_{k+1}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}} \\
+&= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}
 \end{align*}
@@
 \begin{proof}
-If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
+Let $w= \theta_*^{\top} x_t$.
+If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
 $$
@@
 $$
+In this case, we set prefix $B = A$.
 
-Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
+Now suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
 $$
-x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
+x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, t,B_k}, ~~I_k = [x_k, y_k]
 $$
@@
 
+\wei{This lemma needs to be clarified, using Lemma 4.6.
+Also, our regret bound is expected regret but with a high probability? Sound a 
+bit strange.}
 \begin{lemma}
@@
 $$
-E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ].
+E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 $$
@@
 % &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
-&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}].
+&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
 \end{align*}
@@
 \begin{align*}
-\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq \EE[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ]
+\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+&\leq \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
 \end{align*}
@@
 \begin{proof}
-We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$ and
+We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$, 
+\wei{Why? need a citation?} and
 \begin{align*}
@@
 $$
-\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\lambda^d}).
+\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
 $$
@@
 &\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
-&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
+&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
 \end{align*}
@@
 
-For the conjunctive case,
+For the disjunctive case,
 \begin{equation}
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
-&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
-&\leq \EE[\frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
-&\leq \EE[\frac{1}{p^*} (\sqrt{\ln(\frac{\det(\bV_t)}{\det(\lambda I)}) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda}) \\
-&\qquad \qquad \cdot \sqrt{TK \cdot 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)})} ]\\
-&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
+&\leq \EE \left[\frac{1}{p^*} \beta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \EE \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]}
+	\right ]  \\
+&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
+& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)} \right]\\
+&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
 &\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
@@
 
-For the disjunctive case, 
+For the conjunctive case, 
 \begin{equation}
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \\
-&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
-&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
-&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
-&\leq \EE[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{\ln(\frac{\det(\bV_t)}{\det(\lambda I)}) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda}) \\
-&\qquad \qquad \cdot \sqrt{TK \cdot 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)})} ]\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda})\\
+&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
+&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_t)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
+&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)} \right]\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
 &\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]

### 2015-12-08 contextual combinatorial cascading bandits.tex
update Section 3

@@
 \usepackage{empheq}
-\usepackage{bm}
+\usepackage{bbm}
 \usepackage{algorithm,algorithmic}
@@
 
-We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set of $L$ ground items,  $E=\{1,...,L\}$, also referred to as {\em base arms}. 
-Let $\prod^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
-We also refer to each of such tuples as an {\em action}.
-Let $\prod^{\leq K}= \cup_{k=1}^K \prod^{k}$ denote set of all actions with length
-	at most $K$, and let $\cS \subseteq \prod^{\leq K}$ be the set of feasible actions with length no more than $K$.
+We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
+Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}.
+Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
+We call each of such tuples an {\em action} of length $k$.
+We will use $|A|$ to denote the length of an action $A$.
+Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length
+	at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
 
@@
 At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
-Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user.
-Starting from the first item, the user checks the items one by one.
-The checking process stops if the user clicks on one item or has checked all items without clicking anyone.
+\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to a user, where notice that the length of the action is not fixed.
+Starting from the first item $\ba_{1}^t$, the user checks the items $(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$ one by one in that order.
+The checking process stops if the user clicks \shengyu{selects?} on one item or has checked all items without clicking \shengyu{selecting?} anyone.
 We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$ to indicate whether the user has clicked on $a$ or not.

### 2015-12-09 contextual combinatorial cascading bandits.tex
update comments

@@
 \usepackage{empheq}
-\usepackage{bbm}
 \usepackage{algorithm,algorithmic}
@@
 bit strange.}
+\shuai{Yes, our regret bound is expected regret with a high probability. The reason is that NIPS'11 gives such a result.}
+
+Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$.
+However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms.
+So we need the following lemma.
 \begin{lemma}
-Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
+Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
+For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$.
+Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$.
+Then
 $$
@@
 \begin{proof}
-We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$, 
-\wei{Why? need a citation?} and
+Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
+$$
+\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \leq  (\frac{\lambda_1 + \ldots + \lambda_d}{d})^d = (\trace(\bV_t)/d)^d.
+$$
+\wei{Why? need a citation?} \shuai{I have rewritten this part.}
+Also,
 \begin{align*}

### 2015-12-09 contextual combinatorial cascading bandits.tex
update proofs of lemma 4.9 and main theorem

@@
 
+\newcommand{\bbeta}{\boldsymbol{\beta}}
 \newcommand{\EE}{\mathbb{E}}
@@
 $$
-where $R(t, \bA_t) = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t)$.
+where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.
 
@@
 $$
-where $R_{\wedge}(t, \bA_t) = f_{\wedge, t}^{\ast} - f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$.
+where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
 
@@
 $$
-\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
+\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
 $$
@@
 \label{eq:estimateTheta}
-\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \beta_{t}(\delta).
+\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
 \end{equation}
@@
 
-This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm.
+This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm.
 Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
@@
 \label{eq:defU}
-\bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
+\bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
 \end{equation}
@@
 $$
-0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 $$
@@
 \abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
-&\leq \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
 \end{align*}
@@
 $$
-Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$.
+Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$.
 In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
@@
 \STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
-\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
+\STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
 %\STATE{}
@@
 \STATE {$\forall a\in E: $}
-\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
+\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
 %\STATE {}
@@
 \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
+\STATE {$\bbeta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
 \ENDFOR {~~$t$}
@@
 $$
-R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
+R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
 $$
@@
 $$
-R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
 $$
@@
 Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
+Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bbeta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
 We leave all details in the next subsection.
@@
 \end{align*}
-\end{proof}
-
-The following lemma provides the important result on the regret at each time $t$
-	in terms of feature vectors of base arms at the time.
-\begin{lemma}
-	\label{lem:DeltaEstimate}
-	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
-	$$
-	R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
-	$$
-	if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
-	$$
-	R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
-	$$
-\end{lemma}
-\begin{proof}
-By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
-$$
-f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
-$$
-By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
-$$
-f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-$$
-By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
-$$
-f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-$$
-Therefore,
-$$
-R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-$$
-The result for the conjunctive case can be deduced in a similar way.
 \end{proof}
@@
 
+The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.
+\begin{lemma}
+\label{lem:DeltaEstimate}
+For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
+$$
+R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
+$$
+if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
+$$
+R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+$$
+\end{lemma}
+\begin{proof}
+By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
+$$
+f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
+$$
+By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
+$$
+f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
+$$
+f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+Therefore,
+$$
+R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+$$
+The result for the conjunctive case can be deduced in a similar way.
+\end{proof}
+
 \wei{This lemma needs to be clarified, using Lemma 4.6.
@@
 So we need the following lemma.
+
 \begin{lemma}
+\label{lem:DeltaEsimateWithP*}
 Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
@@
 $$
-E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+\EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 $$
@@
 \begin{align*}
-% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
-&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
+% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
+&\EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 \end{align*}
@@
 \begin{proof}
-For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
+For the disjunctive case,  
+\begin{align*}
+&\EE[R(t, \bA_t)|\cH_t] \\
+=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
+=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
+\end{align*}
+The third inequality is because $p_{\bA_t} \geq p^*$ and the forth inequality is by Lemma \ref{lem:DeltaEstimate}.
 % $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
 
-For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
+For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
 Then we have
-$$
-\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}]
-$$
-Because 
+\begin{align*}
+&\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t]\\
+=& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right]\\
+=& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
+\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]
+% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bB_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
+% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
+\end{align*}
+By Lemma \ref{lem:increasing},
 $$
@@
 $$
-by Lemma \ref{lem:increasing} and
+and by Lemma \ref{lem:estimateTech},
 $$
-f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
-by Lemma \ref{lem:estimateTech}, we have
+Therefore,
 $$
-R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
 $$
-Therefore
+Then we can derive the result
 \begin{align*}
-\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-&\leq \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
+&\EE_t[R_{\wedge}(t, \bA_t)] \\
+\leq& \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+\leq& \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
 \end{align*}
@@
 \begin{lemma} % det(V_t)
-$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
+\label{lem:detVt}
+$\det(\bV_t)$ is increasing with respect to $t$ and 
+$$
+\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
+$$
 \end{lemma}
 \begin{proof}
+To prove $\det(\bV_t)$ is increasing with respect to $t$, it is enough to prove that
+$$
+\det(V + xx^{\top}) \geq \det(V)
+$$
+for any symmetric positive definite matrix $V \in \RR^{d \times d}$ and column vector $x \in \RR^{d\times 1}$. In fact,
+\begin{align*}
+&\det(V + xx^{\top}) \\
+=& \det(V) \det(I + V^{-1/2}x x^{\top} V^{-1/2})\\
+=& \det(V) \det(1 + \norm{V^{-1/2}x}^2)\\
+\geq &\det(V).
+\end{align*}
+The second equality is because Sylvester's determinant theorem, which states that $\det(I + AB) = \det(I +BA)$.
+
 Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
-$$
-\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \leq  (\frac{\lambda_1 + \ldots + \lambda_d}{d})^d = (\trace(\bV_t)/d)^d.
-$$
+\begin{align*}
+&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
+\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
+\end{align*}
 \wei{Why? need a citation?} \shuai{I have rewritten this part.}
@@
 \end{align*}
+Thus we have $\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
 \end{proof}
 
-\begin{lemma} % technical lemma for det
+\begin{lemma}
+\label{lem:SumXiEstimateInDet}
 Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
-&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
-&\leq \EE \left[\frac{1}{p^*} \beta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \EE \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]}
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
+&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
 	\right ]  \\
-&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
-& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)} \right]\\
+&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
+& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
 &\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
@@
 \end{equation}
+The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
+The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality.
+The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
+And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 
-For the conjunctive case, 
+Similarly, for the conjunctive case, 
 \begin{equation}
@@
 &R(T) =\sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \\
-&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
-&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_t)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
-&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)} \right]\\
+&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
+&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
+&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
 &\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
@@
 \end{proof}
+
+The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
+The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
+The third inequality is because of mean inequality.
+The forth inequality is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
+And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 

### 2015-12-09 experiment.tex
fix some prints; update document

@@
 
-Let $I=\{e_1,e_2,\dots,e_L\}$ be a set of arms, each associated with a $d$-dimensional vector $x_i$ randomly drawn from $\{x\in R^d : \|x\|_2=1\}$.
-The expected payoff of an superarm $A\subseteq I$, denoted as $r_A$, will be $\sum_{i:e_i\in A, i\leq O_t}{(\theta_\ast^Tx_i + \epsilon_{i,t})\gamma^i z_i}$, where $\theta_\ast$ s.t.
-$\|\theta_\ast\|_2=1$ is randomly initiated and holds throughout the experiment, and $\epsilon_{i,t}\sim N(\mu_i,\sigma_i)$ i.i.d.
+Let $I=\{e_1,e_2,\dots,e_L\}$ be a set of arms, each associated with a $d$-dimensional vector $\mu_i$ randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$.
+At round $t$, the context corresponding to the $i$-th arm, denoted as $x_{t,i}$, is generated using $x_{t,i}=(\mu_i+h\cdot b_{t,i})/\|\mu_i+h\cdot b_{t,i}\|_2$, where $b_{t,i}$ is randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$ and $h$ is a constant throughout the experiment.
+The expectation of the Bernoulli realization of an arm $e\in I$ is $w_t(e)=\theta_\ast^Tx_i + \epsilon_{i,t}$, where $\theta_\ast$ s.t.
+$\|\theta_\ast\|_2=1$ is randomly initialized and holds throughout the experiment, and $\epsilon_{i,t}\sim N(\mu_i,\sigma_i)$ i.i.d.
 be the fluctuation.
 In this experiment, the set of avaiable superarms $S$ is $\{A\subseteq I:|A|=k\}$.
-
-The following approaches are served as baselines:
+The following approaches were tested:
 
@@
 
-  \item The monkey who randomly select $A\in S$ at each round.
+  \item Li Shuai et al. Use linear regression on $\mathbf{O_t}$ observed arms and then UCB to select candidated.
 
-  \item Combinatorial Cascading UCB which maintains its upper confidence bound purely by the historical payoff of the superarms selected.
-The contextual information $x_{i,t}$ is totally ignored so it can only catch the $\epsilon$ part while suffers a lot from noisy.
-The performance of Combinatorial Cascading UCB will mainly depends on the magnitude of $\mu$.
+  \item 2014 Qin Lijing et al. Same w/ Li but takes more information (from $\mathbf{O_t}$ to $k$) with a full feedback.
 
-  \item Contextual Combinatorial UCB which takes full feedback instead of cascading feedback, which is sureal in some settings in real world.
-It's expected to perform better than C3UCB, but as long as their regret being comparable, the result is acceptable.
+  \item 2015 Kveton Branislav et al.
+Combinatorial Cascading UCB which maintains its upper confidence bound purely by the historical payoff of the superarms selected.
+The contextual information $x_{i,t}$ is totally ignored so it can only catch the $\theta_\ast^T\mu$ part while suffers a lot from noisy.
+
+  \item Random.
 
@@
 
-let $Y$ be a matrix in which each entry $y_{ij}\in \{0,1\}$ records the clickthrough history between user $i$ and movie $j$.
-We split $Y$ into training set and test set $Y=Y_{\text{train}}+Y_{\text{test}}$ by categorizing each entry randomly with probability $\delta$.
-Let $USV^T=Y_{\text{train}}$ be the SVD decomposition of $Y_{\text{train}}$, the context corresponding to user $i$ and movie $j$ is defined as $U_i^T(V_j, G_j)$, where $G_i$ records the binary indicators of genres.
+This section introduced Movielens dataset and its movie recommendation challenge.
+Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie.
+We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ accoring to a bernulli distribution.
+At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $H_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.
 
-Upon received a super arm $A\in S$, the reward $\sum_{i:e_i\in I, i\leq O_t}{Y_{\text{test},ij}\gamma^i z_i}$ is returned as well as the terminal of cascade.
-The result is compared with the same baselines as in the above synthetic dateset experiment.
+We formulate the movie recommendation problem into a combinatorial bandit problem.
+Let $A^1=USV^T$ be the SVD decomposition and the movies $I=\{e_1,\dots,e_L\}$ be the set of arms, we define the context associated with $e_j$, at round $t$, as $x_{t,e_j}=u_{i_t}^Tv_j$, where $u_l$, $v_l$ denote the $l$-th row of $U$, $V$, respectively.
+Upon received a super arm $A\in \{A\subseteq I: |A|=k\}$, the reward $r_t$ is calculated using its definition and $w_t(e_j)=A^2_{i_te_j}$.
+Some notes follows:
 
+\begin{enumerate}
+
+  \item Define $x_{t,e_j}=(u_{i_t}, v_j)$ is not applicable because the argmax over arms will ignore the stochastic part of the context.
+
+  \item Split users into training and testing, as 2014 Qin Lijing et al. did, is not applicable because the context is constant for each arm.
+
+  \item Measurement for Movielens is accuracy instead of regret because we have no access to the true $\theta_\ast$, if there is one.
+
+\end{enumerate}
 \end{document}

### 2015-12-09 agent.py

@@ -121,7 +121,6 @@ def contextual_cascading_sherry(e, s, T):
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.log(np.linalg.det(V))- ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
-        #logger.info('Sherry play score {0}/{1}'.format(score[-1], t))
     logger.info('Sherry play score {0}/{1}'.format(score[-1], T))
     if 'theta' in s.__dict__:
         logger.info('theta cosine similarity {0}'.format(1 - cosine(s.theta, theta)))

### 2015-12-09 environment.py

@@ -57,8 +57,6 @@ def contextual_cascading_movielens(s):
             return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms}
         else:
             ctr = [arm in s.ctrh[user[0]] for arm in recommend]
-            logger.debug('Received recommendation {0}'.format(recommend))
-            logger.debug('User ctr history {0}'.format(s.ctrh[user[0]]))
             r, c = reward(ctr, s.gamma, s.disj)
             return r, c
     logger.info('Initializing environment "Contextual Cascading Movielens" done')
@@ -73,8 +71,6 @@ def contextual_full_movielens(s):
             return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms}
         else:
             ctr = [arm in s.ctrh[user[0]] for arm in recommend]
-            logger.debug('Received recommendation {0}'.format(recommend))
-            logger.debug('User ctr history {0}'.format(s.ctrh[user[0]]))
             r, _ = reward(ctr, s.gamma, s.disj)
             return r, [int(click) for click in ctr]
     logger.info('Initializing environment "Contextual Full Movielens" done')

### 2015-12-09 experiment.tex
minor

@@
 We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ accoring to a bernulli distribution.
-At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $H_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.
+At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.
 

### 2015-12-10 contextual combinatorial cascading bandits.tex
update statement of main theorem

@@
 \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
-\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
+\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
 \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
@@
 R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
-&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
 &=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
@@
 R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
-&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
+&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
 &=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
@@
 
-\wei{This lemma needs to be clarified, using Lemma 4.6.
-Also, our regret bound is expected regret but with a high probability? Sound a 
-bit strange.}
-\shuai{Yes, our regret bound is expected regret with a high probability. The reason is that NIPS'11 gives such a result.}
-
 Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
-However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms.
-So we need the following lemma.
+However, it is hard to estimate an upper bound for
+	$\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ 
+	because $\bV_t$ only contains observed base arms. Thus we need the following lemma.
 
@@
 For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. 
-Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$.
-Then
+Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
 $$
@@
 For the disjunctive case,  
-\begin{align*}
-&\EE[R(t, \bA_t)|\cH_t] \\
+\begin{align}
+&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
 =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
@@
 \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
-\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
 \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
-\end{align*}
+\end{align}
 The third inequality is because $p_{\bA_t} \geq p^*$ and the forth inequality is by Lemma \ref{lem:DeltaEstimate}.
@@
 
-For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
+For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
+By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge}
+	\le \frac{1}{4} f^*_{\wedge,t}  $, we have
+	$p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$.
 Then we have
-\begin{align*}
-&\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t]\\
-=& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right]\\
-=& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
-\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]
+\begin{align}
+&\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+=& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
+=& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
+\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
 % \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bB_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
 % \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
-\end{align*}
-By Lemma \ref{lem:increasing},
-$$
-f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
-$$
-and by Lemma \ref{lem:estimateTech},
-$$
+\end{align}
+Next, we have
+\begin{equation} \label{eq:andstarbt}
+f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
+\end{equation}
+where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing},
+	the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected
+	with respect to $\bU_t$, and the last inequality is by
+	Lemma~\ref{lem:prefixRelation}~(2).
+
+Then by Lemma \ref{lem:estimateTech},
+\begin{equation} \label{eq:btuttrue}
 f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
-$$
-Therefore,
-$$
-R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
-$$
-Then we can derive the result
+\end{equation}
+Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
+\begin{align}
+R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
+& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
+\end{align}
+Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}
+we can derive the result
 \begin{align*}
 &\EE_t[R_{\wedge}(t, \bA_t)] \\
-\leq& \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-\leq& \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
+\leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 \end{align*}
@@
 \begin{split}
-&R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
+&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ]\\
 &\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
@@
 	\right ]  \\
-&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
-& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
-&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
+&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \\
+& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
+&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right)\\
 &\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
@@
 \begin{split}
-&R(T) =\sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \\
+&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ]\\
 &\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
@@
 &\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
-&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
-&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\det(\lambda I)} \right)} \right]\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
+&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \\
+&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right)\\
 &\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]

### 2015-12-10 contextual combinatorial cascading bandits.tex

@@
 &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
+&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right),
 \end{align}
@@
 &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
+&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right).
 \end{align}
@@
 Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. 
-For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. 
+%For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. 
 Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
@@
 &\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
-=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
-=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
-\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
-\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right]\\
+=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]
+	\label{eq:addOt}\\
+=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
+\leq &\frac{1}{p^{\ast}} \EE \left[ \left.
+\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
 \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
+\label{eq:relaxindicator}
 \end{align}
-The third inequality is because $p_{\bA_t} \geq p^*$ and the forth inequality is by Lemma \ref{lem:DeltaEstimate}.
+Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$
+	is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$.
+Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed,
+	$\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no
+	need to write the conditional expectation.
+Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition.
+Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and
+	the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because
+	algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to
+	$\bU_t$.
+Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for
+	the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
 % $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
@@
 	$p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$.
-Then we have
+Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar},
+	we have
 \begin{align}
@@
 $$
-\det(I + \sum_{i=1}^n x_i x_i^{\top}) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
+\det\left(I + \sum_{i=1}^n x_i x_i^{\top}\right) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
 $$

### 2015-12-10 contextual combinatorial cascading bandits.tex
update main proof and put lemma 10 after lemma 12

@@
 
+From the above lemma, we can bound the regret at time $t$ in terms of the observed base arms, which we would like to estimate in the following. Before that, we need a technical lemma.
+
+\begin{lemma}
+\label{lem:detTech}
+Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
+$$
+\det\left(I + \sum_{i=1}^n x_i x_i^{\top}\right) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
+$$
+\end{lemma}
+\begin{proof}
+Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
+\begin{align*}
+&\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
+&\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
+&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
+&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
+\end{align*}
+\end{proof}
+
+Now we can give the following estimate about all observed base arms.
+
+\begin{lemma}
+\label{lem:SumXiEstimateInDet}
+If $\lambda \geq C_\gamma$, then
+$$
+\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
+$$
+\end{lemma}
+\begin{proof}
+\begin{align}
+&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top})) \notag\\
+&=\det(\bV_{t-1}) \notag \\
+&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top}) \notag\\
+&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2) \label{eq:detGeq} \\
+&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2), \notag
+\end{align}
+where inequality \eqref{eq:detGeq} is because of Lemma \ref{lem:detTech}.
+
+Because
+$$
+\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
+$$
+we have 
+$$
+\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
+$$
+Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
+\begin{align*}
+&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
+&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
+&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
+&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
+\end{align*}
+\end{proof}
+
+By the above lemma, we need to estimate $\det(\bV_t)$ to bound regret.
+
 \begin{lemma} % det(V_t)
@@
 
-\begin{lemma}
-\label{lem:SumXiEstimateInDet}
-Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
-$$
-\det\left(I + \sum_{i=1}^n x_i x_i^{\top}\right) \geq 1 + \sum_{i=1}^n \norm{x_i}_2^2.
-$$
-\end{lemma}
-\begin{proof}
-Denote the eigenvalues of $I + \sum_{i=1}^n x_i x_i^{\top}$ by $1+\alpha_1,...,1+\alpha_d$ with $\alpha_j \geq 0$, $1\leq j\leq d$. Then
-\begin{align*}
-&\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
-&\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
-&=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
-&=1 + \sum_{i=1}^n \norm{x_i}_2^2.
-\end{align*}
-\end{proof}
-
-\begin{lemma}
-If $\lambda \geq C_\gamma$, then
-$$
-\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
-$$
-\end{lemma}
-\begin{proof}
-\begin{align*}
-&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
-&=\det(\bV_{t-1})\\
-&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
-&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
-&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
-\end{align*}
-Because
-$$
-\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
-$$
-we have 
-$$
-\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
-$$
-Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
-\begin{align*}
-&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
-&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
-&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
-\end{align*}
-\end{proof}
-
 \begin{proof}[ of Theorem \ref{thm:main}]
@@
 For the disjunctive case,
-\begin{equation}
-\begin{split}
-&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ]\\
-&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
+\begin{align}
+&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ] \notag\\
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
 &\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
-	\right ]  \\
-&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \\
-& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
-&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right)\\
-&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
-\end{split}
-\end{equation}
-The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
-The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality.
-The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
-And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+	\right ]  \label{eq:pfMmeanEq}\\
+&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
+&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right) \notag\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ] \label{eq:pfMdetEst}
+\end{align}
+The inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}.
+The second inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
+The third inequality \eqref{eq:pfMmeanEq} is because of mean inequality.
+The fourth inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
+And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 
 Similarly, for the conjunctive case, 
-\begin{equation}
-\begin{split}
-&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ]\\
-&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
-&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \\
-&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right)\\
-&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
-\end{split}
-\end{equation}
+\begin{align}
+&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ] \notag\\
+&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
+&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
+&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right) \notag\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ] \label{eq:pfMCdetEst}
+\end{align}
 \end{proof}
 
-The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
-The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
-The third inequality is because of mean inequality.
-The forth inequality is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
-And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+The first inequality \eqref{eq:pfMCdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}.
+The second inequality \eqref{eq:pfMCbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
+The third inequality \eqref{eq:pfMCmeaneq} is because of mean inequality.
+The forth inequality \eqref{eq:pfMCsumXi} is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
+And the last inequality \eqref{eq:pfMCdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 

### 2015-12-10 contextual combinatorial cascading bandits.tex

--- 2015-12-10 contextual combinatorial cascading bandits.tex
@@
 %\wei{I thought the following is simpler. Should we use the following?}
-$$
-\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
-$$
+\begin{equation}
+\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
+\end{equation}
 Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
@@
 
-\begin{lemma} % det(V_t)
-\label{lem:detVt}
-$\det(\bV_t)$ is increasing with respect to $t$ and 
-$$
-\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
-$$
-\end{lemma}
-\begin{proof}
-To prove $\det(\bV_t)$ is increasing with respect to $t$, it is enough to prove that
-$$
-\det(V + xx^{\top}) \geq \det(V)
-$$
-for any symmetric positive definite matrix $V \in \RR^{d \times d}$ and column vector $x \in \RR^{d\times 1}$. In fact,
-\begin{align*}
-&\det(V + xx^{\top}) \\
-=& \det(V) \det(I + V^{-1/2}x x^{\top} V^{-1/2})\\
-=& \det(V) \det(1 + \norm{V^{-1/2}x}^2)\\
-\geq &\det(V).
-\end{align*}
-The second equality is because Sylvester's determinant theorem, which states that $\det(I + AB) = \det(I +BA)$.
-
-Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
-\begin{align*}
-&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
-\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
-\end{align*}
-\wei{Why? need a citation?} \shuai{I have rewritten this part.}
-Also,
-\begin{align*}
-&\trace(\bV_t)\\
-& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
-& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
-& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
-\end{align*}
-Thus we have $\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
-\end{proof}
+From the above lemma, we can bound the regret at time $t$ in terms of the observed base arms, for which we further bound in Lemma~\ref{lem:SumXiEstimateInDet}.
+But before that, we need the following technical lemma.
 
 \begin{lemma}
-\label{lem:SumXiEstimateInDet}
+\label{lem:detTech}
 Let $x_i \in \RR^{d \times 1}, 1 \leq i \leq n$. Then we have
@@
 \begin{lemma}
+\label{lem:SumXiEstimateInDet}
 If $\lambda \geq C_\gamma$, then
@@
 \begin{proof}
-\begin{align*}
-&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
-&=\det(\bV_{t-1})\\
-&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
-&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
-&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
-\end{align*}
+\begin{align}
+&\det(\bV_t) = \det\left(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k x_{t,\ba_k^{t}})(\gamma_k x_{t, \ba_k^{t}}^{\top}) \right) \nonumber \\
+&=\det(\bV_{t-1}) \notag \\
+&~~~\cdot \det \left(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top} \right) \label{eq:Vfactor}\\
+&\geq \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
+&\geq \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
+\end{align}
+where Equality~\eqref{eq:Vfactor} is by the fact that
+	$V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite
+	matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and
+	Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality
+	\eqref{eq:detGeq}.
+
 Because
@@
 $$
-we have 
+where $\lambda_{\min}(\bV_{s-1})$ is the minimum eigenvalue of
+	$\bV_{s-1}$,  we have 
 $$
@@
 &\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
-&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
-&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
+&\leq 2\sum_{s=1}^t\ln \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right)\\
+& = 2 \ln \prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right) \\
+&\le 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right),
 \end{align*}
+where the last inequality is from Inequality~\eqref{eq:repeatV}.
 \end{proof}
 
-\begin{proof}[ of Theorem \ref{thm:main}]
-Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$.
+Finally the last lemma bound $\det(\bV_t)$.
 
-For the disjunctive case,
-\begin{equation}
-\begin{split}
-&R(T) = \EE[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] ]\\
-&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
-&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
-	\right ]  \\
-&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \\
-& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
-&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right)\\
-&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
-\end{split}
-\end{equation}
-The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
-The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}, and mean inequality.
-The third inequality is because of the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
-And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+\begin{lemma} % det(V_t)
+\label{lem:detVt}
+$\det(\bV_t)$ is increasing with respect to $t$ and 
+$$
+\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
+$$
+\end{lemma}
+\begin{proof}
+To prove $\det(\bV_t)$ is increasing with respect to $t$, it is enough to prove that
+$$
+\det(V + xx^{\top}) \geq \det(V),
+$$
+for any symmetric positive definite matrix $V \in \RR^{d \times d}$ and column vector $x \in \RR^{d\times 1}$. In fact,
+\begin{align*}
+&\det(V + xx^{\top}) \\
+=& \det(V) \det(I + V^{-1/2}x x^{\top} V^{-1/2})\\
+=& \det(V) \det(1 + \norm{V^{-1/2}x}^2)\\
+\geq &\det(V).
+\end{align*}
+The second equality above is due to Sylvester's determinant theorem, which states that $\det(I + AB) = \det(I +BA)$.
 
-Similarly, for the conjunctive case, 
-\begin{equation}
-\begin{split}
-&R(T) = \EE[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] ]\\
-&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right]\\
-&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \\
-&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right]\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right)\\
-&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
-\end{split}
-\end{equation}
+Let the eigenvalues of $\bV_t$ be $\lambda_1, \ldots, \lambda_d > 0$. Then
+\begin{align*}
+&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
+\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
+\end{align*}
+Also,
+\begin{align*}
+&\trace(\bV_t)\\
+& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
+& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
+& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
+\end{align*}
+Thus we have $\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
 \end{proof}
 
-The first inequality is by Lemma \ref{lem:DeltaEsimateWithP*}.
-The second inequality is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
-The third inequality is because of mean inequality.
-The forth inequality is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
-And the last inequality is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+Now we are ready to prove the main theorem.
+
+\begin{proof}[ of Theorem \ref{thm:main}]
+Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is
+	true with probability $1-\delta$.
+
+For the disjunctive case, we have
+\begin{align}
+&R(T) = \EE \left[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \right] \notag\\
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
+&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
+&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
+	\right ]  \label{eq:pfMmeanEq}\\
+&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
+&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right) \notag\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
+\end{align}
+Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
+Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ 
+	(Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
+Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
+Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) 
+	and Lemma \ref{lem:SumXiEstimateInDet}. 
+And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+
+Similarly, for the conjunctive case, we have the following derivation:
+\begin{align}
+&R(T) = \EE \left[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \right] \notag\\
+&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
+&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
+&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
+&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
+&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right) \notag\\
+&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMCdetEst}
+\end{align}
+%The first inequality \eqref{eq:pfMCdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}.
+The second inequality \eqref{eq:pfMCbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
+The third inequality \eqref{eq:pfMCmeaneq} is because of mean inequality.
+The forth inequality \eqref{eq:pfMCsumXi} is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
+And the last inequality \eqref{eq:pfMCdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+\end{proof}
 

### 2015-12-13 agent.py
minor

@@ -1,3 +1,4 @@
+import time
 import heapq
 import numpy as np
 from scipy.spatial.distance import cosine
@@ -110,7 +111,10 @@ def contextual_cascading_sherry(e, s, T):
     X = np.zeros((1, s.d))
     Y = np.zeros(1)
     score = [0]
+    timestamp = time.time()
     for t in range (1, T):
+        if t == 101:
+            logger.info('Sherry 100 rounds with {0}s elapsed'.format(time.time() - timestamp))
         x = e()
         U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in s.arms}
         recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]

### 2015-12-13 flowtest.py

@@ -56,7 +56,7 @@ def flowtest_movielens_conj():
 
 def flowtest_movielens_disj():
     T = 10000
-    s = contextual_movielens_rng(L=15, portion=0.2, d=15, K=4, h=120, gamma=0.95, disj=True)
+    s = contextual_movielens_rng(L=15, portion=0.2, d=15, K=4, h=None, gamma=0.95, disj=True)
     exploit1, explore1 = contextual_cascading_monkey(*contextual_cascading_movielens_environment(s), T=T)
     exploit2, explore2 = contextual_cascading_sherry(*contextual_cascading_movielens_environment(s), T=T)
     exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)

### 2015-12-13 utils.py

@@ -22,4 +22,4 @@ class ucb_settings:
         self.__dict__ = s
         
     def __str__(self):
-        return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items()])
+        return '\n'.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x']])

### 2015-12-17 movielens.py
fix minor index overflow

@@ -41,9 +41,7 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
                 history[user].append(movie)
             else:
                 history[user] = [movie]
-    cox = np.array(cox)
-    coy = np.array(coy)
-    A = sparse.coo_matrix((np.ones(cox.shape), (cox, coy)), shape=(cox.max() + 1, coy.max() + 1), dtype=np.float32)
+    A = sparse.coo_matrix((np.ones(len(cox)), (cox, coy)), shape=(max(list(history) + cox) + 1, max(list(movies) + coy) + 1), dtype=np.float32)
     U, S, VT = svds(A, d)
     for i in range(U.shape[0]):
         U[i] = U[i] / np.linalg.norm(U[i])

### 2015-12-19 contextual combinatorial cascading bandits.tex
update proof outline of main theorem

@@
 
+\newcommand{\CLemmaPrefixExi}{
+	Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
+	$$
+		p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
+	$$ 
+}
+\newcommand{\CLemmaIncre}{
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$.
+Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	$$
+		f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
+	$$
+}
+\newcommand{\CLemmaTech}{
+	Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
+	\begin{align*}
+		&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
+		&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
+	\end{align*}
+	where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
+}
+\newcommand{\CLemmaSumXiEstimateInDet}{
+	If $\lambda \geq C_\gamma$, then
+	$$
+	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
+	$$
+}
+\newcommand{\CLemmaDetVt}{
+	$\det(\bV_t)$ is increasing with respect to $t$ and 
+	$$
+		\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
+	$$
+}
+
 \newcommand{\hidetext}[1]{}
@@
 We will use $|A|$ to denote the length of an action $A$.
-Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length
-	at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
+Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
 
@@
 Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
-\begin{equation}
+\begin{equation} % eq:expectation
 	\label{eq:expectation}
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
-We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is,
-	for some $k=1,2,\ldots, \abs{\bA_t}$, 
+We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
 $$
@@
 At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
-Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t 
-	\mid  k \in[\bO_s], 1 \le s<t \}$.
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
 
@@
 $$
-At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward
-	$\br_{\wedge, t}$:
+At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
 \begin{align*}
@@
 	&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
-&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
- (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+	&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 	\label{eq:functionfstar}
@@
 Then it holds that
-\begin{equation}
+\begin{equation} %eq:ConDisRelation
 	\label{eq:ConDisRelation}
@@
 
-At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent
-	chooses her action. 
-By Equation \eqref{eq:expectation}, we have 
+At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
 $$
@@
 Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. 
-For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any
-	vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on
-	$V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
+For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
 In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
@@
 
-\begin{theorem}[\cite{abbasi2011improved}]
+\begin{theorem}[\cite{abbasi2011improved}] %estimate of theta
 	\label{thm:theta_estimate}
 	Let 
-%$$
-%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
-%$$
-%\wei{I thought the following is simpler. Should we use the following?}
 	\begin{equation}
@@
 The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
-\begin{lemma}
+\begin{lemma} %estimate of U
 	\label{lem:estimateU}
@@
 Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
-First, the learning agent 
-	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
+First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
 Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
@@
 Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$.
-In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
- $\begin{pmatrix} A\\ B\end{pmatrix}$.
+In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.
 
-\begin{algorithm}
+\begin{algorithm} %C^3-UCB algorithm
 	\caption{C$^3$-UCB}
@@
 denote the best expected reward of all time under the conjunctive objective.
-Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
-	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
+Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
 \begin{align*}
@@
 The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
-\begin{theorem}
+\begin{theorem} %main theorem
 	\label{thm:main}
-Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
-$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
 Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$.
@@
 		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
-&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right),
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right),
 	\end{align}
@@
 		R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
-&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
-&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right).
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
 	\end{align}
-%where
-%\begin{align*}
-%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
-%\end{align*}
 \end{theorem}
@@
 	We will re-write a proof outline after revising the proofs.}
-\hidetext{
-\wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
-	they should all be moved to Section 4.3}
-\shuai{I think Section 4.3 will probably be put in the appendix. So I sketch a proof of main theorem here. If all the proofs will be kept, then we don't need Lemma 4.4 and 4.5 here.}
 
-To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
+\begin{proof} %proof outline of main theorem
+	The proof is in Appendix.
+The main idea is to reduce our analysis to that of CombCascade in \cite{kveton2015combinatorial}.
+This reduction is challenging for two reasons.
+First, our setting has contextual information.
+Second, we consider position-discounted weight $\gamma$.
+
+	Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items.
+Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
+	\begin{align*}
+		&\EE[R(t, \bA_t)|\cH_t] \\
+		&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
+		&\EE_t[R_{\wedge}(t, \bA_t)] \\
+		&\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
+	\end{align*}
+	and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
+This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.
+
+	Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
 	\begin{lemma}
-\label{lem:DeltaEstimate}
-For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
-$$
-R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
-$$
-if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
-$$
-R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
-$$
+		\CLemmaPrefixExi
 	\end{lemma}
-
-So if the chosen action $\bA_t$ is not suboptimal, which means
-$$
-f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
-$$
-Then we can derive an estimate of $R(t, \bA_t)$ and $R_{\wedge}(t, \bA_t)$, however, in terms of all base arms in $\bA_t$.
-Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
-
-\wei{I do not understand the above paragraph and the formula below.}
-\shuai{If we choose action of $\bA_t$ instead of $A_t^{\ast}$, then we can know the differece between their expected reward.
-But the regret is bounded by all base arms in $\bA_t$.
-Only the observed base arms can be estimated together.
-So we can only estimate the following formula.
-I rewrite the following formula and can explain to you later.}
-\begin{align*}
-&~~\EE_t[R(t, \bA_t)] \\
-&= \EE[R(t, \bA_t) \bOne\{R(t, \bA_t) > 0\} \EE[(1/p_{t, \bA_t}) \bOne\{\bO_t \geq \abs{\bA_t}\}|\bA_t] | \cH_t]\\
-&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
-&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
-&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
-\end{align*}
-
-In real problems involved with recommendations, the click rate is a very small number.
-Thus for the problem with disjunctive objective, $p^*$ is relatively high and can be regarded as a constant.
-So we have $p_{t, \bA_t} \geq p^*$.
-For the problem with conjunctive objective, $p_{\wedge, t, \bA_t}$ might be small.
-Thus we need the following lemma to find a good substitution of $\bA_t$.
-
-%\begin{lemma}
-%\label{lem:prefixExist}
-%Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
-%$$
-%p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
-%$$
-%\end{lemma}
-From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small.
-Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$.
-Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bbeta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$.
-We leave all details in the next subsection.
-}
+	Then we need to bound $f(A, \bU_t)$ and $f_{\wedge}(A, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
+First we have the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing.
+	\begin{lemma}
+		\CLemmaIncre
+	\end{lemma}
+	Then we have an estimate of the expected reward with UCB $\bU_t$.
+	\begin{lemma}
+		\CLemmaTech
+	\end{lemma}
+	Next we only need to estimate $\det(\bV_t)$ and those contextual information of observed base arms in $\bV$-norms.
+	\begin{lemma}
+		\CLemmaSumXiEstimateInDet
+	\end{lemma}
+	\begin{lemma}
+		\CLemmaDetVt
+	\end{lemma}
+	Then it is easy to derive the proof.
+\end{proof}
 
@@
 
-We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined
-in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
-\begin{lemma}
+We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
+\begin{lemma} %lem:increasing
 	\label{lem:increasing} 
-Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$.
-Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
-$$
-f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
-$$
+	\CLemmaIncre
 \end{lemma}
 \begin{proof}
-Without the loss of generality, we prove for the case
-	of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. 
-First, for $1 \leq k \leq m$, we have
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
 	\begin{align*}
@@
 	\end{align*}
-By letting $\gamma_k = 1 - \gamma_k'$ and using the relation
-	in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
+	By letting $\gamma_k = 1 - \gamma_k'$ and using the relation in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
 \end{proof}
 
-The following lemma provides the relationship between an estimated mean vector $w$
-	and its upper bound vector $u$, in terms of their $f$ function values.
-\begin{lemma}
+The following lemma provides the relationship between an estimated mean vector $w$ and its upper bound vector $u$, in terms of their $f$ function values.
+\begin{lemma} %lem:estimateTech
 	\label{lem:estimateTech}
-Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
-\begin{align*}
-&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
-&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
-\end{align*}
-where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
+	\CLemmaTech
 \end{lemma}
@@
 
-The next lemma provides some properties about a prefix of action $A$
-	in the conjunctive case, 
-	which leads to the finding of a prefix $B$ of $A$ with similar regret
-	and probability of full observation as those of $A$, as given
-	in Lemma~\ref{lem:prefixexists}.
-\begin{lemma}
+The next lemma provides some properties about a prefix of action $A$ in the conjunctive case, which leads to the finding of a prefix $B$ of $A$ with similar regret and probability of full observation as those of $A$, as given in Lemma~\ref{lem:prefixexists}.
+\begin{lemma} %lem:prefixRelation
 	\label{lem:prefixRelation}
-Suppose 
-% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
-$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
-% For the conjunctive case, it holds that
-% $$
-% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
-% $$
+	Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
 	Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
@@
 \end{lemma}
-
 \begin{proof}
-% It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
-% $$
-% f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
-% $$
-% Then for the disjunctive objective,
 	Let $m = |A|$.
@@
 		\begin{align*}
-	f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
-	(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
+			f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i) (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
 			&\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
@@
 
-\begin{lemma} \label{lem:prefixexists}
-Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
-$$
-p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
-$$ 
+\begin{lemma} %lem:prefixexists
+	\label{lem:prefixexists}
+	\CLemmaPrefixExi
 \end{lemma}
@@
 The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.
-\begin{lemma}
+\begin{lemma} %lem:DeltaEstimate
 	\label{lem:DeltaEstimate}
@@
 Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
-However, it is hard to estimate an upper bound for
-	$\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ 
-	because $\bV_t$ only contains observed base arms. Thus we need the following lemma.
+However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
+Thus we need the following lemma.
 
-\begin{lemma}
+\begin{lemma} %lem:DeltaEsimateWithP*
 	\label{lem:DeltaEsimateWithP*}
 	Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
-%For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. 
 	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
@@
 	If we have
-% $$
-% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
-% $$
 	$$
@@
 	then
-\begin{align*}
-% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
-&\EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-\end{align*}
+	$$
+		\EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	$$
 \end{lemma}
@@
 		&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
-=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]
-	\label{eq:addOt}\\
+		=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
 		=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
@@
 \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
-\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
-\label{eq:relaxindicator}
+		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
 	\end{align}
-Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$
-	is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$.
-Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed,
-	$\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no
-	need to write the conditional expectation.
+	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$.
+Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
 Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition.
-Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and
-	the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because
-	algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to
-	$\bU_t$.
-Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for
-	the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
-% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.
+Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
+Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
 
@@
 By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge}
-	\le \frac{1}{4} f^*_{\wedge,t}  $, we have
-	$p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$.
-Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar},
-	we have
+	\le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
 	\begin{align}
@@
 		\leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
-% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bB_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]\\
-% \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
 	\end{align}
@@
 	\end{equation}
-where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing},
-	the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected
-	with respect to $\bU_t$, and the last inequality is by
-	Lemma~\ref{lem:prefixRelation}~(2).
+	where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
 
@@
 	\end{align}
-Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}
-we can derive the result
+	Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
 	\begin{align*}
@@
 		\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-\end{align*}
+	\textbf{lem:DeltaEsimateWithP*}\end{align*}
 \end{proof}
@@
 
-\begin{lemma}
+\begin{lemma} %lem:detTech
 	\label{lem:detTech}
@@
 
-\begin{lemma}
+\begin{lemma} % lem:SumXiEstimateInDet
 	\label{lem:SumXiEstimateInDet}
-If $\lambda \geq C_\gamma$, then
-$$
-\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
-$$
+	\CLemmaSumXiEstimateInDet
 \end{lemma}
@@
 	\end{align}
-where Equality~\eqref{eq:Vfactor} is by the fact that
-	$V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite
-	matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and
-	Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality
-	\eqref{eq:detGeq}.
+	where Equality~\eqref{eq:Vfactor} is by the fact that $V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality \eqref{eq:detGeq}.
 
@@
 	$$
-where $\lambda_{\min}(\bV_{s-1})$ is the minimum eigenvalue of
-	$\bV_{s-1}$,  we have 
+	where $\lambda_{\min}(\bV_{s-1})$ is the minimum eigenvalue of $\bV_{s-1}$,  we have 
 	$$
@@
 	\label{lem:detVt}
-$\det(\bV_t)$ is increasing with respect to $t$ and 
-$$
-\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
-$$
+	\CLemmaDetVt
 \end{lemma}
@@
 \begin{proof}[ of Theorem \ref{thm:main}]
-Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is
-	true with probability $1-\delta$.
+	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$.
 
@@
 		&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
-&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)}
-	\right ]  \label{eq:pfMmeanEq}\\
+		&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
 		&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
 		& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
-&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2} \right) } + \sqrt{\lambda} \right) \notag\\
+		&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
 		&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
@@
 	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
-Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ 
-	(Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
+	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
 	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
-Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) 
-	and Lemma \ref{lem:SumXiEstimateInDet}. 
+	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
 	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
@@
 		&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
-&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda} \right) \notag\\
+		&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda} \right) \notag\\
 		&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMCdetEst}
 	\end{align}
-%The first inequality \eqref{eq:pfMCdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}.
-The second inequality \eqref{eq:pfMCbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by definition of $\bbeta_t(\delta)$ and Lemma \ref{lem:detVt}.
-The third inequality \eqref{eq:pfMCmeaneq} is because of mean inequality.
-The forth inequality \eqref{eq:pfMCsumXi} is by the definition of $\beta_t(\delta)$ and Lemma \ref{lem:SumXiEstimateInDet}.
-And the last inequality \eqref{eq:pfMCdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 \end{proof}

### 2015-12-20 flowtest.py
update log

@@ -48,19 +48,9 @@ def flowtest_monkey_conj():
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_monkey_environment(s), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
 
-def flowtest_movielens_conj():
+def flowtest_movielens():
     T = 10000
-    s = contextual_movielens_rng(L=400, portion=0.2, d=5, K=8, h=None, gamma=0.95, disj=False)
-    exploit1, explore1 = contextual_cascading_monkey(*contextual_cascading_movielens_environment(s), T=T)
-    exploit2, explore2 = contextual_cascading_sherry(*contextual_cascading_movielens_environment(s), T=T)
-    exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)
-    exploit4, explore4 = contextual_full_lijing(*contextual_full_movielens_environment(s), T=T)
-    exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_movielens_environment(s), T=T)
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
-
-def flowtest_movielens_disj():
-    T = 10000
-    kw = {'L':15, 'portion':0.2, 'd':15, 'K':4, 'h':120, 'gamma':0.95, 'disj':True}
+    kw = {'L':950, 'portion':0.2, 'd':15, 'K':15, 'h':30, 'gamma':0.95, 'disj':True}
     logger.info('Movielens flowtest')
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
@@ -72,5 +62,5 @@ def flowtest_movielens_disj():
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_movielens_environment(s), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
 
-flowtest_movielens_disj()
+flowtest_movielens()
 logfile.close()

### 2015-12-20 contextual combinatorial cascading bandits.tex
revise proof outline

@@
 	\end{lemma}
-	Then we need to bound $f(A, \bU_t)$ and $f_{\wedge}(A, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
-First we have the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing.
+	Then we use the prefix to replace $\bA_t$ to compute the expected regret.
+Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
 	\begin{lemma}
@@
 	\end{lemma}
-	Then we have an estimate of the expected reward with UCB $\bU_t$.
 	\begin{lemma}
@@
 	\end{lemma}
-	Next we only need to estimate $\det(\bV_t)$ and those contextual information of observed base arms in $\bV$-norms.
+	From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
 	\begin{lemma}
@@
 	\end{lemma}
-	Then it is easy to derive the proof.
+	Then we can use a mean inequality to derive the result.
 \end{proof}
@@
 		\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-	\textbf{lem:DeltaEsimateWithP*}\end{align*}
+	\end{align*}
 \end{proof}
@@
 	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
-	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
+	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
 	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

### 2015-12-21 contextual combinatorial cascading bandits.tex
update lower bound discussion

@@
 
-\subsection{Proof of Theorem~\ref{thm:main}}
+\subsection{Lower Bounds}
+
+Suppose we have such a graph: 
+$$
+	\xymatrix{
+		S_0 \ar[r]^{0.8} \ar[d]_{0.9} & B \ar[dr]^{0.8} &\\
+		C \ar[r]_{0.8} & D \ar[r]_{0.7} &S_1 
+	}
+$$
+There are two paths in this graph: $A_1 = \{S_0 \to B \to S_1\}$ and $A_2 = \{S_0 \to C \to D \to S_1\}$. 
+Let the feasible action set be $\cS = \{A_1, A_2\}.$ The numbers on the edges denote the probability of that edge being unblocked. 
+For example, the probability of $C \to D$ being unblocked is $0.8$. 
+When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
+So the optimal action is $A_1$ with expected reward $0.64$ and $A_2$ is suboptimal with expected reward $0.504$.
+
+Next we analyze those times when the learning agent selects path $A_2$ instead of the optimal $A_1$. 
+Notice that if the observed edges are $S_0 \to C \to D$ or $S_0 \to C$, we will not abandon $A_2$ because the expected rewards are $0.9 \times 0.8$ and $0.9$, higher than $0.64$. 
+Only the times when all edges in $A_2$ being observed will help to recognize $A_2$ and abandon it. 
+Recall that the probability of all edges of $A_2$ being observed is $p_{A_2} = 0.9 \times 0.8 = 0.72.$ 
+So we have
+$$
+\EE[N_{A_2}]p_{A_2} \leq \frac{c \log(T)}{\Delta^2},
+$$
+where $N_{A_2}$ is the number of times that learning agent selects $A_2$ and $\Delta$ is the difference of the best expected reward minus the expected reward of $A_2$.
+Therefore,
+$$
+\EE[N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta^2}
+$$
+and
+$$
+R(T) \leq \EE[\Delta N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta}.
+$$
+
+% In the unusual situation where you want a paper to appear in the
+% references without citing it in the main text, use \nocite
+%\nocite{langley00}
+
+\bibliography{cascade_reference}
+\bibliographystyle{icml2015}
+
+\appendix
+
+\section{Proof of Theorem~\ref{thm:main}}
 
@@
 
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-%\nocite{langley00}
-
-\bibliography{cascade_reference}
-\bibliographystyle{icml2015}
-
 \end{document}

### 2015-12-21 contextual combinatorial cascading bandits.tex
update format
add one part of related work

@@
 
-\section{Related Works}
+\section{Related Work}
+
+Our work generalizes both the cascading bandits of \cite{kveton2015cascading} and combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount.
+In cascading bandits of \cite{kveton2015cascading}, the feasible set contains any list of $K$ items out of $L$ ground items.
+Our work generalizes the feasible set to be any set of lists of at most $K$ items, like \cite{kveton2015combinatorial}.
+In both \cite{kveton2015cascading} and \cite{kveton2015combinatorial}, even though they define the feasible actions as lists, they regard them as sets.
+The order of a feasible action does not affect the regret bound, which might have problem in real application, especially for recommendations.
+
+In \cite{kveton2015cascading}, they found that recommending items in chosen action in increasing order of their UCBs has better performance than in decreasing order of their UCBs.
+This result might conflict with recommendations in real world.
+To improve the quality of user experience, we usually list items with higher preference first and then lower preference items.
+Our work extends this part by introducing position discounted parameters.
+Under our setting, the items with higher preference will come first.
 
@@
 Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. 
-We call each of such tuples an {\em action} of length $k$.
-We will use $|A|$ to denote the length of an action $A$.
+We call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$.
 Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
@@
 Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
-The more items the learning agent reveals, the more reward the agent should receive.
-It is reasonable to assume that
+The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
 $$
@@
     \STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
-		%\STATE{}
 
@@
       \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
-			%\STATE{}
-
       \STATE {//Compute UCBs}
@@
       \STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
-			%\STATE {}
 
@@
       \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
-			%\STATE {}
 
@@
   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
-By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge}
-	\le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
+  By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
+  Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
   \begin{align}

### 2015-12-22 experiment.tex
update readme
fixed conj/disj;

@@
 \usepackage{fullpage}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{graphicx}
 \usepackage{courier}
 \usepackage{tikz}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\usepackage{amsmath, amssymb, amsfonts, bm}
+\usepackage{algorithm,algorithmic}
+\usepackage{amsthm}
+\usepackage{float}
+\usepackage{graphicx}
+\usepackage{booktabs}
 
@@
 Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie.
-We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ accoring to a bernulli distribution.
+We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ according to a bernulli distribution.
 At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.
@@
 \end{enumerate}
+
+An example output, with $T=10000$, is listed below.
+
+\begin{table}
+    \centering
+    \renewcommand{\arraystretch}{1.2}
+	\begin{tabular}{lc}
+	    \toprule
+		\textbf{Algorithm}  &\textbf{Cumulative Reward $\sum_{t=1}^Tr_i $}\\
+		\midrule
+		Li		    &4342.73 \\
+		Qin		    &4323.26 \\
+		Monkey		    &1765.41 \\
+		Kveton		    &1787.81 \\
+		Perfect Play		    &N/A \\
+		\bottomrule
+	\end{tabular}
+	\caption{\textbf{Cumulative reward w.r.t different baselines, under Movielens setting.}}
+	\label{daily}
+\end{table}
 \end{document}

### 2015-12-22 agent.py

@@ -8,23 +8,6 @@ import random
 import logging
 logger = logging.getLogger('Agent')
 
-def monkey(candidates, K=8, T=150000, verbose=False):
-    def agent(environment):
-        score = 0
-        children, adults = candidates
-        movies = children + adults
-        for t in range(1, T):
-            recc = random.sample(movies, K)
-            c = environment(recc)
-            reward = int(isinstance(c, int))
-            score += reward
-            if verbose:
-                print('Agent: Score={0}/{1}'.format(score, t))
-            else:
-                if t % 10000 == 0:
-                    print('Agent: Score={0}/{1}'.format(score, t))
-    return agent
-
 def contextual_cascading_monkey(e, s, T):
     score = [0]
     for t in range(1, T):
@@ -47,7 +30,7 @@ def absolute_cascading_ucb(e, s, T):
         recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
         r, c = e(recc)
         for k in range(min(s.K, c+1)):
-            W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + ((k == c) ^ s.disj)) / (b[recc[k]] + 1)
+            W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
             b[recc[k]] += 1
         score.append(score[-1] + r)
     logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
@@ -71,7 +54,7 @@ def contextual_cascading_sherry(e, s, T):
         r, c = e(recc)
         V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(s.K, c+1))])
         X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(s.K, c+1))])
-        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) ^ s.disj) * np.ones(1) for k in range(min(s.K, c+1))])
+        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(s.K, c+1))])
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.linalg.slogdet(V)[1] - ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)

### 2015-12-22 flowtest.py

@@ -28,10 +28,7 @@ from movielens import contextual_movielens_rng
 from environment import contextual_cascading_movielens as contextual_cascading_movielens_environment
 from environment import contextual_full_movielens as contextual_full_movielens_environment
 
-def flowtest_monkey():
-    T = 10000
-    #kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':True}
-    kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
+def flowtest_monkey(T, kw):
     logger.info('Monkey flowtest')
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
@@ -43,9 +40,7 @@ def flowtest_monkey():
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_monkey_environment(s), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
 
-def flowtest_movielens():
-    T = 10000
-    kw = {'L':950, 'portion':0.2, 'd':15, 'K':15, 'h':30, 'gamma':0.95, 'disj':True}
+def flowtest_movielens(T, kw):
     logger.info('Movielens flowtest')
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
@@ -55,7 +50,13 @@ def flowtest_movielens():
     exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)
     exploit4, explore4 = contextual_full_lijing(*contextual_full_movielens_environment(s), T=T)
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_movielens_environment(s), T=T)
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
+    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--', range(T), exploit5, 'b--')
 
-flowtest_movielens()
[…]

### 2015-12-22 movielens.py

@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V)
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A)
     logger.info(s)
     return s

### 2015-12-22 utils.py

@@ -9,10 +9,11 @@ def uni(x):
     return x/np.sqrt(x.dot(x))
 
 def reward(ctr, gamma, disj):
+    conj = not disj
     for c, click in enumerate(ctr):
-        if click ^ disj:
-            return int(disj) + gamma ** c * (int(not disj) - int(disj)), c
-    return int(disj), len(ctr)
+        if click == disj:
+            return int(conj) + gamma ** c * (int(disj) - int(conj)), c
+    return int(conj), len(ctr)
 
 def overlap(l1, l2):
     return len(set(l1) & l2)
@@ -22,4 +23,4 @@ class ucb_settings:
         self.__dict__ = s
         
     def __str__(self):
-        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x']])
+        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A']])

### 2015-12-22 experiment.tex

@@
 
+\newcommand{\RR}{\mathbb{R}}
+\newcommand{\cS}{\mathcal{S}}
+
 \begin{document}
@@
 
-\section{Synthetic dataset}
+\section{Preliminary}
 
-Let $I=\{e_1,e_2,\dots,e_L\}$ be a set of arms, each associated with a $d$-dimensional vector $\mu_i$ randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$.
-At round $t$, the context corresponding to the $i$-th arm, denoted as $x_{t,i}$, is generated using $x_{t,i}=(\mu_i+h\cdot b_{t,i})/\|\mu_i+h\cdot b_{t,i}\|_2$, where $b_{t,i}$ is randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$ and $h$ is a constant throughout the experiment.
-The expectation of the Bernoulli realization of an arm $e\in I$ is $w_t(e)=\theta_\ast^Tx_i + \epsilon_{i,t}$, where $\theta_\ast$ s.t.
-$\|\theta_\ast\|_2=1$ is randomly initialized and holds throughout the experiment, and $\epsilon_{i,t}\sim N(\mu_i,\sigma_i)$ i.i.d.
-be the fluctuation.
-In this experiment, the set of avaiable superarms $S$ is $\{A\subseteq I:|A|=k\}$.
-The following approaches were tested:
+\subsection{Synthetic dataset}
 
-\begin{enumerate}
+Let $\cS = \{x \in \RR^d : \|x\|_2 = 1 \}$ be the unit ball of $\RR^d$. 
+Let $E = \{1,...,L\}$ be the set of all base arms. 
+We randomly choose $\theta_{\ast}$ with $\|\theta_{\ast}\|_2 = 1$ and randomly assign a $\mu_i \in \cS$ to $i$ for any $i \in E$.
+At each time $t$, we choose $b_{t,i} \in \cS$ randomly for any base arm $i$.
+Also we fix a constant $h$ to balance weights of $\mu_i$ and disturbance $b_{t,i}$.
+Let $x_{t,i} = \frac{\mu_i + h b_{t,i}}{\|\mu_i+h\cdot b_{t,i}\|_2}$ be the context of base arm $i$ at time $t$.
+And the weight for base arm $i$ at time $t$ is $w_t(i) = \theta_{\ast}^{\top}x_{t,i} + \epsilon_{t,i}$ where $\epsilon_{t,i} \sim N(\mu_i, \sigma_i)$ for fixed $\sigma_i$.
 
-  \item Li Shuai et al. Use linear regression on $\mathbf{O_t}$ observed arms and then UCB to select candidated.
+\subsection{MovieLens}
 
-  \item 2014 Qin Lijing et al. Same w/ Li but takes more information (from $\mathbf{O_t}$ to $k$) with a full feedback.
+Let $L$ be the number of all movies and let $M$ be the number of all users. 
+The MovieLens dataset is a big matrix $A \in \RR^{M \times L}$ where $A(i,j) \in \{0,1\}$ denotes whether user $i$ has watched movie $j$ or not.
+We split $A$ to be $H + F$ by putting entry-$1$ of $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We can regard $H$ as know information about history 'What users have watched' and regard $F$ as future criterion.
+We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = USV^{\top}$ where $U = (u_1; ...;u_M)$ and $V = (v_1;...;v_L)$.
+At every time $t$, use $x_{t,i} = u_{i}v_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
+And use $w_t(j) = F(I_t,j)$ as the weight of base arm $j$.
 
-  \item 2015 Kveton Branislav et al.
-Combinatorial Cascading UCB which maintains its upper confidence bound purely by the historical payoff of the superarms selected.
-The contextual information $x_{i,t}$ is totally ignored so it can only catch the $\theta_\ast^T\mu$ part while suffers a lot from noisy.
+Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
+Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.
 
-  \item Random.
+The measurement for MovieLens is accuracy because we don't know the true $\theta_{\ast}$.
 
-\end{enumerate}
+\section{Disjunctive case}
 
-\section{Movielens}
+\subsection{Need to involve Contextual information}
 
-This section introduced Movielens dataset and its movie recommendation challenge.
-Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie.
-We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ according to a bernulli distribution.
-At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.
+We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$
 
-We formulate the movie recommendation problem into a combinatorial bandit problem.
-Let $A^1=USV^T$ be the SVD decomposition and the movies $I=\{e_1,\dots,e_L\}$ be the set of arms, we define the context associated with $e_j$, at round $t$, as $x_{t,e_j}=u_{i_t}^Tv_j$, where $u_l$, $v_l$ denote the $l$-th row of $U$, $V$, respectively.
-Upon received a super arm $A\in \{A\subseteq I: |A|=k\}$, the reward $r_t$ is calculated using its definition and $w_t(e_j)=A^2_{i_te_j}$.
-Some notes follows:
+\subsection{Need to involve position discount parameter $\gamma$}
 
-\begin{enumerate}
+We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.
 
-  \item Define $x_{t,e_j}=(u_{i_t}, v_j)$ is not applicable because the argmax over arms will ignore the stochastic part of the context.
+\subsection{Cascading Information}
 
-  \item Split users into training and testing, as 2014 Qin Lijing et al. did, is not applicable because the context is constant for each arm.
+We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.
 
-  \item Measurement for Movielens is accuracy instead of regret because we have no access to the true $\theta_\ast$, if there is one.
+\section{Conjunctive case}
 
-\end{enumerate}
+\subsection{Need to involve Contextual information}
+
+We experiment on synthetic data. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$
+
+\subsection{Need to involve position discount parameter $\gamma$}
+
+We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.
+
+\subsection{Cascading Information}
+
+We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.
+
+\section{Results}
 

### 2015-12-22 experiment/flowtest.py
readme/log update

@@ -55,7 +55,7 @@ def flowtest_movielens(T, kw):
 #kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':True}
 #kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
 #flowtest_monkey(T=1000, kw=kw)
-kw = {'L':25, 'portion':0.2, 'd':5, 'K':5, 'h':60, 'gamma':0.95, 'disj':True}
+kw = {'L':90, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'disj':True}
 flowtest_movielens(T=1000, kw=kw)
 
 logfile.close()

### 2015-12-22 experiment/agent.py
fixed training set movies appeared to be candidate

@@ -49,8 +49,8 @@ def contextual_cascading_sherry(e, s, T):
     timestamp = time.time()
     for t in range (1, T):
         x = e()
-        U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in s.arms}
-        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
+        U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
+        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in x])]
         r, c = e(recc)
         V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(s.K, c+1))])
         X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(s.K, c+1))])
@@ -77,8 +77,8 @@ def contextual_full_lijing(e, s, T):
     score = [0]
     for t in range (1, T):
         x = e()
-        U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in s.arms}
-        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
+        U = {arm:theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
+        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in x])]
         r, ctr = e(recc)
         V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(len(recc))])
         b += sum([ctr[k] * x[recc[k]] for k in range(len(recc))])

### 2015-12-22 experiment/environment.py

@@ -56,7 +56,10 @@ def contextual_cascading_movielens(s):
     def environment(recommend=None):
         if recommend is None:
             user[0] = random.sample(s.users, 1)[0]
-            return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms}
+            exc = s.A.getrow(user[0])
+            if len([arm for arm in s.arms if exc[0, arm] == 0]) < s.K + 2:
+                return environment()
+            return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms if exc[0, arm] == 0}
         else:
             ctr = [arm in s.ctrh[user[0]] for arm in recommend]
             r, c = reward(ctr, s.gamma, s.disj)
@@ -70,7 +73,10 @@ def contextual_full_movielens(s):
     def environment(recommend=None):
         if recommend is None:
             user[0] = random.sample(s.users, 1)[0]
-            return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms}
+            exc = s.A.getrow(user[0])
+            if len([arm for arm in s.arms if exc[0, arm] == 0]) < s.K + 2:
+                return environment()
+            return {arm: np.outer(s.U[user[0]], s.V[arm]).flatten() for arm in s.arms if exc[0, arm] == 0}
         else:
             ctr = [arm in s.ctrh[user[0]] for arm in recommend]
             r, _ = reward(ctr, s.gamma, s.disj)

### 2015-12-22 experiment/flowtest.py

@@ -47,7 +47,7 @@ def flowtest_movielens(T, kw):
     s = contextual_movielens_rng(**kw)
     exploit1, explore1 = contextual_cascading_monkey(*contextual_cascading_movielens_environment(s), T=T)
     exploit2, explore2 = contextual_cascading_sherry(*contextual_cascading_movielens_environment(s), T=T)
-    exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)
+    #exploit3, explore3 = contextual_full_monkey(*contextual_full_movielens_environment(s), T=T)
     exploit4, explore4 = contextual_full_lijing(*contextual_full_movielens_environment(s), T=T)
     exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_movielens_environment(s), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--', range(T), exploit5, 'b--')

### 2015-12-22 experiment/movielens.py

@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A)
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
     logger.info(s)
     return s

### 2015-12-23 experiment/movielens.py
file read minor

@@ -13,8 +13,8 @@ from utils import ucb_settings
 from utils import overlap
 
 def movielens_data():
-    fpr = open('ratings.csv')
-    fpt = open('tags.csv')
+    fpr = open('movielens/ratings.csv')
+    fpt = open('movielens/tags.csv')
     gr = csv.reader(fpr, delimiter=',', quotechar='"')
     gt = csv.reader(fpt, delimiter=',', quotechar='"')
     gr.__next__()

### 2015-12-23 experiment/utils.py
add suni random unit vector generator

@@ -8,6 +8,10 @@ def red(s):
 def uni(x):
     return x/np.sqrt(x.dot(x))
 
+def suni(d):
+    x = np.abs(np.random.normal(0, 1, d))
+    return uni(x)
+
 def reward(ctr, gamma, disj):
     conj = not disj
     for c, click in enumerate(ctr):

### 2015-12-23 experiment/isp.py
isp env

@@ -1,0 +1,32 @@
+import logging
+logger = logging.getLogger('Movielens')
+
+from utils import ucb_settings
+from utils import suni
+
+import networkx
+
+def isp_data(isp):
+    assert isp in {1221,1239,1755,2914,3257,3356,3967,4755,6461,7018}
+    for line in open('isp/{0}.cch'.format(isp)):
+        for t in [x for x in line.strip().split() if x.startswith('<')]:
+            yield int(line.strip().split()[0]), int(t[1:-1])
+
+def isp_net(g):
+    G = networkx.Graph()
+    for s, t in g:
+        G.add_edge(s, t)
+    return G
+
+def contextual_isp_rng(isp=1221, d=15, h=0.35, gamma=0.95, disj=True):
+    G = isp_net(isp_data(isp))
+    x = {e: suni(d) for e in G.edges()}
+    theta = suni(d)
+    logger.info('Initializing random settings "ISP" complete')
+    s = ucb_settings(L=len(G.nodes()), d=d, gamma=gamma, disj=disj, G=G, x=x)
+    logger.info(s)
+    return s
+
+g = isp_data(1221)
+G = isp_net(g)
+s = contextual_isp_rng()

### 2015-12-24 experiment/experiment.tex
add rocketfuel isp; agents now have no access to inside the oracle;

--- 2015-12-22 experiment.tex
@@
 
+\subsection{Routing}
+
+Let $G=(V,E=\{e_1,...,e_L\})$ be the topology representation of an ISP network, G is then symmetric by it's definition. 
+When a package is sent from the source node, it's returned back to the source after trying to bypass an edge with high latency.
+The routing is failed if so, and the source will receive the routing history till the failing edge.
+The agent is then motivated to assign an routing path, which can be recognized as an simple path in $G$ from the source node to the destination node, so as to aviod edges with high latency. 
+Assume we have some sort of tell about the dynamics of the network condition between the hosts, where the information is encoded in a $d$-dimentional vector, the network reuting problem is to find the routing path least likely to involve an edge with high latency.
+Denote $x_{i,t}$ be the vector associated with edge $e_i$, at time $t$, assume the corresponding latency is drawn from an exponential distribution with mean $1 - \theta_{\ast}^{\top}x_{t,i}$ independently,
+and define the latency is high iff it's greater than a constant tolerance value.
+We formulate the network routing as an contextual combinatorial cascading problem.
+
+Let $E=\{e_1,...,e_L\}$ be the set of arms, and $x_{i,t}$ be the context associated with arm $e_i$ at time $t$.
+In order to send a package from $u_t$ to $v_t$,
+the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\}$$
+To find the preferred superarm, the agent assigns an weight $\hat{\theta}^{\top}x_{i,t}$ to $e_i$, and runs shortest path algorithm on $G$.
+After the agent choose the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
+
 \section{Disjunctive case}

### 2015-12-24 experiment/agent.py

@@ -1,18 +1,17 @@
 import time
-import heapq
+import logging
+logger = logging.getLogger('Agent')
+
 import numpy as np
 from scipy.spatial.distance import cosine
 import matplotlib.pyplot as plt
 
-import random
-import logging
-logger = logging.getLogger('Agent')
-
 def contextual_cascading_monkey(e, s, T):
     score = [0]
     for t in range(1, T):
-        _ = e()
-        recc = random.sample(s.arms, s.K)
+        _, params = e()
+        U = {arm: np.random.uniform(0, 1) for arm in s.arms}
+        recc = s.oracle(U, *params)
         r, _ = e(recc)
         score.append(score[-1] + r)
     logger.info('Monkey play score {0}/{1}'.format(score[-1], T))
@@ -22,23 +21,22 @@ contextual_full_monkey = contextual_cascading_monkey
 
 def absolute_cascading_ucb(e, s, T):
     score = [0]
-    W = {arm:0.5 for arm in s.arms}
-    b = {arm:1 for arm in s.arms}
+    W = {arm: 0.5 for arm in s.arms}
+    b = {arm: 1 for arm in s.arms}
     for t in range(1, T):
-        _ = e()
-        U = {arm:W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
-        recc = [p[1] for p in heapq.nlargest(s.K, [(U[arm], arm) for arm in s.arms])]
+        _, params = e()
+        U = {arm: W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
+        recc = s.oracle(U, *params)
         r, c = e(recc)
-        for k in range(min(s.K, c+1)):
+        for k in range(min(len(recc), c+1)):
             W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
             b[recc[k]] += 1
         score.append(score[-1] + r)
     logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
     return score, 0
 
-def contextual_cascading_sherry(e, s, T):
-    delta = 0.9
-    lamb = 0.1
+def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
+    assert s.cascade
     theta = np.zeros(s.d)
     beta = 0
[…]

### 2015-12-24 experiment/environment.py

@@ -1,57 +1,48 @@
-import numpy as np
+import heapq
 import random
 import logging
 logger = logging.getLogger('Environment')
 
-from functools import reduce
+import numpy as np
 
 from utils import red
 from utils import uni
+from utils import disturb
 from utils import reward
 from utils import ucb_settings
-from movielens import contextual_movielens_rng
+
+from isp import isp_oracle
+from isp import reachable
 
 def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
     arms = list(range(L))
-    x = {arm:np.random.uniform(0, 1, d) for arm in arms}
+    x = {arm: np.random.uniform(0, 1, d) for arm in arms}
     theta = h * uni(np.random.uniform(0, 1, d))
     logger.info('Initializing random settings "Contextual Monkey" complete')
     s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, disj=disj)
     logger.info(s)
     return s
 
-def contextual_cascading_monkey(s):
-    logger.info('Initializing environment "Contextual Cascading Monkey"')
-    xt = {arm:s.x[arm] for arm in s.x}
+def argmax_oracle(U, K):
+    return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])]
+
+def contextual_monkey(s, cascade):
+    logger.info('Initializing environment "Contextual Monkey"')
+    xt = {arm: s.x[arm] for arm in s.x}
     def environment(recommend=None):
         if recommend == None:
-            for arm in xt:
+            for arm in s.x:
                 xt[arm] = uni(s.x[arm] + np.random.uniform(-s.v, s.v, s.d))
-            return xt
+            return xt, (s.K,)
         else:
             ctr = [np.random.uniform(0, 1) < s.theta.dot(xt[arm]) + np.random.normal(0, s.eps) for arm in recommend]
             r, c = reward(ctr, s.gamma, s.disj)
-            return r, c
-    logger.info('Initializing environment "Contextual Cascading Monkey" complete')
-    return environment, ucb_settings(arms=s.arms, L=s.L, K=s.K, d=s.d, gamma=s.gamma, theta=s.theta, disj=s.disj)
+            return (r, c) if cascade else (r, [int(click) for click in ctr])
[…]

### 2015-12-24 experiment/flowtest.py

@@ -22,41 +22,52 @@ from agent import contextual_full_monkey
 from agent import contextual_full_lijing
 from agent import absolute_cascading_ucb
 from environment import contextual_monkey_rng
-from environment import contextual_cascading_monkey as contextual_cascading_monkey_environment
-from environment import contextual_full_monkey as contextual_full_monkey_environment
+from environment import contextual_monkey
 from movielens import contextual_movielens_rng
-from environment import contextual_cascading_movielens as contextual_cascading_movielens_environment
-from environment import contextual_full_movielens as contextual_full_movielens_environment
+from environment import contextual_movielens
+from isp import contextual_isp_rng
+from environment import contextual_isp
 
 def flowtest_monkey(T, kw):
     logger.info('Monkey flowtest')
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_monkey_rng(**kw)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_cascading_monkey_environment(s), T=T)
-    exploit2, explore2 = contextual_cascading_monkey(*contextual_cascading_monkey_environment(s), T=T)
-    exploit3, explore3 = contextual_full_monkey(*contextual_full_monkey_environment(s), T=T)
-    exploit4, explore4 = contextual_full_lijing(*contextual_full_monkey_environment(s), T=T)
-    exploit5, explore5 = absolute_cascading_ucb(*contextual_cascading_monkey_environment(s), T=T)
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit4, 'b--')
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True), T=T)
+    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True), T=T)
+    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False), T=T)
[…]

### 2015-12-24 experiment/isp.py

@@ -1,10 +1,19 @@
 import logging
-logger = logging.getLogger('Movielens')
+logger = logging.getLogger('ISP')
 
 from utils import ucb_settings
 from utils import suni
 
 import networkx
+
+def reachable(G, u, v):
+    return networkx.has_path(G, u, v)
+
+def isp_oracle(U, G, u, v):
+    for (x, y), z in U.items():
+        G[x][y]['weight'] = max(1 - z, 0)
+    path = networkx.shortest_path(G, u, v, weight='weight')
+    return [tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1)]
 
 def isp_data(isp):
     assert isp in {1221,1239,1755,2914,3257,3356,3967,4755,6461,7018}
@@ -14,19 +23,15 @@ def isp_data(isp):
 
 def isp_net(g):
     G = networkx.Graph()
-    for s, t in g:
-        G.add_edge(s, t)
+    for u, v in g:
+        G.add_edge(u, v, weight=1)
     return G
 
-def contextual_isp_rng(isp=1221, d=15, h=0.35, gamma=0.95, disj=True):
+def contextual_isp_rng(isp=1221, d=10, h=0.35, tlc=1, gamma=0.95, disj=False):
     G = isp_net(isp_data(isp))
     x = {e: suni(d) for e in G.edges()}
     theta = suni(d)
     logger.info('Initializing random settings "ISP" complete')
-    s = ucb_settings(L=len(G.nodes()), d=d, gamma=gamma, disj=disj, G=G, x=x)
+    s = ucb_settings(L=len(G.edges()), d=d, h=h, gamma=gamma, disj=disj, G=G, tlc=tlc, x=x, theta=theta)
     logger.info(s)
     return s
-
-g = isp_data(1221)
-G = isp_net(g)
-s = contextual_isp_rng()

### 2015-12-24 experiment/utils.py

@@ -12,6 +12,10 @@ def suni(d):
     x = np.abs(np.random.normal(0, 1, d))
     return uni(x)
 
+def disturb(x, h):
+    y = x + h * np.random.normal(0, 1, x.shape)
+    return uni(y)
+
 def reward(ctr, gamma, disj):
     conj = not disj
     for c, click in enumerate(ctr):
@@ -27,4 +31,4 @@ class ucb_settings:
         self.__dict__ = s
         
     def __str__(self):
-        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A']])
+        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A', 'oracle', 'theta']])

### 2015-12-24 experiment/environment.py
isp log update; everything is likely end for this experiment. one obvious defect is the highly reproduction of environment functions. it is optimizable by letting all specific rng super the ucb_setting class and put their own random, ctr in. anyway, im gonna go sleep zzzzz

@@ -76,11 +76,3 @@ def contextual_isp(s, cascade):
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual ISP" done')
     return environment, ucb_settings(arms=s.G.edges(), L=len(s.G.edges()), d=s.d, gamma=s.gamma, disj=s.disj, cascade=cascade, oracle=isp_oracle, theta=s.theta)
-
-#from isp import contextual_isp_rng
-#for i in range(15):
-#    e, s = contextual_isp(contextual_isp_rng(), cascade=False)
-#    x, p = e()
-#    U={arm: 1 for arm in x}
-#    recc=isp_oracle(U, *p)
-#    r,c=e(recc)

### 2015-12-24 experiment/isp.py

@@ -1,10 +1,10 @@
 import logging
 logger = logging.getLogger('ISP')
 
+import networkx
+
 from utils import ucb_settings
 from utils import suni
-
-import networkx
 
 def reachable(G, u, v):
     return networkx.has_path(G, u, v)

### 2015-12-25 experiment/experiment.tex
add proximity prove

--- 2015-12-22 experiment.tex
@@
 \newcommand{\cS}{\mathcal{S}}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 The measurement for MovieLens is accuracy because we don't know the true $\theta_{\ast}$.
+
+\subsection{Routing}
+
+Let $G=(V,E=\{e_1,...,e_L\})$ be the topology representation of an ISP network, $G$ is then symmetric by it's definition. 
+Considering the scinario where a package is sent from its source node to its destination, it's returned back to the source after trying to bypass an edge with high latency.
+And the routing is failed if so, and the source will receive the routing history till the failing edge.
+The agent is then motivated to assign an routing path, which can be recognized as an simple path in $G$ from the source node to the destination node, so as to avoid edges with high latency. 
+Assume we have some sort of tell about the dynamics of the network conditions between the hosts, each being encoded in a $d$-dimentional vector, the network routing problem is to find the routing path least likely to involve an edge with high latency.
+Denote $x_{i,t}$ be the vector associated with edge $e_i$, at time $t$, assume the corresponding latency is drawn from an exponential distribution with mean $1 - \theta_{\ast}^{\top}x_{t,i}$ independently,
+and define the latency is high iff it's greater than a constant tolerance value $\tau$.
+We formulate the network routing as an contextual combinatorial cascading problem.
+
+Let $E=\{e_1,...,e_L\}$ be the set of arms, and $x_{i,t}$ be the context associated with arm $e_i$ at time $t$.
+In order to send a package from $u_t$ to $v_t$,
+the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
+with the expected payoffs (opt out discount) $$E[r_A]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta_{\ast}^{\top}x_{k_i,t}))).$$
+The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{Z\in S}\sum_{1\leq i\leq n(Z)}\hat{\theta}^{\top}x_{k_i,t}.$$
+We have then $$\max_{A\in S}E[r_A]/E[r_{A_t}]\leq \alpha(\tau, d) = (1-e^{-\tau})^d/(1-e^{-\tau / d}).$$
+Hence we can realize the $\alpha(\tau, d)$ oracle using shortest path algorithm.
+After the agent choose the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
 

### 2015-12-25 experiment/experiment.tex
minor doc update

@@
 the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
-with the expected payoffs (opt out discount) $$E[r_A]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta_{\ast}^{\top}x_{k_i,t}))).$$
-The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{Z\in S}\sum_{1\leq i\leq n(Z)}\hat{\theta}^{\top}x_{k_i,t}.$$
-We have then $$\max_{A\in S}E[r_A]/E[r_{A_t}]\leq \alpha(\tau, d) = (1-e^{-\tau})^d/(1-e^{-\tau / d}).$$
-Hence we can realize the $\alpha(\tau, d)$ oracle using shortest path algorithm.
-After the agent choose the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
+with the expected payoffs (opt out discount) $$E[r_A]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta_{\ast}^{\top}x_{k(A)_i,t}))),$$
+where $n(A)$ and $k(A)_i$ is the amount of arms in superarm $A$, and the index of the $i$-th arm, separately.
+The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{Z\in S}\sum_{1\leq i\leq n(Z)}\hat{\theta}^{\top}x_{k(Z)_i,t}.$$
+We have then $$E[r_{A_t}]/\min_{A\in S}E[r_A]\geq \alpha(\tau, G) = (1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|},$$
+which shows that we can realize the $\alpha(\tau, G)$-approximation oracle using shortest path algorithm.
+After the agent chooses the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
 

### 2015-12-26 experiment/experiment.tex
minor update

@@
 
-Let $G=(V,E=\{e_1,...,e_L\})$ be the topology representation of an ISP network, $G$ is then symmetric by it's definition. 
+Let $G=(V,E=\{e_1,...,e_L\})$ be the topology representation of an ISP network. $G$ is symmetric by it's definition. 
 Considering the scinario where a package is sent from its source node to its destination, it's returned back to the source after trying to bypass an edge with high latency.
@@
 and define the latency is high iff it's greater than a constant tolerance value $\tau$.
-We formulate the network routing as an contextual combinatorial cascading problem.
+We formulate the network routing problem as an contextual combinatorial cascading problem.
 
@@
 the agent have to choose an superarm from $$S=\{A=(e_{k_1},...,e_{k_n}):e_{k_j}\in E, e_{k_1},...,e_{k_n} \text{is a simple path of } G \text{ from } u_t \text{ to } v_t\},$$
-with the expected payoffs (opt out discount) $$E[r_A]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta_{\ast}^{\top}x_{k(A)_i,t}))),$$
-where $n(A)$ and $k(A)_i$ is the amount of arms in superarm $A$, and the index of the $i$-th arm, separately.
-The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{Z\in S}\sum_{1\leq i\leq n(Z)}\hat{\theta}^{\top}x_{k(Z)_i,t}.$$
-We have then $$E[r_{A_t}]/\min_{A\in S}E[r_A]\geq \alpha(\tau, G) = (1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|},$$
-which shows that we can realize the $\alpha(\tau, G)$-approximation oracle using shortest path algorithm.
+with the expected payoffs (opt out discount) $$E[r_A|\theta]=\Pi_{1\leq i\leq n(A)}(1-\exp(-\tau/(1-\theta^{\top}x_{k(A)_i,t}))),$$
+where $n(A)$ and $k(A)_i$ are the amount of arms in superarm $A$, and the index of the $i$-th arm, separately.
+The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{A\in S}\sum_{1\leq i\leq n(A)}\hat{\theta}^{\top}x_{k(A)_i,t}.$$
+For $A\in S$, denote $\hat{\mu}(A)_i=1-\hat{\theta}^{\top}x_{k(A_t)_i,t},$ we have then 
+\begin{align*}
+  E[r_{A_t}|\hat{\theta}]/E[r_A|\hat{\theta}] &= \frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
+  &\geq \min_{0\leq \sigma \leq n(A), \sum_i \hat{\mu}(A_t)_i=\sum_i \hat{\mu}(A)_i=\sigma}\frac{\Pi_{1\leq i\leq n(A_t)}(1-e^{-\tau/\hat{\mu}(A_t)_i})}{\Pi_{1\leq i\leq n(A)}(1-e^{-\tau/\hat{\mu}(A)_i})}\\
+  &\geq \min_{0\leq \sigma \leq n(A)}\frac{(1-e^{-\tau})^\sigma}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
+  &\geq \min_{0\leq \sigma \leq n(A)}\frac{1-e^{-\tau/\sigma}}{(1-e^{-\tau n(A)/\sigma})^{n(A)}}\\
+  &\geq 1-e^{-\tau/n(A)}/(1-e^{-\tau})^{n(A)}\\
+  &\geq (1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}.\\
+\end{align*}
+Let $\alpha(\tau, G)=(1-e^{-\tau/|V|})/(1-e^{-\tau})^{|V|}$, the above inequality shows that we can realize the $\alpha(\tau, G)$-approximation oracle using shortest path algorithm.
 After the agent chooses the shortest path as the superarm, the reward and the first ever edge with high latency, if any, is feedbacked.
@@
 
-An example output, with $T=10000$, is listed below.
+Example results, with $T=10000$ and $T=30000$ seperately, are listed on Table~\ref{movielens} and Table~\ref{isp}.
 
@@
 	\caption{\textbf{Cumulative reward w.r.t different baselines, under Movielens setting.}}
-	\label{daily}
+	\label{movielens}
+\end{table}
+
+\begin{table}
+    \centering
+    \renewcommand{\arraystretch}{1.2}
+	\begin{tabular}{lc}
+	    \toprule
+		\textbf{Algorithm}  &\textbf{Cumulative Reward $\sum_{t=1}^Tr_i $}\\
+		\midrule
+		Li		    &7676.54 \\
+		Qin		    &7165.70 \\
+		Monkey		    &5428.52 \\
+		Kveton		    &5468.97 \\
+		Perfect Play		    &N/A \\
+		\bottomrule
+	\end{tabular}
+	\caption{\textbf{Cumulative reward w.r.t different baselines, under ISP routing setting.}}
+	\label{isp}
 \end{table}

### 2015-12-26 experiment/utils.py

@@ -31,4 +31,4 @@ class ucb_settings:
         self.__dict__ = s
         
     def __str__(self):
-        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A', 'oracle', 'theta']])
+        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A', 'G', 'oracle', 'theta']])

### 2016-01-07 contextual combinatorial cascading bandits.tex
update lower bound(not helpful to our results) and one paragraph of introduction

@@
 \section{Introduction}
+
+The cascade model is popular to describe user behavior in recommendation systems.
+When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
+The items before the selected one are not attractive and the items after the selected one are unobserved.
+Also in networking routing problem, if we want to check whether a path is unblocked, we can just stop checking if an blocked edge appears.
+The cascade model is useful to describe such kind of partial-observation problem.
+In both recommendation and network routing problem, historical information will usually help to provide more effective choices.
 
@@
   \xymatrix{
-  	S_0 \ar[r]^{0.8} \ar[d]_{0.9} & B \ar[dr]^{0.8} &\\
-  	C \ar[r]_{0.8} & D \ar[r]_{0.7} &S_1
+  	S_0 \ar[r]^{\mu_{11}} \ar[d]_{\mu_{21}} & B_1 \ar[d]^{\mu_{12}} &\\
+  	B_2 \ar[r]_{\mu_{22}} & S_1
   }
 $$
-There are two paths in this graph: $A_1 = \{S_0 \to B \to S_1\}$ and $A_2 = \{S_0 \to C \to D \to S_1\}$. 
-Let the feasible action set be $\cS = \{A_1, A_2\}.$ The numbers on the edges denote the probability of that edge being unblocked. 
-For example, the probability of $C \to D$ being unblocked is $0.8$. 
+There are two paths in this graph: $A_1 = \{S_0 \to B_1 \to S_1\}$ and $A_2 = \{S_0 \to B_2 \to S_1\}$. 
+Let the feasible action set be $\cS = \{A_1, A_2\}.$ The $\mu$'s on the edges denote the probability of that edge being unblocked. 
+For example, the probability of $S_0 \to B_2$ being unblocked is $\mu_3$. 
 When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
-So the optimal action is $A_1$ with expected reward $0.64$ and $A_2$ is suboptimal with expected reward $0.504$.
+Suppose we have $\mu_3 \geq \mu_1 \geq \mu_1\mu_2 > \mu_3 \mu_4$.
+So the optimal action is $A_1$ with expected reward $\mu_1 \mu_2$ and $A_2$ is suboptimal with expected reward $\mu_3 \mu_4$.
 
-Next we analyze those times when the learning agent selects path $A_2$ instead of the optimal $A_1$. 
-Notice that if the observed edges are $S_0 \to C \to D$ or $S_0 \to C$, we will not abandon $A_2$ because the expected rewards are $0.9 \times 0.8$ and $0.9$, higher than $0.64$. 
-Only the times when all edges in $A_2$ being observed will help to recognize $A_2$ and abandon it. 
-Recall that the probability of all edges of $A_2$ being observed is $p_{A_2} = 0.9 \times 0.8 = 0.72.$ 
-So we have
+Similar to the proof of Lai and Robbins 1985, we could get
 $$
-  \EE[N_{A_2}]p_{A_2} \leq \frac{c \log(T)}{\Delta^2},
+	\EE[N_{A_2}]\mu_{21} \leq \frac{c \log(T)}{kl(\mu_{22}, \frac{\mu_{11}\mu_{12}}{\mu_{21}})}
 $$
-where $N_{A_2}$ is the number of times that learning agent selects $A_2$ and $\Delta$ is the difference of the best expected reward minus the expected reward of $A_2$.
-Therefore,
-$$
-  \EE[N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta^2}
-$$
-and
-$$
-  R(T) \leq \EE[\Delta N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta}.
-$$
+
+%Next we analyze those times when the learning agent selects path $A_2$ instead of the optimal $A_1$. 
+%Notice that if the observed edges are $S_0 \to C \to D$ or $S_0 \to C$, we will not abandon $A_2$ because the expected rewards are $0.9 \times 0.8$ and $0.9$, higher than $0.64$. 
+%Only the times when all edges in $A_2$ being observed will help to recognize $A_2$ and abandon it. 
+%Recall that the probability of all edges of $A_2$ being observed is $p_{A_2} = 0.9 \times 0.8 = 0.72.$ 
+%So we have
+% $$
+%   \EE[N_{A_2}]p_{A_2} \leq \frac{c \log(T)}{\Delta^2},
+% $$
+%where $N_{A_2}$ is the number of times that learning agent selects $A_2$ and $\Delta$ is the difference of the best expected reward minus the expected reward of $A_2$.
+%Therefore,
+% $$
+%   \EE[N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta^2}
+% $$
+% and
+% $$
+%   R(T) \leq \EE[\Delta N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta}.
+% $$
 

### 2016-01-07 experiment/flowtest.py
add sort parameter

@@ -62,12 +62,13 @@ def flowtest_isp(T, kw):
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 #kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':True}
-#kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
-#flowtest_monkey(T=3000, kw=kw)
+kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'sort': False, 'disj':False}
+flowtest_monkey(T=3000, kw=kw)
 
 #kw = {'L':90, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'disj':True}
 #flowtest_movielens(T=1000, kw=kw)
 
-kw = {'isp':1221, 'd':10, 'h':0.35, 'tlc':1, 'gamma':0.95, 'disj':False}
-flowtest_isp(T=3000, kw=kw)
+#kw = {'isp':1221, 'd':15, 'h':0.35, 'tlc':0.8, 'gamma':0.95, 'disj':False}
+#flowtest_isp(T=30000, kw=kw)
+
 logfile.close()

### 2016-01-07 experiment/movielens.py

@@ -21,7 +21,7 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, sort=False, disj=False):
     cox = []
     coy = []
     history = {}
@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
     logger.info(s)
     return s

### 2016-01-07 experiment/flowtest.py
minor

@@ -62,11 +62,11 @@ def flowtest_isp(T, kw):
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 #kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':True}
-kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'sort': False, 'disj':False}
-flowtest_monkey(T=3000, kw=kw)
+#kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'sort': False, 'disj':False}
+#flowtest_monkey(T=3000, kw=kw)
 
-#kw = {'L':90, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'disj':True}
-#flowtest_movielens(T=1000, kw=kw)
+kw = {'L':90, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'sort': False, 'disj':True}
+flowtest_movielens(T=1000, kw=kw)
 
 #kw = {'isp':1221, 'd':15, 'h':0.35, 'tlc':0.8, 'gamma':0.95, 'disj':False}
 #flowtest_isp(T=30000, kw=kw)

### 2016-01-07 experiment/agent.py
add absolute gamma; add rgamma

@@ -35,6 +35,22 @@ def absolute_cascading_ucb(e, s, T):
     logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
     return score, 0
 
+def absolute_cascading_gammaucb(e, s, T):
+    score = [0]
+    W = {arm: 0.5 for arm in s.arms}
+    b = {arm: 1 for arm in s.arms}
+    for t in range(1, T):
+        _, params = e()
+        U = {arm: W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
+        recc = s.oracle(U, *params)
+        r, c = e(recc)
+        for k in range(min(len(recc), c+1)):
+            W[recc[k]] = (s.rgamma ** (2*k) * (b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
+            b[recc[k]] += s.rgamma ** k
+        score.append(score[-1] + r)
+    logger.info('Absolute(Gamma) play score {0}/{1}'.format(score[-1], T))
+    return score, 0
+
 def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
     assert s.cascade
     theta = np.zeros(s.d)
@@ -50,9 +66,9 @@ def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
         recc = s.oracle(U, *params)
         r, c = e(recc)
-        V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
-        X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
-        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(len(recc), c+1))])
+        V += sum([s.rgamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
+        X = np.concatenate([X] + [s.rgamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
[…]

### 2016-01-07 experiment/environment.py

@@ -14,12 +14,12 @@ from utils import ucb_settings
 from isp import isp_oracle
 from isp import reachable
 
-def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, sort=False, disj=False):
+def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, rgamma=0.95, eps=0.1, v=0.35, sort=False, disj=False):
     arms = list(range(L))
     x = {arm: np.random.uniform(0, 1, d) for arm in arms}
     theta = h * uni(np.random.uniform(0, 1, d))
     logger.info('Initializing random settings "Contextual Monkey" complete')
-    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, sort=sort, disj=disj)
+    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, rgamma=rgamma, eps=eps, v=v, sort=sort, disj=disj)
     logger.info(s)
     return s
 
@@ -39,7 +39,7 @@ def contextual_monkey(s, cascade):
             r, c = reward(ctr, s.gamma, s.disj)
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual Monkey" complete')
-    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=s.gamma, disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
+    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=s.gamma, rgamma=s.rgamma, disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
 
 def contextual_movielens(s, cascade):
     logger.info('Initializing environment "Contextual Movielens"')
@@ -56,7 +56,7 @@ def contextual_movielens(s, cascade):
             r, c = reward(ctr, s.gamma, s.disj)
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual Movielens" done')
-    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d ** 2, gamma=s.gamma, disj=s.disj, cascade=cascade, oracle=argmax_oracle)
[…]

### 2016-01-07 experiment/flowtest.py

@@ -21,6 +21,7 @@ from agent import contextual_cascading_monkey
 from agent import contextual_full_monkey
 from agent import contextual_full_lijing
 from agent import absolute_cascading_ucb
+from agent import absolute_cascading_gammaucb
 from environment import contextual_monkey_rng
 from environment import contextual_monkey
 from movielens import contextual_movielens_rng
@@ -37,6 +38,7 @@ def flowtest_monkey(T, kw):
     exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True), T=T)
     exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False), T=T)
     exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True), T=T)
+    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 def flowtest_movielens(T, kw):
@@ -62,11 +64,11 @@ def flowtest_isp(T, kw):
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 #kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':True}
-#kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'sort': False, 'disj':False}
-#flowtest_monkey(T=3000, kw=kw)
+kw = {'L':20, 'd':10, 'h':0.75, 'K':4, 'gamma':0.95, 'rgamma':0.95, 'eps':0.1, 'v':0.35, 'sort': False, 'disj':False}
+flowtest_monkey(T=3000, kw=kw)
 
-kw = {'L':90, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'sort': False, 'disj':True}
-flowtest_movielens(T=1000, kw=kw)
[…]

### 2016-01-07 experiment/movielens.py

@@ -21,7 +21,7 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, sort=False, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, rgamma=0.95, sort=False, disj=False):
     cox = []
     coy = []
     history = {}
@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, rgamma=rgamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
     logger.info(s)
     return s

### 2016-01-07 contextual combinatorial cascading bandits.tex

@@
 
-The cascade model is popular to describe user behavior in recommendation systems.
+The cascade model is popular to describe user behaviors in recommendation systems.
 When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
 The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, if we want to check whether a path is unblocked, we can just stop checking if an blocked edge appears.
+Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge.
 The cascade model is useful to describe such kind of partial-observation problem.
-In both recommendation and network routing problem, historical information will usually help to provide more effective choices.
+
+Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need.
+Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user.
+Usually, both users and content are represented by feature sets.
+User features may contain basic attributes, like age, gender and nationality, and historical behaviors.
+Content features may contain categories and descriptive information.
+Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.
 

### 2016-01-07 experiment/agent.py
removed rgamma for rng; add rgamma for env, meaning if env tells gamma to agent

@@ -45,8 +45,8 @@ def absolute_cascading_gammaucb(e, s, T):
         recc = s.oracle(U, *params)
         r, c = e(recc)
         for k in range(min(len(recc), c+1)):
-            W[recc[k]] = (s.rgamma ** (2*k) * (b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
-            b[recc[k]] += s.rgamma ** k
+            W[recc[k]] = (s.gamma ** (2*k) * (b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
+            b[recc[k]] += s.gamma ** k
         score.append(score[-1] + r)
     logger.info('Absolute(Gamma) play score {0}/{1}'.format(score[-1], T))
     return score, 0
@@ -66,9 +66,9 @@ def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
         recc = s.oracle(U, *params)
         r, c = e(recc)
-        V += sum([s.rgamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
-        X = np.concatenate([X] + [s.rgamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
-        Y = np.concatenate([Y] + [s.rgamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(len(recc), c+1))])
+        V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
+        X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
+        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(len(recc), c+1))])
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.linalg.slogdet(V)[1] - ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)

### 2016-01-07 experiment/environment.py

@@ -14,19 +14,19 @@ from utils import ucb_settings
 from isp import isp_oracle
 from isp import reachable
 
-def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, rgamma=0.95, eps=0.1, v=0.35, sort=False, disj=False):
+def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, sort=False, disj=False):
     arms = list(range(L))
     x = {arm: np.random.uniform(0, 1, d) for arm in arms}
     theta = h * uni(np.random.uniform(0, 1, d))
     logger.info('Initializing random settings "Contextual Monkey" complete')
-    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, rgamma=rgamma, eps=eps, v=v, sort=sort, disj=disj)
+    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, sort=sort, disj=disj)
     logger.info(s)
     return s
 
 def argmax_oracle(U, K, sort):
     return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])[::2*sort-1]]
 
-def contextual_monkey(s, cascade):
+def contextual_monkey(s, cascade, rgamma):
     logger.info('Initializing environment "Contextual Monkey"')
     xt = {arm: s.x[arm] for arm in s.x}
     def environment(recommend=None):
@@ -39,9 +39,9 @@ def contextual_monkey(s, cascade):
             r, c = reward(ctr, s.gamma, s.disj)
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual Monkey" complete')
-    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=s.gamma, rgamma=s.rgamma, disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
+    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
 
-def contextual_movielens(s, cascade):
+def contextual_movielens(s, cascade, rgamma):
     logger.info('Initializing environment "Contextual Movielens"')
[…]

### 2016-01-07 experiment/flowtest.py

@@ -34,11 +34,11 @@ def flowtest_monkey(T, kw):
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_monkey_rng(**kw)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True), T=T)
-    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True), T=T)
-    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False), T=T)
-    exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True), T=T)
-    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True), T=T)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
+    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
+    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=True), T=T)
+    exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
+    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 def flowtest_movielens(T, kw):
@@ -46,10 +46,10 @@ def flowtest_movielens(T, kw):
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_movielens_rng(**kw)
-    exploit1, explore1 = contextual_cascading_monkey(*contextual_movielens(s, cascade=True), T=T)
-    exploit2, explore2 = contextual_cascading_sherry(*contextual_movielens(s, cascade=True), T=T)
[…]

### 2016-01-07 experiment/movielens.py

@@ -21,7 +21,7 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, rgamma=0.95, sort=False, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, sort=False, disj=False):
     cox = []
     coy = []
     history = {}
@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, rgamma=rgamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
     logger.info(s)
     return s

### 2016-01-07 experiment/environment.py
removed sort in rng; add sort in monkey and movielens env params

@@ -14,26 +14,26 @@ from utils import ucb_settings
 from isp import isp_oracle
 from isp import reachable
 
-def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, sort=False, disj=False):
+def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
     arms = list(range(L))
     x = {arm: np.random.uniform(0, 1, d) for arm in arms}
     theta = h * uni(np.random.uniform(0, 1, d))
     logger.info('Initializing random settings "Contextual Monkey" complete')
-    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, sort=sort, disj=disj)
+    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, disj=disj)
     logger.info(s)
     return s
 
 def argmax_oracle(U, K, sort):
     return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])[::2*sort-1]]
 
-def contextual_monkey(s, cascade, rgamma):
+def contextual_monkey(s, cascade, rgamma, sort):
     logger.info('Initializing environment "Contextual Monkey"')
     xt = {arm: s.x[arm] for arm in s.x}
     def environment(recommend=None):
         if recommend == None:
             for arm in s.x:
                 xt[arm] = uni(s.x[arm] + np.random.uniform(-s.v, s.v, s.d))
-            return xt, (s.K, s.sort)
+            return xt, (s.K, sort)
         else:
             ctr = [np.random.uniform(0, 1) < s.theta.dot(xt[arm]) + np.random.normal(0, s.eps) for arm in recommend]
             r, c = reward(ctr, s.gamma, s.disj)
@@ -41,7 +41,7 @@ def contextual_monkey(s, cascade, rgamma):
     logger.info('Initializing environment "Contextual Monkey" complete')
     return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
 
-def contextual_movielens(s, cascade, rgamma):
+def contextual_movielens(s, cascade, rgamma, sort):
[…]

### 2016-01-07 experiment/flowtest.py

@@ -34,11 +34,11 @@ def flowtest_monkey(T, kw):
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_monkey_rng(**kw)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
-    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
-    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=True), T=T)
-    exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
-    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True, rgamma=True), T=T)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=True, sort=False), T=T)
+    exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
 def flowtest_movielens(T, kw):
@@ -46,10 +46,10 @@ def flowtest_movielens(T, kw):
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_movielens_rng(**kw)
-    exploit1, explore1 = contextual_cascading_monkey(*contextual_movielens(s, cascade=True, rgamma=True), T=T)
[…]

### 2016-01-07 experiment/movielens.py

@@ -21,7 +21,7 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, sort=False, disj=False):
+def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, disj=False):
     cox = []
     coy = []
     history = {}
@@ -56,6 +56,6 @@ def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95,
     selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
     eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
     logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, sort=sort, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
+    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
     logger.info(s)
     return s

### 2016-01-07 experiment/environment.py
modify

@@ -56,7 +56,7 @@ def contextual_movielens(s, cascade, rgamma, sort):
             r, c = reward(ctr, s.gamma, s.disj)
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual Movielens" done')
-    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d ** 2, gamma=1-rgamma*(1-s.gamma), runtimegamma=s.runtimegamma, disj=s.disj, cascade=cascade, oracle=argmax_oracle)
+    return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d ** 2, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=argmax_oracle)
 
 def contextual_isp(s, cascade, rgamma):
     logger.info('Initializing environment "Contextual ISP"')

### 2016-01-07 experiment/flowtest.py

@@ -35,22 +35,30 @@ def flowtest_monkey(T, kw):
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_monkey_rng(**kw)
     exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit3, explore3 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=True, sort=False), T=T)
-    exploit4, explore4 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit5, explore5 = absolute_cascading_gammaucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=False, sort=False), T=T)
+    exploit3, explore3 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=False, sort=True), T=T)
+    # exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit4, explore4 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=False, sort=False), T=T)
+    exploit5, explore5 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit6, explore6 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=False, sort=False), T=T)
+    exploit7, explore7 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=False, sort=True), T=T)
[…]

### 2016-01-07 experiment/movielens.py

@@ -13,8 +13,8 @@ from utils import ucb_settings
 from utils import overlap
 
 def movielens_data():
-    fpr = open('movielens/ratings.csv')
-    fpt = open('movielens/tags.csv')
+    fpr = open('movielens/ratings.csv', encoding='utf-8')
+    fpt = open('movielens/tags.csv', encoding='utf-8')
     gr = csv.reader(fpr, delimiter=',', quotechar='"')
     gt = csv.reader(fpt, delimiter=',', quotechar='"')
     gr.__next__()

### 2016-01-08 experiment/environment.py
env now logs its parameters

@@ -27,7 +27,7 @@ def argmax_oracle(U, K, sort):
     return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])[::2*sort-1]]
 
 def contextual_monkey(s, cascade, rgamma, sort):
-    logger.info('Initializing environment "Contextual Monkey"')
+    logger.info('Initializing environment "Contextual Monkey"| cascade:{0} rgamma:{1} sort:{2}'.format(cascade, rgamma, sort))
     xt = {arm: s.x[arm] for arm in s.x}
     def environment(recommend=None):
         if recommend == None:
@@ -42,7 +42,7 @@ def contextual_monkey(s, cascade, rgamma, sort):
     return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=argmax_oracle, theta=s.theta)
 
 def contextual_movielens(s, cascade, rgamma, sort):
-    logger.info('Initializing environment "Contextual Movielens"')
+    logger.info('Initializing environment "Contextual Movielens"| cascade:{0} rgamma:{1} sort:{2}'.format(cascade, rgamma, sort))
     user = random.sample(s.users, 1)
     def environment(recommend=None):
         if recommend is None:
@@ -59,7 +59,7 @@ def contextual_movielens(s, cascade, rgamma, sort):
     return environment, ucb_settings(arms=s.arms, L=s.L, d=s.d ** 2, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=argmax_oracle)
 
 def contextual_isp(s, cascade, rgamma):
-    logger.info('Initializing environment "Contextual ISP"')
+    logger.info('Initializing environment "Contextual ISP"| cascade:{0} rgamma:{1}'.format(cascade, rgamma))
     p = random.sample(s.G.nodes(), 2)
     xt = {arm: s.x[arm] for arm in s.x}
     def environment(recommend=None):

### 2016-01-08 contextual combinatorial cascading bandits.tex
modify
update a result

@@
 
+Combinatorial multi-armed bandit(MAB) problem has been studied extensively in statistics and machine learning.
+
 The cascade model is popular to describe user behaviors in recommendation systems.
@@
 Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.
+
+Stochastic online learning with combinatorial actions has been studies with semi-bandit feedback \cite{chen2013combinatorial}.
 
@@
 % $$
+
+\section{Experiments}
+
+\section{Conclusions}
+
+In this paper, we propose contextual combinatorial cascading bandits, a class of contextual combinatorial bandits with partial observations.
 

### 2016-01-08 experiment/flowtest.py

@@ -55,10 +55,12 @@ def flowtest_movielens(T, kw):
     exploit2, explore2 = contextual_cascading_sherry(*contextual_movielens(s, cascade=True, rgamma=False, sort=False), T=T)
     exploit3, explore3 = contextual_cascading_sherry(*contextual_movielens(s, cascade=True, rgamma=False, sort=True), T=T)
     # exploit2, explore2 = contextual_cascading_monkey(*contextual_movielens(s, cascade=True, rgamma=True, sort=False), T=T)
-    # exploit3, explore3 = contextual_full_lijing(*contextual_movielens(s, cascade=False, rgamma=True, sort=False), T=T)
-    # exploit4, explore4 = absolute_cascading_ucb(*contextual_movielens(s, cascade=True, rgamma=True, sort=False), T=T)
-    # plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'b--', range(T), exploit3, 'g--')
+    exploit4, explore4 = contextual_full_lijing(*contextual_movielens(s, cascade=False, rgamma=False, sort=False), T=T)
+    exploit5, explore5 = absolute_cascading_ucb(*contextual_movielens(s, cascade=True, rgamma=True, sort=False), T=T)
+    exploit6, explore6 = absolute_cascading_ucb(*contextual_movielens(s, cascade=True, rgamma=False, sort=False), T=T)
+    exploit7, explore7 = absolute_cascading_ucb(*contextual_movielens(s, cascade=True, rgamma=False, sort=True), T=T)
+    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'b--', range(T), exploit3, 'g--', range(T), exploit4, 'b--', range(T), exploit5, 'y--', range(T), exploit6, 'k--', range(T), exploit7, 'm--')
+    #plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'b--', range(T), exploit3, 'g--')
 
 def flowtest_isp(T, kw):
     logger.info('ISP flowtest')
@@ -76,8 +78,8 @@ def flowtest_isp(T, kw):
 # flowtest_monkey(T=3000, kw=kw)
 
 
[…]

### 2016-01-08 contextual combinatorial cascading bandits.tex
update introduction and reference

@@
 
-Combinatorial multi-armed bandit(MAB) problem has been studied extensively in statistics and machine learning.
-
-The cascade model is popular to describe user behaviors in recommendation systems.
-When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
-The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge.
-The cascade model is useful to describe such kind of partial-observation problem.
+A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the according reward.
+When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.
 
@@
 Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.
+
+In real applications, the cascade model is popular to describe user behaviors in recommendation systems.
+When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
+The items before the selected one are not attractive and the items after the selected one are unobserved.
+Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge.
+The cascade model is useful to describe such kind of partial-observation problem.
 

### 2016-01-08 experiment/experiment.tex
fixed minor exp doc

@@
 The agent finds $A_t$ by running shortest path algorithm on $G$ with weight $\hat{\theta}^{\top}x_{k_i,t}$ assigned to $e_i$, which yields $$A_t=\argmin_{A\in S}\sum_{1\leq i\leq n(A)}\hat{\theta}^{\top}x_{k(A)_i,t}.$$
-For $A\in S$, denote $\hat{\mu}(A)_i=1-\hat{\theta}^{\top}x_{k(A_t)_i,t},$ we have then 
+For $A\in S$, denote $\hat{\mu}(A)_i=1-\hat{\theta}^{\top}x_{k(A)_i,t},$ we have then 
 \begin{align*}

### 2016-01-08 experiment/agent.py
removed obselete gammaucb; ucb now respect gamma

@@ -29,26 +29,10 @@ def absolute_cascading_ucb(e, s, T):
         recc = s.oracle(U, *params)
         r, c = e(recc)
         for k in range(min(len(recc), c+1)):
-            W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
-            b[recc[k]] += 1
-        score.append(score[-1] + r)
-    logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
-    return score, 0
-
-def absolute_cascading_gammaucb(e, s, T):
-    score = [0]
-    W = {arm: 0.5 for arm in s.arms}
-    b = {arm: 1 for arm in s.arms}
-    for t in range(1, T):
-        _, params = e()
-        U = {arm: W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
-        recc = s.oracle(U, *params)
-        r, c = e(recc)
-        for k in range(min(len(recc), c+1)):
-            W[recc[k]] = (s.gamma ** (2*k) * (b[recc[k]]) * W[recc[k]] + ((k == c) == s.disj)) / (b[recc[k]] + 1)
+            W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + s.gamma ** k * ((k == c) == s.disj)) / (b[recc[k]] + s.gamma ** k)
             b[recc[k]] += s.gamma ** k
         score.append(score[-1] + r)
-    logger.info('Absolute(Gamma) play score {0}/{1}'.format(score[-1], T))
+    logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
     return score, 0
 
 def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
@@ -94,7 +78,7 @@ def contextual_full_lijing(e, s, T, delta=0.9, lamb=0.1):
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
         recc = s.oracle(U, *params)
         r, ctr = e(recc)
-        V += sum([np.outer(x[recc[k]], x[recc[k]]) for k in range(len(recc))])
+        V += sum([(s.gamma)**(2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(len(recc))])
[…]

### 2016-01-08 experiment/flowtest.py

@@ -21,7 +21,6 @@ from agent import contextual_cascading_monkey
 from agent import contextual_full_monkey
 from agent import contextual_full_lijing
 from agent import absolute_cascading_ucb
-from agent import absolute_cascading_gammaucb
 from environment import contextual_monkey_rng
 from environment import contextual_monkey
 from movielens import contextual_movielens_rng
@@ -73,15 +72,15 @@ def flowtest_isp(T, kw):
     exploit4, explore4 = absolute_cascading_ucb(*contextual_isp(s, cascade=True, rgamma=True), T=T)
     plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
 
-# kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.9, 'eps':0.1, 'v':0.35, 'disj':True}
-# kw = {'L':100, 'd':10, 'h':0.75, 'K':10, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
-# flowtest_monkey(T=3000, kw=kw)
+#kw = {'L':20, 'd':10, 'h':0.35, 'K':4, 'gamma':0.9, 'eps':0.1, 'v':0.35, 'disj':True}
+#kw = {'L':100, 'd':10, 'h':0.75, 'K':10, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
+#flowtest_monkey(T=3000, kw=kw)
 
 
-kw = {'L':100, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'disj':True}
-flowtest_movielens(T=1000, kw=kw)
+#kw = {'L':100, 'portion':0.2, 'd':5, 'K':4, 'h':60, 'gamma':0.95, 'disj':True}
+#flowtest_movielens(T=1000, kw=kw)
 
-#kw = {'isp':1221, 'd':15, 'h':0.35, 'tlc':0.8, 'gamma':0.95, 'disj':False}
-#flowtest_isp(T=30000, kw=kw)
+kw = {'isp':1221, 'd':15, 'h':0.35, 'tlc':0.8, 'gamma':0.95, 'disj':False}
+flowtest_isp(T=3000, kw=kw)
 plt.show()
 logfile.close()

### 2016-01-09 contextual combinatorial cascading bandits.tex
update introduction

@@
 Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user.
-Usually, both users and content are represented by feature sets.
+Usually, both users and content are represented by feature vectors.
 User features may contain basic attributes, like age, gender and nationality, and historical behaviors.
@@
 
-In real applications, the cascade model is popular to describe user behaviors in recommendation systems.
+In real applications, the cascade model is popular to describe user behaviors in recommender systems.
 When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
 The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge.
-The cascade model is useful to describe such kind of partial-observation problem.
+Also in networking routing problem, to determine whether a path is blocked, we check from the source to the end and can stop when meeting a blocked edge without need of knowing states of every edge in the path.
+In both of the two applications, we the feedback of items before some threshold, which is that user selects one item in recommender system and meeting a blocked edge in network routing.
+We call this kind of feedback as {\it cascading feedback}.
 
-Stochastic online learning with combinatorial actions has been studies with semi-bandit feedback \cite{chen2013combinatorial}.
+Motivated by the above challenges, we develop an approach called {\it contextual combinatorial cascading bandits}.
+This is a general framework which can describe many applications besides the above two applications.
+
+The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{T})$ for $T$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
+
+%Stochastic online learning with combinatorial actions has been studied with semi-bandit feedback \cite{chen2013combinatorial}.
 

### 2016-01-09 experiment/flowtest.py

@@ -66,11 +66,39 @@ def flowtest_isp(T, kw):
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_isp_rng(**kw)
-    exploit1, explore1 = contextual_cascading_monkey(*contextual_isp(s, cascade=True, rgamma=True), T=T)
-    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T)
-    exploit3, explore3 = contextual_full_lijing(*contextual_isp(s, cascade=False, rgamma=True), T=T)
+    #exploit1, explore1 = contextual_cascading_monkey(*contextual_isp(s, cascade=True, rgamma=True), T=T)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T)
+    exploit3, explore3 = contextual_full_lijing(*contextual_isp(s, cascade=False, rgamma=False), T=T)
     exploit4, explore4 = absolute_cascading_ucb(*contextual_isp(s, cascade=True, rgamma=True), T=T)
-    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
+    exploit5, explore5 = absolute_cascading_ucb(*contextual_isp(s, cascade=True, rgamma=False), T=T)
+    # plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'r--', range(T), exploit3, 'b--', range(T), exploit4, 'b--')
+    plt.plot(range(T), exploit1, 'r--', range(T), exploit2, 'b--', range(T), exploit3, 'g--', range(T), exploit4, 'k--', range(T), exploit5, 'y--')
+    file_object = open('exploit1.txt', 'w')
+    file_object.writelines(str(exploit1))
+    # for i in range(len(exploit1))
+    #     file_object.writelines(str(exploit1[i]))
+    file_object.close()
+    file_object = open('exploit2.txt', 'w')
+    file_object.writelines(str(exploit2))
+    # for i in range(len(exploit2))
[…]

### 2016-01-11 contextual combinatorial cascading bandits.tex
update related work

@@
 
-Our work generalizes both the cascading bandits of \cite{kveton2015cascading} and combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount.
-In cascading bandits of \cite{kveton2015cascading}, the feasible set contains any list of $K$ items out of $L$ ground items.
-Our work generalizes the feasible set to be any set of lists of at most $K$ items, like \cite{kveton2015combinatorial}.
-In both \cite{kveton2015cascading} and \cite{kveton2015combinatorial}, even though they define the feasible actions as lists, they regard them as sets.
-The order of a feasible action does not affect the regret bound, which might have problem in real application, especially for recommendations.
+Our work generalizes combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount.
+Our generalization expands the applicability of this model and we evaluate it on two real-world problems.
+\cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid.
+They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs.
+To improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
+Our work extends this part by introducing position discounted parameters.
+Under our setting, the items with higher UCB will come first.
+\cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only.
+In our setting, users and items are represented by feature vectors which is more general.
 
-In \cite{kveton2015cascading}, they found that recommending items in chosen action in increasing order of their UCBs has better performance than in decreasing order of their UCBs.
-This result might conflict with recommendations in real world.
-To improve the quality of user experience, we usually list items with higher preference first and then lower preference items.
-Our work extends this part by introducing position discounted parameters.
-Under our setting, the items with higher preference will come first.
+Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
+\cite{li2010contextual} studied multi-armed bandit with context information.
+\cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+Their setting is more informative than ours but our algorithm is competitive to theirs.
+
+Our problem is a combinatorial partial monitoring problem where the learning agent may observe part of chosen items.
+\cite{agrawal1989asymptotically,bartok2012adaptive} studied partial monitoring problems but their algorithm is inefficient in our setting.
+\cite{lin2014combinatorial} studied combinatorial partial monitoring problem and their feedback is a fixed (with respect to chosen action) combination of weights.
+If chosen action is fixed, the combination of the weights to constitute feedback is not fixed in our setting.
+
+A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit
 

### 2016-01-13 contextual combinatorial cascading bandits.tex
update experiment structure
update experiment -network

@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{epstopdf}
+%\usepackage{epsfig}
+%\usepackage{times}
+%\usepackage{helvet}
+%\usepackage{courier}
+%\usepackage{graphicx,subfigure}
+%\usepackage{pdfpages}
+%\usepackage{multirow}
+%\usepackage{multicol}
 
@@
 
+We evaluate $C^3$-UCB in three experiments.
+
+\subsection{Synthetic}
+
+\subsection{MovieLens}
+
+\subsection{Network Routing}
+
+In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.
+
+The ground set $E$ is the set of links in the network and the feasible action set $\cS$ is the set of all paths in the network.
+Before learning, the environment randomly chooses a $d$-dimensional vector $\theta \in [0,1]^d$.
+At each time $t$, any link $e$ is assigned with a random $d$-dimensional context vector $x_{t,e}$ and the corresponding latency follows exponential distribution with mean $1-\theta^{\top}x$, which has been scaled into $[0,1]$.
+We call the latency is {\it high} if it is larger than a threshold $\tau$.
+A pair of source and terminal nodes $(v_s, v_t)$ are chosen randomly.
+The agent recommends a feasible path $A = (a_1,...,a_{|A|})$ from $v_s$ to $v_t$ with expected reward
+$$
+\prod_{k=1}^{|A|} (1- \exp(-\frac{\tau}{1-\theta^{\top}x_{t,a_k}})).
+$$
+Notice that the expression is not of the form $\prod_{k=1}^{|A|}\theta_*^{\top}x_{t,a_k}$ in our model. However, our algorithm could also apply to it.
+
+\begin{figure}
+	\centering
+	\subfigure[Network 1755]{
+		\includegraphics[height = 1.8cm, width = 2.6 cm]{network3-1.eps}}
+	\subfigure[Network ]{
+		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
+	\subfigure[Network]{
+		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
+	\caption{sample number and accuracy}
+	\label{fig:sample number} % 用于交叉引用
+\end{figure}
+
 \section{Conclusions}

### 2016-01-14 contextual combinatorial cascading bandits.tex
update experiment

@@
 \newcommand{\cA}{\mathcal{A}}
+\newcommand{\cB}{\mathcal{B}}
 \newcommand{\cH}{\mathcal{H}}
@@
 
+In the first experiment, we compare $C^3$-UCB to $C^2$UCB and CombCascade on two synthetic problems. chiao tsing path
+
+Let $\cB = \{x \in \RR^d : \|x\|_2 = 1 \}$ be the unit ball of $\RR^d$ and let $E = \{1,...,L\}$ be the set of all base arms.
+We randomly choose $\theta_{\ast}$ with $\|\theta_{\ast}\|_2 = 1$ and randomly assign a $\mu_i \in \cB$ to $i$ for any $i \in E$.
+At each time $t$, $b_{t,i} \in \cB$ is randomly assigned to base arm $i$.
+Also we fix a constant $h$ to balance weights of $\mu_i$ and disturbance $b_{t,i}$.
+Let $x_{t,i} = \frac{\mu_i + h b_{t,i}}{\|\mu_i+h\cdot b_{t,i}\|_2}$ be the context of base arm $i$ at time $t$.
+And the weight for base arm $i$ at time $t$ is $w_t(i) = \theta_{\ast}^{\top}x_{t,i} + \epsilon_{t,i}$ where $\epsilon_{t,i} \sim N(\mu_i, \sigma_i)$ for fixed $\sigma_i$.
+
 \subsection{MovieLens}
+
+In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of March 2015.
+
+The Learning problem is formulated as follows.
+There is a big sparse matrix $A \in \{0,1\}^{N_u \times N_m}$ where $A(u,m) = 1$ denotes user $u$ has watched movie $m$.We split $A$ to be $H + F$ by putting entry-$1$ of $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We can regard $H$ as know information about history 'What users have watched' and regard $F$ as future criterion.
+We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = USV^{\top}$ where $U = (u_1; ...;u_M)$ and $V = (v_1;...;v_L)$.
+At every time $t$, use $x_{t,i} = u_{i}v_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
+And use $w_t(j) = F(I_t,j)$ as the weight of base arm $j$.
+
+Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
+Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.
+
+\begin{figure}
+	\centering
+	\subfigure[MovieLens]{
+		\includegraphics[height = 3cm, width = 5 cm]{movie-1.eps}}
+	\caption{MovieLens}
+	\label{fig:movielens} % 用于交叉引用
+\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
+	\subfigure[Network 1221]{
+		\includegraphics[height = 3 cm, width = 5 cm]{network1-1.eps}}
 	\subfigure[Network 1755]{
-		\includegraphics[height = 1.8cm, width = 2.6 cm]{network3-1.eps}}
-	\subfigure[Network ]{
-		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
-	\subfigure[Network]{
-		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
-	\caption{sample number and accuracy}
+		\includegraphics[height = 3 cm, width = 5 cm]{network3-1.eps}}
+	\subfigure[Network 3257 ]{
+		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
+	\caption{Network with latency}
 	\label{fig:sample number} % 用于交叉引用
-\end{figure}
+\end{figure*}
 

### 2016-01-14 experiment/flowtest.py
all theta.dot(x) now range from -1~1 instad of 0~1; isp now use pass/loss binary instead of latency; add squni and scat rng;

@@ -109,6 +109,6 @@ def flowtest_isp(T, kw):
 #flowtest_movielens(T=1000, kw=kw)
 
 kw = {'isp':1239, 'd':15, 'h':0.35, 'tlc':0.8, 'gamma':0.95, 'disj':False}
-flowtest_isp(T=10000, kw=kw)
+flowtest_isp(T=500, kw=kw)
 plt.show()
 logfile.close()

### 2016-01-14 experiment/utils.py

@@ -1,16 +1,43 @@
+import random
+
+from scipy.linalg import sqrtm
 import numpy as np
 import colorama
 colorama.init()
 
 def red(s):
-    return(colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE)
+    return colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE
+
+def pendium():
+    return np.random.uniform(-1, 1)
 
 def uni(x):
     return x/np.sqrt(x.dot(x))
 
 def suni(d):
-    x = np.abs(np.random.normal(0, 1, d))
+    x = np.random.normal(0, 1, d)
     return uni(x)
+
+def scat(d):
+    e = uni(np.ones(d))
+    x = [abs(suni(d)) for _ in range(int(15**(np.sqrt(d))))]
+    x = [v for v in x if np.random.uniform() < v.dot(e)]
+    v = random.sample(x, 1)[0]
+    return v / v.sum()
+
+def squni(d, linear=1):
+    Z = np.random.uniform(0, 1, (d, d))
+    V = Z.dot(np.linalg.inv(sqrtm(Z.T.dot(Z))))
+    theta = suni(d)
+    theta *= 1.145 * linear
+    lamb = suni(d)
+    alpha = lamb + V.dot(theta)
+    if all(alpha > 0) or all(alpha < 0):
+        return squni(d, linear)
+    theta /= np.abs(alpha).max()
+    lamb /= np.abs(alpha).max()
+    Q = V.dot(np.diagflat(lamb)).dot(V.T)
+    return theta, Q, lamb, V
 
 def disturb(x, h):
     y = x + h * np.random.normal(0, 1, x.shape)
@@ -23,12 +50,16 @@ def reward(ctr, gamma, disj):
             return int(conj) + gamma ** c * (int(disj) - int(conj)), c
     return int(conj), len(ctr)
 
-def overlap(l1, l2):
-    return len(set(l1) & l2)
-
 class ucb_settings:
     def __init__(self, **s):
         self.__dict__ = s
-        
+
     def __str__(self):
         return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A', 'G', 'oracle', 'theta']])
+
+if __name__ == '__main__':
+    theta, Q, lamb, V = squni(5)
+    for _ in range(10000):
[…]

### 2016-01-15 contextual combinatorial cascading bandits.tex
update experiment

--- 2016-01-13 contextual combinatorial cascading bandits.tex
@@
 
+In the first experiment, we compare $C^3$-UCB to $C^2$UCB and CombCascade on synthetic problems.
+This problem is a contextual cascading bandit with $L=20$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
+At first, we randomly choose $\theta_* \in \RR^d$ with $\|\theta_{\ast}\|_2 = 1$.
+Then at each time $t$, we randomly assign $x_{t,a} \in \RR^d$ with $\theta_*^{\top}x_{t,a} \in [0,1]$ to arm $a$.
+And the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experiment on four settings and report our results in Figure \ref{fig:synthetic}.
+The first experiment is with disjunctive objective and $\gamma=1$ and the second is also with disjunctive objective but with $\gamma=0.95$.
+The third experiment is conducted with conjunctive objective and $\gamma=1$.
+The fourth experiment is using network 1755 structure.
+The algorithm $C^2$UCB has semi-bandit feedback and our algorithm has only cascading feedback.
+However from the results, our performance is competitive to their's.
+The $CombCascade$ algorithm does not make use of contextual information, so it is not as good as the other two algorithms.
+
+\begin{figure*}
+	\centering
+	\subfigure[Disjunctive, $\gamma=1$]{
+		\includegraphics[height = 3 cm, width = 5 cm]{synD-1.eps}}
+	\subfigure[Disjunctive, $\gamma=0.95$]{
+		\includegraphics[height = 3 cm, width = 5 cm]{synD-95.eps}}
+	\subfigure[Network 3257 ]{
+		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
+	\subfigure[Conjunctive, network 1755, $\gamma=1$ ]{
+		\includegraphics[height = 3 cm, width = 5 cm]{network3B-1.eps}}
+	\caption{Synthetic Data Set, L=20, K=4}
+	\label{fig:synthetic} % 用于交叉引用
+\end{figure*}
+
 \subsection{MovieLens}
+
+In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of March 2015.
+
+The Learning problem is formulated as follows.
+There is a big sparse matrix $A \in \{0,1\}^{N_u \times N_m}$ where $A(u,m) = 1$ denotes user $u$ has watched movie $m$.
+We split $A$ to be $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
+We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = VSZ^{\top}$ where $V = (v_1; ...;v_{N_u})$ and $Z = (z_1;...;z_{N_m})$.
+At every time $t$, use $x_{t,i} = v_{i}z_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $u_t$.
+And use $w_t(m) = F(u_t,m)$ as the weight of movie $m$.
+
+Notice that
+
+Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
+Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.
+
+\begin{figure*}
+	\centering
+	\subfigure[MovieLens]{
+		\includegraphics[height = 3cm, width = 5 cm]{movie-1.eps}}
+	\caption{MovieLens}
+	\label{fig:movielens} % 用于交叉引用
+\end{figure*}
 

### 2016-01-15 contextual combinatorial cascading bandits.tex

@@
 	\subfigure[Disjunctive, $\gamma=1$]{
-		\includegraphics[height = 3 cm, width = 5 cm]{synD-1.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-1.eps}}
 	\subfigure[Disjunctive, $\gamma=0.95$]{
-		\includegraphics[height = 3 cm, width = 5 cm]{synD-95.eps}}
-	\subfigure[Network 3257 ]{
-		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-95.eps}}
+	\subfigure[Conjunctive, $\gamma=1$ ]{
+		\includegraphics[height = 3 cm, width = 4 cm]{synC-1.eps}}
 	\subfigure[Conjunctive, network 1755, $\gamma=1$ ]{
-		\includegraphics[height = 3 cm, width = 5 cm]{network3B-1.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{network3B-1.eps}}
 	\caption{Synthetic Data Set, L=20, K=4}

### 2016-01-15 contextual combinatorial cascading bandits.tex
add two paragraphs for problem formulation in general case

@@
 
+\section{Problem Formulation-general case}
+
+We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
+Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}.
+Let $\cS$ be the set of \textit{feasible actions}.
+For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$.
+In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning.
+In social influence problem, a feasible action is a subset of people in graph structure.
+In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set.
+We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$.
+We assume all feasible actions considered in this paper have size at most $K$.
+
+As a convention, we always use boldface symbols to represent random variables.
+
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
+\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm.
+\shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
+Notice that the size of the action is not fixed.
+Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of base arms in $\bO_t \subset \bA_t$.
+For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.
+
+We use random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$.
+Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
+Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
+Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
+\begin{equation} % eq:expectation
+	\label{eq:expectation}
+	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
+\end{equation}
+where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+
+We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
+$$
+\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
+$$
+or 
+$$
+\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
+$$
+At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
+
+The agent receives some reward if the user clicks on some item.
+Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
+Usually the importance of the positions is decreasing: the first position is most important.
+So it is a reasonable assumption that
+$$
+1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
+$$
+At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+$$
+\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
+$$
+where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
+
+Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
+\begin{align}
+&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
+&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
+\label{eq:functionf}
+\end{align}
+Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+\begin{align*}
+A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
+\end{align*}
+The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+$$
+R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
+$$
+where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.
+
+The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+Similarly, we could also consider the case of conjunctive objective. 
+We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
+The learning agent observes all items until the first one with weight $0$. 
+Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
+The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
+$$
+0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
+$$
+At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
+\begin{align*}
+\br_{\wedge, t} &= \begin{cases}
+\gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
+1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
+\end{cases}\\
+&=\begin{cases}
+\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
+1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
+\end{cases}
+\end{align*}
+
+If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
+\begin{align}
+&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
+&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+\label{eq:functionfstar}
+\end{align}
+then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
+To simplify notations, we assume
+$$
+\gamma_k' = 1 - \gamma_k.
+$$
+Then it holds that
+\begin{equation} %eq:ConDisRelation
+\label{eq:ConDisRelation}
+f_{\wedge}(A, w) = 1 - f(A, 1 - w).
+\end{equation}
+Let 
+\begin{align*}
+A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
+\end{align*}
+For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+$$
+R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
+$$
+where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
+
 \section{Algorithms and Results}

### 2016-01-16 contextual combinatorial cascading bandits.tex
update two requirements for general reward

@@
 We assume all feasible actions considered in this paper have size at most $K$.
+In many of applications, the expected reward of an action relates not only the underlying set but also the structure, or the order of the base arms.
+For example in recommender systems, to improve user experience, the items with higher preference will be listed higher.
 
@@
 
-We use random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$.
+We use random variable $\bw_{t}(a) \in [0,1]$ as the {\em weight} of base arm $a$ at time $t$.
 Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
@@
 \begin{equation} % eq:expectation
-	\label{eq:expectation}
+	% \label{eq:expectation}
 	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
@@
 
-We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
-$$
-\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
-$$
-or 
-$$
-\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
-$$
-At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
-Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
-
-The agent receives some reward if the user clicks on some item.
+The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.
+
+Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
+
+Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$.
+In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
+$$
+	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
+$$
+
+We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $O(A, w)$.
+
+% We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
+% $$
+% \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
+% $$
+% or 
+% $$
+% \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
+% $$
+% At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
+% Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
+
+% The agent receives some reward if the user clicks on some item.
 Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
@@
 So it is a reasonable assumption that
-$$
-1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
-$$
-At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
-$$
-\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
-$$
-where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
-
-Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
-\begin{align}
-&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
-&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
-\label{eq:functionf}
-\end{align}
-Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
-\begin{align*}
-A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
-f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
-\end{align*}
-The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
-$$
-R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
-$$
-where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.
-
-The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
-Similarly, we could also consider the case of conjunctive objective. 
-We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
-The learning agent observes all items until the first one with weight $0$. 
-Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
-The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
-$$
-0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
-$$
-At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
-\begin{align*}
-\br_{\wedge, t} &= \begin{cases}
-\gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
-1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
-\end{cases}\\
-&=\begin{cases}
-\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
-1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
-\end{cases}
-\end{align*}
-
-If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
-\begin{align}
-&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
-&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
-\label{eq:functionfstar}
-\end{align}
-then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
+% $$
+% 1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
+% $$
+% At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+% $$
+% \br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
+% $$
+% where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
+
+% Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
+% \begin{align}
+% &f : \cS \times [0,1]^E \to [0,1] \nonumber \\
+% &f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
+% \label{eq:functionf}
+% \end{align}
+% Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
+% \begin{align*}
+% A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+% f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
+% \end{align*}
+% The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+% $$
+% R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
+% $$
+% where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.
+
+% The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+% Similarly, we could also consider the case of conjunctive objective. 
+% We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
+% The learning agent observes all items until the first one with weight $0$. 
+% Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
+% The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
+% $$
+% 0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
+% $$
+% At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
+% \begin{align*}
+% \br_{\wedge, t} &= \begin{cases}
+% \gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
+% 1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
+% \end{cases}\\
+% &=\begin{cases}
+% \gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
+% 1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
+% \end{cases}
+% \end{align*}
+
+% If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
+% \begin{align}
+% &f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
+% &f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+% \label{eq:functionfstar}
+% \end{align}
+% then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
 To simplify notations, we assume
-$$
-\gamma_k' = 1 - \gamma_k.
-$$
-Then it holds that
-\begin{equation} %eq:ConDisRelation
-\label{eq:ConDisRelation}
-f_{\wedge}(A, w) = 1 - f(A, 1 - w).
-\end{equation}
-Let 
-\begin{align*}
-A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
-f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
-\end{align*}
-For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
-$$
-R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
-$$
-where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
+% $$
+% \gamma_k' = 1 - \gamma_k.
+% $$
+% Then it holds that
+% \begin{equation} %eq:ConDisRelation
+% \label{eq:ConDisRelation}
+% f_{\wedge}(A, w) = 1 - f(A, 1 - w).
+% \end{equation}
+% Let 
+% \begin{align*}
+% A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
+% f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
+% \end{align*}
+% For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
+% $$
+% R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
+% $$
+% where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
 

### 2016-01-17 contextual combinatorial cascading bandits.tex
update problem formulation-general case

--- 2016-01-15 contextual combinatorial cascading bandits.tex
@@
 \newcommand{\cH}{\mathcal{H}}
+\newcommand{\cO}{\mathcal{O}}
 \newcommand{\cS}{\mathcal{S}}
@@
 
+\section{Problem Formulation-general case}
+
+We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
+Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}.
+Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
+We call each of such tuples an {\em action} of length $k$.
+We will use $|A|$ to denote the length of an action $A$.
+Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
+
+As a convention, we always use boldface symbols to represent random variables.
+
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
+\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm.
+\shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed.
+Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$.
+For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.
+
+Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
+Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
+Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
+\begin{equation} % eq:expectation
+  % \label{eq:expectation}
+  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
+\end{equation}
+where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+
+We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$.
+At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$.
+We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
+
+We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.
+
+The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.
+
+Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
+
+Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$.
+In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
+$$
+	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
+$$
+
+We don't require the agent knows how the function $f(A, w)$ is defined.
+We only assume the agent has access to an oracle $\cO(A, w)$.
+More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).
+
+The $\alpha$-regret on time $t$ can be written as
+$$
+R_t = \alpha opt_{w_t} - f(w_t, A_t).
+$$
+Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.
+
 \section{Algorithms and Results}
@@
       \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
-      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
+      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
       \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}

### 2016-01-18 experiment/agent.py
isp sherry/gamma test

@@ -35,8 +35,9 @@ def absolute_cascading_ucb(e, s, T):
     logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
     return score, 0
 
-def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
+def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1, gamma=0):
     assert s.cascade
+    gamma = s.gamma if not gamma else gamma
     theta = np.zeros(s.d)
     beta = 0
     V = lamb * np.eye(s.d)
@@ -46,20 +47,21 @@ def contextual_cascading_sherry(e, s, T, delta=0.9, lamb=0.1):
     score = [0]
     timestamp = time.time()
     for t in range(1, T):
+        #print('Turn No.{0}'.format(t))
         x, params = e()
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
-        recc = s.oracle(U, *params)
+        recc = s.oracle(U, *params[:-1], gamma)
         r, c = e(recc)
-        V += sum([s.gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
-        X = np.concatenate([X] + [s.gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
-        Y = np.concatenate([Y] + [s.gamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(len(recc), c+1))])
+        V += sum([gamma ** (2*k) * np.outer(x[recc[k]], x[recc[k]]) for k in range(min(len(recc), c+1))])
+        X = np.concatenate([X] + [gamma ** k * x[recc[k]].reshape(1, s.d) for k in range(min(len(recc), c+1))])
+        Y = np.concatenate([Y] + [gamma ** k * ((k == c) == s.disj) * np.ones(1) for k in range(min(len(recc), c+1))])
         theta = np.linalg.inv(X.T.dot(X) + lamb * np.eye(s.d)).dot(X.T.dot(Y))
         beta = np.sqrt(np.linalg.slogdet(V)[1] - ldV - 2 * np.log(delta)) + np.sqrt(lamb)
         score.append(score[-1] + r)
         #logger.debug(r)
-        if t % 500 == 0:
[…]

### 2016-01-18 experiment/environment.py

@@ -14,6 +14,7 @@ from utils import reward
 from utils import ucb_settings
 
 from isp import isp_oracle
+from isp import isp_Coracle
 from isp import reachable
 
 def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
@@ -71,11 +72,11 @@ def contextual_isp(s, cascade, rgamma):
                 return environment()
             for arm in s.x:
                 xt[arm] = disturb(s.x[arm], s.h)
-            return xt, (s.G, p[0], p[1])
+            return xt, (s.G, p[0], p[1], s.gamma)
         else:
             #ctr = [s.tlc > np.random.exponential(1 - s.theta.dot(xt[arm])) for arm in recommend]
             ctr = [pendium() < s.theta.dot(xt[arm]) for arm in recommend]
             r, c = reward(ctr, s.gamma, s.disj)
             return (r, c) if cascade else (r, [int(click) for click in ctr])
     logger.info('Initializing environment "Contextual ISP" done')
-    return environment, ucb_settings(arms=s.G.edges(), L=len(s.G.edges()), d=s.d, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=isp_oracle, theta=s.theta)
+    return environment, ucb_settings(arms=s.G.edges(), L=len(s.G.edges()), d=s.d, gamma=1-rgamma*(1-s.gamma), disj=s.disj, cascade=cascade, oracle=isp_Coracle, theta=s.theta)

### 2016-01-18 experiment/flowtest.py

@@ -67,8 +67,17 @@ def flowtest_isp(T, kw):
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = contextual_isp_rng(**kw)
     #exploit1, explore1 = contextual_cascading_monkey(*contextual_isp(s, cascade=True, rgamma=True), T=T)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T)
-    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=1)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=0.98)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=0.96)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=0.94)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=0.92)
+    exploit1, explore1 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=True), T=T, gamma=0.9)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T, gamma=0.88)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T, gamma=0.86)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T, gamma=0.84)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T, gamma=0.82)
+    exploit2, explore2 = contextual_cascading_sherry(*contextual_isp(s, cascade=True, rgamma=False), T=T, gamma=0.80)
[…]

### 2016-01-18 experiment/isp.py

@@ -1,3 +1,5 @@
+from functools import reduce
+from itertools import islice
 import logging
 logger = logging.getLogger('ISP')
 
@@ -9,11 +11,21 @@ from utils import suni
 def reachable(G, u, v):
     return networkx.has_path(G, u, v)
 
-def isp_oracle(U, G, u, v):
+def isp_oracle(U, G, u, v, gamma):
     for (x, y), z in U.items():
         G[x][y]['weight'] = max(1 - z, 0)
     path = networkx.shortest_path(G, u, v, weight='weight')
     return [tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1)]
+
+def isp_Coracle(U, G, u, v, gamma):
+    for (x, y), z in U.items():
+        G[x][y]['weight'] = max(1 - z, 0)
+    s = {}
+    for path in islice(networkx.shortest_simple_paths(G, u, v), 40):
+        sarms = tuple(tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1))
+        psarms = [(U[e] + 1) / 2 for e in sarms]
+        s[sarms] = sum([(1 - gamma**i) * reduce(float.__mul__, [1.,] + psarms[:i-1]) * (1 - psarms[i]) for i in range(len(psarms))]) + reduce(float.__mul__, psarms)
+    return list(max(s, key=s.get))
 
 def isp_data(isp):
     assert isp in {1221,1239,1755,2914,3257,3356,3967,4755,6461,7018}
@@ -30,7 +42,7 @@ def isp_net(g):
 def contextual_isp_rng(isp=1221, d=10, h=0.35, tlc=1, gamma=0.95, disj=False):
     G = isp_net(isp_data(isp))
     x = {e: suni(d) for e in G.edges()}
-    theta = suni(d)
+    theta = 1.2 * suni(d)
     logger.info('Initializing random settings "ISP" complete')
     s = ucb_settings(L=len(G.edges()), d=d, h=h, gamma=gamma, disj=disj, G=G, tlc=tlc, x=x, theta=theta)
     logger.info(s)

### 2016-01-18 experiment/utils.py

@@ -25,17 +25,13 @@ def scat(d):
     v = random.sample(x, 1)[0]
     return v / v.sum()
 
-def squni(d, linear=1):
-    Z = np.random.uniform(0, 1, (d, d))
+def squni(d, linear=0.6):
+    Z = np.random.uniform(-1, 1, (d, d))
     V = Z.dot(np.linalg.inv(sqrtm(Z.T.dot(Z))))
     theta = suni(d)
-    theta *= 1.145 * linear
+    theta *= linear / np.abs(V.dot(theta)).max()
     lamb = suni(d)
-    alpha = lamb + V.dot(theta)
-    if all(alpha > 0) or all(alpha < 0):
-        return squni(d, linear)
-    theta /= np.abs(alpha).max()
-    lamb /= np.abs(alpha).max()
+    lamb *= (1 - linear) / np.abs(lamb).max()
     Q = V.dot(np.diagflat(lamb)).dot(V.T)
     return theta, Q, lamb, V
 

### 2016-01-18 contextual combinatorial cascading bandits.tex

--- 2016-01-16 contextual combinatorial cascading bandits.tex
@@
 %\usepackage{multicol}
-
 \newcommand{\bbeta}{\boldsymbol{\beta}}
@@
 
-\section{Problem Formulation}
-
-We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. 
-Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}. 
-Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. 
-We call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$.
-Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
-
-As a convention, we always use boldface symbols to represent random variables.
-
-At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
+% and / or case	
+% \section{Problem Formulation}
+
+% We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. 
+% Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}. 
+% Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. 
+% We call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$.
+% Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
+
+% As a convention, we always use boldface symbols to represent random variables.
+
+% At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
 \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to a user, where notice that the length of the action is not fixed.
@@
 
-Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
-\begin{equation} % eq:expectation
-  \label{eq:expectation}
-  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
-\end{equation}
-where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
-We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
-$$
-  \bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
-$$
-or 
-$$
-  \bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
-$$
-At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
-Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
-
-The agent receives some reward if the user clicks on some item.
-Suppose we consider the position discount: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
-Usually the importance of the positions is decreasing: the first position is most important.
-So it is a reasonable assumption that
-$$
-  1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
-$$
-At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
-$$
-  \br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
-$$
-where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
-
-Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
-\begin{align}
-  &f : \cS \times [0,1]^E \to [0,1] \nonumber \\
-  &f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
-  \label{eq:functionf}
-\end{align}
-Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
-\begin{align*}
-  A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
-  f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
-\end{align*}
-The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
-$$
-  R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
-$$
-where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.
-
-The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
-Similarly, we could also consider the case of conjunctive objective. 
-We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). 
-The learning agent observes all items until the first one with weight $0$. 
-Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$.
-The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
-$$
-  0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
-$$
-At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward $\br_{\wedge, t}$:
-\begin{align*}
-  \br_{\wedge, t} &= \begin{cases}
-    \gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
-    1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
-  \end{cases}\\
-  &=\begin{cases}
-    \gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
-    1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
-  \end{cases}
-\end{align*}
-
-If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
-\begin{align}
-  &f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
-  &f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
-  \label{eq:functionfstar}
-\end{align}
-then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
-To simplify notations, we assume
-$$
-  \gamma_k' = 1 - \gamma_k.
-$$
-Then it holds that
-\begin{equation} %eq:ConDisRelation
-  \label{eq:ConDisRelation}
-  f_{\wedge}(A, w) = 1 - f(A, 1 - w).
-\end{equation}
-Let 
-\begin{align*}
-  A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
-  f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
-\end{align*}
-For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
-$$
-  R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
-$$
-where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.
-
-\section{Problem Formulation-general case}
-
-We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
-Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}.
-Let $\cS$ be the set of \textit{feasible actions}.
-For any feasible action $A \in \cS$, $A$ has an underlying set, which is a subset of $E$, together with a structure $s_A$.
-In website recommender systems, a feasible action $A$ is a set of $K$ websites listed in linear order and the user, faced with such a website list, will check the website one by one from the beginning.
-In social influence problem, a feasible action is a subset of people in graph structure.
-In the rest of the paper, we abuse the notation of $A$ to denote the feasible action and also the corresponding underlying set.
-We define the {\it size} of feasible action $A$ to be the number of base arms in the underlying set of $A$, denoted by $|A|$.
-We assume all feasible actions considered in this paper have size at most $K$.
-In many of applications, the expected reward of an action relates not only the underlying set but also the structure, or the order of the base arms.
-For example in recommender systems, to improve user experience, the items with higher preference will be listed higher.
-
-As a convention, we always use boldface symbols to represent random variables.
-
-At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
-\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm.
-\shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
-Notice that the size of the action is not fixed.
-Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of base arms in $\bO_t \subset \bA_t$.
-For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.
-
-We use random variable $\bw_{t}(a) \in [0,1]$ as the {\em weight} of base arm $a$ at time $t$.
-Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
-Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
-\begin{equation} % eq:expectation
+% Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
+% Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
+% \begin{equation} % eq:expectation
 %   \label{eq:expectation}
-	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
-\end{equation}
-where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
-
-The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.
-
-Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
-
-Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$.
-In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
-$$
-	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
-$$
-
-We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $O(A, w)$.
-
+%   \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
+% \end{equation}
+% where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
 % We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
@@
 
+\section{Problem Formulation-general case}
+
+We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
+Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}.
+Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
+We call each of such tuples an {\em action} of length $k$.
+We will use $|A|$ to denote the length of an action $A$.
+Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.
+
+As a convention, we always use boldface symbols to represent random variables.
+
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
+\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm.
+\shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed.
+Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$.
+For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.
+
+Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
+Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
+Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
+\begin{equation} % eq:expectation
+  \label{eq:expectation}
+  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
+\end{equation}
+where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+
+We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$.
+At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$.
+We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
+
+We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.
+
+The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.
+
+Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
+
+Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$.
+In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
+$$
+	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
+$$
+
+We don't require the agent knows how the function $f(A, w)$ is defined.
+We only assume the agent has access to an oracle $\cO(A, w)$.
+More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).
+
+The $\alpha$-regret on time $t$ can be written as
+$$
+R_t = \alpha opt_{w_t} - f(w_t, A_t).
+$$
+Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.
+
 \section{Algorithms and Results}
@@
 For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
-In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
+%In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
 
@@
 
-\begin{theorem}[\cite{abbasi2011improved}] %estimate of theta
+\begin{lemma} $\mathrm{\cite{abbasi2011improved}}$ %estimate of theta
   \label{thm:theta_estimate}
@@
   \end{equation}
-\end{theorem}
+\end{lemma}
 
@@
 
-The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
+The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
 \begin{lemma} %estimate of U
@@
   $$
-    0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
   $$
@@
 \begin{proof}
+	$w_{t, a} = \theta_*^{\top} x_{t,a}$. First by Holder's inequality,
 	\begin{align*}
@@
 		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+	\end{align*}
+	Then
+	\begin{align*}
+		\bU_t(a) - w_{t,a} &\leq \hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_{\ast}^{\top}x_{t,a} \\
+		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
+	\end{align*}
+	and 
+	\begin{align*}
+		&\bU_t(a) - w_{t,a} \\
+		&\qquad \geq \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_*^{\top} x_{t,a}, 1 - \theta_*^{\top} x_{t,a}  \} \\
+		&\qquad \geq 0		
 	\end{align*}
@@
 Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$.
-Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
-$$
-  \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
-$$ 
-or
-$$
-  \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
-$$
+Third, she checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm.
+% Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
+% $$
+%   \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
+% $$ 
+% or
+% $$
+%   \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
+% $$
 Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. 
@@
   \begin{algorithmic}[1]
-    \STATE {//Initialization}
-    \STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
-    \STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
-    \STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
+  	\STATE {Parameters:}
+  	\STATE {\qquad $\gamma_k\in[0,1], k \leq K; \delta > 0; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
+  	\STATE {Initialization:}
+    \STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
 
@@
       \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
-      \STATE {//Compute UCBs}
-      \STATE {$\forall a\in E: $}
-      \STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
+      \STATE {$\forall a\in E$, compute}
+      \STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
 
       \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
-      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
-      \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
-      \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
+      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
+      \STATE {Play $\bA_t$ and observe $\bO_t； \bw_t(\ba_k^t), k\in[\bO_t]$}
 
@@
 
-To state our main theorem, we need some definitions. Let
-$$
-  f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
-$$
-denote the best expected reward of all time under the conjunctive objective.
-Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
-\begin{align*}
-  &p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
-  &p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
-\end{align*}
-We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective.
-The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
+To state our main theorem, we need some definitions.
+Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ will be observed at time $t$.
+Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time.
+The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.
+
 \begin{theorem} %main theorem
 	\label{thm:main}
-  Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$. 
-  Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
-  Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
+	Suppose the expected reward function, with parameters $\gamma_k, k\leq K$, is a function of expected weights of base arms and satisfies the requirements stated in section 3.
+Assume there is an $\alpha$-approximation oracle $\cO$.
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
 	\begin{align}
@@
 		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-    &=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right),
+		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
 	\end{align}
+\end{theorem}
+\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
+	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. In particular,
+	\begin{align*}
+    	&\EE[R(t, \bA_t)|\cH_t] \\
+    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
+    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
+    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
+    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
+    \end{align*}
+    Also, by monotonicity and Lipschitz continuity,
+    $$
+    	R(t, \bA_t) \leq C \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
+    $$
+
+	our analysis to that of CombCascade in \cite{kveton2015combinatorial}.
+This reduction is challenging for two reasons.
+First, our setting has contextual information.
+Second, we consider position-discounted weight $\gamma$.
+
+	Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items.
+Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
+	\begin{align*}
+    	&\EE[R(t, \bA_t)|\cH_t] \\
+    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
+    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
+    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
+    \end{align*}
+    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
+
+\end{proof}
+
+In the special case of single-choice-recommendations, the learning agent recommends a list of items to the user.
+Then the user checks from the first item and stops if she finds one interesting or has checked all items.
+Suppose we also consider position discount here.
+If the user interests in the $k$-th item, then the learning agent will receive reward $\gamma_k$.
+It is easy to check that in this case, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$.
+And if the parameters satisfy $1\geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$, then $f$ satisfies the requirements.
+(We leave all these verifications in appendix.) In this case, $p(t,A) p^* = $ Then we have
+\begin{corollary}
+	In the problem of single-choice-recommendations, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$.
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
+	\begin{align}
+		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
+	\end{align}
+\end{corollary}
+
+This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.
+
+  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
+  \begin{lemma}
+    \CLemmaPrefixExi
+  \end{lemma}
+  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
+  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
+  \begin{lemma}
+  	\CLemmaIncre
+  \end{lemma}
+  \begin{lemma}
+  	\CLemmaTech
+  \end{lemma}
+  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
+  \begin{lemma}
+  	\CLemmaSumXiEstimateInDet
+  \end{lemma}
+  \begin{lemma}
+  	\CLemmaDetVt
+  \end{lemma}
+  Then we can use a mean inequality to derive the result.
+
+In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small.
+So we have the following improvements.
+Suppose we also consider position discount here.
+\begin{theorem} %main theorem
+	\label{thm:conjunctive}
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4} f_{\wedge}^{\ast}$. 
+	Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
+	Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
 	\begin{align}
@@
 
-\wei{I hided some paragraphs trying to explain the proof here.
-	We will re-write a proof outline after revising the proofs.}
-
-\begin{proof} %proof outline of main theorem
-  The proof is in Appendix. 
-  The main idea is to reduce our analysis to that of CombCascade in \cite{kveton2015combinatorial}. 
-  This reduction is challenging for two reasons. 
-  First, our setting has contextual information. 
-  Second, we consider position-discounted weight $\gamma$.
-
-  Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items. 
-  Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
-  \begin{align*}
-    &\EE[R(t, \bA_t)|\cH_t] \\
-    &\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
-    &\EE_t[R_{\wedge}(t, \bA_t)] \\
-    &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
-  \end{align*}
-  and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
-This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.
-
-  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
-  \begin{lemma}
-    \CLemmaPrefixExi
-  \end{lemma}
-  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
-  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
-  \begin{lemma}
-  	\CLemmaIncre
-  \end{lemma}
-  \begin{lemma}
-  	\CLemmaTech
-  \end{lemma}
-  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
-  \begin{lemma}
-  	\CLemmaSumXiEstimateInDet
-  \end{lemma}
-  \begin{lemma}
-  	\CLemmaDetVt
-  \end{lemma}
-  Then we can use a mean inequality to derive the result.
-\end{proof}
-
-\subsection{Lower Bounds}
-
-Suppose we have such a graph: 
-$$
-  \xymatrix{
-  	S_0 \ar[r]^{\mu_{11}} \ar[d]_{\mu_{21}} & B_1 \ar[d]^{\mu_{12}} &\\
-  	B_2 \ar[r]_{\mu_{22}} & S_1
-  }
-$$
-There are two paths in this graph: $A_1 = \{S_0 \to B_1 \to S_1\}$ and $A_2 = \{S_0 \to B_2 \to S_1\}$. 
-Let the feasible action set be $\cS = \{A_1, A_2\}.$ The $\mu$'s on the edges denote the probability of that edge being unblocked. 
-For example, the probability of $S_0 \to B_2$ being unblocked is $\mu_3$. 
-When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
-Suppose we have $\mu_3 \geq \mu_1 \geq \mu_1\mu_2 > \mu_3 \mu_4$.
-So the optimal action is $A_1$ with expected reward $\mu_1 \mu_2$ and $A_2$ is suboptimal with expected reward $\mu_3 \mu_4$.
-
-Similar to the proof of Lai and Robbins 1985, we could get
-$$
-	\EE[N_{A_2}]\mu_{21} \leq \frac{c \log(T)}{kl(\mu_{22}, \frac{\mu_{11}\mu_{12}}{\mu_{21}})}
-$$
+The proof of this theorem is different in the following lemmas.
+
+\subsection{Dissutions}
+
+Our setting generalizes several existing works but not limited to them. Our setting generalizes cascading bandit and combinatorial bandit to involve position discount,
+
+to involve context
+
+there are cases that can not be fit into their
+
+our method generalize Qin's method and has a regret bound proof.
+
+% are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
+
+% To state our main theorem, we need some definitions. Let
+% $$
+%   f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
+% $$
+% denote the best expected reward of all time under the conjunctive objective.
+% Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
+% \begin{align*}
+%   &p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
+%   &p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
+% \end{align*}
+% We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective.
+The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
+% \begin{theorem} %main theorem
+%   \label{thm:main}
+%   Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$. 
+%   Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
+%   Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
+%   \begin{align}
+%     R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
+%     &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+%     &=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right),
+%   \end{align}
+%   \begin{align}
+%     R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
+%     &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+%     &=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
+%   \end{align}
+% \end{theorem}
+
+% \subsection{Lower Bounds}
+
+% Suppose we have such a graph: 
+% $$
+%   \xymatrix{
+%   	S_0 \ar[r]^{\mu_{11}} \ar[d]_{\mu_{21}} & B_1 \ar[d]^{\mu_{12}} &\\
+%   	B_2 \ar[r]_{\mu_{22}} & S_1
+%   }
+% $$
+% There are two paths in this graph: $A_1 = \{S_0 \to B_1 \to S_1\}$ and $A_2 = \{S_0 \to B_2 \to S_1\}$. 
+% Let the feasible action set be $\cS = \{A_1, A_2\}.$ The $\mu$'s on the edges denote the probability of that edge being unblocked. 
+% For example, the probability of $S_0 \to B_2$ being unblocked is $\mu_3$. 
+% When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
+% Suppose we have $\mu_3 \geq \mu_1 \geq \mu_1\mu_2 > \mu_3 \mu_4$.
+% So the optimal action is $A_1$ with expected reward $\mu_1 \mu_2$ and $A_2$ is suboptimal with expected reward $\mu_3 \mu_4$.
+
+% Similar to the proof of Lai and Robbins 1985, we could get
+% $$
+% 	\EE[N_{A_2}]\mu_{21} \leq \frac{c \log(T)}{kl(\mu_{22}, \frac{\mu_{11}\mu_{12}}{\mu_{21}})}
+% $$
 

### 2016-01-18 experiment/utils.py
moved exp readme; add optimal scat func;

@@ -19,6 +19,10 @@ def suni(d):
     return uni(x)
 
 def scat(d):
+    x = np.random.exponential(1, d)
+    return x / x.sum()
+
+def scat1(d):
     e = uni(np.ones(d))
     x = [abs(suni(d)) for _ in range(int(15**(np.sqrt(d))))]
     x = [v for v in x if np.random.uniform() < v.dot(e)]

### 2016-01-18 contextual combinatorial cascading bandits.tex
update proof for 'or'

@@
 }
-\newcommand{\CLemmaIncre}{
-  Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$.
-Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
-  $$
-    f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
-  $$
-}
-\newcommand{\CLemmaTech}{
-  Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
-  \begin{align*}
-    &f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
-    &f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
-  \end{align*}
-  where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
-}
 \newcommand{\CLemmaSumXiEstimateInDet}{
@@
 
-\section{Problem Formulation-general case}
+\section{Problem Formulation}
 
@@
 Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}.
-Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$.
-We call each of such tuples an {\em action} of length $k$.
+Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$; we call each of such tuples an {\em action} of length $k$.
 We will use $|A|$ to denote the length of an action $A$.
@@
 At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
-\shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm.
-\shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed.
-Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$.
-For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.
+For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be the combined feature vector of base arm $a$ at time $t$.
+Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
+Next according to the user behavior and the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$.
+For example in recommender systems, the stopping criterion might be the user finds the first interesting item or has checked all items.
 
 Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$.
+Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$.
 Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.
 
@@
 We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
-Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.
-
-We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.
-
-The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.
-
-Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
-
-Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$.
-In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
-$$
-	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
-$$
-
-We don't require the agent knows how the function $f(A, w)$ is defined.
-We only assume the agent has access to an oracle $\cO(A, w)$.
-More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s) \}_{k\leq \bO_s, s\leq t}$ and $\{x_t\}$, where $x_s = (x_{s,a})_{a \in E}$ denotes all context information at time $s$.
+
+We also consider the position discount $\gamma_k, k\leq K$.
+For example in recommender systems, the positions to display advertisements might have difference prices, hence of different values when user clicks on.
+
+The reward function on round $t$ is an application dependent function.
+We assume the expected reward function of action $A$ is a function of expected weights $w$, denoted by $f(A,w)$, and satisfies the following two assumptions.
+
+\paragraph{Monotonicity}
+The expected reward function $f(A, w)$ is a non-decreasing with respect to $w$. For any $w,w'\in \RR^E$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
+
+\paragraph{Lipschitz continuity}
+The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
+In particular, there is a constant $B>0$ such that, for any $w,w'$, we have
+$$
+	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{k=1}^{|A|} \gamma_k^2(w(a_k) - w'(a_k))^2},
+$$
+where $A = (a_1, \ldots, a_{|A|})$.
+
+Notice that we don't require the knowledge how $f(A, w)$ is defined.
+We only assume the agent has access to an oracle $\cO_{\cS}(w)$.
+More precisely, an oracle $\cO_{\cS}(w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$, the oracle always returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
 
@@
 $$
-R_t = \alpha opt_{w_t} - f(w_t, A_t).
-$$
-Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.
+R_t = \alpha f(A_t^*, w_t) - f(A_t, w_t),
+$$
+where $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R_t$.
 
@@
 For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
-%In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.
-
-Next we build on a good estimate of differences between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.
+Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.
 
@@
 \begin{proof}
-	$w_{t, a} = \theta_*^{\top} x_{t,a}$. First by Holder's inequality,
+	$w_{t,a} = \theta_*^{\top} x_{t,a}$. By Holder's inequality,
 	\begin{align*}
@@
 	\end{align*}
-	Then
-	\begin{align*}
-		\bU_t(a) - w_{t,a} &\leq \hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_{\ast}^{\top}x_{t,a} \\
-		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
-	\end{align*}
-	and 
-	\begin{align*}
-		&\bU_t(a) - w_{t,a} \\
-		&\qquad \geq \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_*^{\top} x_{t,a}, 1 - \theta_*^{\top} x_{t,a}  \} \\
-		&\qquad \geq 0		
-	\end{align*}
+	Then because
+	\begin{align*}
+		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
+		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}
+	\end{align*}
+	and the definition of $\bU_t$ in \ref{lem:estimateU}, we can obtain the result.
 \end{proof}
@@
 Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}.
-First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$.
-Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$.
-Third, she checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm.
-% Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
-% $$
-%   \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
-% $$ 
-% or
-% $$
-%   \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
-% $$
+First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$.
+Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$.
+Third, the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$.
 Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$.
@@
 To state our main theorem, we need some definitions.
-Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ will be observed at time $t$.
+Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$.
 Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time.
@@
 	\label{thm:main}
-	Suppose the expected reward function, with parameters $\gamma_k, k\leq K$, is a function of expected weights of base arms and satisfies the requirements stated in section 3.
-Assume there is an $\alpha$-approximation oracle $\cO$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
+	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity.
+Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$.
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
 	\begin{align}
-		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
+		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
 	\end{align}
@@
     $$
-    	R(t, \bA_t) \leq C \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
-    $$
-
-	our analysis to that of CombCascade in \cite{kveton2015combinatorial}.
+    	R(t, \bA_t) \leq B \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
+    $$
+
+	% our analysis to that of CombCascade in \cite{kveton2015combinatorial}.
 This reduction is challenging for two reasons.
@@
 
-	Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items.
+	% Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items.
 Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
-	\begin{align*}
-    	&\EE[R(t, \bA_t)|\cH_t] \\
-    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
-    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
-    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
-    \end{align*}
-    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
+	% \begin{align*}
+ %    	&\EE[R(t, \bA_t)|\cH_t] \\
+ %    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
+ %    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
+ %    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
+ %    \end{align*}
+ %    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
 
@@
 
-In the special case of single-choice-recommendations, the learning agent recommends a list of items to the user.
-Then the user checks from the first item and stops if she finds one interesting or has checked all items.
-Suppose we also consider position discount here.
-If the user interests in the $k$-th item, then the learning agent will receive reward $\gamma_k$.
-It is easy to check that in this case, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$.
-And if the parameters satisfy $1\geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$, then $f$ satisfies the requirements.
-(We leave all these verifications in appendix.) In this case, $p(t,A) p^* = $ Then we have
+\subsubsection{Disjunctive Objective}
+
+In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order.
+The checking process stops if the user selects one item or has checked all items without selecting anyone.
+In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a}$, is binary to indicate whether the user has clicked on $a$ or not.
+Then the random variable $\bO_t$ satisfies
+$$
+\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
+$$
+or 
+$$
+\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
+$$
+
+The agent receives some reward if the user clicks on some item: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
+Usually the importance of the positions is decreasing: the first position is most important.
+So it is reasonable to assume that
+$$
+1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
+$$
+At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
+$$
+\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
+$$
+where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
+
+Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
+\begin{align}
+&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
+&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
+\end{align}
+Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$.
+So $f$ is the expected reward function and also a function of expected weights.
+It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity.
+(We leave all verifications in the appendix.) Then we have the following corollary.
 \begin{corollary}
-	In the problem of single-choice-recommendations, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
+	\label{cor:or}
+	In the problem of cascading recommendation, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$ where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$.
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
 	\begin{align}
-		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
+		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
 	\end{align}
@@
 
-This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.
-
-  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
-  \begin{lemma}
-    \CLemmaPrefixExi
-  \end{lemma}
-  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
-  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
-  \begin{lemma}
-  	\CLemmaIncre
-  \end{lemma}
-  \begin{lemma}
-  	\CLemmaTech
-  \end{lemma}
-  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
-  \begin{lemma}
-  	\CLemmaSumXiEstimateInDet
-  \end{lemma}
-  \begin{lemma}
-  	\CLemmaDetVt
-  \end{lemma}
-  Then we can use a mean inequality to derive the result.
+\subsubsection{Conjunctive Objective}
+
+The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+Similarly, we could also consider the case of conjunctive objective.
+In this case, we can derive a slightly better result.
+
+We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}.
+The learning agent observes all items until the first one with weight $0$.
+Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
+
+The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
+$$
+1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
+$$
+At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
+\begin{align*}
+	\br_{t} &= \begin{cases}
+		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
+		1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
+	\end{cases}\\
+	&=\begin{cases}
+		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
+		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
+	\end{cases}
+\end{align*}
+
+If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
+\begin{align}
+	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
+	&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+\label{eq:functionfstar}
+\end{align}
+then we have $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
 
@@
 \begin{theorem} %main theorem
-	\label{thm:conjunctive}
+	\label{thm:and}
 	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4} f_{\wedge}^{\ast}$. 
@@
 
+  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
+  \begin{lemma}
+    \CLemmaPrefixExi
+  \end{lemma}
+  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
+  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
+  \begin{lemma}
+  	%\CLemmaIncre
+  \end{lemma}
+  \begin{lemma}
+  	%\CLemmaTech
+  \end{lemma}
+  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
+  \begin{lemma}
+  	\CLemmaSumXiEstimateInDet
+  \end{lemma}
+  \begin{lemma}
+  	\CLemmaDetVt
+  \end{lemma}
+  Then we can use a mean inequality to derive the result.
+
 \subsection{Dissutions}
@@
 our method generalize Qin's method and has a regret bound proof.
+
+network latency
+
+If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$.
+We call the latency is {\it high} if it is larger than a threshold $\tau$.
+A path is blocked if some of its edges has high latency.
+So a path is unblocked with probability
+$$
+\prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
+$$
 
@@
 
-We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
-\begin{lemma} %lem:increasing
-  \label{lem:increasing} 
-  \CLemmaIncre
-\end{lemma}
-\begin{proof}
-  Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
-  \begin{align*}
-  	&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
-  	\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-  	\geq &~\gamma_{k} \cdot 0 = 0.
-  \end{align*}
-  Then it implies that
-  \begin{align*}
-  	&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
-  	\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
-  \end{align*}
-  Therefore, 
-  \begin{align*}
-  	& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
-  	&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
-  	&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-  	&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
-  	&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-  	&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
-  \end{align*}
-  By letting $\gamma_k = 1 - \gamma_k'$ and using the relation in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
-\end{proof}
-
-The following lemma provides the relationship between an estimated mean vector $w$ and its upper bound vector $u$, in terms of their $f$ function values.
-\begin{lemma} %lem:estimateTech
-  \label{lem:estimateTech}
-  \CLemmaTech
-\end{lemma}
-\begin{proof}
-  We prove this by induction. It holds obviously for $m = 1$.
-  \begin{align*}
-  	&~~f(A^{(m+1)}, u)\\
-  	&= f(A^{(m)}, u) + \gamma_{m+1}\prod_{k=1}^m(1 - u_k) u_{m+1}\\
-  	&\leq f(A^{(m)}, u) +  \gamma_{m+1} \prod_{k=1}^m(1 - w_k) (w_{m+1} + r_{m+1})\\
-  	&\leq f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k r_k \\
-  	&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w_k) w_{m+1} + \gamma_{m+1} r_{m+1}\\
-  	&= f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k r_k
-  \end{align*}
-  \begin{align*}
-  	&~~f_{\wedge}(A^{(m+1)}, u) \\
-  	&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
-  	&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{m} u_k) (1 - u_{m+1})+ \prod_{k=1}^{m+1} u_k\\
-  	&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
-  	&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
-  	&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
-  	&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
-  	&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
-  	&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
-  \end{align*}
-\end{proof}
-
 The next lemma provides some properties about a prefix of action $A$ in the conjunctive case, which leads to the finding of a prefix $B$ of $A$ with similar regret and probability of full observation as those of $A$, as given in Lemma~\ref{lem:prefixexists}.
@@
 
+\section{Proof of Corollary~\ref{cor:or}}
+
+In this section, we prove the expected reward function
+$$
+f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
+$$
+defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and Lipschitz continuity.
+
+\begin{lemma}[monotonicity]
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
+Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	$$
+	f(A, w) \leq f(A, w').
+	$$
+\end{lemma}
+\begin{proof}
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
+	\begin{align*}
+		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
+		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		\geq &~\gamma_{k} \cdot 0 = 0.
+	\end{align*}
+	Then it implies that
+	\begin{align*}
+		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
+		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
+	\end{align*}
+	Therefore, 
+	\begin{align*}
+		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
+		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
+	\end{align*}
+\end{proof}
+
+\begin{lemma}[Lipschitz continuity]
+	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
+	$$
+	|f(A, w) - f(A, w')| \leq \sqrt{K}\sqrt{\sum_{k=1}^{|A|} \gamma_k^2 |w(a_k) - w'(a_k)|^2},
+	$$
+	where $A = (a_1, \ldots, a_{|A|})$.
+\end{lemma}
+\begin{proof}
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, suppose $w \leq w'$ and $w' = w + v$.
+
+	We prove this by induction. It holds obviously for $m = 1$. Suppose it holds for $m$. Then
+	\begin{align*}
+		&f(A^{(m+1)}, w')\\
+		=&f(A^{(m)}, w') + \gamma_{m+1}\prod_{k=1}^m(1 - w'(k)) w'(m+1)\\
+		\leq &f(A^{(m)}, w') +  \gamma_{m+1} \prod_{k=1}^m(1 - w(k)) (w(m+1) + v(m+1))\\
+		\leq &f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k v(k) \\
+		&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w(k)) w(m+1) + \gamma_{m+1} v(m+1)\\
+		=& f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k v(k).
+	\end{align*}
+	So it holds for $m+1$.
+
+	For general $w,w' \in [0,1]^L$, by last lemma, we have
+	$$
+	f(A, w\wedge w') \leq f(A, w), f(A, w') \leq f(A, w\vee w'),
+	$$
+	where $(w\wedge w')(k) = \min\{w(k), w'(k)\}$ and $(w\vee w')(k) = \max\{w(k), w'(k)\}$. Then
+	\begin{align*}
+		&|f(A,w) - f(A,w')| \leq f(A, w\vee w') - f(A, w\wedge w')\\
+		\leq & \sum_{k=1}^{|A|} \gamma_k [(w\vee w')(a_k) - (w\wedge w')(a_k)]\\
+		=& \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|\\
+		\leq & \sqrt{K}\sqrt{\sum_{k=1}^{|A|} \gamma_k^2 |w(a_k) - w'(a_k)|^2}
+	\end{align*}
+\end{proof}
+
+We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then by Theorem \ref{thm:main}, the corollary can be obtained.
+
+\section{Proof of Theorem~\ref{thm:and}}
+
+In this section, we prove Theorem \ref{thm:and}. Recall the expected reward function is defined as
+
+By letting $\gamma_k = 1 - \gamma_k'$ and using the relation in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
+
+Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
+\begin{align*}
+&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
+&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
+\end{align*}
+where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
+
+\begin{align*}
+&~~f_{\wedge}(A^{(m+1)}, u) \\
+&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
+&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{m} u_k) (1 - u_{m+1})+ \prod_{k=1}^{m+1} u_k\\
+&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
+&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
+&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
+&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
+\end{align*}
+
 \end{document}

### 2016-01-19 contextual combinatorial cascading bandits.tex
update proof for general case

@@
 \newcommand{\CLemmaPrefixExi}{
-  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
-  $$
-    p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
+	$$
+	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
 	$$ 
@@
 $$
-	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{k=1}^{|A|} \gamma_k^2(w(a_k) - w'(a_k))^2},
+	|f(A, w) - f(A, w')| \leq B \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
 $$
@@
 \subsection{Results}
+
+\subsubsection{General Results}
 
@@
 	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
-	&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
-\label{eq:functionfstar}
+	&f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+\label{eq:AndRewardFunc}
 \end{align}
@@
 
-The next lemma provides some properties about a prefix of action $A$ in the conjunctive case, which leads to the finding of a prefix $B$ of $A$ with similar regret and probability of full observation as those of $A$, as given in Lemma~\ref{lem:prefixexists}.
-\begin{lemma} %lem:prefixRelation
-  \label{lem:prefixRelation}
-  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
-  Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
-  Suppose we have expected weights $w$ for the base arms of action $A$. 
-  Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
-  $$
-    p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
-  $$
-  Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
-  \begin{itemize}
-  	\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
-  	\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
-  	\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
-  	\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}$.
-  \end{itemize}
-\end{lemma}
-\begin{proof}
-  Let $m = |A|$.
-  By the definition of $f_{\wedge}(A,w)$ in Eq.~\eqref{eq:functionfstar}, we have
-  \begin{itemize}
-  	\item[(1)]
-  	\begin{align*}
-  	  f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i) (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
-  	  &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
-  	  &\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
-  	\end{align*}
-
-  	\item[(2)]
-  	\begin{align*}
-  	  &f_{\wedge}(B_k, w) - f_{\wedge}(B_{k+1}, w)\\
-  	  &=\prod_{i=1}^{k}w_i - \gamma_{k+1}' (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
-  	  &=(1 - \gamma_{k+1}') (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0;
-  	\end{align*}
-
-  	\item[(3)]
-  	$p_{\wedge, B_{k+1}} = \prod_{i=1}^{k} w_i \leq \prod_{i=1}^{k-1} w_i = p_{\wedge, B_k}$;
-
-  	\item[(4)]
-  	\begin{align*}
-  	  f_{\wedge}(B_k, w) & \leq \gamma_{k}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}}\\
-  	  &\leq \gamma_{k+1}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}} \\
-  	  &= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}
-  	  \end{align*}
- \end{itemize}
-\end{proof}
-
-\begin{lemma} %lem:prefixexists
-  \label{lem:prefixexists}
-  \CLemmaPrefixExi
-\end{lemma}
-\begin{proof}
-  Let $w= \theta_*^{\top} x_t$.
-  If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
-  $$
-    p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
-  $$
-  In this case, we set prefix $B = A$.
-
-  Now suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
-  $$
-    x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, t,B_k}, ~~I_k = [x_k, y_k]
-  $$
-  Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$.
-Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$.
-Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$.
-Thus
-  $$
-    [f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
-  $$
-  Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
-  $$
-    f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
-  $$
-  Therefore, the results are derived.
-\end{proof}
-
 The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.
+
 \begin{lemma} %lem:DeltaEstimate
 	\label{lem:DeltaEstimate}
-  For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
-  $$
-    R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
-  $$
-  if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
-  $$
-    R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
+	$$
+		R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 \begin{proof}
-  By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
-  $$
-    f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
-  $$
-  By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
+	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then by monotonicity property of $f$,
+	$$
+	f_t^{\ast} = f(A_t^{\ast}, w_t) \leq f(A_t^{\ast}, \bU_t).
+	$$
+	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
 	$$
@@
 	$$
-  By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
+	Then by the condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
 	$$
@@
 	$$
-  The result for the conjunctive case can be deduced in a similar way.
 \end{proof}
@@
 	\label{lem:DeltaEsimateWithP*}
-  Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
 	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
@@
 	$$
-  If we have
-  $$
-    \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
-  $$
-  then
-  $$
-    \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-  $$
 \end{lemma}
 \begin{proof}
-  For the disjunctive case,  
 	\begin{align}
 		&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
-    =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
-    =& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
-    \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
+		=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
+		=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
+		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
 		\leq &\frac{1}{p^{\ast}} \EE \left[ \left.
-\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
+\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
 		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
 	\end{align}
-  Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$. 
+	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$.
 Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
@@
 Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
-  Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
-
-  For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
-  By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
-  Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
-  \begin{align}
-    &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
-    =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
-    =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
-    \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
-  \end{align}
-  Next, we have
-  \begin{equation} \label{eq:andstarbt}
-    f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
-  \end{equation}
-  where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
-
-  Then by Lemma \ref{lem:estimateTech},
-  \begin{equation} \label{eq:btuttrue}
-    f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
-  \end{equation}
-  Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
-  \begin{align}
-    R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
-    & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
-  \end{align}
-  Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
-  \begin{align*}
-    &\EE_t[R_{\wedge}(t, \bA_t)] \\
-    \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-    \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-  \end{align*}
+Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
 \end{proof}
+
+% \begin{lemma} %lem:DeltaEstimate
+%   \label{lem:DeltaEstimate}
+%   For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
+%   $$
+%     R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
+%   $$
+%   if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
+%   $$
+%     R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+%   $$
+% \end{lemma}
+% \begin{proof}
+%   By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
+%   $$
+%     f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
+%   $$
+%   By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
+%   $$
+%     f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+%   $$
+%   By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
+%   $$
+%     f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+%   $$
+%   Therefore,
+%   $$
+%     R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
+%   $$
+%   The result for the conjunctive case can be deduced in a similar way.
+% \end{proof}
+
+% Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
+% However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
+Thus we need the following lemma.
+
+% \begin{lemma} %lem:DeltaEsimateWithP*
+%   \label{lem:DeltaEsimateWithP*}
+%   Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
+%   Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
+%   $$
+%     \EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+%   $$
+%   If we have
+%   $$
+%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
+%   $$
+%   then
+%   $$
+%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+%   $$
+% \end{lemma}
+% \begin{proof}
+%   For the disjunctive case,  
+%   \begin{align}
+%     &\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
+%     =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
+%     =& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
+%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
+%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left.
+\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
+%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
+%   \end{align}
+%   Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$. 
+%   Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
+%   Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. 
+%   Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
+%   Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
+
+%   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
+%   By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
+%   Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
+%   \begin{align}
+%     &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+%     =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
+%     =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
+%     \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
+%   \end{align}
+%   Next, we have
+%   \begin{equation} \label{eq:andstarbt}
+%     f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
+%   \end{equation}
+%   where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
+
+%   Then by Lemma \ref{lem:estimateTech},
+%   \begin{equation} \label{eq:btuttrue}
+%     f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+%   \end{equation}
+%   Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
+%   \begin{align}
+%     R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
+%     & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
+%   \end{align}
+%   Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
+%   \begin{align*}
+%     &\EE_t[R_{\wedge}(t, \bA_t)] \\
+%     \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+%     \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+%   \end{align*}
+% \end{proof}
 
@@
 
-Finally the last lemma bound $\det(\bV_t)$.
+Finally the last lemma bounds $\det(\bV_t)$.
 
@@
 \begin{proof}[ of Theorem \ref{thm:main}]
-	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$.
-
-	For the disjunctive case, we have
+	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
 	\begin{align}
-	&R(T) = \EE \left[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \right] \notag\\
-	&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
-	&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
-	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
+	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
+	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
 	&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
-	& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
+	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
 	&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
-	&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
+	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
 	\end{align}
@@
 	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+\end{proof}
+
+\section{Proof of Corollary~\ref{cor:or}}
+
+In this section, we prove the expected reward function
+$$
+f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
+$$
+where $A = (a_1, \ldots, a_{|A|})$, defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and Lipschitz continuity.
+
+\begin{lemma}[monotonicity]
+	\label{lem:orMonotonicity}
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
+Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	$$
+	f(A, w) \leq f(A, w').
+	$$
+\end{lemma}
+\begin{proof}
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
+	\begin{align*}
+		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
+		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		\geq &~\gamma_{k} \cdot 0 = 0.
+	\end{align*}
+	Then it implies that
+	\begin{align*}
+		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
+		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
+	\end{align*}
+	Therefore, 
+	\begin{align*}
+		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
+		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
+		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
+	\end{align*}
+\end{proof}
+
+\begin{lemma}[Lipschitz continuity]
+	\label{lem:orLip}
+	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
+	$$
+	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
+	$$
+	where $A = (a_1, \ldots, a_{|A|})$.
+\end{lemma}
+\begin{proof}
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, suppose $w \leq w'$ and $w' = w + v$.
+
+	We prove this by induction. It holds obviously for $m = 1$. Suppose it holds for $m$. Then
+	\begin{align*}
+		&f(A^{(m+1)}, w')\\
+		=&f(A^{(m)}, w') + \gamma_{m+1}\prod_{k=1}^m(1 - w'_k) w'_{m+1}\\
+		\leq &f(A^{(m)}, w') +  \gamma_{m+1} \prod_{k=1}^m(1 - w_k) (w_{m+1} + v_{m+1})\\
+		\leq &f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k v_k \\
+		&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w_k) w_{m+1} + \gamma_{m+1} v_{m+1}\\
+		=& f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k v_k.
+	\end{align*}
+	So it holds for $m+1$.
+
+	For general $w,w' \in [0,1]^L$, by last lemma, we have
+	$$
+	f(A, w\wedge w') \leq f(A, w), f(A, w') \leq f(A, w\vee w'),
+	$$
+	where 
+	$$
+	(w\wedge w')_k = \min\{w_k, w'_k\}, ~ (w\vee w')_k = \max\{w_k, w'_k\}.
+	$$
+	Then
+	\begin{align*}
+		&|f(A,w) - f(A,w')| \leq f(A, w\vee w') - f(A, w\wedge w')\\
+		\leq & \sum_{k=1}^{|A|} \gamma_k [(w\vee w')(a_k) - (w\wedge w')(a_k)]\\
+		=& \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|
+	\end{align*}
+\end{proof}
+
+We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then by Theorem \ref{thm:main}, the corollary can be obtained.
+
+\section{Proof of Theorem~\ref{thm:and}}
+
+In this section, we prove Theorem \ref{thm:and}. Recall the expected reward function is
+$$
+f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+$$
+where $A = (a_1, \ldots, a_{|A|})$, as defined in~Eq.\eqref{eq:AndRewardFunc}.
+First, similar to last section, we prove this reward function satisfies the properties of monotonicity and Lipschitz continuity.
+
+\begin{lemma}[monotonicity]
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
+Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	$$
+	f(A, w) \leq f(A, w').
+	$$
+\end{lemma}
+\begin{proof}
+	Denote $A = (a_1, \ldots, a_{|A|})$. Because
+	\begin{align*}
+	&1 - f(A, 1-w) \\
+	=& 1- \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} (1-w(a_i))w(a_k) - \prod_{i=1}^{\abs{A}}(1-w(a_i))\\
+	=& \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
+	\end{align*}
+	then by the proof of Lemma \ref{lem:orMonotonicity} and $1-f(A,1-w)$ is increasing in $w$, we can get $f$ is increasing in $w$.
+\end{proof}
+
+\begin{lemma}[Lipschitz continuity]
+	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
+	$$
+	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
+	$$
+	where $A = (a_1, \ldots, a_{|A|})$.
+\end{lemma}
+\begin{proof}
+	Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.
+
+	We prove this by induction. It holds obviously for $m = 1$. Suppose it holds for $m$. Then
+	\begin{align*}
+		&f(A^{(m+1)}, w') \\
+		= &f(A^{(m)}, w') -\prod_{k=1}^{m} w'_k \\
+		&\qquad+ (1-\gamma_{m+1}) (\prod_{k=1}^{m} w'_k) (1 - w'_{m+1})+ \prod_{k=1}^{m+1} w'_k\\
+		=& f(A^{(m)}, w') - \gamma_{m+1} (\prod_{k=1}^{m} w'_k) (1 - w'_{m+1})\\
+		\leq& f(A^{(m)}, w') - \gamma_{m+1} (\prod_{k=1}^{m} w_k) (1 - w'_{m+1})\\
+		\leq& f(A^{(m)}, w') -\gamma_{m+1} (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - v_{m+1})\\
+		\leq& (f(A^{(m)}, w) +  \sum_{k=1}^{m} \gamma_k v_k) \\
+		&\qquad - \gamma_{m+1}  (\prod_{k=1}^{m} w_k)(1 - w_{m+1}) + \gamma_{m+1} v_{m+1}\\
+		\leq& (A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k v_k.
+	\end{align*}
+\end{proof}
+
+The next lemma provides some properties about a prefix of action $A$ in the conjunctive case, which leads to the finding of a prefix $B$ of $A$ with similar regret and probability of full observation as those of $A$, as given in Lemma~\ref{lem:prefixexists}.
+
+\begin{lemma} %lem:prefixRelation
+	\label{lem:prefixRelation}
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$.
+Let $A = (a_1, ..., a_{\abs{A}})$.
+Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$.
+The expected weights are denoted by $w$.
+The probability of full observation of $A$, $p_{A}$, can be formulated as
+	$$
+	p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
+	$$
+	Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
+	\begin{itemize}
+		\item[(1)] $f(A, w) \leq (1-\gamma_{\abs{A}}) + \gamma_{\abs{A}} p_{A}$;
+		\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
+		\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
+		\item[(4)] $f(B_k, w) \leq (1-\gamma_{k+1}) + \gamma_{k+1} p_{B_{k+1}}$.
+	\end{itemize}
+\end{lemma}
+\begin{proof}
+	Let $m = |A|$. By the definition of $f(A,w)$ in Eq.~\eqref{eq:AndRewardFunc}, we have
+	\begin{itemize}
+		\item[(1)]
+		\begin{align*}
+		&f_{\wedge}(A,w) \\
+		=& \sum_{k = 1}^{\abs{A}} (1-\gamma_k) \prod_{i = 1}^{k - 1} w(a_i) (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
+		\leq& (1-\gamma_m)(1 - p_{A} w_m) + p_{A} w_m \\
+		\leq& (1-\gamma_m) + \gamma_m p_{\wedge, A};
+		\end{align*}
+
+		\item[(2)]
+		\begin{align*}
+		&f(B_k, w) - f(B_{k+1}, w)\\
+		=&\prod_{i=1}^{k}w_i - (1-\gamma_{k+1}) (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \\
+		&\qquad \qquad - (\prod_{i=1}^{k}w_i) w_{k+1}\\
+		=&\gamma_{k+1} (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0;
+		\end{align*}
+
+		\item[(3)]
+		$p_{B_{k+1}} = \prod_{i=1}^{k} w_i \leq \prod_{i=1}^{k-1} w_i = p_{B_k}$;
+
+		\item[(4)]
+		\begin{align*}
+		f(B_k, w) & \leq (1-\gamma_k) (1 - p_{B_{k+1}}) + p_{B_{k+1}}\\
+		&\leq (1-\gamma_{k+1}) (1 - p_{B_{k+1}}) + p_{B_{k+1}} \\
+		&= (1-\gamma_{k+1}) + \gamma_{k+1} p_{B_{k+1}}
+		\end{align*}
+	\end{itemize}
+\end{proof}
+
+\begin{lemma} %lem:prefixexists
+	\label{lem:prefixexists}
+	\CLemmaPrefixExi
+\end{lemma}
+\begin{proof}
+	$w_t = \theta_*^{\top} x_t$. If $f(A, w_t) \geq \frac{1}{2} f_{t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
+	$$
+	p_{t, A} \geq \frac{1}{2} f_{t}^{\ast} - 1 + \gamma_{\abs{A}}.
+	$$
+	In this case, we set prefix $B = A$.
+
+	Now suppose $f(A, w_t) \leq \frac{1}{2} f_{t}^{\ast}$. Let
+	$$
+	x_k = f(B_k,w), ~~ y_k = 1 - \gamma_k + \gamma_k p_{t,B_k}, ~~I_k = [x_k, y_k]
+	$$
+	Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$.
+Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$.
+Also, $x_{\abs{A}} = f(A, w)$ and $y_1 = 1$.
+Thus
+	$$
+	[f(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
+	$$
+	Then there exists a $k$ such that $\frac{1}{2}f_{t}^{\ast} \in I_k$:
+	$$
+	f(B_k,w) \leq \frac{1}{2}f_{t}^{\ast} \leq 1 - \gamma_k + \gamma_k p_{\wedge, t, B_k}
+	$$
+	Therefore, the results are derived.
+\end{proof}
+
+%   If we have
+%   $$
+%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
+%   $$
+%   then
+%   $$
+%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+%   $$
+
+	%   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
+	%   By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
+	%   Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
+	%   \begin{align}
+	%     &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+	%     =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
+	%     =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
+	%     \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
+	%   \end{align}
+	%   Next, we have
+	%   \begin{equation} \label{eq:andstarbt}
+	%     f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
+	%   \end{equation}
+	%   where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
+
+	%   Then by Lemma \ref{lem:estimateTech},
+	%   \begin{equation} \label{eq:btuttrue}
+	%     f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+	%   \end{equation}
+	%   Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
+	%   \begin{align}
+	%     R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
+	%     & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
+	%   \end{align}
+	%   Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
+	%   \begin{align*}
+	%     &\EE_t[R_{\wedge}(t, \bA_t)] \\
+	%     \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+	%     \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	%   \end{align*}
 
@@
 	\end{align}
-\end{proof}
-
-\section{Proof of Corollary~\ref{cor:or}}
-
-In this section, we prove the expected reward function
-$$
-f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
-$$
-defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and Lipschitz continuity.
-
-\begin{lemma}[monotonicity]
-	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
-Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
-	$$
-	f(A, w) \leq f(A, w').
-	$$
-\end{lemma}
-\begin{proof}
-	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
-	\begin{align*}
-		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
-		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-		\geq &~\gamma_{k} \cdot 0 = 0.
-	\end{align*}
-	Then it implies that
-	\begin{align*}
-		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
-		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
-	\end{align*}
-	Therefore, 
-	\begin{align*}
-		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
-		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
-		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
-		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
-	\end{align*}
-\end{proof}
-
-\begin{lemma}[Lipschitz continuity]
-	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
-	$$
-	|f(A, w) - f(A, w')| \leq \sqrt{K}\sqrt{\sum_{k=1}^{|A|} \gamma_k^2 |w(a_k) - w'(a_k)|^2},
-	$$
-	where $A = (a_1, \ldots, a_{|A|})$.
-\end{lemma}
-\begin{proof}
-	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, suppose $w \leq w'$ and $w' = w + v$.
-
-	We prove this by induction. It holds obviously for $m = 1$. Suppose it holds for $m$. Then
-	\begin{align*}
-		&f(A^{(m+1)}, w')\\
-		=&f(A^{(m)}, w') + \gamma_{m+1}\prod_{k=1}^m(1 - w'(k)) w'(m+1)\\
-		\leq &f(A^{(m)}, w') +  \gamma_{m+1} \prod_{k=1}^m(1 - w(k)) (w(m+1) + v(m+1))\\
-		\leq &f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k v(k) \\
-		&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w(k)) w(m+1) + \gamma_{m+1} v(m+1)\\
-		=& f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k v(k).
-	\end{align*}
-	So it holds for $m+1$.
-
-	For general $w,w' \in [0,1]^L$, by last lemma, we have
-	$$
-	f(A, w\wedge w') \leq f(A, w), f(A, w') \leq f(A, w\vee w'),
-	$$
-	where $(w\wedge w')(k) = \min\{w(k), w'(k)\}$ and $(w\vee w')(k) = \max\{w(k), w'(k)\}$. Then
-	\begin{align*}
-		&|f(A,w) - f(A,w')| \leq f(A, w\vee w') - f(A, w\wedge w')\\
-		\leq & \sum_{k=1}^{|A|} \gamma_k [(w\vee w')(a_k) - (w\wedge w')(a_k)]\\
-		=& \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|\\
-		\leq & \sqrt{K}\sqrt{\sum_{k=1}^{|A|} \gamma_k^2 |w(a_k) - w'(a_k)|^2}
-	\end{align*}
-\end{proof}
-
-We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then by Theorem \ref{thm:main}, the corollary can be obtained.
-
-\section{Proof of Theorem~\ref{thm:and}}
-
-In this section, we prove Theorem \ref{thm:and}. Recall the expected reward function is defined as
-
-By letting $\gamma_k = 1 - \gamma_k'$ and using the relation in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
-
-Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
-\begin{align*}
-&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
-&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
-\end{align*}
-where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
-
-\begin{align*}
-&~~f_{\wedge}(A^{(m+1)}, u) \\
-&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
-&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{m} u_k) (1 - u_{m+1})+ \prod_{k=1}^{m+1} u_k\\
-&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
-&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
-&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
-&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
-\end{align*}
-
 \end{document}

### 2016-01-20 contextual combinatorial cascading bandits.tex
update proof and sub-Gaussion

@@
 }
+\newcommand{\CEqDeltaEstAnd}{
+	$$
+	\EE_t [R(t, \bA_t) ] \leq \frac{8}{f^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	$$
+}
 \newcommand{\CLemmaSumXiEstimateInDet}{
@@
 
+Usually in recommendations, different positions have different values. It is natural to introduce position discounts.
+
 Motivated by the above challenges, we develop an approach called {\it contextual combinatorial cascading bandits}.
@@
 
-The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{T})$ for $T$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
+The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
 
@@
 \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid.
-They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs.
-To improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
+They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs; the reason might be that the items with lower preference come first, so the learning agent will collect more data.
+However, this might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
 Our work extends this part by introducing position discounted parameters.
@@
 \cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
-Their setting is more informative than ours but our algorithm is competitive to theirs.
+Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.
 
@@
 
-A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit
+A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit.
+When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$.
+Our setting is more specific than theirs.
+The base arms in a super arm are triggered in list order; only the previous ones are triggered, the base arm can have the chance to be triggered.
+Also, they don't consider the contextual information and position discounts.
 
@@
 Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.
+Following standard assumptions of stochastic MABs, we assume that all reward distributions have R-sub-Gaussian tails for some known constant $R > 0$; formally, for all $\lambda \in \RR$, one has
+$$
+\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2)/2.
+$$
 
@@
   \begin{equation}
-    \bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
+    \bbeta_{t}(\delta) = R\sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
   \end{equation}
@@
 		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
 		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
@@
 \begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
-	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. In particular,
+	The complete proof is in the Appendix.
+The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
+This reduction is challenging for two reasons.
+First, our setting has contextual information.
+Second, we consider position-discounted weight $\gamma$.
+
+	In particular, by monotonicity and Lipschitz continuity, we have
+	$$
+		R(t, \bA_t) \leq B \sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
+	$$
+	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
+Thus we need the following deduction.
 	\begin{align*}
@@
     \end{align*}
-    Also, by monotonicity and Lipschitz continuity,
-    $$
-    	R(t, \bA_t) \leq B \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
-    $$
-
-	% our analysis to that of CombCascade in \cite{kveton2015combinatorial}.
-This reduction is challenging for two reasons.
-First, our setting has contextual information.
-Second, we consider position-discounted weight $\gamma$.
-
-	% Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items.
-Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
-	% \begin{align*}
- %    	&\EE[R(t, \bA_t)|\cH_t] \\
- %    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
- %    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
- %    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
- %    \end{align*}
- %    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.
-
+    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
+    \begin{lemma}
+    	\label{lem:XNormSumEst}
+    	If $\lambda \geq C_{\gamma}$, then
+    	$$
+    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
+    	$$
+    \end{lemma}
+    Then we can prove this theorem.
 \end{proof}
@@
 	\br_{t} &= \begin{cases}
-		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
-		1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
+		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
+		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
 	\end{cases}\\
@@
 	\label{thm:and}
-	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4} f_{\wedge}^{\ast}$. 
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$.
 Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$.
-	Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
+Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
 	\begin{align}
-	R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
-	&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-	&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
+		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
+		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
+		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
 	\end{align}
 \end{theorem}
-
-The proof of this theorem is different in the following lemmas.
-
-  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
+\begin{proof}
+	We will prove it in the appendix.
+The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
+And then use the following lemma to replace $\bA_t$ with a prefix.
 	\begin{lemma}
@@
 	\end{lemma}
-  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
-  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
-  \begin{lemma}
-  	%\CLemmaIncre
-  \end{lemma}
-  \begin{lemma}
-  	%\CLemmaTech
-  \end{lemma}
-  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
-  \begin{lemma}
-  	\CLemmaSumXiEstimateInDet
-  \end{lemma}
-  \begin{lemma}
-  	\CLemmaDetVt
-  \end{lemma}
-  Then we can use a mean inequality to derive the result.
+
+	Therefore we can get
+	\CEqDeltaEstAnd
+
+	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem.
+\end{proof}
 
 \subsection{Dissutions}
+
+1. Our setting generalizes theirs, and our results with restricted to theirs is of same order except log
+
+2. there is also other problem that can't be explained in their model even if without context information
 
@@
 	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
-	&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
-	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
-	&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
-	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
+	&\leq \EE\left[\frac{1}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
+	&\leq \frac{\sqrt{2}}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
+	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
 	\end{align}
@@
 \begin{lemma}[monotonicity]
+	\label{lem:andMonotonicity}
 	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
@@
 \begin{lemma}[Lipschitz continuity]
+	\label{lem:andLip}
 	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
@@
 	$$
-	p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
+	p_{A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
 	$$
@@
 		\begin{align*}
-		&f_{\wedge}(A,w) \\
+		&f(A,w) \\
 		=& \sum_{k = 1}^{\abs{A}} (1-\gamma_k) \prod_{i = 1}^{k - 1} w(a_i) (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
@@
 
-%   If we have
-%   $$
-%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
-%   $$
-%   then
-%   $$
-%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-%   $$
-
-	%   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
-	%   By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
-	%   Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
-	%   \begin{align}
-	%     &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
-	%     =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
-	%     =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
-	%     \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
-	%   \end{align}
-	%   Next, we have
-	%   \begin{equation} \label{eq:andstarbt}
-	%     f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
-	%   \end{equation}
-	%   where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
-
-	%   Then by Lemma \ref{lem:estimateTech},
-	%   \begin{equation} \label{eq:btuttrue}
-	%     f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
-	%   \end{equation}
-	%   Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
-	%   \begin{align}
-	%     R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
-	%     & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
-	%   \end{align}
-	%   Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
-	%   \begin{align*}
-	%     &\EE_t[R_{\wedge}(t, \bA_t)] \\
-	%     \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-	%     \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-	%   \end{align*}
-
-	Similarly, for the conjunctive case, we have the following derivation:
+The key difference from the proof of Theorem \ref{thm:main} is the following lemma. This lemma corresponds to Lemma \ref{lem:DeltaEsimateWithP*} and uses $f^{\ast}$ to replace $p^{\ast}$.
+
+\begin{lemma}
+	If we have $\gamma_K \geq 1 -  \frac{1}{4} f^{\ast}$, where $f^{\ast} = \min_{1 \leq t \leq T} f_{t}^{\ast}$, then
+	\CEqDeltaEstAnd
+\end{lemma}
+\begin{proof}
+	By Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{t, \bB_t} \geq \frac{1}{2}f_{t}^* - 1 + \gamma_{|\bB_t|}$ and $R(t, \bB_t) \geq \frac{1}{2} R(t, \bA_t)$.
+By the assumption that $1-\gamma_{|\bB_t|} \leq 1-\gamma_K \leq \frac{1}{4} f^{\ast} \leq \frac{1}{4} f^*_{t}  $, we have $p_{t, \bB_t} \geq \frac{1}{4}f_{t}^*$.
+
+	Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
 	\begin{align}
-	&R(T) = \EE \left[ \sum_{t=1}^{T} \EE_{t}[R_{\wedge}(t, \bA_t)] \right] \notag\\
-	&\leq \EE \left[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
-	&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
-	&\leq \EE\left[\frac{8}{f_{\wedge}^{\ast}} \bbeta_{T}(\delta) \sqrt{ \left(\sum_{t=1}^{T} \bO_t \right) \EE_t \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
-	&\leq \EE \left[\frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_T)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
-	&\qquad \qquad \left. \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
-	&\leq \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda} \right) \notag\\
-	&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMCdetEst}
+		&\EE_t[R(t, \bA_t)] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+		=& 2 \EE \left[ \left. R(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
+		=& 2\EE \left[ \left. R(t, \bB_t) \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
+		\leq &\frac{8}{f_{t}^{\ast}} \EE \left[ \left. R(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
 	\end{align}
+	Next, we have
+	\begin{equation} \label{eq:andstarbt}
+		f(A_t^*, w_t) \leq f(A_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t),
+	\end{equation}
+	where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:andMonotonicity}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
+
+	Then by Lemma \ref{lem:andLip},
+	\begin{equation} 
+		\label{eq:btuttrue}
+		f(\bB_t,\bU_t) \leq f(\bB_t, w_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
+	\end{equation}
+	Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
+	\begin{align}
+		R(t, \bB_t) & = f_{t}^{\ast} - f(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
+		& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
+	\end{align}
+	Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
+	\begin{align*}
+		&\EE_t[R(t, \bA_t)] \\
+		\leq& \frac{8}{f_{t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+		\leq& \frac{8}{f^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	\end{align*}
+\end{proof}
+
+Then we have the proof of Theorem \ref{thm:and}.
+
+\begin{proof}[of Theorem \ref{thm:and}]
+	Similar to the proof of Theorem \ref{thm:main}, we have the following derivation:
+	\begin{align}
+	&R(n) = \EE \left[ \sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
+	\leq& \EE \left[\sum_{t=1}^{n} \frac{8}{f^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
+	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
+	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
+	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
+	&\qquad \qquad \left. \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
+	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda} \right) \notag\\
+	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMCdetEst}
+	\end{align}
+\end{proof}
+
 \end{document}

### 2016-01-21 contextual combinatorial cascading bandits.tex
update discussion part

@@
 
-1. Our setting generalizes theirs, and our results with restricted to theirs is of same order except log
-
-2. there is also other problem that can't be explained in their model even if without context information
-
-Our setting generalizes several existing works but not limited to them. Our setting generalizes cascading bandit and combinatorial bandit to involve position discount,
-
-to involve context
-
-there are cases that can not be fit into their
-
-our method generalize Qin's method and has a regret bound proof.
-
-network latency
-
-If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$.
+In the above, we formulate the general setting of contextual combinatorial cascading bandit with position discount. This setting generalizes several existing results.
+
+If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial}, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result; the reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandit is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved}.
+
+If our setting restricts to contextual combinatorial bandit \cite{qin2014contextual}, the random variable $\bO_t$ of observed base arms is $|\bA_t|$, which the number of base arms in chosen action $\bA_t$, and the minimal probability $p^*$ of observing all base arms in chosen actions should always be $1$.
+So our regret bound is of the same order with theirs.
+Notice that when applying their setting, the bound $C$ for Lipschitz continuity in our problem should be $\sqrt{K}$.
+
+Our setting generalizes several existing works but not limited to them.
+For example, in medical treatment, a patient will be recommended with a series of treatments.
+The patient has to take the treatments one by one, so the series of treatment actually is a list.
+Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$, where $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment.
+We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$.
+So a treatment $a$ is successful with probability
+\begin{equation}
+\label{eq:betaTau}
+1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
+\end{equation}
+where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number.
+We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful.
+So the expected reward function is
+$$
+f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
+$$
+where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.
+
+By the expression of $f$, it is a function of the expected reward $w$.
+Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$.
+Therefore, the expected reward has the property of monotonicity.
+For the Lipschitz continuity, by the Lipschitz continuity of expected reward function, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.
+
+Thus this expected reward function satisfies our setting but can not be fit into previous works.
+Similarly, a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.
+
+% network latency
+
+% If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$.
 We call the latency is {\it high} if it is larger than a threshold $\tau$.
@@
 So a path is unblocked with probability
-$$
-\prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
-$$
+% $$
+% \prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
+% $$
 

### 2016-01-21 contextual combinatorial cascading bandits.tex
update experiment

@@
 \begin{abstract} 
-The purpose of this document is to provide both the basic paper template and submission guidelines.
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at problem-specific criterion.
+In recommendation, the stopping criterion might be the first item a user selects.
+In network, the stopping criterion might be the first edge being blocked in a path.
+We also considers position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
+We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases.
+Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, context information and partial observability.
+We experiment on both synthetic data and real data and show that our algorithm performs well.
 \end{abstract}
@@
 \subsection{Synthetic}
-
-In the first experiment, we compare $C^3$-UCB to $C^2$UCB and CombCascade on synthetic problems.
-This problem is a contextual cascading bandit with $L=20$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly choose $\theta_* \in \RR^d$ with $\|\theta_{\ast}\|_2 = 1$.
-Then at each time $t$, we randomly assign $x_{t,a} \in \RR^d$ with $\theta_*^{\top}x_{t,a} \in [0,1]$ to arm $a$.
-And the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experiment on four settings and report our results in Figure \ref{fig:synthetic}.
-The first experiment is with disjunctive objective and $\gamma=1$ and the second is also with disjunctive objective but with $\gamma=0.95$.
-The third experiment is conducted with conjunctive objective and $\gamma=1$.
-The fourth experiment is using network 1755 structure.
-The algorithm $C^2$UCB has semi-bandit feedback and our algorithm has only cascading feedback.
-However from the results, our performance is competitive to their's.
-The $CombCascade$ algorithm does not make use of contextual information, so it is not as good as the other two algorithms.
-
+\label{sec:ExpSyn}
+
+% experiment - synthetic - results
 \begin{figure*}
@@
 	\subfigure[Disjunctive, $\gamma=1$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-1.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-T10000-L100-K4-1.eps}}
 	\subfigure[Disjunctive, $\gamma=0.95$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-95.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-T10000-L100-K4-95.eps}}
 	\subfigure[Conjunctive, $\gamma=1$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synC-1.eps}}
-	\subfigure[Conjunctive, network 1755, $\gamma=1$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{network3B-1.eps}}
-	\caption{Synthetic Data Set, L=20, K=4}
+		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-1.eps}}
+	\subfigure[Conjunctive, $\gamma=0.95$ ]{
+		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-95.eps}}
+	\caption{Synthetic Data Set, L=100, K=4, d=10}
 	\label{fig:synthetic} % 用于交叉引用
@@
 
+In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems.
+This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
+At first, we randomly choose $\theta_* \in \RR^{d-1}$ with $\|\theta_{\ast}\|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} \in [0,1]$.
+Next the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experiment on four settings and demonstrate the results in Figure \ref{fig:synthetic}.
+The first two are of disjunctive objective with different position discount and the last two are of conjunctive objectives.
+Our algorithm outperforms than {\it CombCascade} algorithm because it does not use the context information.
+
 \subsection{MovieLens}
 
-In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of March 2015.
+\begin{figure}
+	\centering
+	\subfigure[$\gamma = 1$]{
+		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-1.eps}}
+	\subfigure[$\gamma = 0.95$]{
+		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-95.eps}}
+	\caption{MovieLens}
+	\label{fig:movielens} % 用于交叉引用
+\end{figure}
+
+In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of 2015.
 
 The Learning problem is formulated as follows.
-There is a big sparse matrix $A \in \{0,1\}^{N_u \times N_m}$ where $A(u,m) = 1$ denotes user $u$ has watched movie $m$.
+There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
 We split $A$ to be $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
 We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
-We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = VSZ^{\top}$ where $V = (v_1; ...;v_{N_u})$ and $Z = (z_1;...;z_{N_m})$.
-At every time $t$, use $x_{t,i} = v_{i}z_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $u_t$.
-And use $w_t(m) = F(u_t,m)$ as the weight of movie $m$.
-
-Notice that
-
-Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
-Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.
-
-\begin{figure*}
-	\centering
-	\subfigure[MovieLens]{
-		\includegraphics[height = 3cm, width = 5 cm]{movie-1.eps}}
-	\caption{MovieLens}
-	\label{fig:movielens} % 用于交叉引用
-\end{figure*}
+We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
+At every time $t$, use $x_{t,i} = u_{i}m_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
+And use $w_t(m) = F(I_t,m)$ as the weight of movie $m$ at time $t$.
+
+This problem is required to recommend fixed number of movies.
+Notice that it might have problem if we use $(u_{I_t}, m_j)$ as context information.
+Denote $\theta$ by $(\theta_u, \theta_m)$.
+So the expected mean of a base arm is of the form $\theta_u^{\top} u_{I_t} + \theta_m^{\top} m_j$ but the first term $\theta_u^{\top} u_{I_t}$ is fixed at time $t$ no matter what $\theta_u$ is.
+Therefore, to find the best super arm, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
+So to make use of the user's context information, we need some quadratic terms of user's information $u_i$ and movie's information $m_j$.
+That's why we use the convolution $u_{i}m_j^{\top}$ to denote the context of movie $j$ at time $t$.
+
+We experiment with different position discount and compare our algorithm with {\it CombCascade}.
+We show the results in Fig.~\ref{fig:movielens}.
+Our algorithms outperforms theirs, which demonstrate the advantage of introducing context information in real applications.
 
 \subsection{Network Routing}
-
-In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.
-
-The ground set $E$ is the set of links in the network and the feasible action set $\cS$ is the set of all paths in the network.
-Before learning, the environment randomly chooses a $d$-dimensional vector $\theta \in [0,1]^d$.
-At each time $t$, any link $e$ is assigned with a random $d$-dimensional context vector $x_{t,e}$ and the corresponding latency follows exponential distribution with mean $1-\theta^{\top}x$, which has been scaled into $[0,1]$.
-We call the latency is {\it high} if it is larger than a threshold $\tau$.
-A pair of source and terminal nodes $(v_s, v_t)$ are chosen randomly.
-The agent recommends a feasible path $A = (a_1,...,a_{|A|})$ from $v_s$ to $v_t$ with expected reward
-$$
-\prod_{k=1}^{|A|} (1- \exp(-\frac{\tau}{1-\theta^{\top}x_{t,a_k}})).
-$$
-Notice that the expression is not of the form $\prod_{k=1}^{|A|}\theta_*^{\top}x_{t,a_k}$ in our model. However, our algorithm could also apply to it.
 
@@
 	\caption{Network with latency}
-	\label{fig:sample number} % 用于交叉引用
+	\label{fig:network} % 用于交叉引用
 \end{figure*}
+
+In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.
+
+The ground set $E$ is the set of links in the network and the feasible action set $\cS$ is the set of all paths in the network.
+Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$ and at each time $t$, any link $e$ is assigned with a random $d$-dimensional context vector $x_{t,e}$.
+Notice here both $\theta$ and $x$ have been processed like section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
+The weight for each edge $e$ is a Bernoulli random variable with mean $\theta_*^{\top}x$.
+
+At each time $t$, A pair of source and terminal nodes $(v_s, v_t)$ are chosen randomly.
+The learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between $v_s$ and $v_t$ to maximize the expected reward in the conjunctive objective.
+
+We experiment with different position discounts and on different networks. The results are shown in Fig.~\ref{fig:network}. Our algorithm ourperforms {\it CombCascade} algorithm.
+
+% we randomly generate a pair of starting and ending nodes, and the learning agent chooses a routing path between the two nodes to maximize the expected reward with position discount.
+
+%  and the corresponding latency follows exponential distribution with mean $1-\theta^{\top}x$, which has been scaled into $[0,1]$.
+We call the latency is {\it high} if it is larger than a threshold $\tau$.
+% $$
+% \prod_{k=1}^{|A|} (1- \exp(-\frac{\tau}{1-\theta^{\top}x_{t,a_k}})).
+% $$
+% Notice that the expression is not of the form $\prod_{k=1}^{|A|}\theta_*^{\top}x_{t,a_k}$ in our model. However, our algorithm could also apply to it.
+
+% the environment randomly choose
 

### 2016-01-22 contextual combinatorial cascading bandits.tex
change movielens results with bigger T

@@
 	\subfigure[$\gamma = 1$]{
-		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-1.eps}}
-	\subfigure[$\gamma = 0.95$]{
-		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-95.eps}}
+		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
+	\subfigure[$\gamma = 0.9$]{
+		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
 	\caption{MovieLens}

### 2016-01-24 experiment/agent.py
modified structure, now each expriment setting is under one and one only class; tested: c3synthetic-monkey, c3synthetic-isp;

@@ -6,88 +6,135 @@ import numpy as np
 from scipy.spatial.distance import cosine
 import matplotlib.pyplot as plt
 
-def contextual_cascading_monkey(e, s, T):
-    score = [0]
+def contextual_cascading_monkey(s, T):
+    reward = [0]
+    regret = [0]
     for t in range(1, T):
-        _, params = e()
+        _, params = s.new()
         U = {arm: np.random.uniform(0, 1) for arm in s.arms}
         recc = s.oracle(U, *params)
-        r, _ = e(recc)
-        score.append(score[-1] + r)
-    logger.info('Monkey play score {0}/{1}'.format(score[-1], T))
-    return score, 0
+        r, _, z = s.play(recc)
+        reward.append(reward[-1] + r)
+        regret.append(regret[-1] + z)
+    logger.info('Monkey play reward {0}/{1}'.format(reward[-1], T))
+    if s.regret is True:
+        logger.info('regret {0}/{1}'.format(regret[-1], T))
+    return reward, regret, None
 
 contextual_full_monkey = contextual_cascading_monkey
 
-def absolute_cascading_ucb(e, s, T):
-    score = [0]
+def absolute_cascading_ucb(s, T):
+    reward = [0]
+    regret = [0]
     W = {arm: 0.5 for arm in s.arms}
     b = {arm: 1 for arm in s.arms}
     for t in range(1, T):
-        _, params = e()
+        _, params = s.new()
         U = {arm: W[arm] + np.sqrt(1.5 * np.log(t) / b[arm]) for arm in s.arms}
         recc = s.oracle(U, *params)
-        r, c = e(recc)
+        r, c, z = s.play(recc)
         for k in range(min(len(recc), c+1)):
             W[recc[k]] = ((b[recc[k]]) * W[recc[k]] + s.gamma ** k * ((k == c) == s.disj)) / (b[recc[k]] + s.gamma ** k)
             b[recc[k]] += s.gamma ** k
-        score.append(score[-1] + r)
-    logger.info('Absolute play score {0}/{1}'.format(score[-1], T))
-    return score, 0
+        reward.append(reward[-1] + r)
+        regret.append(regret[-1] + z)
+    logger.info('Absolute play reward {0}/{1}'.format(reward[-1], T))
+    if s.regret is True:
[…]

### 2016-01-24 experiment/environment.py

@@ -1,4 +1,4 @@
-import heapq
+
 import random
 import logging
 logger = logging.getLogger('Environment')
@@ -6,77 +6,58 @@ logger = logging.getLogger('Environment')
 import numpy as np
 
 from utils import red
-from utils import pendium
-from utils import uni
+from utils import pendulum
 from utils import suni
 from utils import disturb
 from utils import reward
+from utils import ereward
 from utils import ucb_settings
+from utils import serialize
+from utils import argmax_oracle
 
-from isp import isp_oracle
-from isp import isp_Coracle
-from isp import reachable
+class c3synthetic_monkey_rng:
 
-def contextual_monkey_rng(L=20, d=10, h=0.35, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False):
-    arms = list(range(L))
-    x = {arm: suni(d) for arm in arms}
-    theta = h * suni(d)
-    logger.info('Initializing random settings "Contextual Monkey" complete')
-    s = ucb_settings(arms=arms, L=L, x=x, theta=theta, K=K, d=d, gamma=gamma, eps=eps, v=v, disj=disj)
-    logger.info(s)
-    return s
+    # contextual_monkey_rng(self, L=20, d=10, b=0, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False)
+    
+    def __init__(self, **kwarg):
+        logger.info('Initializing random settings "Contextual Monkey"')
+        self.__dict__.update(kwarg)
+        self.name = 'c3synthetic-monkey'
+        self.arms = list(range(self.L))
+        self.x = {arm: suni(self.d) for arm in self.arms}
+        self.theta = suni(self.d)
+        self.oracle = argmax_oracle
+        self.regret_avl = True
+        logger.info(self)
 
-def argmax_oracle(U, K, sort):
-    return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])[::2*sort-1]]
+    def __str__(self):
+        return serialize(self, 'arms', 'x')
 
-def contextual_monkey(s, cascade, rgamma, sort):
-    logger.info('Initializing environment "Contextual Monkey"| cascade:{0} rgamma:{1} sort:{2}'.format(cascade, rgamma, sort))
-    xt = {arm: s.x[arm] for arm in s.x}
-    def environment(recommend=None):
-        if recommend == None:
-            for arm in s.x:
[…]

### 2016-01-24 experiment/flowtest.py

@@ -17,107 +17,82 @@ logger.info('===== Numpy/Python random seed = {0}'.format(seed))
 import matplotlib.pyplot as plt
 
 from agent import contextual_cascading_sherry
+from agent import contextual_cascading_gsherry
 from agent import contextual_cascading_monkey
 from agent import contextual_full_monkey
 from agent import contextual_full_lijing
 from agent import absolute_cascading_ucb
-from environment import contextual_monkey_rng
-from environment import contextual_monkey
-from movielens import contextual_movielens_rng
-from environment import contextual_movielens
-from isp import contextual_isp_rng
-from environment import contextual_isp
+from environment import contextual
+from environment import c3synthetic_monkey_rng
+from movielens import c3_movielens_rng
+from isp import c3synthetic_isp_rng
+from isp import c3synthetic_Zisp_rng
+from isp import c3synthetic_Cisp_rng
 
-def flowtest_monkey(T, kw):
+def flowtest_monkey(T, **kw):
     logger.info('Monkey flowtest')
     logger.info('Require rng initialization')
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
-    s = contextual_monkey_rng(**kw)
-    exploit1, explore1 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit2, explore2 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=False, sort=False), T=T)
-    exploit3, explore3 = contextual_cascading_sherry(*contextual_monkey(s, cascade=True, rgamma=False, sort=True), T=T)
-    # exploit2, explore2 = contextual_cascading_monkey(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit4, explore4 = contextual_full_lijing(*contextual_monkey(s, cascade=False, rgamma=False, sort=False), T=T)
-    exploit5, explore5 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=True, sort=False), T=T)
-    exploit6, explore6 = absolute_cascading_ucb(*contextual_monkey(s, cascade=True, rgamma=False, sort=False), T=T)
[…]

### 2016-01-24 experiment/isp.py

@@ -1,30 +1,44 @@
 from functools import reduce
 from itertools import islice
+import random
 import logging
 logger = logging.getLogger('ISP')
 
 import networkx
 
-from utils import ucb_settings
 from utils import suni
+from utils import disturb
+from utils import serialize
+from utils import pendulum
+from utils import ereward
 
 def reachable(G, u, v):
     return networkx.has_path(G, u, v)
 
-def isp_oracle(U, G, u, v, gamma):
+def isp_oracle(U, G, u, v):
     for (x, y), z in U.items():
         G[x][y]['weight'] = max(1 - z, 0)
     path = networkx.shortest_path(G, u, v, weight='weight')
     return [tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1)]
 
-def isp_Coracle(U, G, u, v, gamma):
+def isp_Zoracle(U, G, u, v, k, gamma):
     for (x, y), z in U.items():
         G[x][y]['weight'] = max(1 - z, 0)
     s = {}
-    for path in islice(networkx.shortest_simple_paths(G, u, v), 40):
+    for path in islice(networkx.shortest_simple_paths(G, u, v), k):
         sarms = tuple(tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1))
         psarms = [(U[e] + 1) / 2 for e in sarms]
-        s[sarms] = sum([(1 - gamma**i) * reduce(float.__mul__, [1.,] + psarms[:i-1]) * (1 - psarms[i]) for i in range(len(psarms))]) + reduce(float.__mul__, psarms)
+        s[sarms] = ereward(psarms, gamma, False)
+    return list(max(s, key=s.get))
+
+def isp_Coracle(U, G, u, v, k, gamma):
+    for (x, y), _ in U.items():
+        G[x][y]['weight'] = max(1, 0)
+    s = {}
+    for path in islice(networkx.shortest_simple_paths(G, u, v), k):
+        sarms = tuple(tuple(sorted((path[i], path[i+1]))) for i in range(len(path) - 1))
+        psarms = [(U[e] + 1) / 2 for e in sarms]
+        s[sarms] = ereward(psarms, gamma, False)
     return list(max(s, key=s.get))
 
 def isp_data(isp):
@@ -39,11 +53,62 @@ def isp_net(g):
         G.add_edge(u, v, weight=1)
     return G
 
-def contextual_isp_rng(isp=1221, d=10, h=0.35, tlc=1, gamma=0.95, disj=False):
[…]

### 2016-01-24 experiment/movielens.py

@@ -1,6 +1,6 @@
-import csv
 from itertools import chain
-
+import csv
+import random
 import logging
 logger = logging.getLogger('Movielens')
 
@@ -8,7 +8,9 @@ import numpy as np
 from scipy import sparse
 from scipy.sparse.linalg import svds
 
-from utils import ucb_settings
+from utils import uni
+from utils import argmax_oracle
+from utils import serialize
 
 def overlap(l1, l2):
     return len(set(l1) & l2)
@@ -22,41 +24,88 @@ def movielens_data():
     gt.__next__()
     return chain(gr, gt)
 
-def contextual_movielens_rng(L=None, portion=0.5, d=15, K=6, h=None, gamma=0.95, disj=False):
-    cox = []
-    coy = []
-    history = {}
-    movies = {}
-    for idx, (user, movie, rate, timestamp) in enumerate(movielens_data()):
-        user = int(user) - 1
-        movie = int(movie) - 1
-        if movie in movies:
-            movies[movie] += 1
-        else:
-            movies[movie] = 1
-        if np.random.uniform(0,1) > portion:
-            cox.append(user)
-            coy.append(movie)
-        else:
-            if user in history:
-                history[user].append(movie)
-            else:
-                history[user] = [movie]
-    A = sparse.coo_matrix((np.ones(len(cox)), (cox, coy)), shape=(max(list(history) + cox) + 1, max(list(movies) + coy) + 1), dtype=np.float32)
-    U, S, VT = svds(A, d)
-    for i in range(U.shape[0]):
-        U[i] = U[i] / np.linalg.norm(U[i])
-    V = VT.T
-    for i in range(V.shape[0]):
-        V[i] = V[i] / np.linalg.norm(V[i])
+class c3_movielens_rng:
 
-    if L is None:
-        L = len(movies)
-    if h is None:
-        h = len(history)
-    selected_movies = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-L:]])
-    eligable_users = [x[1] for x in sorted([(overlap(history[user], selected_movies), user) for user in history])[-h:]]
-    logger.info('Initializing random settings "Contextual Movielens" complete')
-    s = ucb_settings(L=L, d=d, K=K, gamma=gamma, disj=disj, users=eligable_users, arms=selected_movies, ctrh=history, U=U, V=V, A=A.astype(np.int32))
-    logger.info(s)
-    return s
[…]

### 2016-01-24 experiment/utils.py

@@ -1,4 +1,6 @@
+from functools import reduce
 import random
+import heapq
 
 from scipy.linalg import sqrtm
 import numpy as np
@@ -8,7 +10,7 @@ colorama.init()
 def red(s):
     return colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE
 
-def pendium():
+def pendulum():
     return np.random.uniform(-1, 1)
 
 def uni(x):
@@ -43,6 +45,9 @@ def disturb(x, h):
     y = x + h * np.random.normal(0, 1, x.shape)
     return uni(y)
 
+def argmax_oracle(U, K, descend):
+    return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])][::2*descend-1]
+
 def reward(ctr, gamma, disj):
     conj = not disj
     for c, click in enumerate(ctr):
@@ -50,12 +55,22 @@ def reward(ctr, gamma, disj):
             return int(conj) + gamma ** c * (int(disj) - int(conj)), c
     return int(conj), len(ctr)
 
+def ereward(psarms, gamma, disj):
+    if disj:
+        return sum([gamma**i * reduce(float.__mul__, [1.,] + [1 - p for p in psarms][:i]) * psarms[i] for i in range(len(psarms))])
+    else:
+        return sum([(1 - gamma**i) * reduce(float.__mul__, [1.,] + psarms[:i]) * (1 - psarms[i]) for i in range(len(psarms))]) + reduce(float.__mul__, psarms)
+
+def serialize(s, *blst):
+    blst_local = blst + ('oracle', 'slot', 'realize', 'regret', 'params')
+    return '\n    '.join([' '.join([str(k), str(v)]) for k, v in s.__dict__.items() if not k in blst_local])
+
 class ucb_settings:
     def __init__(self, **s):
         self.__dict__ = s
 
     def __str__(self):
-        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if not k in ['arms', 'ctrh', 'users', 'U', 'V', 'x', 'A', 'G', 'oracle', 'theta']])
+        return '\n    '.join([str(k) + ' ' + str(v) for k, v in self.__dict__.items() if len(str(v)) < 15])
 
 if __name__ == '__main__':
     theta, Q, lamb, V = squni(5)

### 2016-01-25 contextual combinatorial cascading bandits.tex
update more comparisons

@@
 In network, the stopping criterion might be the first edge being blocked in a path.
-We also considers position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
+We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
 We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases.
-Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, context information and partial observability.
+Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, contextual information and partial observability.
 We experiment on both synthetic data and real data and show that our algorithm performs well.
@@
 
-A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the according reward.
+A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the corresponding reward.
 When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.
 
-Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need.
+Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive contents to meet specific user's need.
 Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user.
-Usually, both users and content are represented by feature vectors.
+Usually, both users and contents are represented by feature vectors.
 User features may contain basic attributes, like age, gender and nationality, and historical behaviors.
@@
 In real applications, the cascade model is popular to describe user behaviors in recommender systems.
-When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item.
+When recommended with a list of items, such as web pages or advertisements, the user checks from the first item until she finds an attractive item and selects it.
 The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, to determine whether a path is blocked, we check from the source to the end and can stop when meeting a blocked edge without need of knowing states of every edge in the path.
-In both of the two applications, we the feedback of items before some threshold, which is that user selects one item in recommender system and meeting a blocked edge in network routing.
+Also in networking routing problem, to determine whether a path is blocked, we check from the source node until we meet a blocked edge, where we don't have to know the states of all edges in the path.
+In both of the two applications, we observe the feedback of items before some threshold, which is user selecting one item in recommender system and meeting a blocked edge in network routing.
 We call this kind of feedback as {\it cascading feedback}.
 
-Usually in recommendations, different positions have different values. It is natural to introduce position discounts.
+Besides, in recommendations, different positions always have different values.
+In advertisement display, there are different positions in a website, the front middle, the left/right column, and the bottom and the positions in the front middle might charge highest price.
+Also in search, the first position in the first page for results might be the most important.
+So it is natural to introduce position discounts.
 
@@
 
+\begin{table}
+	\renewcommand{\arraystretch}{1.1}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		 &context &triggering &position discounts \\
+		\hline
+		CMAB &no &yes &no \\
+		\hline
+		CombCascade	&no &yes &no  \\
+		\hline
+		C$^2$UCB &yes &no &no  \\
+		\hline
+		C$^3$-UCB(our) &yes &yes &yes \\
+		\hline
+	\end{tabular}
+	\caption{Comparisons of our setting with previous ones }
+	\label{table:outline}
+\end{table}
+
 %Stochastic online learning with combinatorial actions has been studied with semi-bandit feedback \cite{chen2013combinatorial}.
@@
 
-Our work generalizes combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount.
-Our generalization expands the applicability of this model and we evaluate it on two real-world problems.
-\cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid.
-They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs; the reason might be that the items with lower preference come first, so the learning agent will collect more data.
-However, this might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
-Our work extends this part by introducing position discounted parameters.
-Under our setting, the items with higher UCB will come first.
+A simplified comparison is listed in Table \ref{table:outline}. We will explain in details.
+
+\cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective where the set of feasible actions form a uniform matroid and the reward of an action is $1$ if and only if there is at least an item with weight $1$.
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} generalized the framework with a {\it CombCascade} algorithm, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective where each feasible action is a chain of items and reward is $1$ if and only if all items have weight $1$.
+Our work generalizes this model to involve both contextual information and position discounts.
+The generalization expands the applicability of the model and we evaluate our algorithm on two real-world problems.
+
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that the user first examines the items with lower preference and is likely to examine more items to find one attractive, so the learning agent will collect more data.
+However, this result might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
+Our work extends this part by introducing position discounted parameters which can make the items with higher UCBs come first.
+They also experimented on an imperfect model, DBN, which does not fit their model.
+Our generalized setting can contain such models.
 \cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only.
-In our setting, users and items are represented by feature vectors which is more general.
+In our setting, users and items are represented by general feature vectors.
 
@@
 \cite{li2010contextual} studied multi-armed bandit with context information.
-\cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+They introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
 Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.
@@
 When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$.
-Our setting is more specific than theirs.
-The base arms in a super arm are triggered in list order; only the previous ones are triggered, the base arm can have the chance to be triggered.
-Also, they don't consider the contextual information and position discounts.
+Our method can generalize their setting with contextual information.
+It is hard to introduce position discounts for general combinatorial bandits except when feasible actions are lists, where items are triggered in list order.
+To introduce position discounts, we focus on the setting where feasible actions are lists.
 
@@
 
-We formulate the problem of {\em contextual combinatorial cascading bandit} as follows.
+We formulate the problem of {\em contextual combinatorial cascading bandits} as follows.
 Suppose we have a finite set $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}.
@@
 At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
-For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be the combined feature vector of base arm $a$ at time $t$.
+For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a} = (u_t, v_a)$ be the combined feature vector of base arm $a$ at time $t$.
 Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
-Next according to the user behavior and the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$.
-For example in recommender systems, the stopping criterion might be the user finds the first interesting item or has checked all items.
+Next according to the user behaviors under the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$.
+For example in recommender systems, the stopping criterion might be that the user has found an attractive item or has checked all items.
 
 Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$.
-Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
+Thus $\cH_t$ contains all information including observations at time $s < t$ and context information at time $t$.
+Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent random variables with sub-Gaussian tails and satisfy
 \begin{equation} % eq:expectation
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
+Following standard assumptions of stochastic MABs, a reward distribution has R-sub-Gaussian tail if for some known constant $R > 0$ and all $\lambda \in \RR$, one has
+$$
+\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
+$$
 Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.
-Following standard assumptions of stochastic MABs, we assume that all reward distributions have R-sub-Gaussian tails for some known constant $R > 0$; formally, for all $\lambda \in \RR$, one has
-$$
-\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2)/2.
-$$
 
@@
 
-We also consider the position discount $\gamma_k, k\leq K$.
-For example in recommender systems, the positions to display advertisements might have difference prices, hence of different values when user clicks on.
+We introduce position discounts $\gamma_k \in [0,1], k\leq K$.
+For example in website recommendations, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.
 
@@
 
+The assumption of Lipschitz continuity gives an estimate of changes in reward function.
+To obtain a good estimation of reward function, the position $k$ with large discount number $\gamma_k$ need a good estimation of $w(a_k)$.
+This means the positions with large discount numbers are more important to the reward function, or the reward function is more sensitive to these positions.
+For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.
+
 Notice that we don't require the knowledge how $f(A, w)$ is defined.
@@
 
-The $\alpha$-regret on time $t$ can be written as
-$$
-R_t = \alpha f(A_t^*, w_t) - f(A_t, w_t),
-$$
-where $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R_t$.
+The $\alpha$-regret of action $A$ on time $t$ can be written as
+$$
+R(t, A) = \alpha f_t^{\ast} - f(A, w_t),
+$$
+where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R(t, \bA_t)$.
 
@@
 \subsection{Algorithm}
+
+\begin{algorithm} %C^3-UCB algorithm
+	\caption{C$^3$-UCB}
+	\label{alg:ConComCascade}
+	\begin{algorithmic}[1]
+		\STATE {Parameters:}
+		\STATE {\qquad $\gamma_k\in[0,1], k \leq K; \delta > 0; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
+		\STATE {Initialization:}
+		\STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
+
+		\FORALL {$t=1,2,\ldots$}
+		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
+		\STATE {$\forall a\in E$, compute}
+		\STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
+
+		\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
+		\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
+		\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
+
+		\STATE {//Update statistics}
+		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
+		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
+		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
+		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
+		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
+		\ENDFOR {~~$t$}
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
-\begin{algorithm} %C^3-UCB algorithm
-  \caption{C$^3$-UCB}
-  \label{alg:ConComCascade}
-  \begin{algorithmic}[1]
-  	\STATE {Parameters:}
-  	\STATE {\qquad $\gamma_k\in[0,1], k \leq K; \delta > 0; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
-  	\STATE {Initialization:}
-    \STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
-
-    \FORALL {$t=1,2,\ldots$}
-      \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
-      \STATE {$\forall a\in E$, compute}
-      \STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
-
-      \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
-      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
-      \STATE {Play $\bA_t$ and observe $\bO_t； \bw_t(\ba_k^t), k\in[\bO_t]$}
-
-      \STATE {//Update statistics}
-      \STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
-      \STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
-      \STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
-      \STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-      \STATE {$\bbeta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
-    \ENDFOR {~~$t$}
-  \end{algorithmic}
-\end{algorithm}
-
 \subsection{Results}
@@
 	\begin{align}
-		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
 		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
@@
 First, our setting has contextual information.
-Second, we consider position-discounted weight $\gamma$.
-
-	In particular, by monotonicity and Lipschitz continuity, we have
-	$$
-		R(t, \bA_t) \leq B \sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
-	$$
-	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
+Second, we consider position discounts $\gamma_k, k \leq K$.
+
+	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
+	$$
+		R(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
+	$$
+	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms.
 Thus we need the following deduction.
@@
 The checking process stops if the user selects one item or has checked all items without selecting anyone.
-In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a}$, is binary to indicate whether the user has clicked on $a$ or not.
+In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has clicked on $a$ or not.
 Then the random variable $\bO_t$ satisfies
@@
 	\label{cor:or}
-	In the problem of cascading recommendation, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$ where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$.
+	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$.
 Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
@@
 \subsubsection{Conjunctive Objective}
-
-The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
+\label{sec:conj}
+
+The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and the learning agent receives reward $\gamma_k$ as the result.
 Similarly, we could also consider the case of conjunctive objective.
@@
 The learning agent observes all items until the first one with weight $0$.
-Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
-
-The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
+Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
+
+The more items reveals, the more reward the agent should receive. It is reasonable to assume that
 $$
@@
 		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
+		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right)
 	\end{align}
+	where $f^* = \min_{t} f_t^{\ast}$.
 \end{theorem}
@@
 The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
-And then use the following lemma to replace $\bA_t$ with a prefix.
+And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
 	\begin{lemma}
@@
 
-\subsection{Dissutions}
+\subsection{Discussions}
 
@@
 
-If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial}, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result; the reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandit is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved}.
-
-If our setting restricts to contextual combinatorial bandit \cite{qin2014contextual}, the random variable $\bO_t$ of observed base arms is $|\bA_t|$, which the number of base arms in chosen action $\bA_t$, and the minimal probability $p^*$ of observing all base arms in chosen actions should always be $1$.
-So our regret bound is of the same order with theirs.
-Notice that when applying their setting, the bound $C$ for Lipschitz continuity in our problem should be $\sqrt{K}$.
+If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial} which coincides with our section \ref{sec:conj} without contextual information and with position discounts $\gamma_k = 1$, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result.
+The reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandits is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved} and we use the technique of linear bandits to derive a confidence ellipsoid of $\theta_{\ast}$.
+
+If our setting restricts to contextual combinatorial bandits \cite{qin2014contextual}, where there are no triggering and no position discounts, so every base arm in action $\bA_t$ will be observed.
+The random variable $\bO_t$ of observed base arms should be $|\bA_t|$.
+The probability of full observation of $A$, $p_{t, A}$, should be $1$, so $p^{\ast} = 1$.
+And the position discounts $\gamma_k$ are all $1$.
+Then our regret bound is of the same order with theirs.
+Notice that if a reward function satisfies our assumptions of monotonicity and Lipschitz continuity, then the reward function satisfies their assumptions with the bound $C$ for Lipschitz continuity be $\sqrt{K}$.
+
+Our algorithm can also apply to the setting of \cite{chen2013combinatorial} with context information.
+However, the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notations) will be triggered.
 
@@
 The patient has to take the treatments one by one, so the series of treatment actually is a list.
-Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$, where $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment.
+Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$.
+$\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment.
 We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$.
@@
 Therefore, the expected reward has the property of monotonicity.
-For the Lipschitz continuity, by the Lipschitz continuity of expected reward function, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.
-
-Thus this expected reward function satisfies our setting but can not be fit into previous works.
-Similarly, a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.
+For the Lipschitz continuity, by the Lipschitz continuity of expected reward function with conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.
+
+Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives.
+Similarly, there exists a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.
 
@@
 
-\section{Experiments}
-
-We evaluate $C^3$-UCB in three experiments.
-
-\subsection{Synthetic}
-\label{sec:ExpSyn}
-
 % experiment - synthetic - results
@@
 
-In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems.
-This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly choose $\theta_* \in \RR^{d-1}$ with $\|\theta_{\ast}\|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
-This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} \in [0,1]$.
-Next the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experiment on four settings and demonstrate the results in Figure \ref{fig:synthetic}.
-The first two are of disjunctive objective with different position discount and the last two are of conjunctive objectives.
-Our algorithm outperforms than {\it CombCascade} algorithm because it does not use the context information.
-
-\subsection{MovieLens}
-
 \begin{figure}
@@
 \end{figure}
-
-In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of 2015.
-
-The Learning problem is formulated as follows.
-There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
-We split $A$ to be $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
-We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
-We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
-At every time $t$, use $x_{t,i} = u_{i}m_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
-And use $w_t(m) = F(I_t,m)$ as the weight of movie $m$ at time $t$.
-
-This problem is required to recommend fixed number of movies.
-Notice that it might have problem if we use $(u_{I_t}, m_j)$ as context information.
-Denote $\theta$ by $(\theta_u, \theta_m)$.
-So the expected mean of a base arm is of the form $\theta_u^{\top} u_{I_t} + \theta_m^{\top} m_j$ but the first term $\theta_u^{\top} u_{I_t}$ is fixed at time $t$ no matter what $\theta_u$ is.
-Therefore, to find the best super arm, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
-So to make use of the user's context information, we need some quadratic terms of user's information $u_i$ and movie's information $m_j$.
-That's why we use the convolution $u_{i}m_j^{\top}$ to denote the context of movie $j$ at time $t$.
-
-We experiment with different position discount and compare our algorithm with {\it CombCascade}.
-We show the results in Fig.~\ref{fig:movielens}.
-Our algorithms outperforms theirs, which demonstrate the advantage of introducing context information in real applications.
-
-\subsection{Network Routing}
 
@@
 
+\section{Experiments}
+
+We evaluate $C^3$-UCB in three experiments.
+
+\subsection{Synthetic}
+\label{sec:ExpSyn}
+
+In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems.
+This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
+At first, we randomly choose $\theta_* \in \RR^{d-1}$ with $\|\theta_{\ast}\|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} \in [0,1]$.
+Next the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experiment on four settings and demonstrate the results in Figure \ref{fig:synthetic}.
+The first two are of disjunctive objective with different position discount and the last two are of conjunctive objectives.
+Our algorithm outperforms than {\it CombCascade} algorithm because it does not use the context information.
+
+\subsection{MovieLens}
+
+In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of 2015.
+
+The Learning problem is formulated as follows.
+There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
+We split $A$ to be $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
+We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
+At every time $t$, use $x_{t,i} = u_{i}m_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
+And use $w_t(m) = F(I_t,m)$ as the weight of movie $m$ at time $t$.
+
+This problem is required to recommend fixed number of movies.
+Notice that it might have problem if we use $(u_{I_t}, m_j)$ as context information.
+Denote $\theta$ by $(\theta_u, \theta_m)$.
+So the expected mean of a base arm is of the form $\theta_u^{\top} u_{I_t} + \theta_m^{\top} m_j$ but the first term $\theta_u^{\top} u_{I_t}$ is fixed at time $t$ no matter what $\theta_u$ is.
+Therefore, to find the best super arm, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
+So to make use of the user's context information, we need some quadratic terms of user's information $u_i$ and movie's information $m_j$.
+That's why we use the convolution $u_{i}m_j^{\top}$ to denote the context of movie $j$ at time $t$.
+
+We experiment with different position discount and compare our algorithm with {\it CombCascade}.
+We show the results in Fig.~\ref{fig:movielens}.
+Our algorithms outperforms theirs, which demonstrate the advantage of introducing context information in real applications.
+
+\subsection{Network Routing}
+
 In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.
@@
 	\label{lem:DeltaEstimate}
-	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
-	$$
-		R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
+	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, 
+	%and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, 
+	then we have
+	$$
+		R(t, \bA_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 \begin{proof}
-	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then by monotonicity property of $f$,
-	$$
-	f_t^{\ast} = f(A_t^{\ast}, w_t) \leq f(A_t^{\ast}, \bU_t).
-	$$
+	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then
+	\begin{align*}
+		f(\bA_t, \bU_t) \geq \alpha f(\bA_t^{\bU_t}, \bU_t) \geq \alpha f(A_t^*, \bU_t) \geq \alpha f(A_t^*, w_t),
+	\end{align*}
+	where $f(\bA_t^{\bU_t}, \bU_t) = \max_{A \in \cS} f(A, \bU_t)$.
+The first inequality is because we choose $\bA_t$ by the $\alpha$-approximation oracle with input $\bU_t$; the second inequality is because the maximum of $f(\bA_t^{\bU_t}, \bU_t)$ given $\bU_t$; the third inequality is by the monotonicity of $f$ and the property $\bU_t \geq w_t$.
+Then
+	\begin{align*}
+		R(t, \bA_t) = &\alpha f(A_t^*, w_t) - f(\bA_t, w_t) \\
+		\leq &f(\bA_t, \bU_t) - f(\bA_t, w_t).
+	\end{align*}
 	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
 	$$
-	f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-	$$
-	Then by the condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
-	$$
-	f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-	$$
-	Therefore,
-	$$
-	R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-	$$
-\end{proof}
-
-Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$.
-However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
+	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+	$$
+	Then we have
+	\begin{align*}
+		R(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
+		\leq &\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+	\end{align*}
+\end{proof}
+
+Notice that the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$.
+However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms.
 Thus we need the following lemma.

### 2016-01-25 contextual combinatorial cascading bandits.tex
update synthetic experiment

@@
 \twocolumn[
-\icmltitle{Contextual Combinatorial Cascading Bandits}
+\icmltitle{Combinatorial Cascading Bandits with contextual information and position discounts}
 
@@
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
-Following standard assumptions of stochastic MABs, a reward distribution has R-sub-Gaussian tail if for some known constant $R > 0$ and all $\lambda \in \RR$, one has
+Following standard assumptions of stochastic MABs, a reward distribution has R-sub-Gaussian tail if for some known constant $R > 0$ and all $\lambda \in \RR$,
 $$
@@
 	\begin{align}
-		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		R(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
 		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
+		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
 	\end{align}
@@
 	\subfigure[Disjunctive, $\gamma=1$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-T10000-L100-K4-1.eps}}
-	\subfigure[Disjunctive, $\gamma=0.95$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-T10000-L100-K4-95.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
+	\subfigure[Disjunctive, $\gamma=0.9$]{
+		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
 	\subfigure[Conjunctive, $\gamma=1$ ]{
@@
 
-We evaluate $C^3$-UCB in three experiments.
+We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k, k\leq K$ have the form of $\gamma^{k-1}$ for some $\gamma$.
 
@@
 This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly choose $\theta_* \in \RR^{d-1}$ with $\|\theta_{\ast}\|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+At first, we randomly choose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
 Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
-This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} \in [0,1]$.
-Next the weight for arm $a$ at time $t$ is a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experiment on four settings and demonstrate the results in Figure \ref{fig:synthetic}.
-The first two are of disjunctive objective with different position discount and the last two are of conjunctive objectives.
-Our algorithm outperforms than {\it CombCascade} algorithm because it does not use the context information.
+This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
+Next we generate the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experiment on four settings.
+Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
+The first two are of the disjunctive objective where the learning agent observes from the first one of the chosen $K$ items until first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$.
+Notice that with $\gamma \leq 1$, the oracle to select a feasible action is to select the set of $K$ items with highest UCBs; $\gamma < 1$ will force the items in the optimal action list in the decreasing order of their UCBs and we also use this order when $\gamma = 1$.
+The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not use the context information.
 
@@
 	$$
-		R(t, \bA_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
+		R(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 	$$
-	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 		R(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
-		\leq &\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+		\leq &B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
 	\end{align*}
@@
 	$$
-	\EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	\EE_t[R(t, \bA_t)] \leq \frac{B}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 	$$
@@
 		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
-		\leq &\frac{1}{p^{\ast}} \EE \left[ \left.
+		\leq &\frac{B}{p^{\ast}} \EE \left[ \left.
 \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
-		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
+		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
 	\end{align}
@@
 	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
-	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
-	&\leq \EE\left[\frac{1}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
+	&\leq \EE \left[\frac{B}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
+	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
 	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
-	&\leq \frac{\sqrt{2}}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
+	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
 	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}

### 2016-01-26 contextual combinatorial cascading bandits.tex
update experiment

@@
 	\subfigure[Conjunctive, $\gamma=1$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-1.eps}}
-	\subfigure[Conjunctive, $\gamma=0.95$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-95.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-1.eps}}
+	\subfigure[Conjunctive, $\gamma=0.9$ ]{
+		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-9.eps}}
 	\caption{Synthetic Data Set, L=100, K=4, d=10}
@@
 Notice that with $\gamma \leq 1$, the oracle to select a feasible action is to select the set of $K$ items with highest UCBs; $\gamma < 1$ will force the items in the optimal action list in the decreasing order of their UCBs and we also use this order when $\gamma = 1$.
-The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not use the context information.
+The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
 

### 2016-01-27 contextual combinatorial cascading bandits.tex
modifications

@@
 \begin{abstract}
-We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at problem-specific criterion.
+
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at some problem-specific criterion.
 In recommendation, the stopping criterion might be the first item a user selects.
@@
 We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
-We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases.
-Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, contextual information and partial observability.
-We experiment on both synthetic data and real data and show that our algorithm performs well.
+We propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases.
+Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discounts, contextual information and partial observability.
+We experiment on synthetic and real data and demonstrate the advantage to involve contextual information and position discounts.
+
 \end{abstract}
@@
 
-A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the corresponding reward.
+Stochastic multi-armed bandit has been extensively studied in statistics and machine learning.
+The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown mean.
+The learning agent pulls one arm every time and tries to make the cumulative regret, the expected reward difference from the best arm with highest mean, as small as possible.
+The problem of MAB has to deal with the trade-off between exploitation (pull the best empirical arm) and exploration (try other arms which are not sufficiently estimated).
+
+Recently, stochastic combinatorial bandit started to draw attention \cite{gai2012combinatorial,chen2013combinatorial}.
+At every time step, a learning agent chooses a subset of ground items under certain combinatorial constraints and receives the corresponding reward.
+
 When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.

### 2016-01-27 contextual combinatorial cascading bandits.tex
update abstract, intro, related work and icml16 style

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%% ICML 2015 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % resulting PDF.  If this breaks your system, please commend out the
-% following usepackage line and replace \usepackage{icml2015} with
-% \usepackage[nohyperref]{icml2015} above.
+% following usepackage line and replace \usepackage{icml2016} with
+% \usepackage[nohyperref]{icml2016} above.
 \usepackage{hyperref}
@@
 % the note in the first column to ``Under review.  Do not distribute.''
-%\usepackage{icml2015}
+%\usepackage{icml2016}
 
@@
 % note in the first column to ``Proceedings of the...''
-\usepackage[accepted]{icml2015}
+\usepackage[accepted]{icml2016}
 
@@
 \twocolumn[
-\icmltitle{Combinatorial Cascading Bandits with contextual information and position discounts}
+\icmltitle{Contextual Combinatorial Cascading Bandits}
 
@@
 
-We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at some problem-specific criterion.
-In recommendation, the stopping criterion might be the first item a user selects.
-In network, the stopping criterion might be the first edge being blocked in a path.
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then recommends a list of items, and observes weights from the first item until some problem-specific stopping criterion happens.
+In recommendation, the stopping criterion might be the first item a user selects; in network, the stopping criterion might be the first edge being blocked in a path.
 We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
@@
 Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discounts, contextual information and partial observability.
-We experiment on synthetic and real data and demonstrate the advantage to involve contextual information and position discounts.
+The experiments on synthetic and real data demonstrate the advantage to involve contextual information and position discounts.
 
@@
 
-Stochastic multi-armed bandit has been extensively studied in statistics and machine learning.
-The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown mean.
+Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning.
+The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
 The learning agent pulls one arm every time and tries to make the cumulative regret, the expected reward difference from the best arm with highest mean, as small as possible.
@@
 Recently, stochastic combinatorial bandit started to draw attention \cite{gai2012combinatorial,chen2013combinatorial}.
-At every time step, a learning agent chooses a subset of ground items under certain combinatorial constraints and receives the corresponding reward.
-
-When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.
-
-Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive contents to meet specific user's need.
+At every time step, a learning agent chooses a subset of ground items (super arm) under certain combinatorial constraints.
+There are several different kinds of feedback: (1) bandit feedback, where the learning agent can only obtain the reward of chosen super arm; (2) semi-bandit feedback, where the learning agent can not only obtain the reward of the chosen super arm but also the weights (or rewards) of all base arms constituting the chosen super arm; (3) cascading feedback, where the learning agent can obtain the reward of the chosen super arm and the weights of some base arms in the chosen super arm, according to some problem-specific stopping criterion for observation.
+
+For recommendations, the cascade model is usually adopted to describe certain user behaviors.
+When recommended with a ordered list of items, such as web pages or advertisements, the user checks from the first item until she finds an attractive item and selects it.
+The items before the selected one are not attractive and the items after the selected one are unobserved.
+Also in networking routing problem, to determine whether a path is blocked, we check from the source node until we meet a blocked edge.
+The edges before the blocked one are unblocked and the edges after the blocked one are unobserved.
+In both of the two applications, we observe the feedbacks of a prefix of items in the chosen ordered list.
+The bandit problem with cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}.
+
+Personalized recommendation is a key feature of online recommendations to improve user satisfaction by providing attractive contents to meet specific user's need.
 Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user.
@@
 Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.
-
-In real applications, the cascade model is popular to describe user behaviors in recommender systems.
-When recommended with a list of items, such as web pages or advertisements, the user checks from the first item until she finds an attractive item and selects it.
-The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, to determine whether a path is blocked, we check from the source node until we meet a blocked edge, where we don't have to know the states of all edges in the path.
-In both of the two applications, we observe the feedback of items before some threshold, which is user selecting one item in recommender system and meeting a blocked edge in network routing.
-We call this kind of feedback as {\it cascading feedback}.
-
-Besides, in recommendations, different positions always have different values.
-In advertisement display, there are different positions in a website, the front middle, the left/right column, and the bottom and the positions in the front middle might charge highest price.
-Also in search, the first position in the first page for results might be the most important.
-So it is natural to introduce position discounts.
-
-Motivated by the above challenges, we develop an approach called {\it contextual combinatorial cascading bandits}.
+When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.
+
+In this paper, we propose a general framework for contextual cascading bandits encompassing the applications of recommendations and network routing problems as special cases.
+In addition, we take position discounts into consideration.
+In recommendations, different positions usually give different values.
+In advertisement display, there are different positions in a website, the front middle, the left/right column and the bottom, and the positions in the front middle might charge highest price.
+Users are most satisfied if the first returned result is what they want.
+We introduce the position discounts to model this variant of rewards.
+
+Putting context, cascading and position discounts together, we develop an approach called {\it contextual combinatorial cascading bandits}.
 This is a general framework which can describe many applications besides the above two applications.
 
-The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
+The main contributions of this paper can be summarized as follows: (1) we propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
 
@@
 		\hline
+		C$^2$UCB &yes &no &no  \\
+		\hline
 		CombCascade	&no &yes &no  \\
-		\hline
-		C$^2$UCB &yes &no &no  \\
 		\hline
@@
 
-A simplified comparison is listed in Table \ref{table:outline}. We will explain in details.
-
-\cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective where the set of feasible actions form a uniform matroid and the reward of an action is $1$ if and only if there is at least an item with weight $1$.
-The combinatorial cascading bandits of \cite{kveton2015combinatorial} generalized the framework with a {\it CombCascade} algorithm, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective where each feasible action is a chain of items and reward is $1$ if and only if all items have weight $1$.
-Our work generalizes this model to involve both contextual information and position discounts.
-The generalization expands the applicability of the model and we evaluate our algorithm on two real-world problems.
-
-The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that the user first examines the items with lower preference and is likely to examine more items to find one attractive, so the learning agent will collect more data.
-However, this result might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items.
-Our work extends this part by introducing position discounted parameters which can make the items with higher UCBs come first.
-They also experimented on an imperfect model, DBN, which does not fit their model.
-Our generalized setting can contain such models.
-\cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only.
+A summarized comparison of settings is listed in Table \ref{table:outline}, which we will explain in details next.
+And a comparison of regret bounds by different methods will be discussed in section \ref{set:diss}.
+
+The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least a "good" item (with weight $1$).
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good" (have weight $1$).
+Our work generalizes these model and involves both contextual information and position discounts.
+
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that the user first examines the items with lower preference and the learning agent will probably collect more data.
+The position discounts introduced will force the recommended set in the decreasing order of UCBs.
+The work of \cite{combes2015learning} considered a similar recommendation model to cascading bandits with position discount but they assumed that a user is interested in a single topic.
 In our setting, users and items are represented by general feature vectors.
@@
 \cite{li2010contextual} studied multi-armed bandit with context information.
-They introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
-Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.
+\cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+Their setting is more informative than ours and we have generalized their model with the same order of regret bound.
 
@@
 
-A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit.
+A newer version of \cite{chen2013combinatorial} (refered to as 'CMAB' in Table \ref{table:outline}) considered probabilistic triggering base arms in stochastic combinatorial semi-bandit.
 When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$.
@@
 \subsection{Discussions}
+\label{set:diss}
 
@@
 \bibliography{cascade_reference}
-\bibliographystyle{icml2015}
+\bibliographystyle{icml2016}
 

### 2016-01-28 contextual combinatorial cascading bandits.tex
update related work and problem formulation

@@
 
-The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that the user first examines the items with lower preference and the learning agent will probably collect more data.
-The position discounts introduced will force the recommended set in the decreasing order of UCBs.
-The work of \cite{combes2015learning} considered a similar recommendation model to cascading bandits with position discount but they assumed that a user is interested in a single topic.
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that better items come first, thus the user has a higher chance to pick a later item, thereby observing more feedbacks (of low weights in the front).
+The position discounts introduced in this paper forces the recommended set in the decreasing order of UCBs.
+The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward".
 In our setting, users and items are represented by general feature vectors.
@@
 Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
-\cite{li2010contextual} studied multi-armed bandit with context information.
-\cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
-Their setting is more informative than ours and we have generalized their model with the same order of regret bound.
-
-Our problem is a combinatorial partial monitoring problem where the learning agent may observe part of chosen items.
-\cite{agrawal1989asymptotically,bartok2012adaptive} studied partial monitoring problems but their algorithm is inefficient in our setting.
-\cite{lin2014combinatorial} studied combinatorial partial monitoring problem and their feedback is a fixed (with respect to chosen action) combination of weights.
-If chosen action is fixed, the combination of the weights to constitute feedback is not fixed in our setting.
-
-A newer version of \cite{chen2013combinatorial} (refered to as 'CMAB' in Table \ref{table:outline}) considered probabilistic triggering base arms in stochastic combinatorial semi-bandit.
+The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
+A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+Their feedback is more informative than ours.
+We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.
+
+There have been several pieces of work on partial monitoring MAB, but the results are not applicable to our setting.
+The papers of \cite{agrawal1989asymptotically,bartok2012adaptive} studied partial monitoring problems but their algorithms are inefficient in our setting.
+The work \cite{lin2014combinatorial} studied combinatorial partial monitoring problem and their feedback is a fixed (with respect to chosen action) combination of weights.
+In our setting, if chosen action is fixed, the number of observed items varies with the user's behavior, thus the combination constituting feedback is not fixed.
+
+The most updated version of \cite{chen2013combinatorial} (refered to as 'CMAB' in Table \ref{table:outline}) considered probabilistic triggering of base arms in stochastic combinatorial semi-bandit.
 When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$.
-Our method can generalize their setting with contextual information.
-It is hard to introduce position discounts for general combinatorial bandits except when feasible actions are lists, where items are triggered in list order.
-To introduce position discounts, we focus on the setting where feasible actions are lists.
+Our method generalizes their setting with contextual information.
+For general combinatorial multi-armed bandits, it is hard to introduce position discounts unless, like in our setting, feasible actions are lists and items are triggered in list order.
 
@@
 
-At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm.
-For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a} = (u_t, v_a)$ be the combined feature vector of base arm $a$ at time $t$.
+At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent.
+Each feature vector combines the information of the user and the corresponding base arm.
+For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = (u_t, v_a)$ , the concatenation of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$.
+Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$.
 Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
-Next according to the user behaviors under the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$.
-For example in recommender systems, the stopping criterion might be that the user has found an attractive item or has checked all items.
+In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion.
+For example in recommender systems, the stopping criterion might be that the user finds an attractive item.
+Then the learning agent observes the weights of first $\bO_t$ many base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.
 
 Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains all information including observations at time $s < t$ and context information at time $t$.
-Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent random variables with sub-Gaussian tails and satisfy
+Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$.
+Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$.
+Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
 \begin{equation} % eq:expectation
 \label{eq:expectation}
-  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
+\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
 \end{equation}
 where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
-Following standard assumptions of stochastic MABs, a reward distribution has R-sub-Gaussian tail if for some known constant $R > 0$ and all $\lambda \in \RR$,
-$$
-\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
-$$
-Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.
-
-We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$.
-At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$.
+Define by $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ the expected weight of base arm $a$ at time $t$.
+We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$,
+$$
+\EE[\exp(\lambda(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
+$$
+
+Recall that the random variable $\bO_t$ is the number of observed base arms in $\bA_t$ and at the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$.
 We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.
-Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s) \}_{k\leq \bO_s, s\leq t}$ and $\{x_t\}$, where $x_s = (x_{s,a})_{a \in E}$ denotes all context information at time $s$.
+Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s) \}_{k\leq \bO_s, s < t}$ and $\{x_t\}$.
 
 We introduce position discounts $\gamma_k \in [0,1], k\leq K$.
-For example in website recommendations, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.
+For example in website recommendations by a search engine, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.
 
 The reward function on round $t$ is an application dependent function.
-We assume the expected reward function of action $A$ is a function of expected weights $w$, denoted by $f(A,w)$, and satisfies the following two assumptions.
+We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E}$) and satisfies the following two assumptions.
 
 \paragraph{Monotonicity}
-The expected reward function $f(A, w)$ is a non-decreasing with respect to $w$. For any $w,w'\in \RR^E$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.
+The expected reward function $f(A, w)$ is a non-decreasing with respect to $w$: for any $w,w'\in [0,1]^E$, if $w(a) \leq w'(a)$, we have $f(A, w) \leq f(A, w')$.
 
@@
 The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
-In particular, there is a constant $B>0$ such that, for any $w,w'$, we have
+In particular, there is a constant $B>0$ such that, for any $w,w' \in [0,1]^E$, we have
 $$
@@
 The assumption of Lipschitz continuity gives an estimate of changes in reward function.
-To obtain a good estimation of reward function, the position $k$ with large discount number $\gamma_k$ need a good estimation of $w(a_k)$.
-This means the positions with large discount numbers are more important to the reward function, or the reward function is more sensitive to these positions.
+To obtain a good estimation of reward function, the position $k$ with large discount number $\gamma_k$ needs a good estimation of $w(a_k)$.
+This means the positions with large discount numbers $\gamma_k$ are more important to the reward function.
 For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.
 
-Notice that we don't require the knowledge how $f(A, w)$ is defined.
-We only assume the agent has access to an oracle $\cO_{\cS}(w)$.
-More precisely, an oracle $\cO_{\cS}(w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$, the oracle always returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
-
-The $\alpha$-regret of action $A$ on time $t$ can be written as
+Notice that we do not require the knowledge how $f(A, w)$ is defined.
+We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$.
+More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
+
+The $\alpha$-regret of action $A$ on time $t$ is
 $$
@@
 $$
-where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R(t, \bA_t)$.
+where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative (pseudo-)regret
+$$
+R(n) = \sum_{t=1}^n R(t, \bA_t).
+$$
 

### 2016-01-28 contextual combinatorial cascading bandits.tex
update experiments

@@
 		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
-	\caption{MovieLens}
+	\caption{MovieLens, L=200, K=4, d=5}
 	\label{fig:movielens} % 用于交叉引用
@@
 	\centering
-	\subfigure[Network 1221]{
-		\includegraphics[height = 3 cm, width = 5 cm]{network1-1.eps}}
+	\subfigure[Network 1239, $\gamma=1$]{
+		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
 	\subfigure[Network 1755]{
-		\includegraphics[height = 3 cm, width = 5 cm]{network3-1.eps}}
+		\includegraphics[height = 3 cm, width = 4 cm]{network3-1.eps}}
 	\subfigure[Network 3257 ]{
-		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
-	\caption{Network with latency}
+		\includegraphics[height = 3 cm, width = 4 cm]{network4-1.eps}}
+	\subfigure[Comparison of different $\gamma$ ]{
+		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
+	\caption{Network, $d=10$}
 	\label{fig:network} % 用于交叉引用
@@
 
-In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of 2015.
+In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset \cite{lam2013movie} of 2015.
 
@@
 There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
-We split $A$ to be $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We split $A$ as $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
 We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
@@
 
-This problem is required to recommend fixed number of movies.
-Notice that it might have problem if we use $(u_{I_t}, m_j)$ as context information.
+In this problem, any combination of $K$ movies is a feasible action.
+Notice that it might have problem if we use $(u_{I_t}, m_j)$, the concatenation of $u_{I_t}$ and $m_j$, as the context information.
 Denote $\theta$ by $(\theta_u, \theta_m)$.
 So the expected mean of a base arm is of the form $\theta_u^{\top} u_{I_t} + \theta_m^{\top} m_j$ but the first term $\theta_u^{\top} u_{I_t}$ is fixed at time $t$ no matter what $\theta_u$ is.
-Therefore, to find the best super arm, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
-So to make use of the user's context information, we need some quadratic terms of user's information $u_i$ and movie's information $m_j$.
-That's why we use the convolution $u_{i}m_j^{\top}$ to denote the context of movie $j$ at time $t$.
-
-We experiment with different position discount and compare our algorithm with {\it CombCascade}.
-We show the results in Fig.~\ref{fig:movielens}.
-Our algorithms outperforms theirs, which demonstrate the advantage of introducing context information in real applications.
+To recommend a list of movies by our algorithm, it is equivalent to recommend the first $K$ movies with highest UCBs listing in decreasing order.
+Thus, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
+So to make use of the user's context information, some quadratic terms of user's information $u_i$ and movie's information $m_j$ are needed.
+We use the convolution $u_{i}m_j^{\top}$ as the context information of movie $j$ at time $t$.
+
+First, we randomly choose $L=200$ movies and recommend $K=4$ movies on each round.
+We experiment with $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}.
+The results are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
 
@@
 
-In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.
+In the last experiment, we evaluate $C^3$-UCB on a problem of network routing with the {\it RocketFuel} dataset \cite{spring2004measuring}.
 
@@
 Notice here both $\theta$ and $x$ have been processed like section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
-The weight for each edge $e$ is a Bernoulli random variable with mean $\theta_*^{\top}x$.
-
-At each time $t$, A pair of source and terminal nodes $(v_s, v_t)$ are chosen randomly.
+The weight for each edge $e$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x$.
+
+At each time $t$, a pair of source and terminal nodes are chosen randomly.
 The learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between $v_s$ and $v_t$ to maximize the expected reward in the conjunctive objective.
-
-We experiment with different position discounts and on different networks. The results are shown in Fig.~\ref{fig:network}. Our algorithm ourperforms {\it CombCascade} algorithm.
+We experiment with different position discounts and different networks.
+The results are shown in Fig.~\ref{fig:network}.
+
+We also experiment on the influence of different $\gamma$'s to the regret.
+In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value.
+Suppose the true position discount $\gamma = 0.9$ and the learning agent sets $\gamma$ by her experience.
+We experiment on different setting $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma = 0.9$.
+The regrets with different $\gamma$'s are illustrated in Figure~\ref{fig:network}(d).
+The setting $\gamma$ is more close to the true $\gamma$, the regret is tending to be smaller.
+This experiment shows when there are position discounts in real application, it is better to represent this information to the model.
 
@@
 
-In this paper, we propose contextual combinatorial cascading bandits, a class of contextual combinatorial bandits with partial observations.
+In this paper, we propose contextual combinatorial cascading bandits with position discounts, a class of contextual combinatorial bandits with partial observations.
 

### 2016-01-28 contextual combinatorial cascading bandits.tex
add generalized reward function in the introduction

@@
 
-We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then recommends a list of items, and observes weights from the first item until some problem-specific stopping criterion happens.
-In recommendation, the stopping criterion might be the first item a user selects; in network, the stopping criterion might be the first edge being blocked in a path.
-We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item.
-We propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases.
-Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discounts, contextual information and partial observability.
-The experiments on synthetic and real data demonstrate the advantage to involve contextual information and position discounts.
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of the selected items
+	sequentially following the list order
+	until some problem-specific stopping criterion happens.
+In online recommendation, the stopping criterion might be the first item a user clicks; in networking, the stopping criterion might be the first edge blocked in a path. 
+We further consider position discounts in the list order, which means the agent's reward may
+	be discounted depending on the position where the stopping criterion is met.
+We formulate this problem in a general contextual combinatorial cascading bandit setting.
+We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
+Our work generalizes existing studies in several directions, including contextual information,
+	position discounts, and a more general cascading bandit model.
+Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.
 
@@
 The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
-The learning agent pulls one arm every time and tries to make the cumulative regret, the expected reward difference from the best arm with highest mean, as small as possible.
-The problem of MAB has to deal with the trade-off between exploitation (pull the best empirical arm) and exploration (try other arms which are not sufficiently estimated).
-
-Recently, stochastic combinatorial bandit started to draw attention \cite{gai2012combinatorial,chen2013combinatorial}.
+ The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
+ the difference in cumulative rewards between always pulling the best arm in expectation and
+ playing according to the agent's strategy.
+The problem of MAB has to deal with the trade-off between exploitation (pulling the best empirical arm) and exploration (trying other arms which are not sufficiently pulled).
+
+Recently, stochastic combinatorial bandit started to draw many attention \cite{gai2012combinatorial,chen2013combinatorial,lin2014combinatorial,GMM14,chen2014pure,KWAEE14,kveton2014tight,kveton2015cascading,kveton2015combinatorial,lin2015online,Combes2015}.
 At every time step, a learning agent chooses a subset of ground items (super arm) under certain combinatorial constraints.
-There are several different kinds of feedback: (1) bandit feedback, where the learning agent can only obtain the reward of chosen super arm; (2) semi-bandit feedback, where the learning agent can not only obtain the reward of the chosen super arm but also the weights (or rewards) of all base arms constituting the chosen super arm; (3) cascading feedback, where the learning agent can obtain the reward of the chosen super arm and the weights of some base arms in the chosen super arm, according to some problem-specific stopping criterion for observation.
-
-For recommendations, the cascade model is usually adopted to describe certain user behaviors.
-When recommended with a ordered list of items, such as web pages or advertisements, the user checks from the first item until she finds an attractive item and selects it.
-The items before the selected one are not attractive and the items after the selected one are unobserved.
-Also in networking routing problem, to determine whether a path is blocked, we check from the source node until we meet a blocked edge.
+There are several different kinds of feedback: (1) bandit feedback, where the learning agent can only obtain the reward of chosen super arm; (2) semi-bandit feedback, where the learning agent can also obtain the stochastic outcomes of the all base arms constituting the chosen super arm;
+(3) cascading feedback, where the learning agent can obtain the reward of the chosen super arm and the weights of some base arms in the chosen super arm, according to some problem-specific stopping criterion for observation.
+
+Cascading feedback model fits into many real application scenarios.
+For example, in online or mobile recommendation, it is a typical practice that an ordered list
+	(instead of a single item) is recommended to a user, who
+	usually goes over the list based on the recommended order and selects one of her interest to
+	click through.
+Thus it is reasonable to assume that items before the clicked item is of no interest to the user
+	while user's interest to items after the clicked item is unclear.
+Another example is in networking routing, where the agent needs to select a routing path that is least
+	likely of being blocked.
+To determine whether a path is blocked, the agent checks from the source node until meeting a blocked edge. 
 The edges before the blocked one are unblocked and the edges after the blocked one are unobserved.
-In both of the two applications, we observe the feedbacks of a prefix of items in the chosen ordered list.
+In both of the above applications, we observe the feedbacks of a prefix of items in the chosen ordered list.
 The bandit problem with cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}.
-
-Personalized recommendation is a key feature of online recommendations to improve user satisfaction by providing attractive contents to meet specific user's need.
+In this paper, we generalize their work in several directions to cover more realistic scenarios.
+
+First, we incorporate contextual information into cascading bandits.
+In online recommendation, contextual information includes various user and item information, 
+	and user behaviors in different contexts are different.
+Therefore utilizing contextual information is crucial for personalized recommendation.
+In network routing, temporal and spacial contextual information may also be useful to
+	determine better routing paths.
+Therefore, we incorporate contextual information into the cascading bandit formulation.
+Second, cascading bandits studied in \cite{kveton2015cascading,kveton2015combinatorial}
+	treats all positions in the cascading list equally, but in applications different positions
+	may bring different rewards.
+For example, in online recommendation, we usually prefer users to find their interested item
+	in the list as early as possible to increase user satisfaction.
+In network routing, we may prefer to hit a blocked edge as late as possible.
+To model these preference, we introduce position discounts to the cascading bandit, and
+	we show through experiments that incorporating position discounts may significantly
+	improve the learning result.
+Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial}
+	that are based on disjunctive and conjunctive binary random variables to more general
+	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
+This generalization allows us to covers new realistic scenarios not covered in
+	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
+	in Section~\ref{sec:diss}.
+
+%Personalized recommendation is a key feature of online recommendations to improve user satisfaction by providing attractive contents to meet specific user's need.
 Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user.
@@
 
-In this paper, we propose a general framework for contextual cascading bandits encompassing the applications of recommendations and network routing problems as special cases.
+%In this paper, we propose a general framework for contextual cascading bandits encompassing the applications of recommendations and network routing problems as special cases.
 In addition, we take position discounts into consideration.
@@
 
-Putting context, cascading and position discounts together, we develop an approach called {\it contextual combinatorial cascading bandits}.
-This is a general framework which can describe many applications besides the above two applications.
-
-The main contributions of this paper can be summarized as follows: (1) we propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.
+Putting context, position discounts, and generalized reward function together, we call
+	our learning model the {\it contextual combinatorial cascading bandits}. 
+We formally define this model, provide a complete algorithm and its regret analysis,
+	and conduct experiments on both synthetic and real-world recommendation
+	and network routing datasets to validate our approach.
+
+The main contributions of this paper can be summarized as follows: (1) we propose a general framework called contextual combinatorial cascading bandit that can many real-world application scenarios; 
+(2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
+	and real-world datasets and the results show that our algorithm effectively
+	incorporates contextual information and position discounts with significant performance gains.
 
@@
 A summarized comparison of settings is listed in Table \ref{table:outline}, which we will explain in details next.
-And a comparison of regret bounds by different methods will be discussed in section \ref{set:diss}.
+And a comparison of regret bounds by different methods will be discussed in section \ref{sec:diss}.
 
@@
 \subsection{Discussions}
-\label{set:diss}
+\label{sec:diss}
 

### 2016-01-28 contextual combinatorial cascading bandits.tex

@@
 
-The main contributions of this paper can be summarized as follows: (1) we propose a general framework called contextual combinatorial cascading bandit that can many real-world application scenarios; 
+The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information,
+position discounts, and general reward function to cover many real-world application scenarios; 
 (2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
@@
 	incorporates contextual information and position discounts with significant performance gains.
+
+\wei{The last two paragraphs have some repetition. 
+	Is there any technical part in the algorithm and analysis that we would like to 
+	mention in the introduction? So far the intro is only about conceptual additions to the model,
+	and nothing about technical challenges and our solution. 
+	It is ok if conceptual contribution is what we want to emphasize, but if there is any
+	technical contribution we can say, we can also say it here.}
 

### 2016-01-28 contextual combinatorial cascading bandits.tex

@@
 	\centering
-	\begin{tabular}{|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|}
 		\hline
-		 &context &triggering &position discounts \\
+		 &context &cascading &position  & general \\
+		 &         &          &discount & reward \\
 		\hline
-		CMAB &no &yes &no \\
+		CUCB &no &yes &no & yes \\
 		\hline
-		C$^2$UCB &yes &no &no  \\
+		C$^2$UCB &yes &no &no & yes  \\
 		\hline
-		CombCascade	&no &yes &no  \\
+		CombCascade	&no &yes &no  & no \\
 		\hline
-		C$^3$-UCB(our) &yes &yes &yes \\
+		C$^3$-UCB(ours) &yes &yes &yes & yes \\
 		\hline
@@
 
-A summarized comparison of settings is listed in Table \ref{table:outline}, which we will explain in details next.
-And a comparison of regret bounds by different methods will be discussed in section \ref{sec:diss}.
-
-The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least a "good" item (with weight $1$).
-The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good" (have weight $1$).
+We first discuss several studies most relevant to our work.
+Table \ref{table:outline} summarizes the different settings of these work, 
+	which we will explain in details next.
+A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
+	after we provide the full result of our regret bound.
+
+\wei{I revised the table, including adding a column about general reward, to match the introduction.}
+
+The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
 Our work generalizes these model and involves both contextual information and position discounts.
 
-The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference will come first) has a better performance than in decreasing order of their UCBs; the reason might be that better items come first, thus the user has a higher chance to pick a later item, thereby observing more feedbacks (of low weights in the front).
-The position discounts introduced in this paper forces the recommended set in the decreasing order of UCBs.
+\wei{I removed all references to "weight" so far. I think it is a bit unclear and could be confusing.}
+
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
+This unnatural result is perhaps because the order of items does not affect the reward and thus
+	putting low preference items first and high preference items last may result in more feedbacks
+	in the cascade.
+The position discounts introduced in this paper forces the recommended set in the decreasing order 
+	of UCBs, which is more realistic.
 The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward".
+\wei{So, does that mean \cite{combes2015learning}, comparing to ours, only lacks of contextual
+	information? or it our reward function is also more general? It is not very clear to me.}
 In our setting, users and items are represented by general feature vectors.
-
 Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
@@
 
-The most updated version of \cite{chen2013combinatorial} (refered to as 'CMAB' in Table \ref{table:outline}) considered probabilistic triggering of base arms in stochastic combinatorial semi-bandit.
-When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$.
-Our method generalizes their setting with contextual information.
-For general combinatorial multi-armed bandits, it is hard to introduce position discounts unless, like in our setting, feasible actions are lists and items are triggered in list order.
+\wei{please cite the arxiv version below}
+\citet{chen2013combinatorial} consider general reward functions and probabilistic triggering of base arms
+	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
+Cascading bandits can be viewed as a particular type of probabilistic triggering, where
+	only the head of the list is deterministically triggered and all the remaining items are
+	probabilistically triggered.
+However, their work does not consider contextual information, and it is also difficult to
+	incorporate position discounts in a general triggering model.
 
@@
 For example in recommender systems, the stopping criterion might be that the user finds an attractive item.
-Then the learning agent observes the weights of first $\bO_t$ many base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.
+Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.
 
@@
 \paragraph{Lipschitz continuity}
-The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
+The expected reward function $f(A, w)$ is Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
 In particular, there is a constant $B>0$ such that, for any $w,w' \in [0,1]^E$, we have
@@
 The assumption of Lipschitz continuity gives an estimate of changes in reward function.
-To obtain a good estimation of reward function, the position $k$ with large discount number $\gamma_k$ needs a good estimation of $w(a_k)$.
-This means the positions with large discount numbers $\gamma_k$ are more important to the reward function.
+To obtain a good estimation of reward function, the position $k$ with large discount value $\gamma_k$ needs a good estimation of $w(a_k)$.
+This means the positions with large discount $\gamma_k$ are more important to the reward function.
 For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.
+
+\wei{"large discount is more important" sounds weird. Usually large discount means cheaper and less
+	important products. 
+Perhaps we should seriously consider not using "position discount". It is a position weight, but
+since weight is already used, we should call it something else. Perhaps "position factor"? 	
+}
 
@@
 $$
+
+\wei{I think just writing $f(A,w_t)$ misses the context part. 
+	$f$ as such defined is only a function of action $A$ and expected reward $w$, the subscript $t$
+	is part of $w_t$, so is not an effective parameter. 
+	We may need to explicitly write context into $f$, such as
+	$f(A, w_t, x_t)$. 
+	}
+
+\wei{About approximation ratio $\alpha$: Do we have an example with an approximation oracle? 
+	If not, we could remove it.
+	It is also ok to keep it, but then in Theorems, like Theorem 4.3, we should say 
+	$\alpha$-regret.
+}
 

### 2016-01-29 contextual combinatorial cascading bandits.tex
update

@@
 
+\shuai{Our proofs build on previous work but also generalize their proof in our setting.
+Two challenges have been dealt with, partial observability on contextual bandits and general reward function with position discounts.
+}
+
 \begin{table}
@@
 	information? or it our reward function is also more general? It is not very clear to me.}
+\shuai{They dealt with discounted 'or' reward.
+At each time, suppose the user is from class $c$, then recommending her with $K$ items from item-class $h(c)$.
+We have more general reward function and more general context information.}
 In our setting, users and items are represented by general feature vectors.
@@
 \wei{please cite the arxiv version below}
-\citet{chen2013combinatorial} consider general reward functions and probabilistic triggering of base arms
+\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
 	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
@@
 }
+\shuai{What if I change this part by 'large $\gamma_k$'?}
 
@@
 }
+
+\shuai{There is no experiment with an approximation oracle. But if we want to add some experiment beyond our setting, maybe we can keep it.}
 
@@
 Our setting generalizes several existing works but not limited to them.
-For example, in medical treatment, a patient will be recommended with a series of treatments.
+If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in
+
+in medical treatment, a patient will be recommended with a series of treatments.
 The patient has to take the treatments one by one, so the series of treatment actually is a list.

### 2016-01-31 contextual combinatorial cascading bandits.tex
update until discussion

@@
 % my settings
-\usepackage{amssymb,amsfonts,amsmath,bbm}
+\usepackage{amsmath}\allowdisplaybreaks
+\usepackage{amssymb,amsfonts,bbm}
 \usepackage{mathrsfs}
@@
 	$$
-	\EE_t [R(t, \bA_t) ] \leq \frac{8}{f^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	\EE [R(t, \bA_t) |\cH_t ] \leq \frac{8}{f^{\ast}} \EE \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} | \cH_t\right].
 	$$
@@
 
-Putting context, position discounts, and generalized reward function together, we call
-	our learning model the {\it contextual combinatorial cascading bandits}. 
-We formally define this model, provide a complete algorithm and its regret analysis,
-	and conduct experiments on both synthetic and real-world recommendation
-	and network routing datasets to validate our approach.
-
-The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information,
-position discounts, and general reward function to cover many real-world application scenarios; 
-(2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
-	and real-world datasets and the results show that our algorithm effectively
-	incorporates contextual information and position discounts with significant performance gains.
-
-\wei{The last two paragraphs have some repetition. 
-	Is there any technical part in the algorithm and analysis that we would like to 
-	mention in the introduction? So far the intro is only about conceptual additions to the model,
-	and nothing about technical challenges and our solution. 
-	It is ok if conceptual contribution is what we want to emphasize, but if there is any
-	technical contribution we can say, we can also say it here.}
-
-\shuai{Our proofs build on previous work but also generalize their proof in our setting.
+%Putting context, position discounts, and generalized reward function together, we call our learning model the {\it contextual combinatorial cascading bandits}.
+We formally define this model, provide a complete algorithm and its regret analysis, and conduct experiments on both synthetic and real-world recommendation and network routing datasets to validate our approach.
+
+%The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information, position discounts, and general reward function to cover many real-world application scenarios; (2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic and real-world datasets and the results show that our algorithm effectively incorporates contextual information and position discounts with significant performance gains.
+
+The organization of this paper is as follows: section 2 compares our work with previous works; section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; section 5 demonstrates the experimental results; and section 6 gives a final conclusion.
+
+%\wei{The last two paragraphs have some repetition.
+Is there any technical part in the algorithm and analysis that we would like to mention in the introduction?
+So far the intro is only about conceptual additions to the model, and nothing about technical challenges and our solution.
+It is ok if conceptual contribution is what we want to emphasize, but if there is any technical contribution we can say, we can also say it here.}
+
+%\shuai{Our proofs build on previous work but also generalize their proof in our setting.
 Two challenges have been dealt with, partial observability on contextual bandits and general reward function with position discounts.
@@
 
-\wei{I revised the table, including adding a column about general reward, to match the introduction.}
-
 The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
@@
 Our work generalizes these model and involves both contextual information and position discounts.
-
-\wei{I removed all references to "weight" so far. I think it is a bit unclear and could be confusing.}
 
@@
 	of UCBs, which is more realistic.
-The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward".
-\wei{So, does that mean \cite{combes2015learning}, comparing to ours, only lacks of contextual
-	information? or it our reward function is also more general? It is not very clear to me.}
-\shuai{They dealt with discounted 'or' reward.
-At each time, suppose the user is from class $c$, then recommending her with $K$ items from item-class $h(c)$.
-We have more general reward function and more general context information.}
+The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where at each time step, the category, which the user belongs to, is known and the user is recommended with $K$ items from a user-related group of items.
+Under this setting, they considered position discounts.
 In our setting, users and items are represented by general feature vectors.
+
 Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
@@
 
-\wei{please cite the arxiv version below}
 \citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
@@
 \end{equation}
-where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.
-Define by $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ the expected weight of base arm $a$ at time $t$.
-We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$,
+where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
+$$
+w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
+$$
+the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$, 
 $$
@@
 The reward function on round $t$ is an application dependent function.
-We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E}$) and satisfies the following two assumptions.
+We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E} = (\theta_{\ast}x_{t,a})_{a \in E}) $ and satisfies the following two assumptions.
 
@@
 The assumption of Lipschitz continuity gives an estimate of changes in reward function.
-To obtain a good estimation of reward function, the position $k$ with large discount value $\gamma_k$ needs a good estimation of $w(a_k)$.
-This means the positions with large discount $\gamma_k$ are more important to the reward function.
+To obtain a good estimation of reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$.
+This means the positions with large $\gamma_k$ are more important to the reward function.
 For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.
-
-\wei{"large discount is more important" sounds weird. Usually large discount means cheaper and less
-	important products. 
-Perhaps we should seriously consider not using "position discount". It is a position weight, but
-since weight is already used, we should call it something else. Perhaps "position factor"? 	
-}
-\shuai{What if I change this part by 'large $\gamma_k$'?}
 
@@
 $$
-R(t, A) = \alpha f_t^{\ast} - f(A, w_t),
-$$
-where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative (pseudo-)regret
-$$
-R(n) = \sum_{t=1}^n R(t, \bA_t).
-$$
-
-\wei{I think just writing $f(A,w_t)$ misses the context part. 
-	$f$ as such defined is only a function of action $A$ and expected reward $w$, the subscript $t$
-	is part of $w_t$, so is not an effective parameter. 
-	We may need to explicitly write context into $f$, such as
-	$f(A, w_t, x_t)$. 
-	}
-
-\wei{About approximation ratio $\alpha$: Do we have an example with an approximation oracle? 
-	If not, we could remove it.
-	It is also ok to keep it, but then in Theorems, like Theorem 4.3, we should say 
-	$\alpha$-regret.
-}
-
-\shuai{There is no experiment with an approximation oracle. But if we want to add some experiment beyond our setting, maybe we can keep it.}
+R^{\alpha}(t, A) = \alpha f_t^{\ast} - f(A, w_t),
+$$
+where $f_t^{\ast} = f(A_t^*, w_t)$, $A_t^* = \argmax_{A\in\cS} f(A, w_t)$ and $w_t = (\theta_{\ast}^{\top}x_{t,a})_{a \in E}$. Our goal is to minimize the $\alpha$-regret
+$$
+R^{\alpha}(n) = \EE[ \sum_{t=1}^n R^{\alpha}(t, \bA_t)].
+$$
 
@@
 		\STATE {Parameters:}
-		\STATE {\qquad $\gamma_k\in[0,1], k \leq K; \delta > 0; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
+		\STATE {\qquad $\{\gamma_k \in [0,1]\}_{k\leq K}; \delta = \frac{1}{\sqrt{n}}; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
 		\STATE {Initialization:}
@@
 
-At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
+%At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action.
+
+By Equation \eqref{eq:expectation}, we have 
 $$
@@
 	\label{thm:main}
-	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity.
+	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$.
 Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
+Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
 	\begin{align}
-		R(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
+		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
 	\end{align}
+	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
 \end{theorem}
@@
 	The complete proof is in the Appendix.
-The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
+The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
 This reduction is challenging for two reasons.
@@
 	$$
-		R(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
+		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
 	$$
@@
 	\begin{align*}
-    	&\EE[R(t, \bA_t)|\cH_t] \\
-    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
-    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
+    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
+    	&\qquad = \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
+    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
     % &\EE_t[R_{\wedge}(t, \bA_t)] \\
@@
 So $f$ is the expected reward function and also a function of expected weights.
-It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity.
-(We leave all verifications in the appendix.) Then we have the following corollary.
+It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity with bound $B=1$.
+(We leave all verifications in the appendix.) Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order.
+So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
+Then we have the following corollary.
 \begin{corollary}
@@
 	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
+Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
 	\begin{align}
 		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
+		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
+		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
 	\end{align}
@@
 	\label{thm:and}
-	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$.
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$.
 Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$.
-Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
+Then the $\alpha$-regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
 	\begin{align}
 		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right)
+		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
+		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
 	\end{align}
-	where $f^* = \min_{t} f_t^{\ast}$.
 \end{theorem}

### 2016-01-31 contextual combinatorial cascading bandits.tex
update discussion and conclusion

@@
 % the note in the first column to ``Under review.  Do not distribute.''
-%\usepackage{icml2016}
+\usepackage{icml2016}
 
@@
 % note in the first column to ``Proceedings of the...''
-\usepackage[accepted]{icml2016}
+%\usepackage[accepted]{icml2016}
 
@@
 
-%Stochastic online learning with combinatorial actions has been studied with semi-bandit feedback \cite{chen2013combinatorial}.
-
 \section{Related Work}
@@
 
-Our setting generalizes several existing works but not limited to them.
+Our setting generalizes several existing works but does not limit to them.
+Consider in network routing problem, the observed information would be the latency on specific edges.
+The latency, or {\it weight}, on an edge is an exponential variable with mean $\theta_{\ast}^{\top}x$.
+Suppose we treat an edge as blocked if the latency on it is larger than some tolerance $\tau$.
+And we wait the edge to respond for at most $2\tau$ time.
+Then the real observed latency is new random variable from a cut-off exponential distribution with mean $\theta_{\ast}^{\top}x$.
+Then the edge is unblocked, or with reward $1$, if the new random vairable is less than the tolerance $\tau$ and the expectation is a function, say $g$, of $\theta_{\ast}^{\top}x$.
+It is not difficult to check that $g$ satisfies the properties of monotonicity and Lipschitz continuity.
+And the expected reward of a path is a composition of the expected reward function of conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the function $g$.
+(In original formulation, $g$ is the identity function, where $g(w) = w$.) Such an expected reward function satisfies the properties of monotonicity and Lipschitz continuity and can not be represented in conjunctive/disjunctive objectives, like in \cite{kveton2015cascading,kveton2015combinatorial}.
+
+%Our setting generalizes several existing works but not limited to them.
 If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in
 
-in medical treatment, a patient will be recommended with a series of treatments.
+%in medical treatment, a patient will be recommended with a series of treatments.
 The patient has to take the treatments one by one, so the series of treatment actually is a list.
@@
 So a treatment $a$ is successful with probability
-\begin{equation}
-\label{eq:betaTau}
-1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
-\end{equation}
-where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number.
+% \begin{equation}
+% \label{eq:betaTau}
+% 1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
+% \end{equation}
+% where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number.
 We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful.
 So the expected reward function is
-$$
-f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
-$$
-where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.
-
-By the expression of $f$, it is a function of the expected reward $w$.
+% $$
+% f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
+% $$
+% where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.
+
+%By the expression of $f$, it is a function of the expected reward $w$.
 Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$.
@@
 
-Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives.
+%Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives.
 Similarly, there exists a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.
@@
 
-\subsection{Synthetic}
+\subsection{Synthetic Data}
 \label{sec:ExpSyn}
@@
 
-\subsection{MovieLens}
+\subsection{MovieLens Data}
 
@@
 
-\subsection{Network Routing}
+\subsection{Network Routing Data}
 
@@
 
-In this paper, we propose contextual combinatorial cascading bandits with position discounts, a class of contextual combinatorial bandits with partial observations.
+In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action can be observed each time.
+We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions.
+The experiments conducted demonstrate the advantage to involve context information and position discounts.
+In the next, we want to derive a lower bound for this problem.
 

### 2016-01-31 contextual combinatorial cascading bandits.tex
update alpha, delta

@@
 Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$.
-Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time.
+In the same spirit of \cite{kveton2015combinatorial}, let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time.
 The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.
@@
 
-We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k, k\leq K$ have the form of $\gamma^{k-1}$ for some $\gamma$.
+We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
 
@@
 At first, we randomly choose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\| = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
 This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
@@
 	$$
-		R(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
+		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 	\begin{align*}
-		R(t, \bA_t) = &\alpha f(A_t^*, w_t) - f(\bA_t, w_t) \\
+		R^{\alpha}(t, \bA_t) = &\alpha f(A_t^*, w_t) - f(\bA_t, w_t) \\
 		\leq &f(\bA_t, \bU_t) - f(\bA_t, w_t).
@@
 	\begin{align*}
-		R(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
+		R^{\alpha}(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
 		\leq &B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
@@
 
-Notice that the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$.
+Notice that the upper bound of $R^{\alpha}(t, \bA_t)$ is in terms of all base arms of $\bA_t$.
 However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms.
@@
 	$$
-	\EE_t[R(t, \bA_t)] \leq \frac{B}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
 	$$
@@
 	\begin{align}
-		&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
-		=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
-		=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
-		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
+		&\EE[R^{\alpha}(t, \bA_t)|\cH_t]  \nonumber \\
+		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
+		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
+		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
 		\leq &\frac{B}{p^{\ast}} \EE \left[ \left.
@@
 	\begin{align}
-	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
-	&\leq \EE \left[\frac{B}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
-	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+	&R^{\alpha}(n) = \EE \left[\sum_{t=1}^{n} \EE[R^{\alpha}(t, \bA_t) | \cH_t] \right] \notag\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE \left[ \left.
+\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right| \cH_t \right] \right] \label{eq:pfMdeltaEst}\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
+	&\leq \EE \left[\frac{B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
+	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
 	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
-	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
+	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
 	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
@@
 	\begin{align}
-		&\EE_t[R(t, \bA_t)] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+		&\EE[R(t, \bA_t) | \cH_t] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
 		=& 2 \EE \left[ \left. R(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
@@
 	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
-	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d \delta^2}\right) } + \sqrt{\lambda} \right) \right. \notag\\
+	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d /n}\right) } + \sqrt{\lambda} \right) \right. \notag\\
 	&\qquad \qquad \left. \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
-	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda} \right) \notag\\
+	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{ \ln [ (1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda} \right) \notag\\
 	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMCdetEst}

### 2016-02-01 contextual combinatorial cascading bandits.tex
update until discussion

@@
 	until some problem-specific stopping criterion happens.
-In online recommendation, the stopping criterion might be the first item a user clicks; in networking, the stopping criterion might be the first edge blocked in a path. 
-We further consider position discounts in the list order, which means the agent's reward may
-	be discounted depending on the position where the stopping criterion is met.
+In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
+We further consider position discounts in the list order, which means the agent's reward is discounted depending on the position where the stopping criterion is met.
 We formulate this problem in a general contextual combinatorial cascading bandit setting.
@@
  The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
- the difference in cumulative rewards between always pulling the best arm in expectation and
+which is the difference in cumulative rewards between always pulling the best arm in expectation and
  playing according to the agent's strategy.
@@
 
-The organization of this paper is as follows: section 2 compares our work with previous works; section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; section 5 demonstrates the experimental results; and section 6 gives a final conclusion.
+The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; Section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; Section 5 demonstrates the experimental results; and section 6 gives a final conclusion.
 
@@
 	of UCBs, which is more realistic.
-The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where at each time step, the category, which the user belongs to, is known and the user is recommended with $K$ items from a user-related group of items.
-Under this setting, they considered position discounts.
+The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group.
+Under this particular setting, they considered position discounts.
 In our setting, users and items are represented by general feature vectors.
@@
 
-\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
+\citet{chen2015combinatorial} considered general reward functions and probabilistic triggering of base arms
 	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
@@
 $$
-the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$, 
-$$
-\EE[\exp(\lambda(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
+the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $b \in \RR$, 
+$$
+\EE[\exp(b(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(b^2 R^2 / 2).
 $$
@@
 We introduce position discounts $\gamma_k \in [0,1], k\leq K$.
-For example in website recommendations by a search engine, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.
+For example in website recommendations by a search engine, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive a discounted reward $\gamma_k$.
 
@@
 
-		\FORALL {$t=1,2,\ldots$}
+		\FORALL {$t=1,2,\ldots, n$}
 		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
@@
 \end{theorem}
-\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
+\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
 	The complete proof is in the Appendix.
@@
     	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
-    	&\qquad = \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
-    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
+    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
+    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
     % &\EE_t[R_{\wedge}(t, \bA_t)] \\
@@
 The checking process stops if the user selects one item or has checked all items without selecting anyone.
-In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has clicked on $a$ or not.
+In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has selected item $a$ or not.
 Then the random variable $\bO_t$ satisfies
@@
 
-The agent receives some reward if the user clicks on some item: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
+The agent receives some reward if the user selects an item: if the user selects $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
 Usually the importance of the positions is decreasing: the first position is most important.
@@
 $$
-where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
+where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.
 
@@
 
-We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}.
+We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
 The learning agent observes all items until the first one with weight $0$.
@@
 
-In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small.
+%In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small.
 So we have the following improvements.
 Suppose we also consider position discount here.
+
+In this case, we have the following improvements.
+Notice that in this case, given weights $w$, there is an oracle that outputs the best action.
+So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
 \begin{theorem} %main theorem
@@
 	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$.
-Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$.
-Then the $\alpha$-regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
+Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
 	\begin{align}
@@
 		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
-	\subfigure[Network 1755]{
-		\includegraphics[height = 3 cm, width = 4 cm]{network3-1.eps}}
+	\subfigure[Network 3356, $\gamma = 0.9$]{
+		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
 	\subfigure[Network 3257 ]{

### 2016-02-01 contextual combinatorial cascading bandits.tex
update experiments and conclusions

@@
 \subsubsection{Disjunctive Objective}
+\label{sec:disj}
 
@@
 
-In the above, we formulate the general setting of contextual combinatorial cascading bandit with position discount. This setting generalizes several existing results.
-
-If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial} which coincides with our section \ref{sec:conj} without contextual information and with position discounts $\gamma_k = 1$, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result.
+In the above, we formulate the general setting of contextual combinatorial cascading bandit with position discounts. This setting generalizes several existing results.
+
+If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial} which coincides with our Section \ref{sec:conj} without contextual information and with position discounts $\gamma_k = 1$, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result.
 The reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandits is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved} and we use the technique of linear bandits to derive a confidence ellipsoid of $\theta_{\ast}$.
+A similar comparison exists between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.
 
@@
 And the position discounts $\gamma_k$ are all $1$.
-Then our regret bound is of the same order with theirs.
-Notice that if a reward function satisfies our assumptions of monotonicity and Lipschitz continuity, then the reward function satisfies their assumptions with the bound $C$ for Lipschitz continuity be $\sqrt{K}$.
+Then our regret bound of Theorem \ref{thm:main} is of the same order with theirs.
+Notice that the Lipschitz bound $C$ in their setting is $\sqrt{K}$.
 
@@
 		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
-	\subfigure[Network 3257 ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{network4-1.eps}}
+	\subfigure[reward on network 1755 with latency, $\gamma = 0.9$ ]{
+		\includegraphics[height = 3 cm, width = 4 cm]{isp1755-T300000-gamma9-latency.eps}}
 	\subfigure[Comparison of different $\gamma$ ]{
@@
 
-We evaluate $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
+We evaluated $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
 
@@
 
-In the first experiment, we compare $C^3$-UCB to CombCascade on synthetic problems.
+In the first experiment, we compared $C^3$-UCB to CombCascade on synthetic problems.
 This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly choose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+At first, we randomly chose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
 This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
-Next we generate the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experiment on four settings.
+Next we generated the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experimented on four settings.
 Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
-The first two are of the disjunctive objective where the learning agent observes from the first one of the chosen $K$ items until first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$.
-Notice that with $\gamma \leq 1$, the oracle to select a feasible action is to select the set of $K$ items with highest UCBs; $\gamma < 1$ will force the items in the optimal action list in the decreasing order of their UCBs and we also use this order when $\gamma = 1$.
+The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$.
+Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order.
 The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
 
-\subsection{MovieLens Data}
-
-In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset \cite{lam2013movie} of 2015.
+\subsection{Movie Recommendation}
+
+In this experiment, we evaluated $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.
 
@@
 There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
-We split $A$ as $H + F$ by putting entry-$1$ in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
-We can regard $H$ as known information about history 'what users have watched' and regard $F$ as future criterion.
+Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+We regard $H$ as known information about history "what users have watched" and regard $F$ as future criterion.
 We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
@@
 Thus, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
-So to make use of the user's context information, some quadratic terms of user's information $u_i$ and movie's information $m_j$ are needed.
-We use the convolution $u_{i}m_j^{\top}$ as the context information of movie $j$ at time $t$.
-
-First, we randomly choose $L=200$ movies and recommend $K=4$ movies on each round.
-We experiment with $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}.
+So to make use of the user's context information, some nonlinear terms of user's information $u_i$ and movie's information $m_j$ are needed.
+To address this, we used the outer product $u_{i}m_j^{\top}$ as the context information of movie $j$ at time $t$.
+
+First, we randomly chose $L=200$ movies and recommended $K=4$ movies on each round.
+We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}.
 The results are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
@@
 
-In the last experiment, we evaluate $C^3$-UCB on a problem of network routing with the {\it RocketFuel} dataset \cite{spring2004measuring}.
-
-The ground set $E$ is the set of links in the network and the feasible action set $\cS$ is the set of all paths in the network.
-Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$ and at each time $t$, any link $e$ is assigned with a random $d$-dimensional context vector $x_{t,e}$.
+In the last experiment, we evaluated $C^3$-UCB on a problem of network routing with the {\it RocketFuel} dataset \cite{spring2004measuring}.
+
+The ground set $E$ is the set of links in the network.
+Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$.
+At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ is all simple paths between the source and destination nodes.
+Any edge $a$ in the set $\cS$ is assigned with a random $d$-dimensional context vector $x_{t,a}$.
 Notice here both $\theta$ and $x$ have been processed like section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
-The weight for each edge $e$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x$.
-
-At each time $t$, a pair of source and terminal nodes are chosen randomly.
-The learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between $v_s$ and $v_t$ to maximize the expected reward in the conjunctive objective.
-We experiment with different position discounts and different networks.
-The results are shown in Fig.~\ref{fig:network}.
-
-We also experiment on the influence of different $\gamma$'s to the regret.
+The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective.
+We experimented with different position discounts and different networks.
+The results are shown in Fig.~\ref{fig:network} (a) (b).
+
+We also experimented on the network with latency, where the latency on an edge is an exponential random variable with mean $\theta_{\ast}^{\top}x$ and the reward is $1$ if the latency is less than a tolerance $\tau = 0.75$.
+The comparison of rewards of our algorithm with {\it CombCascade} is shown in Fig.~\ref{fig:network} (c).
+
+We also experimented on the influence of different $\gamma$'s to the regret.
 In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value.

### 2016-02-02 contextual combinatorial cascading bandits.tex
modify
update

@@
 Each feature vector combines the information of the user and the corresponding base arm.
-For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = (u_t, v_a)$ , the concatenation of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$.
+For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$.
 Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$.
@@
 \paragraph{Lipschitz continuity}
-The expected reward function $f(A, w)$ is Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
-In particular, there is a constant $B>0$ such that, for any $w,w' \in [0,1]^E$, we have
+The expected reward function $f(A, w)$ is $B$-Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$.
+More specifically, for any $w,w' \in [0,1]^E$, we have
 $$
@@
 
-\begin{algorithm} %C^3-UCB algorithm
-	\caption{C$^3$-UCB}
-	\label{alg:ConComCascade}
-	\begin{algorithmic}[1]
-		\STATE {Parameters:}
-		\STATE {\qquad $\{\gamma_k \in [0,1]\}_{k\leq K}; \delta = \frac{1}{\sqrt{n}}; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
-		\STATE {Initialization:}
-		\STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
-
-		\FORALL {$t=1,2,\ldots, n$}
-		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
-		\STATE {$\forall a\in E$, compute}
-		\STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
-
-		\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
-		\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
-		\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
-
-		\STATE {//Update statistics}
-		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
-		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
-		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
-		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
-		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
-		\ENDFOR {~~$t$}
-	\end{algorithmic}
-\end{algorithm}
-
-%At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action.
+Before presenting the algorithm, we explain the main ideas in the design.
 
@@
 \end{proof}
+
+\begin{algorithm} %C^3-UCB algorithm
+	\caption{C$^3$-UCB}
+	\label{alg:ConComCascade}
+	\begin{algorithmic}[1]
+		\STATE {Parameters:}
+		\STATE {\qquad $\{\gamma_k \in [0,1]\}_{k\leq K}; \delta = \frac{1}{\sqrt{n}}; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
+		\STATE {Initialization:}
+		\STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
+
+		\FORALL {$t=1,2,\ldots, n$}
+		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
+		\STATE {$\forall a\in E$, compute}
+		\STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
+
+		\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
+		\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
+		\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
+
+		\STATE {//Update statistics}
+		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
+		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
+		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw_t(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
+		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
+		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
+		\ENDFOR {~~$t$}
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
-In the last experiment, we evaluated $C^3$-UCB on a problem of network routing with the {\it RocketFuel} dataset \cite{spring2004measuring}.
+In the last experiment, we evaluated $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.
 

### 2016-02-02 contextual combinatorial cascading bandits.tex
update algorithm to disjunctive

@@
 % the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{boring formatting information, machine learning, ICML}
+\icmlkeywords{combinatorial cascading bandits, context information, position discounts}
 
@@
 
+\section{Related Work}
+
+We first discuss several studies most relevant to our work.
+Table \ref{table:outline} summarizes the different settings of these work, 
+	which we will explain in details next.
+A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
+	after we provide the full result of our regret bound.
+
+The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
+Our work generalizes these model and involves both contextual information and position discounts.
+
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
+This unnatural result is perhaps because the order of items does not affect the reward and thus
+	putting low preference items first and high preference items last may result in more feedbacks
+	in the cascade.
+The position discounts introduced in this paper forces the recommended set in the decreasing order 
+	of UCBs, which is more realistic.
+The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group.
+Under this particular setting, they considered position discounts.
+In our setting, users and items are represented by general feature vectors.
+
+Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
+The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
+A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+Their feedback is more informative than ours.
+We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.
+
 \begin{table}
@@
 
-\section{Related Work}
-
-We first discuss several studies most relevant to our work.
-Table \ref{table:outline} summarizes the different settings of these work, 
-	which we will explain in details next.
-A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
-	after we provide the full result of our regret bound.
-
-The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
-The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
-Our work generalizes these model and involves both contextual information and position discounts.
-
-The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
-This unnatural result is perhaps because the order of items does not affect the reward and thus
-	putting low preference items first and high preference items last may result in more feedbacks
-	in the cascade.
-The position discounts introduced in this paper forces the recommended set in the decreasing order 
-	of UCBs, which is more realistic.
-The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group.
-Under this particular setting, they considered position discounts.
-In our setting, users and items are represented by general feature vectors.
-
-Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
-The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
-A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
-Their feedback is more informative than ours.
-We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.
-
 There have been several pieces of work on partial monitoring MAB, but the results are not applicable to our setting.
@@
 
-By Equation \eqref{eq:expectation}, we have 
+By Eq.~\eqref{eq:expectation}, we have 
 $$
@@
 $$
-Using the ridge regression of data 
+To estimate the expected reward, we reduce to the estimation of $\theta_{\ast}$, which can be obtained by the ridge regression on $x$ and samples of $\bw$.
+In details, using the ridge regression on data
 $$
@@
 For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
-Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.
+Next we obtain a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, restated as follows.
 
@@
 
-This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$ with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm. 
-Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
+Thus with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$ with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm. 
+Building on this, we can define an upper confidence bound of the expected weight for each base arm $a$ by
 \begin{equation}
@@
 \begin{proof}
-	$w_{t,a} = \theta_*^{\top} x_{t,a}$. By Holder's inequality,
-	\begin{align*}
-		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
-		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
-	\end{align*}
-	Then because
+	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
+	\begin{align*}
+		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
+		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
+		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
+		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
+	\end{align*}
+	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
 	\begin{align*}
 		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
-		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}
-	\end{align*}
-	and the definition of $\bU_t$ in \ref{lem:estimateU}, we can obtain the result.
+		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
+	\end{align*}
+	we can obtain the claimed result.
 \end{proof}
@@
 
-Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}.
+Based on the above analysis, we design our algorithm as follows.
 First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$.
 Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$.
-Third, the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$.
+Third, assume that the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$.
 Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$.
-In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.
+Our proposed algorithm, C$^3$-UCB, is described in $\mathbf{Algorithm}$ \ref{alg:ConComCascade}.
+There we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.
 
@@
 To state our main theorem, we need some definitions.
-Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$.
-In the same spirit of \cite{kveton2015combinatorial}, let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time.
+Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is, the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$.
+Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ be the minimal probability that an action could have all base arms observed over all time.
 The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.
@@
 	\label{thm:main}
-	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$.
+	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity.
 Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$.
@@
 \end{theorem}
+The regret bound deteriorates as $p^*$ gets small.
+But unfortunately, this reciprocal dependence on $p^*$ is not known how to improve, even in the special case of disjunctive objective.
+Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$.
+However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.
+
 \begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
@@
 The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
-This reduction is challenging for two reasons.
-First, our setting has contextual information.
-Second, we consider position discounts $\gamma_k, k \leq K$.
-
-	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
-	$$
-		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
+This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$.
+
+	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. First by monotonicity and $B$-Lipschitz continuity, we can prove
+	$$
+		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
 	$$
@@
     	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
-    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
-    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
-    \end{align*}
-    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
+    \end{align*}
+    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
     \begin{lemma}
@@
     \end{lemma}
-    Then we can prove this theorem.
+    The claimed result thus follows.
 \end{proof}
@@
 
-In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order.
+In the problem of cascading recommendation, when recommended with an ordered list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks the list in that order.
 The checking process stops if the user selects one item or has checked all items without selecting anyone.
-In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has selected item $a$ or not.
+The weight of base arm $a$ at time $t$, $\bw_{t,a}$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not.
 Then the random variable $\bO_t$ satisfies
@@
 
-The agent receives some reward if the user selects an item: if the user selects $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$.
-Usually the importance of the positions is decreasing: the first position is most important.
-So it is reasonable to assume that
+If the user selects the $k$-th item, then the learning agent receives reward $\gamma_k \in [0,1]$.
+Usually the importance of the positions is decreasing: the first position is the most important.
+Based on this, we assume that
 $$
@@
 $$
-At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
-$$
-\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
-$$
+If the user does not select any item, the agent gets no reward. At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
+$\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t}$. It is not hard to see that $\br_t = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t)$ is the disjunctive of discounted weights,
 where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.
@@
 \end{align}
-Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$.
+It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$.
 So $f$ is the expected reward function and also a function of expected weights.
-It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity with bound $B=1$.
-(We leave all verifications in the appendix.) Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order.
+It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity.
+(All verifications are left in the Appendix.)
+%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order.
 So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
-Then we have the following corollary.
+We have the following corollary.
 \begin{corollary}
@@
 	\begin{align}
-		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		R^{\alpha}(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
 		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
@@
 
-The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and the learning agent receives reward $\gamma_k$ as the result.
+The above formulation is on the disjunctive objective, that is, at each time step the user stops once she selects one item or has checked all recommended items.
 Similarly, we could also consider the case of conjunctive objective.
-In this case, we can derive a slightly better result.
-
-We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
+In this case, we derive a slightly better result.
+
+The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
 The learning agent observes all items until the first one with weight $0$.
-Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
-
-The more items reveals, the more reward the agent should receive. It is reasonable to assume that
+We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
+
+The more items reveals, the more reward the agent should receive. Based on this, we assume that
 $$
@@
 \end{align}
-then we have $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.
-
-%In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small.
-So we have the following improvements.
-Suppose we also consider position discount here.
-
-In this case, we have the following improvements.
-Notice that in this case, given weights $w$, there is an oracle that outputs the best action.
-So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
+then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$.
+Next is our result for the conjunctive objective with a slightly improved bound than Theorem \ref{thm:main}.
+
 \begin{theorem} %main theorem
@@
 	\begin{align}
-		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
+		R^{\alpha}(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
 		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
-		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
+		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(n) \right).
 	\end{align}
@@
 \begin{proof}
-	We will prove it in the appendix.
+	We will prove it in the Appendix.
 The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
@@
 
-%Our setting generalizes several existing works but not limited to them.
-If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in
-
-%in medical treatment, a patient will be recommended with a series of treatments.
-The patient has to take the treatments one by one, so the series of treatment actually is a list.
-Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$.
-$\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment.
-We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$.
-So a treatment $a$ is successful with probability
-% \begin{equation}
-% \label{eq:betaTau}
-% 1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
-% \end{equation}
-% where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number.
-We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful.
-So the expected reward function is
-% $$
-% f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
-% $$
-% where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.
-
-%By the expression of $f$, it is a function of the expected reward $w$.
-Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$.
-Therefore, the expected reward has the property of monotonicity.
-For the Lipschitz continuity, by the Lipschitz continuity of expected reward function with conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.
-
-%Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives.
-Similarly, there exists a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.
-
-% network latency
-
-% If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$.
-We call the latency is {\it high} if it is larger than a threshold $\tau$.
-A path is blocked if some of its edges has high latency.
-So a path is unblocked with probability
-% $$
-% \prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
-% $$
-
-% are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
-
-% To state our main theorem, we need some definitions. Let
-% $$
-%   f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
-% $$
-% denote the best expected reward of all time under the conjunctive objective.
-% Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is
-% \begin{align*}
-%   &p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
-%   &p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
-% \end{align*}
-% We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective.
-The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
-% \begin{theorem} %main theorem
-%   \label{thm:main}
-%   Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$. 
-%   Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
-%   Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
-%   \begin{align}
-%     R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
-%     &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-%     &=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right),
-%   \end{align}
-%   \begin{align}
-%     R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
-%     &\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
-%     &=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
-%   \end{align}
-% \end{theorem}
-
-% \subsection{Lower Bounds}
-
-% Suppose we have such a graph: 
-% $$
-%   \xymatrix{
-%   	S_0 \ar[r]^{\mu_{11}} \ar[d]_{\mu_{21}} & B_1 \ar[d]^{\mu_{12}} &\\
-%   	B_2 \ar[r]_{\mu_{22}} & S_1
-%   }
-% $$
-% There are two paths in this graph: $A_1 = \{S_0 \to B_1 \to S_1\}$ and $A_2 = \{S_0 \to B_2 \to S_1\}$. 
-% Let the feasible action set be $\cS = \{A_1, A_2\}.$ The $\mu$'s on the edges denote the probability of that edge being unblocked. 
-% For example, the probability of $S_0 \to B_2$ being unblocked is $\mu_3$. 
-% When we select a path, we get reward $1$ if and only if the path is unblocked and get reward $0$ if the path is blocked somewhere. 
-% Suppose we have $\mu_3 \geq \mu_1 \geq \mu_1\mu_2 > \mu_3 \mu_4$.
-% So the optimal action is $A_1$ with expected reward $\mu_1 \mu_2$ and $A_2$ is suboptimal with expected reward $\mu_3 \mu_4$.
-
-% Similar to the proof of Lai and Robbins 1985, we could get
-% $$
-% 	\EE[N_{A_2}]\mu_{21} \leq \frac{c \log(T)}{kl(\mu_{22}, \frac{\mu_{11}\mu_{12}}{\mu_{21}})}
-% $$
-
-%Next we analyze those times when the learning agent selects path $A_2$ instead of the optimal $A_1$. 
-%Notice that if the observed edges are $S_0 \to C \to D$ or $S_0 \to C$, we will not abandon $A_2$ because the expected rewards are $0.9 \times 0.8$ and $0.9$, higher than $0.64$. 
-%Only the times when all edges in $A_2$ being observed will help to recognize $A_2$ and abandon it. 
-%Recall that the probability of all edges of $A_2$ being observed is $p_{A_2} = 0.9 \times 0.8 = 0.72.$ 
-%So we have
-% $$
-%   \EE[N_{A_2}]p_{A_2} \leq \frac{c \log(T)}{\Delta^2},
-% $$
-%where $N_{A_2}$ is the number of times that learning agent selects $A_2$ and $\Delta$ is the difference of the best expected reward minus the expected reward of $A_2$.
-%Therefore,
-% $$
-%   \EE[N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta^2}
-% $$
-% and
-% $$
-%   R(T) \leq \EE[\Delta N_{A_2}] \leq \frac{c \log(T)}{p_{A_2} \Delta}.
-% $$
-
-% experiment - synthetic - results
 \begin{figure*}
@@
 
+\section{Experiments}
+
+We evaluated $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
+
+\subsection{Synthetic Data}
+\label{sec:ExpSyn}
+
+In the first experiment, we compared $C^3$-UCB to CombCascade on synthetic problems.
+This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
+At first, we randomly chose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
+Next we generated the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We experimented on four settings.
+Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
+The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$.
+Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order.
+The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
+
 \begin{figure}
@@
 
-\section{Experiments}
-
-We evaluated $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
-
-\subsection{Synthetic Data}
-\label{sec:ExpSyn}
-
-In the first experiment, we compared $C^3$-UCB to CombCascade on synthetic problems.
-This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly chose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
-This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
-Next we generated the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experimented on four settings.
-Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
-The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$.
-Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order.
-The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
-
 \subsection{Movie Recommendation}
@@
 We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
-At every time $t$, use $x_{t,i} = u_{i}m_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
-And use $w_t(m) = F(I_t,m)$ as the weight of movie $m$ at time $t$.
-
-In this problem, any combination of $K$ movies is a feasible action.
-Notice that it might have problem if we use $(u_{I_t}, m_j)$, the concatenation of $u_{I_t}$ and $m_j$, as the context information.
-Denote $\theta$ by $(\theta_u, \theta_m)$.
-So the expected mean of a base arm is of the form $\theta_u^{\top} u_{I_t} + \theta_m^{\top} m_j$ but the first term $\theta_u^{\top} u_{I_t}$ is fixed at time $t$ no matter what $\theta_u$ is.
-To recommend a list of movies by our algorithm, it is equivalent to recommend the first $K$ movies with highest UCBs listing in decreasing order.
-Thus, it is equivalent to rank the scores $\theta_m^{\top} m_j$ for each movie $j$.
-So to make use of the user's context information, some nonlinear terms of user's information $u_i$ and movie's information $m_j$ are needed.
-To address this, we used the outer product $u_{i}m_j^{\top}$ as the context information of movie $j$ at time $t$.
-
-First, we randomly chose $L=200$ movies and recommended $K=4$ movies on each round.
+At every time $t$, we randomly choose a user $I_t \in [N_1]$.
+Then in the same spirit of \cite{li2010contextual}, use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{i}$ and $m_{j}$, as the context information for each movie $j$.
+The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.
+
+For this experiment, we randomly chose $L=200$ movies and recommended $K=4$ movies at each time.
 We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}.
@@
 
+\newpage
 \bibliography{cascade_reference}
@@
 
+\newpage
+
 \appendix
@@
 	\label{lem:DeltaEstimate}
-	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, 
+	For any time $t$ and $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t)$, if $f$ satisfies the two assumptions of monotonicity and $B$-Lipschitz continuity, 
 	%and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, 
@@
 	$$
-		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
+		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k}}_{\bV_{t-1}^{-1}}.
 	$$
@@
 	\begin{align*}
-		f(\bA_t, \bU_t) \geq \alpha f(\bA_t^{\bU_t}, \bU_t) \geq \alpha f(A_t^*, \bU_t) \geq \alpha f(A_t^*, w_t),
-	\end{align*}
-	where $f(\bA_t^{\bU_t}, \bU_t) = \max_{A \in \cS} f(A, \bU_t)$.
-The first inequality is because we choose $\bA_t$ by the $\alpha$-approximation oracle with input $\bU_t$; the second inequality is because the maximum of $f(\bA_t^{\bU_t}, \bU_t)$ given $\bU_t$; the third inequality is by the monotonicity of $f$ and the property $\bU_t \geq w_t$.
+		f(\bA_t, \bU_t) \geq \alpha f(\bA^{\bU_t}, \bU_t) \geq \alpha f(A_t^*, \bU_t) \geq \alpha f(A_t^*, w_t),
+	\end{align*}
+	where $\bA^{\bU_t} = \argmax_{A \in \cS} f(A, \bU_t)$.
+The first inequality is because we choose $\bA_t$ by the $\alpha$-approximation oracle with input $\bU_t$; the second inequality is because the maximum of $f(\bA^{\bU_t}, \bU_t)$ given $\bU_t$; the third inequality is by the monotonicity of $f$ and the property $\bU_t \geq w_t$.
 Then
@@
 	\end{align*}
-	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
-	$$
-	f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
-	$$
+	By Lipschitz continuity of $f$ and Lemma \ref{lem:estimateU},
+	\begin{align*}
+		f(\bA_t, \bU_t) &\leq f(\bA_t, w_t) + B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \abs{\bU_t(\ba_k^t) - w_t(\ba_k^t)}\\
+		& \leq f(\bA_t, w_t) + 2B \sum_{k=1}^{\abs{\bA_t}} \gamma_k\bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+	\end{align*}
 	Then we have
@@
 		R^{\alpha}(t, A) \leq &f(\bA_t, \bU_t) - f(\bA_t, w_t) \\
-		\leq &B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
+		\leq &2B \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
 	\end{align*}
@@
 	\label{lem:DeltaEsimateWithP*}
-	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
-	$$
-	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
+	Suppose the Eq.~\eqref{eq:estimateTheta} holds for time $t-1$. Then
+	$$
+	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{2B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
 	$$
@@
 		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
-		\leq &\frac{B}{p^{\ast}} \EE \left[ \left.
+		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left.
 \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
-		\leq &\frac{B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
+		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
 	\end{align}
@@
 \end{proof}
-
-% \begin{lemma} %lem:DeltaEstimate
-%   \label{lem:DeltaEstimate}
-%   For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
-%   $$
-%     R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
-%   $$
-%   if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
-%   $$
-%     R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
-%   $$
-% \end{lemma}
-% \begin{proof}
-%   By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
-%   $$
-%     f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
-%   $$
-%   By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
-%   $$
-%     f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-%   $$
-%   By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
-%   $$
-%     f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-%   $$
-%   Therefore,
-%   $$
-%     R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
-%   $$
-%   The result for the conjunctive case can be deduced in a similar way.
-% \end{proof}
-
-% Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
-% However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms.
-Thus we need the following lemma.
-
-% \begin{lemma} %lem:DeltaEsimateWithP*
-%   \label{lem:DeltaEsimateWithP*}
-%   Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
-%   Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
-%   $$
-%     \EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-%   $$
-%   If we have
-%   $$
-%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
-%   $$
-%   then
-%   $$
-%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-%   $$
-% \end{lemma}
-% \begin{proof}
-%   For the disjunctive case,  
-%   \begin{align}
-%     &\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
-%     =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
-%     =& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
-%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
-%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left.
-\sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
-%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
-%   \end{align}
-%   Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$. 
-%   Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
-%   Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. 
-%   Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
-%   Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.
-
-%   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$.
-%   By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
-%   Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
-%   \begin{align}
-%     &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
-%     =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
-%     =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
-%     \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
-%   \end{align}
-%   Next, we have
-%   \begin{equation} \label{eq:andstarbt}
-%     f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
-%   \end{equation}
-%   where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
-
-%   Then by Lemma \ref{lem:estimateTech},
-%   \begin{equation} \label{eq:btuttrue}
-%     f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
-%   \end{equation}
-%   Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
-%   \begin{align}
-%     R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
-%     & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
-%   \end{align}
-%   Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
-%   \begin{align*}
-%     &\EE_t[R_{\wedge}(t, \bA_t)] \\
-%     \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-%     \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
-%   \end{align*}
-% \end{proof}
 

### 2016-02-02 contextual combinatorial cascading bandits.tex
update proof

@@
 	$$
-	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
+	p_{t, B} \geq \frac{\alpha}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R^{\alpha}(t, B) \geq \frac{1}{2} R^{\alpha}(t, A).
 	$$ 
@@
 	$$
-	\EE [R(t, \bA_t) |\cH_t ] \leq \frac{8}{f^{\ast}} \EE \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} | \cH_t\right].
+	\EE [R^{\alpha}(t, \bA_t) |\cH_t ] \leq \frac{8}{\alpha f^{\ast}} \EE \left[ \left. \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t\right].
 	$$
@@
 	\begin{align}
-		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
+		R^{\alpha}(n) &\le \frac{2\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
 		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
@@
 	\begin{align}
-		R^{\alpha}(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
+		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
+		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
 		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
@@
 	\label{thm:and}
-	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$.
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$.
 Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
 	\begin{align}
-		R^{\alpha}(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
-		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(n) \right).
+		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
+		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
+		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
 	\end{align}
@@
 
-Now we are ready to prove the main theorem.
+Lemma \ref{lem:SumXiEstimateInDet} and Lemma \ref{lem:detVt} combined imply Lemma \ref{lem:XNormSumEst}. Now we are ready to prove the main theorem.
 
 \begin{proof}[ of Theorem \ref{thm:main}]
-	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
+	Suppose Ineq.~\eqref{eq:estimateTheta} holds for all time $t$, which is true with probability $1-\delta$. Then with probablity $1-\delta$, we have
 	\begin{align}
 	&R^{\alpha}(n) = \EE \left[\sum_{t=1}^{n} \EE[R^{\alpha}(t, \bA_t) | \cH_t] \right] \notag\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \EE \left[ \left.
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{2B}{p^*} \EE \left[ \left.
 \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right| \cH_t \right] \right] \label{eq:pfMdeltaEst}\\
-	&\leq \EE\left[\sum_{t=1}^{n} \frac{B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
-	&\leq \EE \left[\frac{B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
-	&\leq \EE\left[\frac{B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
+	&\leq \EE\left[\sum_{t=1}^{n} \frac{2B}{p^*} \bbeta_{n}(\delta) \EE \left[ \left. \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right] \right] \label{eq:pfMbeta}\\
+	&\leq \EE \left[\frac{2B}{p^*} \bbeta_n(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
+	&\leq \EE\left[\frac{2B}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d / n} \right)} + \sqrt{\lambda} \right) \right. \notag\\
 	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
-	&\leq \frac{\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
+	&\leq \frac{2\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \notag\\
 	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
@@
 	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+
+	Also $R^{\alpha}(n) \leq n$ and $\delta = \frac{1}{\sqrt{n}}$. We have 
+	\begin{align*}
+		R^{\alpha}(n) &\leq \frac{2\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \\
+		&\qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} + \sqrt{n}.
+	\end{align*}
 \end{proof}
@@
 $$
-where $A = (a_1, \ldots, a_{|A|})$, defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and Lipschitz continuity.
+where $A = (a_1, \ldots, a_{|A|})$, defined in~Eq.\eqref{eq:OrRewardFunc}, satisfies the properties of monotonicity and $1$-Lipschitz continuity.
 
@@
 	\label{lem:orMonotonicity}
-	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
-Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$, that is, if $w \leq w' \in [0,1]^E$, then for any $A \in \prod^{\leq K}$, it holds that
 	$$
@@
 \begin{proof}
-	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$. First, for $1 \leq k \leq m$, we have
 	\begin{align*}
@@
 	\label{lem:orLip}
-	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
+	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{E}$. Then
 	$$
@@
 \begin{proof}
-	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, suppose $w \leq w'$ and $w' = w + v$.
+	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$.
+Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$.
+First, suppose $w \leq w'$ and $w' = w + v$.
 
@@
 
-	For general $w,w' \in [0,1]^L$, by last lemma, we have
-	$$
-	f(A, w\wedge w') \leq f(A, w), f(A, w') \leq f(A, w\vee w'),
+	For general $w,w' \in [0,1]^L$, by Lemma \ref{lem:orMonotonicity}, we have
+	$$
+	f(A, w\wedge w') \leq \{f(A, w), f(A, w') \}\leq f(A, w\vee w'),
 	$$
@@
 
-We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then by Theorem \ref{thm:main}, the corollary can be obtained.
+We have proved the monotonicity and Lipschitz continuity of expected reward function $f$. Then the corollary follows Theorem \ref{thm:main}.
 
@@
 where $A = (a_1, \ldots, a_{|A|})$, as defined in~Eq.\eqref{eq:AndRewardFunc}.
-First, similar to last section, we prove this reward function satisfies the properties of monotonicity and Lipschitz continuity.
+First, similar to last section, we prove this reward function satisfies the properties of monotonicity and $1$-Lipschitz continuity.
 
@@
 	\label{lem:andMonotonicity}
-	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$.
-Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
+	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $w \leq w' \in [0,1]^E$, then for any $A \in \prod^{\leq K}$, it holds that
 	$$
@@
 \begin{proof}
-	Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.
+	Denote $w = (w_a)_{a \in E}$ and $w' = (w'_a)_{a \in E}$. Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.
 
@@
 		\leq& (1-\gamma_m)(1 - p_{A} w_m) + p_{A} w_m \\
-		\leq& (1-\gamma_m) + \gamma_m p_{\wedge, A};
+		\leq& (1-\gamma_m) + \gamma_m p_{A};
 		\end{align*}
@@
 \begin{proof}
-	$w_t = \theta_*^{\top} x_t$. If $f(A, w_t) \geq \frac{1}{2} f_{t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
-	$$
-	p_{t, A} \geq \frac{1}{2} f_{t}^{\ast} - 1 + \gamma_{\abs{A}}.
+	Recall $w_t = \theta_*^{\top} x_t$. If $f(A, w_t) \geq \frac{\alpha}{2} f_{t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
+	$$
+	p_{t, A} \geq \frac{\alpha}{2} f_{t}^{\ast} - 1 + \gamma_{\abs{A}}.
 	$$
@@
 
-	Now suppose $f(A, w_t) \leq \frac{1}{2} f_{t}^{\ast}$. Let
+	Now suppose $f(A, w_t) \leq \frac{\alpha}{2} f_{t}^{\ast}$. Let
 	$$
@@
 	$$
-	Then there exists a $k$ such that $\frac{1}{2}f_{t}^{\ast} \in I_k$:
-	$$
-	f(B_k,w) \leq \frac{1}{2}f_{t}^{\ast} \leq 1 - \gamma_k + \gamma_k p_{\wedge, t, B_k}
-	$$
-	Therefore, the results are derived.
+	Then there exists a $k$ such that $\frac{\alpha}{2}f_{t}^{\ast} \in I_k$:
+	$$
+	f(B_k,w) \leq \frac{\alpha}{2}f_{t}^{\ast} \leq 1 - \gamma_k + \gamma_k p_{t, B_k}
+	$$
+	Then 
+	$$
+	R^{\alpha}(t,B_k) = \alpha f_t^* - f(B_k, w_t) \geq \frac{\alpha}{2}f_t^* \geq \frac{1}{2} R^{\alpha}(A, w_t),
+	$$
+	and
+	$$
+	p_{t, B_k} \geq \frac{\alpha}{2}f_t^* - 1 + \gamma_{|B_k|}.
+	$$
 \end{proof}
@@
 \begin{lemma}
-	If we have $\gamma_K \geq 1 -  \frac{1}{4} f^{\ast}$, where $f^{\ast} = \min_{1 \leq t \leq T} f_{t}^{\ast}$, then
+	If we have $\gamma_K \geq 1 -  \frac{\alpha}{4} f^{\ast}$, where $f^{\ast} = \min_{1 \leq t \leq T} f_{t}^{\ast}$, then
 	\CEqDeltaEstAnd
@@
 \begin{proof}
-	By Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{t, \bB_t} \geq \frac{1}{2}f_{t}^* - 1 + \gamma_{|\bB_t|}$ and $R(t, \bB_t) \geq \frac{1}{2} R(t, \bA_t)$.
-By the assumption that $1-\gamma_{|\bB_t|} \leq 1-\gamma_K \leq \frac{1}{4} f^{\ast} \leq \frac{1}{4} f^*_{t}  $, we have $p_{t, \bB_t} \geq \frac{1}{4}f_{t}^*$.
+	By Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{t, \bB_t} \geq \frac{\alpha}{2}f_{t}^* - 1 + \gamma_{|\bB_t|}$ and $R(t, \bB_t) \geq \frac{1}{2} R(t, \bA_t)$.
+By the assumption that $1-\gamma_{|\bB_t|} \leq 1-\gamma_K \leq \frac{\alpha}{4} f^{\ast} \leq \frac{\alpha}{4} f^*_{t}  $, we have $p_{t, \bB_t} \geq \frac{\alpha}{4}f_{t}^*$.
 
@@
 	\begin{align}
-		&\EE[R(t, \bA_t) | \cH_t] \leq 2 \EE[R(t, \bB_t) \left. \right| \cH_t] \nonumber \\
-		=& 2 \EE \left[ \left. R(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
-		=& 2\EE \left[ \left. R(t, \bB_t) \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
-		\leq &\frac{8}{f_{t}^{\ast}} \EE \left[ \left. R(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
+		&\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq 2 \EE[R^{\alpha}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
+		=& 2 \EE \left[ \left. R^{\alpha}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
+		=& 2\EE \left[ \left. R^{\alpha}(t, \bB_t) \frac{1}{p_{t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
+		\leq &\frac{8}{\alpha f_{t}^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
 	\end{align}
@@
 	\begin{align}
-		R(t, \bB_t) & = f_{t}^{\ast} - f(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
+		R^{\alpha}(t, \bB_t) & = f_{t}^{\ast} - f(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
 		& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
@@
 	\begin{align*}
-		&\EE_t[R(t, \bA_t)] \\
-		\leq& \frac{8}{f_{t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
-		\leq& \frac{8}{f^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
+		&\EE_t[R^{\alpha}(t, \bA_t)] \\
+		\leq& \frac{8}{\alpha f_{t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
+		\leq& \frac{8}{\alpha f^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
 	\end{align*}
@@
 \begin{proof}[of Theorem \ref{thm:and}]
-	Similar to the proof of Theorem \ref{thm:main}, we have the following derivation:
+	Similar to the proof of Theorem \ref{thm:main}, we have the following derivation. Suppose Ineq.\eqref{eq:estimateTheta} holds for all time $t$, then
 	\begin{align}
-	&R(n) = \EE \left[ \sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
-	\leq& \EE \left[\sum_{t=1}^{n} \frac{8}{f^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
-	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
-	\leq& \EE\left[\frac{8}{f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
-	\leq& \EE \left[\frac{\sqrt{128}}{f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d /n}\right) } + \sqrt{\lambda} \right) \right. \notag\\
+	&R^{\alpha}(n) = \EE \left[ \sum_{t=1}^{n} \EE_{t}[R^{\alpha}(t, \bA_t)] \right] \notag\\
+	\leq& \EE \left[\sum_{t=1}^{n} \frac{8}{\alpha f^{\ast}} \EE_t\left[\bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \right] \label{eq:pfMCdeltaEst}\\
+	\leq& \EE\left[\frac{8}{\alpha f^{\ast}} \bbeta_{n}(\delta) \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right] \label{eq:pfMCbeta}\\
+	\leq& \EE\left[\frac{8}{\alpha f^{\ast}} \bbeta_{n}(\delta) \sqrt{ \left(\sum_{t=1}^{n} \bO_t \right) \EE_t \left[\sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]} \right] \label{eq:pfMCmeaneq}\\
+	\leq& \EE \left[\frac{\sqrt{128}}{\alpha f^{\ast}} \left(\sqrt{\ln\left(\frac{\det(\bV_n)}{\lambda^d /n}\right) } + \sqrt{\lambda} \right) \right. \notag\\
 	&\qquad \qquad \left. \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMCsumXi}\\
-	\leq& \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \left(\sqrt{ \ln [ (1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda} \right) \notag\\
+	\leq& \frac{\sqrt{128}}{\alpha f^{\ast}} \left(\sqrt{ \ln [ (1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda} \right) \notag\\
 	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMCdetEst}
 	\end{align}
+	By Lemma \ref{thm:theta_estimate}, $R^{\alpha}(n) \leq \alpha n$ and $\delta = \frac{1}{\sqrt{n}}$, we have
+	\begin{align*}
+		&R^{\alpha}(n) \leq \frac{\sqrt{128}}{\alpha f^{\ast}} \left(\sqrt{ \ln [ (1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda} \right) \notag\\
+		&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} + \alpha \sqrt{n}.
+	\end{align*}
 \end{proof}

### 2016-02-03 contextual combinatorial cascading bandits.tex
update conj and discuss

@@
 We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$.
+In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve.
+For this reason, in the regret defined next, we compare our online algorithm with the best offline algorithm generates, $\alpha f_t^{\ast}$.
 More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
@@
 		R^{\alpha}(n) &\le \frac{2\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
+		&~~ \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
 		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
@@
 		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
-		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \sqrt{n}\nonumber \\
+		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
 		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
@@
 
-The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
-The learning agent observes all items until the first one with weight $0$.
+The Bernoulli random variables $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
+The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$.
 We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
 
-The more items reveals, the more reward the agent should receive. Based on this, we assume that
+The more items reveals, the more reward the agent should receive.
+This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor.
+Based on this, we assume that
 $$
@@
 	&=\begin{cases}
-		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
-		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
+		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
+		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
 	\end{cases}
@@
 
-If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
-\begin{align}
-	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
-	&f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+If we define a function $f : \cS \times [0,1]^E \to [0,1]$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS \text{ and } w = (w(1), \ldots, w(L))$ by
+\begin{equation}
 	\label{eq:AndRewardFunc}
-\end{align}
-then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$.
+	f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
+\end{equation}
+then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$.
 Next is our result for the conjunctive objective with a slightly improved bound than Theorem \ref{thm:main}.
@@
 	\label{thm:and}
-	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$.
+	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$ with $f_t^{\ast} = \max_{A \in \cS} f(A, w_t)$.
 Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
@@
 \begin{proof}
-	We will prove it in the Appendix.
-The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
-And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
+	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
+And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
 	\begin{lemma}
@@
 
-	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem.
+	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem. See the Appendix for the complete proof.
 \end{proof}
@@
 
-If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial} which coincides with our Section \ref{sec:conj} without contextual information and with position discounts $\gamma_k = 1$, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result.
-The reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandits is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved} and we use the technique of linear bandits to derive a confidence ellipsoid of $\theta_{\ast}$.
-A similar comparison exists between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.
-
-If our setting restricts to contextual combinatorial bandits \cite{qin2014contextual}, where there are no triggering and no position discounts, so every base arm in action $\bA_t$ will be observed.
+The combinatorial cascading bandit \cite{kveton2015combinatorial} has a setting similar to ours in Section \ref{sec:conj}, but theirs has no context information or position discounts (i.e.
+all $\gamma_k = 1$).
+So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ compared to their result.
+The loss is because to handle the context information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\ln(n))$ than the standard stochastic MAB bound $O(\frac{\ln(n)}{\Delta})$.
+A similar comparison can be made between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.
+
+We can also compare to the work \cite{qin2014contextual}, where there are no triggering and no position discounts, and all base arms in action $\bA_t$ will be observed.
 The random variable $\bO_t$ of observed base arms should be $|\bA_t|$.

### 2016-02-04 contextual combinatorial cascading bandits.tex
update discuss and experiment

@@
 
-We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of the selected items
-	sequentially following the list order
-	until some problem-specific stopping criterion happens.
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion.
 In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
@@
 	position discounts, and a more general cascading bandit model.
-Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.
+Our experiments on synthetic and real datasets demonstrate the advantage of involving context information and position discounts.
 
@@
 
-We can also compare to the work \cite{qin2014contextual}, where there are no triggering and no position discounts, and all base arms in action $\bA_t$ will be observed.
-The random variable $\bO_t$ of observed base arms should be $|\bA_t|$.
-The probability of full observation of $A$, $p_{t, A}$, should be $1$, so $p^{\ast} = 1$.
-And the position discounts $\gamma_k$ are all $1$.
+We can also compare to the work \cite{qin2014contextual}, where there are no triggering and no position discounts, and all base arms in action $\bA_t$ can be observed.
+So in their setting, our random variable $\bO_t$ becomes a deterministic value $|\bA_t|$ and the probability, $p_{t, \bA_t}$, is $1$.
+Thus $p^{\ast} = 1$.
+Also all position discounts $\gamma_k = 1$.
 Then our regret bound of Theorem \ref{thm:main} is of the same order with theirs.
@@
 
-Our algorithm can also apply to the setting of \cite{chen2013combinatorial} with context information.
-However, the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notations) will be triggered.
-
-Our setting generalizes several existing works but does not limit to them.
-Consider in network routing problem, the observed information would be the latency on specific edges.
-The latency, or {\it weight}, on an edge is an exponential variable with mean $\theta_{\ast}^{\top}x$.
-Suppose we treat an edge as blocked if the latency on it is larger than some tolerance $\tau$.
+Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information.
+Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notations) will be triggered.
+
+Our setting generalizes several existing works on cascading feedback but covers more cases.
+Consider in network routing problem, the observed information is the latency on edges.
+The latency, or {\it weight}, on an edge follows the exponential distribution with mean $\theta_{\ast}^{\top}x$.
+Suppose we treat an edge as blocked if its latency is larger than some tolerance $\tau$.
 And we wait the edge to respond for at most $2\tau$ time.
-Then the real observed latency is new random variable from a cut-off exponential distribution with mean $\theta_{\ast}^{\top}x$.
-Then the edge is unblocked, or with reward $1$, if the new random vairable is less than the tolerance $\tau$ and the expectation is a function, say $g$, of $\theta_{\ast}^{\top}x$.
+Then the real observed latency is a new random variable from a cut-off exponential distribution with mean $\theta_{\ast}^{\top}x$.
+The edge has reward $1$ if it is unblocked; otherwise, the reward is $0$.
+Then the expectation of the reward is a function, say $g$, of $\theta_{\ast}^{\top}x$.
 It is not difficult to check that $g$ satisfies the properties of monotonicity and Lipschitz continuity.
-And the expected reward of a path is a composition of the expected reward function of conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the function $g$.
-(In original formulation, $g$ is the identity function, where $g(w) = w$.) Such an expected reward function satisfies the properties of monotonicity and Lipschitz continuity and can not be represented in conjunctive/disjunctive objectives, like in \cite{kveton2015cascading,kveton2015combinatorial}.
+A path has reward $1$ only when all its edges have rewards $1$.
+So the expected reward of a path is the expected reward function of conjunctive objective, defined in Eq.\eqref{eq:AndRewardFunc}, by replacing $w$ with $g(\theta_{\ast}^{\top}x)$.
+Such an expected reward function satisfies the properties of monotonicity and Lipschitz continuity, and can not be represented in conjunctive/disjunctive objectives as in \cite{kveton2015cascading,kveton2015combinatorial}.
 
@@
 
-We evaluated $C^3$-UCB in three experiments. In the following experiments, we let the position discounts $\gamma_k$ have the form of $\gamma^{k-1}$ for some $\gamma$.
+We evaluated $C^3$-UCB in three experiments and compare our algorithm to {\it CombCascade}, the most related one to ours.
+And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
 
@@
 This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly chose $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
-This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{\theta^{\top}x + 1}{2} \in [0,1]$.
-Next we generated the weight for arm $a$ at time $t$ by a random sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We experimented on four settings.
+At first, we randomly chose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$.
+Next we generated the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We conducted experiments in four settings.
 Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
@@
 		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
-	\subfigure[reward on network 1755 with latency, $\gamma = 0.9$ ]{
+	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
 		\includegraphics[height = 3 cm, width = 4 cm]{isp1755-T300000-gamma9-latency.eps}}
-	\subfigure[Comparison of different $\gamma$ ]{
+	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
 		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
@@
 There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
-Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
+Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$.
 We regard $H$ as known information about history "what users have watched" and regard $F$ as future criterion.
@@
 At every time $t$, we randomly choose a user $I_t \in [N_1]$.
-Then in the same spirit of \cite{li2010contextual}, use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{i}$ and $m_{j}$, as the context information for each movie $j$.
+Then in the same spirit of \cite{li2010contextual}, use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$.
 The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.
@@
 We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}.
-The results are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
+The results for rewards are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
 
@@
 Any edge $a$ in the set $\cS$ is assigned with a random $d$-dimensional context vector $x_{t,a}$.
-Notice here both $\theta$ and $x$ have been processed like section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
+Notice here both $\theta$ and $x$ have been processed like Section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
 The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
@@
 In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value.
-Suppose the true position discount $\gamma = 0.9$ and the learning agent sets $\gamma$ by her experience.
-We experiment on different setting $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma = 0.9$.
-The regrets with different $\gamma$'s are illustrated in Figure~\ref{fig:network}(d).
-The setting $\gamma$ is more close to the true $\gamma$, the regret is tending to be smaller.
-This experiment shows when there are position discounts in real application, it is better to represent this information to the model.
+Suppose the true position discount $\gamma^{\ast} = 0.9$ and the learning agent sets $\gamma$ by her experience.
+We experiment on different setting $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma^{\ast} = 0.9$.
+The regrets with different $\gamma$'s are illustrated in Figure~\ref{fig:network}(d), from which it can be seen that the regret is minimized around the true $\gamma^{\ast}$.
+The big gap between the regret at $\gamma = 1$ and $\gamma^{\ast} = 0.9$ shows that it significantly benefits by exploiting position discounts in the model when such discounts indeed exist in applications.
 
@@
 
-% the environment randomly choose
-
 \section{Conclusions}
 
-In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action can be observed each time.
-We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions.
+In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time.
+We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for a general reward function and two special reward functions.
 The experiments conducted demonstrate the advantage to involve context information and position discounts.
-In the next, we want to derive a lower bound for this problem.
+A matching lower bound on the regret bound is left for a future study.
 
@@
 
-	Also $R^{\alpha}(n) \leq n$ and $\delta = \frac{1}{\sqrt{n}}$. We have 
+	Also $R^{\alpha}(n) \leq \alpha n$ and $\delta = \frac{1}{\sqrt{n}}$. We have 
 	\begin{align*}
 		R^{\alpha}(n) &\leq \frac{2\sqrt{2}B}{p^*} \left(R\sqrt{ \ln[ (1 + C_\gamma n/(\lambda d))^d n ]} + \sqrt{\lambda} \right) \\
-		&\qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} + \sqrt{n}.
+		&\qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} + \alpha \sqrt{n}.
 	\end{align*}

### 2016-02-04 contextual combinatorial cascading bandits.tex
update

@@
 	position discounts, and a more general cascading bandit model.
-Our experiments on synthetic and real datasets demonstrate the advantage of involving context information and position discounts.
+Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.
 
@@
 
-The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; Section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; Section 5 demonstrates the experimental results; and section 6 gives a final conclusion.
+The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} with general reward functions and position discounts; Section 4 gives our algorithm and main results both on general reward functions and two special reward functions; Section 5 demonstrates the experimental results; and Section 6 gives a final conclusion.
 
@@
 A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
-	after we provide the full result of our regret bound.
+	after we provide the full results of our regret bounds.
 
@@
 
-The assumption of Lipschitz continuity gives an estimate of changes in reward function.
-To obtain a good estimation of reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$.
+The assumption of Lipschitz continuity gives an estimate of changes in the reward function.
+To obtain a good estimation of the reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$.
 This means the positions with large $\gamma_k$ are more important to the reward function.
-For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.
+For example in website recommendations, the learning agent will receive the highest reward if the user selects the first item, so the first position is the most important.
 
@@
 We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$.
+More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
 In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve.
 For this reason, in the regret defined next, we compare our online algorithm with the best offline algorithm generates, $\alpha f_t^{\ast}$.
-More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.
 
@@
 
-Before presenting the algorithm, we explain the main ideas in the design.
-
-By Eq.~\eqref{eq:expectation}, we have 
+Before presenting the algorithm, we explain the main ideas in the design. By Eq.\eqref{eq:expectation}, we have 
 $$
@@
 \end{equation}
-where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
+where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is a column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$.
 Let
@@
 	\end{align*}
-	we can obtain the claimed result.
+	the claimed result is obtained.
 \end{proof}
@@
 
-Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
-\begin{align}
-&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
-&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
-\end{align}
+Now let us introduce a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
+\begin{equation}
+\label{eq:OrRewardFunc}
+f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
+\end{equation}
 It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$.
@@
 		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
-		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
+		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
 	\end{cases}\\
-	&=\begin{cases}
-		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
-		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
-	\end{cases}
+	%&=\begin{cases}
+	%	1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
+	%	1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
+	%\end{cases}
 \end{align*}
@@
 \begin{proof}
-	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first.
+	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity.
 And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
 	\subfigure[Disjunctive, $\gamma=1$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-1.eps}}
 	\subfigure[Disjunctive, $\gamma=0.9$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-9.eps}}\\
 	\subfigure[Conjunctive, $\gamma=1$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-1.eps}}
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-1.eps}}
 	\subfigure[Conjunctive, $\gamma=0.9$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-9.eps}}
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-9.eps}}
 	\caption{Synthetic Data Set, L=100, K=4, d=10}
 	\label{fig:synthetic} % 用于交叉引用
-\end{figure*}
+\end{figure}
 
@@
 
-We evaluated $C^3$-UCB in three experiments and compare our algorithm to {\it CombCascade}, the most related one to ours.
+We evaluated $C^3$-UCB in three experiments and compared our algorithm to {\it CombCascade}, the most related one to ours.
 And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
@@
 	\subfigure[$\gamma = 1$]{
-		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
+		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
 	\subfigure[$\gamma = 0.9$]{
-		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
+		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
 	\caption{MovieLens, L=200, K=4, d=5}
@@
 \end{figure}
-
-\begin{figure*}
-	\centering
-	\subfigure[Network 1239, $\gamma=1$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
-	\subfigure[Network 3356, $\gamma = 0.9$]{
-		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
-	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{isp1755-T300000-gamma9-latency.eps}}
-	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
-		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
-	\caption{Network, $d=10$}
-	\label{fig:network} % 用于交叉引用
-\end{figure*}
 
@@
 We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}.
-The results for rewards are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
+The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
 
 \subsection{Network Routing Data}
+\begin{figure}
+	\centering
+	\subfigure[Network 1239, $\gamma=1$]{
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1239-T5-k100-1.eps}}
+	\subfigure[Network 3356, $\gamma = 0.9$]{
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp3356-T5-k100-9.eps}}\\
+	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1755-T300000-gamma9-latency.eps}}
+	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
+		\includegraphics[height = 2.9 cm, width = 3.95 cm]{network-gamma-with-point.eps}}
+	\caption{Network, $d=10$}
+	\label{fig:network} % 用于交叉引用
+\end{figure}
 
@@
 In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time.
-We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for a general reward function and two special reward functions.
+We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions.
 The experiments conducted demonstrate the advantage to involve context information and position discounts.

### 2016-02-04 contextual combinatorial cascading bandits.tex
modify

@@
 
-We evaluated $C^3$-UCB in three experiments and compared our algorithm to {\it CombCascade}, the most related one to ours.
-And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
+We evaluated our algorithm, $C^3$-UCB, in a synthetic setting and two real applications.
+The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts.
+In experiments, we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
 

### 2016-02-04 contextual combinatorial cascading bandits.tex
modify

@@
 	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
-This generalization allows us to covers new realistic scenarios not covered in
+This generalization allows us to cover new realistic scenarios not covered in
 	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
@@
 A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
-	after we provide the full results of our regret bounds.
+	after we provide full results of our regret bounds.
 
 The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
-The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
 Our work generalizes these model and involves both contextual information and position discounts.
@@
 The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
-A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+A recent work \cite{qin2014contextual} (referred to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
 Their feedback is more informative than ours.
@@
   \label{lem:estimateU}
-  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
+  When Ineq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
   $$
@@
 
-The Bernoulli random variables $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}.
+The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicates the weight of item $a$ at time $t$ satisfying Eq.
+\eqref{eq:expectation}.
 The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$.
@@
 \begin{align*}
-	\br_{t} &= \begin{cases}
-		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
-		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
-	\end{cases}\\
-	%&=\begin{cases}
-	%	1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
-	%	1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
-	%\end{cases}
+	\br_{t} %&= \begin{cases}
+		%1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
+		%1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
+	%\end{cases}\\
+	&=\begin{cases}
+		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
+		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
+	\end{cases}
 \end{align*}
@@
 
-We evaluated our algorithm, $C^3$-UCB, in a synthetic setting and two real applications.
+We evaluate our algorithm, $C^3$-UCB, in a synthetic setting and two real applications.
 The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts.
@@
 
-In the first experiment, we compared $C^3$-UCB to CombCascade on synthetic problems.
+In the first experiment, we compare $C^3$-UCB to {\it CombCascade} on synthetic problems.
 This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user.
-At first, we randomly chose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+At first, we randomly choose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
+Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
 This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$.
-Next we generated the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
-
-We conducted experiments in four settings.
+Next we generate the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
+
+We conduct experiments in four settings.
 Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items.
@@
 
-In this experiment, we evaluated $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.
+In this experiment, we evaluate $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.
 
@@
 At every time $t$, we randomly choose a user $I_t \in [N_1]$.
-Then in the same spirit of \cite{li2010contextual}, use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$.
+Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$.
 The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.
 
-For this experiment, we randomly chose $L=200$ movies and recommended $K=4$ movies at each time.
-We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}.
-The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.
+For this experiment, we randomly choose $L=200$ movies and recommend $K=4$ movies at each time.
+We experiment with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}.
+The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve contextual information in real applications.
 
@@
 
-In the last experiment, we evaluated $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.
+In the last experiment, we evaluate $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.
 
@@
 At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ is all simple paths between the source and destination nodes.
-Any edge $a$ in the set $\cS$ is assigned with a random $d$-dimensional context vector $x_{t,a}$.
-Notice here both $\theta$ and $x$ have been processed like Section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$.
+Any edge $a$ in the set $\cS_t$ is assigned with a random $d$-dimensional contextual information vector $x_{t,a}$.
+Notice here both $\theta$ and $x$ have been processed like in Section \ref{sec:ExpSyn} such that $\theta_*^{\top}x \in [0,1]$.
 The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.
 Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective.
-We experimented with different position discounts and different networks.
+We experiment on different position discounts.
 The results are shown in Fig.~\ref{fig:network} (a) (b).
 
-We also experimented on the network with latency, where the latency on an edge is an exponential random variable with mean $\theta_{\ast}^{\top}x$ and the reward is $1$ if the latency is less than a tolerance $\tau = 0.75$.
-The comparison of rewards of our algorithm with {\it CombCascade} is shown in Fig.~\ref{fig:network} (c).
-
-We also experimented on the influence of different $\gamma$'s to the regret.
+Another experiment is conducted on the network with latency, where the latency on an edge is an exponential random variable with mean $\theta_{\ast}^{\top}x$ and the reward is $1$ if the latency is less than a tolerance $\tau = 0.75$.
+The comparison of the cumulative rewards of our algorithm with {\it CombCascade} is shown in Fig.~\ref{fig:network} (c).
+
+We also conduct an experiment on the influence of different $\gamma$'s to the regret.
 In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value.
 Suppose the true position discount $\gamma^{\ast} = 0.9$ and the learning agent sets $\gamma$ by her experience.
-We experiment on different setting $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma^{\ast} = 0.9$.
-The regrets with different $\gamma$'s are illustrated in Figure~\ref{fig:network}(d), from which it can be seen that the regret is minimized around the true $\gamma^{\ast}$.
+We experiment on different $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma^{\ast} = 0.9$.
+The regrets with different $\gamma$'s are illustrated in Fig.~\ref{fig:network}(d), from which it can be seen that the regret is minimized around the true $\gamma^{\ast}$.
 The big gap between the regret at $\gamma = 1$ and $\gamma^{\ast} = 0.9$ shows that it significantly benefits by exploiting position discounts in the model when such discounts indeed exist in applications.
@@
 We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions.
-The experiments conducted demonstrate the advantage to involve context information and position discounts.
+The experiments conducted demonstrate the advantage to involve contextual information and position discounts.
 A matching lower bound on the regret bound is left for a future study.
@@
 	\label{lem:DeltaEsimateWithP*}
-	Suppose the Eq.~\eqref{eq:estimateTheta} holds for time $t-1$. Then
+	Suppose the Ineq.\eqref{eq:estimateTheta} holds for time $t-1$. Then
 	$$
@@
 	\end{align}
-	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$.
-Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
-Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition.
-Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
-Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
+	Eq.\eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$.
+Eq.\eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation.
+Ineq.\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition.
+Ineq.\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$.
+Ineq.\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
 \end{proof}
@@
 	\end{align}
-	where Equality~\eqref{eq:Vfactor} is by the fact that $V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality \eqref{eq:detGeq}.
+	where Eq.\eqref{eq:Vfactor} is by the fact that $V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite matrix $V$, Ineq.\eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and Ineq.\eqref{eq:repeatV} is by repeatedly applying Ineq.\eqref{eq:detGeq}.
 
@@
 	\end{align*}
-	where the last inequality is from Inequality~\eqref{eq:repeatV}.
+	where the last inequality is from Ineq.\eqref{eq:repeatV}.
 \end{proof}
@@
 \begin{proof}[ of Theorem \ref{thm:main}]
-	Suppose Ineq.~\eqref{eq:estimateTheta} holds for all time $t$, which is true with probability $1-\delta$. Then with probablity $1-\delta$, we have
+	Suppose Ineq.\eqref{eq:estimateTheta} holds for all time $t$, which is true with probability $1-\delta$. Then with probability $1-\delta$, we have
 	\begin{align}
@@
 	\end{align}
-	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
-	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
-	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
-	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
-	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
+	Ineq.\eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
+	Ineq.\eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
+	Ineq.\eqref{eq:pfMmeanEq} is by the mean inequality. 
+	Ineq.\eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
+	And the last Ineq.\eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
 
@@
 	\end{align}
-	Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
+	Finally from Ineq. \eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
 	\begin{align*}

### 2016-02-05 contextual combinatorial cascading bandits.tex
modify

@@
 In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path.
-We further consider position discounts in the list order, which means the agent's reward is discounted depending on the position where the stopping criterion is met.
-We formulate this problem in a general contextual combinatorial cascading bandit setting.
-We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
+We consider position discounts in the list order, so that the agent's reward is discounted depending on the position where the stopping criterion is met.
+%We formulate this problem in a general contextual combinatorial cascading bandit setting.
+We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
 Our work generalizes existing studies in several directions, including contextual information,
@@
 
-Recently, stochastic combinatorial bandit started to draw many attention \cite{gai2012combinatorial,chen2013combinatorial,lin2014combinatorial,GMM14,chen2014pure,KWAEE14,kveton2014tight,kveton2015cascading,kveton2015combinatorial,lin2015online,Combes2015}.
+Recently, stochastic combinatorial bandit started to draw much attention \cite{gai2012combinatorial,chen2013combinatorial,lin2014combinatorial,GMM14,chen2014pure,KWAEE14,kveton2014tight,kveton2015cascading,kveton2015combinatorial,lin2015online,Combes2015}.
 At every time step, a learning agent chooses a subset of ground items (super arm) under certain combinatorial constraints.
-There are several different kinds of feedback: (1) bandit feedback, where the learning agent can only obtain the reward of chosen super arm; (2) semi-bandit feedback, where the learning agent can also obtain the stochastic outcomes of the all base arms constituting the chosen super arm;
+There are several different kinds of feedback: (1) bandit feedback, where the learning agent can only obtain the reward of the chosen super arm; (2) semi-bandit feedback, where the learning agent can also obtain the stochastic outcomes of the all base arms constituting the chosen super arm;
 (3) cascading feedback, where the learning agent can obtain the reward of the chosen super arm and the weights of some base arms in the chosen super arm, according to some problem-specific stopping criterion for observation.
@@
 In both of the above applications, we observe the feedbacks of a prefix of items in the chosen ordered list.
-The bandit problem with cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}.
+The bandit problem with such cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}.
 In this paper, we generalize their work in several directions to cover more realistic scenarios.
@@
 In network routing, we may prefer to hit a blocked edge as late as possible.
-To model these preference, we introduce position discounts to the cascading bandit, and
+To model these preferences, we introduce position discounts to the cascading bandit, and
 	we show through experiments that incorporating position discounts may significantly
 	improve the learning result.
-Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial}
-	that are based on disjunctive and conjunctive binary random variables to more general
+Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial},
+	which are based on disjunctive and conjunctive binary random variables, to more general
 	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
@@
 
-The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} with general reward functions and position discounts; Section 4 gives our algorithm and main results both on general reward functions and two special reward functions; Section 5 demonstrates the experimental results; and Section 6 gives a final conclusion.
+The organization of this paper is as follows: Section 2 compares our work to previous work; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} with general reward functions and position discounts; Section 4 gives our algorithm and main results both on general reward functions and two special reward functions; Section 5 demonstrates the experimental results; and Section 6 gives a final conclusion.
 
@@
 The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list.
-The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good".
+The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as `CombCascade' in Table \ref{table:outline}) generalized the framework, allowing each feasible action to be a subset of ground items under combinatorial constraints.
+It studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are ``good''.
 Our work generalizes these model and involves both contextual information and position discounts.
 
-The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
+The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference come early) has a better performance than in decreasing order of their UCBs.
 This unnatural result is perhaps because the order of items does not affect the reward and thus
@@
 	in the cascade.
-The position discounts introduced in this paper forces the recommended set in the decreasing order 
+The position discounts introduced in this paper makes the recommended set in the decreasing order 
 	of UCBs, which is more realistic.
@@
 The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
-A recent work \cite{qin2014contextual} (referred to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
+A recent work \cite{qin2014contextual} (referred to as `C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
 Their feedback is more informative than ours.
@@
 The papers of \cite{agrawal1989asymptotically,bartok2012adaptive} studied partial monitoring problems but their algorithms are inefficient in our setting.
-The work \cite{lin2014combinatorial} studied combinatorial partial monitoring problem and their feedback is a fixed (with respect to chosen action) combination of weights.
-In our setting, if chosen action is fixed, the number of observed items varies with the user's behavior, thus the combination constituting feedback is not fixed.
+The work \cite{lin2014combinatorial} studied combinatorial partial monitoring problem and their feedback is a fixed (with respect to the chosen action) combination of weights.
+In our setting, if the chosen action is fixed, the number of observed items varies with the user's behavior, thus the combination constituting feedback is not fixed.
 
 \citet{chen2015combinatorial} considered general reward functions and probabilistic triggering of base arms
-	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
+	in the  stochastic combinatorial semi-bandit model (refered to as `CUCB' in Table \ref{table:outline}).
 Cascading bandits can be viewed as a particular type of probabilistic triggering, where
@@
 
-As a convention, we always use boldface symbols to represent random variables.
+As a convention, we always use boldface symbols to represent random variables. We also denote $[m] = \{1,\ldots,m\}$.
 
@@
 For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$.
-Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$.
-Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user.
+(See Section \ref{sec:movie} for an application.) Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$.
+Then the learning agent recommends a feasible action $\bA_t=( \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t ) \in \cS$ to the user.
 In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion.
-For example in recommender systems, the stopping criterion might be that the user finds an attractive item.
+For example, in recommender systems, the stopping criterion might be that the user finds the first attractive item.
 Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.
@@
 Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$.
-Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$.
-Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
+Each arm $a$ has a weight $\bw_t(a)$, representing the ``quality'' to the user at time $t$.
+Given history $\cH_t$, we assume that $\bw_{t}(a)$'s are mutually independent random variables with expectation
 \begin{equation} % eq:expectation
@@
 The reward function on round $t$ is an application dependent function.
-We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E} = (\theta_{\ast}x_{t,a})_{a \in E}) $ and satisfies the following two assumptions.
+We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_{t,a})_{a \in E} = (\theta_{\ast}^{\top}x_{t,a})_{a \in E}) $ and satisfies the following two assumptions.
 
@@
 In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve.
-For this reason, in the regret defined next, we compare our online algorithm with the best offline algorithm generates, $\alpha f_t^{\ast}$.
+For this reason, in the regret defined next, we compare our online algorithm with what the best offline algorithm can produce, $\alpha f_t^{\ast}$.
 
@@
 
-Before presenting the algorithm, we explain the main ideas in the design. By Eq.\eqref{eq:expectation}, we have 
+Before presenting the algorithm, we explain the main ideas in the design. By Eq.\eqref{eq:expectation}, at time $s$, we have 
 $$
@@
 $$
-To estimate the expected reward, we reduce to the estimation of $\theta_{\ast}$, which can be obtained by the ridge regression on $x$ and samples of $\bw$.
-In details, using the ridge regression on data
+To estimate the expected reward, we first estimate $\theta_{\ast}$, which can be viewed as a ridge regression problem on samples $x$ and labels $\bw$. In details, using the ridge regression on data 
 $$
@@
 First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$.
-Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$.
+Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = (\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t )$.
 Third, assume that the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$.
@@
 \end{theorem}
-The regret bound deteriorates as $p^*$ gets small.
-But unfortunately, this reciprocal dependence on $p^*$ is not known how to improve, even in the special case of disjunctive objective.
+The regret bound deteriorates as $p^*$ gets smaller.
+But unfortunately, this reciprocal dependence on $p^*$ is not known to be improvable, even in the special case of disjunctive objective.
 Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$.
@@
 Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order.
-The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
+The regrets are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
 
@@
 		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
-	\caption{MovieLens, L=200, K=4, d=5}
+	\caption{Rewards on MovieLens, L=200, K=4, d=5}
 	\label{fig:movielens} % 用于交叉引用
@@
 \subsection{Movie Recommendation}
+\label{sec:movie}
 
@@
 We experiment on different position discounts.
-The results are shown in Fig.~\ref{fig:network} (a) (b).
+The regrets are shown in Fig.~\ref{fig:network} (a) (b).
 

### 2016-02-05 contextual combinatorial cascading bandits.tex
modify

@@
 %We formulate this problem in a general contextual combinatorial cascading bandit setting.
-We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
+We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and give finer analysis for two special cases. 
 Our work generalizes existing studies in several directions, including contextual information,
@@
 Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning. 
-The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
+The problem is usually formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
  The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
@@
 In both of the above applications, we observe the feedbacks of a prefix of items in the chosen ordered list.
-The bandit problem with such cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}.
+The bandit problem with such cascading feedback has been studied in recent papers \cite{kveton2015cascading,kveton2015combinatorial}.
 In this paper, we generalize their work in several directions to cover more realistic scenarios.
@@
 This generalization allows us to cover new realistic scenarios not covered in
-	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
-	in Section~\ref{sec:diss}.
+	\cite{kveton2015cascading,kveton2015combinatorial}, as exhibited in Section~\ref{sec:diss}.
 
@@
 It studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are ``good''.
-Our work generalizes these model and involves both contextual information and position discounts.
+Our work generalizes these models and involves both contextual information and position discounts.
 
@@
 This unnatural result is perhaps because the order of items does not affect the reward and thus
-	putting low preference items first and high preference items last may result in more feedbacks
+	putting low preference items first and high preference items in the back may result in more feedbacks
 	in the cascade.
@@
 In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve.
-For this reason, in the regret defined next, we compare our online algorithm with what the best offline algorithm can produce, $\alpha f_t^{\ast}$.
+For this reason, in the regret defined next, we compare our online algorithm with what the best offline algorithm can produce, i.e.
+$\alpha f_t^{\ast}$.
 
@@
 	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity.
-Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$.
 Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
@@
 Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$.
-However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.
+However, in the special case of conjunctive objective, we will give an improved bound.
 
 \begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
-	The complete proof is in the Appendix.
-The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
+	(sketch) %The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed.
 This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$.
-
-	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. First by monotonicity and $B$-Lipschitz continuity, we can prove
-	$$
-		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
-	$$
-	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms.
+	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. We first employ the monotonicity and $B$-Lipschitz continuity of $f$ to upper bound regret as follows.
+	\begin{equation}
+		\label{eq:regretDeduction}
+		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}^{-1}}.
+	\end{equation}
+	As $\bV_t$ contains only information of observed base arms, our UCB-type algorithm guarantees the sum of the first $\bO_t$ items in the right of Ineq.
+\ref{eq:regretDeduction} to be small, with the leftover sum (from $\bO_t + 1$ to $|\bA_t|$) out of control.
+We cope with this by a reduction to the case that $\bO_t = |\bA_t|$.
+	%However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms.
 Thus we need the following deduction.
-	\begin{align*}
-    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
-    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
-    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
-    \end{align*}
-    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
+	\begin{align}
+    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \nonumber\\
+    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\nonumber\\
+    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right]. \label{eq:ot=at}.
+    \end{align}
+    Combining \ref{eq:regretDeduction} and \ref{eq:ot=at} gives an upper bound of $R^{\alpha}(n)$ in terms of $\sum_{t=1}^n \sum_{k=1}^{\abs{\bO_t}} \gamma_k\norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$.
+The next Lemma upper bounds the sum of norms squared.
+    %the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
     \begin{lemma}
     	\label{lem:XNormSumEst}
-    	If $\lambda \geq C_{\gamma}$, then
-    	$$
-    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
-    	$$
-    \end{lemma}
-    The claimed result thus follows.
+    	If $\lambda \geq C_{\gamma}$, then for any time $t$,
+    	$$
+    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right).
+    	$$
+    \end{lemma}
+    The claimed result thus follows. See the Appendix for a complete proof.
 \end{proof}
@@
 The checking process stops if the user selects one item or has checked all items without selecting anyone.
-The weight of base arm $a$ at time $t$, $\bw_{t,a}$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not.
+The weight of each base arm $a$ at time $t$, $\bw_{t}(a)$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not.
 Then the random variable $\bO_t$ satisfies
 $$
-\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
-$$
-or 
-$$
-\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
-$$
-
-If the user selects the $k$-th item, then the learning agent receives reward $\gamma_k \in [0,1]$.
-Usually the importance of the positions is decreasing: the first position is the most important.
-Based on this, we assume that
+\bO_t = \begin{cases}
+k, &\text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,\\
+\abs{\bA_t}, &\text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
+\end{cases}
+$$
+
+If the user selects the $k$-th item, then the learning agent receives a reward $\gamma_k \in [0,1]$. Usually $\{\gamma_k\}$ are decreasing with $k$:
 $$
@@
 $$
-If the user does not select any item, the agent gets no reward. At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
+If the user does not select any item, the agent gets no reward. At the end of time step $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
 $\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t}$. It is not hard to see that $\br_t = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t)$ is the disjunctive of discounted weights,
@@
 
-Now let us introduce a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
+Now let us define a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
 \begin{equation}
@@
 So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
-We have the following corollary.
+We thus have the following corollary.
 \begin{corollary}
@@
 
-The above formulation is on the disjunctive objective, that is, at each time step the user stops once she selects one item or has checked all recommended items.
-Similarly, we could also consider the case of conjunctive objective.
-In this case, we derive a slightly better result.
+The above formulation is on the disjunctive objective, for which the user stops once she finds a ``good'' item.
+Similarly, we could also consider the case of conjunctive objective, for which the user stops once she finds a ``bad'' item.
+In this case, we derive a better result.
 
@@
 \eqref{eq:expectation}.
-The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$.
+The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $\bw_t(\ba_k^t)=0$.
 We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.
@@
 The more items reveals, the more reward the agent should receive.
-This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor.
+This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions are observed, the more helpful it is to the survey conductor.
 Based on this, we assume that
@@
 $$
-At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
+At the end of time step $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), \forall k \leq \bO_{t}$ and receives a reward $\br_{t}$:
 \begin{align*}
@@
 then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$.
-Next is our result for the conjunctive objective with a slightly improved bound than Theorem \ref{thm:main}.
+Next is our result for the conjunctive objective with an improved bound than Theorem \ref{thm:main}, with $p^{\ast}$ improved by $\alpha f^{\ast}$.
+In network routing problem, the $p^{\ast}$ is related with the bad paths, which can make the probability of observing the whole path very small, and $f^{\ast}$ is related with good paths, which makes $f^{\ast}$ usually large.
 
@@
 \begin{proof}
-	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity.
-And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
+	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity. Then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
 	\begin{lemma}
@@
 
-The combinatorial cascading bandit \cite{kveton2015combinatorial} has a setting similar to ours in Section \ref{sec:conj}, but theirs has no context information or position discounts (i.e.
+The combinatorial cascading bandit \cite{kveton2015combinatorial} has a setting similar to ours in Section \ref{sec:conj}, but theirs has no contextual information or position discounts (i.e.
 all $\gamma_k = 1$).
-So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ compared to their result.
-The loss is because to handle the context information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\ln(n))$ than the standard stochastic MAB bound $O(\frac{\ln(n)}{\Delta})$.
+So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{d}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{d\ln(n)}{f^*}}$ compared to their result.
+The loss is because to handle the context information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\sqrt{d\ln(n)})$ than the standard stochastic MAB bound $O(\sqrt{nd\ln(n)})$.
 A similar comparison can be made between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.
@@
 Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information.
-Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notations) will be triggered.
-
-Our setting generalizes several existing works on cascading feedback but covers more cases.
+Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notation) will be triggered.
+
+Our setting generalizes several existing works on cascading feedback, and actually covers more cases.
 Consider in network routing problem, the observed information is the latency on edges.
@@
 	\subfigure[Disjunctive, $\gamma=1$]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-1.eps}}
+		\includegraphics[height = 3 cm, width = 3.95 cm]{synD-T5-L100-K4-1.eps}}
 	\subfigure[Disjunctive, $\gamma=0.9$]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-9.eps}}\\
+		\includegraphics[height = 3 cm, width = 3.95 cm]{synD-T5-L100-K4-9.eps}}\\
 	\subfigure[Conjunctive, $\gamma=1$ ]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-1.eps}}
+		\includegraphics[height = 3 cm, width = 3.95 cm]{synC-T5-L100-K4-1.eps}}
 	\subfigure[Conjunctive, $\gamma=0.9$ ]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-9.eps}}
+		\includegraphics[height = 3 cm, width = 3.95 cm]{synC-T5-L100-K4-9.eps}}
 	\caption{Synthetic Data Set, L=100, K=4, d=10}
@@
 We evaluate our algorithm, $C^3$-UCB, in a synthetic setting and two real applications.
-The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts.
+The results are compared with {\it CombCascade}, the study most related to ours, and demonstrate the advantage to involve contextual information and position discounts.
 In experiments, we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
@@
 
+\subsection{Movie Recommendation}
+\label{sec:movie}
+
 \begin{figure}
@@
 	\subfigure[$\gamma = 1$]{
-		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
+		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
 	\subfigure[$\gamma = 0.9$]{
-		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
+		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
 	\caption{Rewards on MovieLens, L=200, K=4, d=5}
@@
 
-\subsection{Movie Recommendation}
-\label{sec:movie}
-
 In this experiment, we evaluate $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.
@@
 Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$.
-We regard $H$ as known information about history "what users have watched" and regard $F$ as future criterion.
+We regard $H$ as known information about history ``what users have watched'' and regard $F$ as future criterion.
 We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$.
@@
 We experiment with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}.
-The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve contextual information in real applications.
+The results for rewards are shown in Fig.\ref{fig:movielens}.
+Our rewards increase the {\it CombCascade} ones by $9.2\%$ and $17.74\%$ respectively, which demonstrate the advantage to involve contextual information in real applications.
 
 \subsection{Network Routing Data}
-\begin{figure}
-	\centering
-	\subfigure[Network 1239, $\gamma=1$]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1239-T5-k100-1.eps}}
-	\subfigure[Network 3356, $\gamma = 0.9$]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp3356-T5-k100-9.eps}}\\
-	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1755-T300000-gamma9-latency.eps}}
-	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
-		\includegraphics[height = 2.9 cm, width = 3.95 cm]{network-gamma-with-point.eps}}
-	\caption{Network, $d=10$}
-	\label{fig:network} % 用于交叉引用
-\end{figure}
 
@@
 Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$.
-At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ is all simple paths between the source and destination nodes.
+At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ contains all simple paths between the source and destination.
 Any edge $a$ in the set $\cS_t$ is assigned with a random $d$-dimensional contextual information vector $x_{t,a}$.
@@
 
-We also conduct an experiment on the influence of different $\gamma$'s to the regret.
+We also conduct an experiment on the influence of $\gamma$ to the regret.
 In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value.
@@
 
+\begin{figure}
+	\centering
+	\subfigure[Network 1239, $\gamma=1$]{
+		\includegraphics[height = 3 cm, width = 3.95 cm]{isp1239-T5-k100-1.eps}}
+	\subfigure[Network 3356, $\gamma = 0.9$]{
+		\includegraphics[height = 3 cm, width = 3.95 cm]{isp3356-T5-k100-9.eps}}\\
+	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
+		\includegraphics[height = 3 cm, width = 3.95 cm]{isp1755-T300000-gamma9-latency.eps}}
+	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
+		\includegraphics[height = 3 cm, width = 3.95 cm]{network-gamma-with-point.eps}}
+	\caption{Network, $d=10$}
+	\label{fig:network} % 用于交叉引用
+\end{figure}
+
 % we randomly generate a pair of starting and ending nodes, and the learning agent chooses a routing path between the two nodes to maximize the expected reward with position discount.
@@
 The experiments conducted demonstrate the advantage to involve contextual information and position discounts.
-A matching lower bound on the regret bound is left for a future study.
+In the future, we would like to investigate on lower bound of the regret and cascading on graphs.
 
@@
     &\det(I + \sum_{i=1}^n x_i x_i^{\top})= \prod_{j=1}^d (1 + \alpha_j)\\
-    &\geq 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
-    &=1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
-    &=1 + \sum_{i=1}^n \norm{x_i}_2^2.
+    \geq& 1 +\sum_{j=1}^d \alpha_j =1-d + \sum_{i=1}^d (1+\alpha_i) \\
+    =&1-d + \trace(I + \sum_{i=1}^n x_i x_i^{\top})= 1-d + d + \sum_{i=1}^n \norm{x_i}_2^2\\
+    =&1 + \sum_{i=1}^n \norm{x_i}_2^2.
   \end{align*}
@@
 	&\det(\bV_t) = \det\left(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k x_{t,\ba_k^{t}})(\gamma_k x_{t, \ba_k^{t}}^{\top}) \right) \nonumber \\
-	&=\det(\bV_{t-1}) \notag \\
+	=&\det(\bV_{t-1}) \notag \\
 	&~~~\cdot \det \left(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top} \right) \label{eq:Vfactor}\\
-	&\geq \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
-	&\geq \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
+	\geq& \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
+	\geq& \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
 	\end{align}
@@
 	&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
-	&\leq 2\sum_{s=1}^t\ln \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right)\\
-	& = 2 \ln \prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right) \\
-	&\le 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right),
+	\leq &2\sum_{s=1}^t\ln \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right)\\
+	= &2 \ln \prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right) \\
+	\le& 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right),
 	\end{align*}
@@
 	\begin{align*}
-	&\det(\bV_t) = \lambda_1 \cdot \cdots \cdot \lambda_d \\
-	\leq & \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
+	\det(\bV_t) &= \lambda_1 \cdot \cdots \cdot \lambda_d \\
+	&\leq  \left( \frac{\lambda_1 + \ldots + \lambda_d}{d} \right)^d = (\trace(\bV_t)/d)^d.
 	\end{align*}
@@
 	&\trace(\bV_t)\\
-	& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
-	& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
-	& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
+	=& \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
+	=& d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
+	\leq& d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
 	\end{align*}
@@
 		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
-		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		=&\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
 		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
+		\leq& \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
 		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
-		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
+		=&f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
 	\end{align*}
@@
 		=&\prod_{i=1}^{k}w_i - (1-\gamma_{k+1}) (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \\
-		&\qquad \qquad - (\prod_{i=1}^{k}w_i) w_{k+1}\\
+		&- (\prod_{i=1}^{k}w_i) w_{k+1}\\
 		=&\gamma_{k+1} (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0;

### 2016-02-05 contextual combinatorial cascading bandits.tex
modify

@@
 % the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{combinatorial cascading bandits, context information, position discounts}
+\icmlkeywords{combinatorial cascading bandits, contextual information, position discounts}
 
@@
 
-We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion.
+We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of contextual information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion.
 In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path.
@@
 %We formulate this problem in a general contextual combinatorial cascading bandit setting.
-We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and give finer analysis for two special cases. 
-Our work generalizes existing studies in several directions, including contextual information,
-	position discounts, and a more general cascading bandit model.
-Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.
+We design a UCB-type algorithm, C$^3$-UCB, for this problem, prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in the general setting, and give finer analysis for two special cases. 
+Our work generalizes existing studies in several directions, including contextual information, position discounts, and a more general cascading bandit model.
+Experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.
 
@@
 Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward.
-The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time.
+The paper \cite{li2010contextual} studied multi-armed bandit with contextual information, which recommends one item a time.
 A recent work \cite{qin2014contextual} (referred to as `C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward.
@@
 For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$.
-(See Section \ref{sec:movie} for an application.) Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$.
+(See Section \ref{sec:movie} for an application.) Denote $x_t = (x_{t,a})_{a \in E}$ as all contextual information at time $t$.
 Then the learning agent recommends a feasible action $\bA_t=( \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t ) \in \cS$ to the user.
@@
 Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
-Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$.
+Thus $\cH_t$ contains feedback information at all time $s < t$, as well as contextual information at time $t$.
 Each arm $a$ has a weight $\bw_t(a)$, representing the ``quality'' to the user at time $t$.
@@
     Combining \ref{eq:regretDeduction} and \ref{eq:ot=at} gives an upper bound of $R^{\alpha}(n)$ in terms of $\sum_{t=1}^n \sum_{k=1}^{\abs{\bO_t}} \gamma_k\norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$.
-The next Lemma upper bounds the sum of norms squared.
+The next lemma upper bounds this sum of norms, \emph{squared}.
     %the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
@@
     \end{lemma}
-    The claimed result thus follows. See the Appendix for a complete proof.
+    The claimed result follows from Cauchy-Schwartz inequality. See Appendix for a complete proof.
 \end{proof}
@@
 It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity.
-(All verifications are left in the Appendix.)
+(All verifications are left in Appendix.)
 %Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order.
@@
 then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$.
-Next is our result for the conjunctive objective with an improved bound than Theorem \ref{thm:main}, with $p^{\ast}$ improved by $\alpha f^{\ast}$.
+Next is our result for the conjunctive objective, where the bound in Theorem \ref{thm:main} is improved with $p^{\ast}$ replaced by $\alpha f^{\ast}$.
 In network routing problem, the $p^{\ast}$ is related with the bad paths, which can make the probability of observing the whole path very small, and $f^{\ast}$ is related with good paths, which makes $f^{\ast}$ usually large.
@@
 
-	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem. See the Appendix for the complete proof.
+	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem. See Appendix for the complete proof.
 \end{proof}
@@
 So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{d}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{d\ln(n)}{f^*}}$ compared to their result.
-The loss is because to handle the context information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\sqrt{d\ln(n)})$ than the standard stochastic MAB bound $O(\sqrt{nd\ln(n)})$.
+The loss is because to handle the contextual information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\sqrt{d\ln(n)})$ than the standard stochastic MAB bound $O(\sqrt{nd\ln(n)})$.
 A similar comparison can be made between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.
@@
 
-Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information.
+Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing contextual information.
 Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notation) will be triggered.
@@
 At first, we randomly choose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$.
-Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$.
+Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the contextual information for arm $a$.
 This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$.
@@
 Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order.
-The regrets are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
+The regrets are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the contextual information.
 
@@
 		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
-	\caption{Rewards on MovieLens, L=200, K=4, d=5}
+	\caption{Rewards on MovieLens, $L=200$, $K=4$, $d=5$}
 	\label{fig:movielens} % 用于交叉引用
@@
 
-The Learning problem is formulated as follows.
+The learning problem is formulated as follows.
 There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$.
@@
 At every time $t$, we randomly choose a user $I_t \in [N_1]$.
-Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$.
+Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the contextual information for each movie $j$.
 The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.
@@
 The results for rewards are shown in Fig.\ref{fig:movielens}.
-Our rewards increase the {\it CombCascade} ones by $9.2\%$ and $17.74\%$ respectively, which demonstrate the advantage to involve contextual information in real applications.
+The rewards of our algorithms are higher than those of {\it CombCascade} by $9.2\%$ and $17.74\%$ (for $\gamma = 1$ and $0.9$, respectively), which demonstrate the advantage to involve contextual information in real applications.
 
@@
 We experiment on different position discounts.
-The regrets are shown in Fig.~\ref{fig:network} (a) (b).
+The regrets are shown in Fig.~\ref{fig:network} (a), (b).
 
@@
 The experiments conducted demonstrate the advantage to involve contextual information and position discounts.
-In the future, we would like to investigate on lower bound of the regret and cascading on graphs.
+In future, we would like to investigate on lower bounds of the regret and cascading on general graphs.
 

### 2016-03-10 experiment/experiment.tex
restore experiment.pdf; ignore log syncro; update scat;

@@
 
-\section{Disjunctive case}
-
-\subsection{Need to involve Contextual information}
-
-We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$
-
-\subsection{Need to involve position discount parameter $\gamma$}
-
-We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.
-
-\subsection{Cascading Information}
-
-We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.
-
-\section{Conjunctive case}
-
-\subsection{Need to involve Contextual information}
-
-We experiment on synthetic data. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$
-
-\subsection{Need to involve position discount parameter $\gamma$}
-
-We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.
-
-\subsection{Cascading Information}
-
-We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.
-
 \section{Results}

### 2016-03-10 experiment/bleedtest.py

@@ -1,0 +1,98 @@
+import logging
+logfile = logging.FileHandler('log')
+logfile.setLevel(logging.INFO)
+logconsole = logging.StreamHandler()
+logconsole.setLevel(logging.DEBUG)
+logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.DEBUG, handlers=[logfile, logconsole])
+logger = logging.getLogger('Main')
+
+import time
+seed = int(time.time() * 100) % 339
+import numpy as np
+np.random.seed(seed)
+import random
+random.seed(seed)
+logger.info('===== Numpy/Python random seed = {0}'.format(seed))
+
+import matplotlib.pyplot as plt
+
+from agent import contextual_cascading_sherry
+from agent import contextual_cascading_gsherry
+from agent import contextual_cascading_monkey
+from agent import contextual_full_monkey
+from agent import contextual_full_lijing
+from agent import absolute_cascading_ucb
+from environment import contextual
+from environment import c3synthetic_monkey_rng
+from movielens import c3_movielens_rng
+from isp import c3synthetic_isp_rng
+from isp import c3synthetic_Zisp_rng
+from isp import c3synthetic_Cisp_rng
+
+def flowtest_monkey(T, **kw):
+    logger.info('Monkey flowtest')
+    logger.info('Require rng initialization')
+    logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
+    s = c3synthetic_monkey_rng(**kw)
+    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
+    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=False, descend=False), T=T)
+    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=False, descend=True), T=T)
+    reward, regret, similarity = contextual_full_lijing(contextual(s, cascade=False, rgamma=False, descend=False), T=T)
+    reward, regret, similarity = absolute_cascading_ucb(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
[…]

### 2016-03-10 experiment/utils.py

@@ -21,10 +21,17 @@ def suni(d):
     return uni(x)
 
 def scat(d):
+    np.random.dirichlet((1,)*d)
+
+def scat1(d):
     x = np.random.exponential(1, d)
     return x / x.sum()
 
-def scat1(d):
+def scat2(d):
+    s = sorted(np.random.uniform(0, 1, d-1))
+    return np.array([s[0], *[s[i+1] - s[i] for i in range(d-2)], 1-s[-1]])
+
+def scat3(d):
     e = uni(np.ones(d))
     x = [abs(suni(d)) for _ in range(int(15**(np.sqrt(d))))]
     x = [v for v in x if np.random.uniform() < v.dot(e)]

### 2016-03-27 experiment/agent.py
movielens fixed

@@ -55,7 +55,7 @@ def contextual_cascading_sherry(s, T, delta=0.9, lamb=0.1):
     regret = [0]
     timestamp = time.time()
     for t in range(1, T):
-        print(t)
+        #print(t)
         x, params = s.new()
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
         recc = s.oracle(U, *params)

### 2016-03-27 experiment/bleedtest.py

@@ -49,9 +49,13 @@ def flowtest_movielens(T, **kw):
     logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
     s = c3_movielens_rng(**kw)
     reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
-    #reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=True, descend=True), T=T)
-    #reward, regret, similarity = contextual_full_lijing(contextual(s, cascade=False, rgamma=True, descend=False), T=T)
-    #reward, regret, similarity = absolute_cascading_ucb(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
+    plt.plot(reward, 'r')
+    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=True, descend=True), T=T)
+    plt.plot(reward, 'b')
+    reward, regret, similarity = contextual_full_lijing(contextual(s, cascade=False, rgamma=True, descend=False), T=T)
+    plt.plot(reward, 'g')
+    reward, regret, similarity = absolute_cascading_ucb(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
+    plt.plot(reward, 'y')
     #reward, regret, similarity = absolute_cascading_ucb(contextual(s, cascade=True, rgamma=True, descend=True), T=T)
     return reward, regret
 
@@ -91,9 +95,9 @@ def flowtest_gisp(T, **kw):
 #plt.show()
 
 
-kw = {'n_movies':200, 'train_portion':0.7, 'd':10, 'K':2, 'n_users':300, 'gamma':1.00, 'disj':True}
-reward, regret = flowtest_movielens(1200, **kw)
-plt.plot(reward)
+kw = {'n_movies':200, 'train_portion':0.7, 'd':10, 'K':2, 'baseline':(0.02, 0.04), 'gamma':1.00, 'disj':True}
+reward, regret = flowtest_movielens(7000, **kw)
+#plt.plot(reward)
 plt.show()
 
 #kw = {'isp':6461, 'd':5, 'v':0.35, 'k':10, 'gamma':0.90}

### 2016-03-27 experiment/movielens.py

@@ -27,7 +27,7 @@ def movielens_data():
 
 class c3_movielens_rng:
 
-    # c3synthetic_movielens_rng(n_movies=None, train_portion=0.5, d=15, K=6, n_users=None, gamma=0.95, disj=False)
+    # c3synthetic_movielens_rng(n_movies=None, train_portion=0.5, d=15, K=6, baseline=(0.02, 0.04), gamma=0.95, disj=False)
 
     def __init__(self, **kwarg):
         logger.info('Initializing random settings "Contextual Movielens"')
@@ -47,7 +47,7 @@ class c3_movielens_rng:
         exc = self.A.getrow(self.user)
         #print(len([arm for arm in self.arms if exc[0, arm] == 0]))
         current = [arm for arm in self.arms if exc[0, arm] == 0]
-        print(len(current), sum([arm in self.ctrh[self.user] for arm in current]))
+        #print(len(current), sum([arm in self.ctrh[self.user] for arm in current]))
         return {arm: np.outer(self.U[self.user], self.V[arm]).flatten() for arm in self.arms if exc[0, arm] == 0} if len([arm for arm in self.arms if exc[0, arm] == 0]) > self.K + 2 else self.slot()
 
     def realize(self, action):
@@ -91,10 +91,8 @@ class c3_movielens_rng:
             self.L = len(movies)
         else:
             self.L = self.n_movies
-        if self.n_users is None:
-            self.n_users = len(self.ctrh)
         self.arms = set([x[1] for x in sorted([(movies[movie], movie) for movie in movies])[-self.L:]])
-        self.users = [x[1] for x in sorted([(overlap(self.ctrh[user], self.arms), user) for user in self.ctrh if self.L*0.04 < overlap(self.ctrh[user], self.arms) < self.L*0.06])]#[-self.n_users:]]
+        self.users = [x[1] for x in sorted([(overlap(self.ctrh[user], self.arms), user) for user in self.ctrh if self.L * self.baseline[0] < overlap(self.ctrh[user], self.arms) < self.L * self.baseline[1]])]
         logging.info('total {0} users involved'.format(len(self.users)))
         self.d = self.d ** 2
 

### 2016-03-29 rebuttal_cascadingBandit.txt

- On reviewers’ concern about experimental results

When we demonstrate the experimental results, we focus on the comparison aspect to show the advantage of involving contextual information and position discounts over alternative methods. Actually the learning curves will show a good concave/convex shape when n, the number of rounds, is small. Taking Figure 1(b) for an example, the learning curves show a good concave shape when n <= 2000, during which the cosine similarity between \theta_* and its estimate \hat{\theta} increases to 0.995. This means that our algorithm learns quickly, which is because we use a small d=10 as the dimension of the latent vector \theta_*, making the learning task easy. When n>2000, due to the randomness, the accuracy of $\hat{\theta}$ increases very slowly. Thus there is a very small probability that $\hat{\theta}$ will lead to a wrong choice of the action. Such a small probability is decreasing, but in a very slow rate, which results in the almost linear shape of the curves when n is relatively large. We will test harder learning tasks with larger d values to make the learning curves exhibit more obvious concave shape.

- On reviewer 1’s comment “the authors never give an example of a more general reward function or experiment with it.”, and the request to clarify Sec. 4.3 and Sec. 5.3

We indeed provide an example in the contextual bandit setting that cannot be covered if we simply extend existing cascading bandit results to involve contextual information. The example is given in Section 4.3 and is experimented in Section 5.3 with Figure 3(c). Perhaps our original explanation is unclear, so we provide further details here.

This example considers a network routing problem with edge latency. The latency of each edge follows an exponential distribution with a cutoff value, say 2\tau. That is, after time 2\tau, we do not wait for the actual delay feedback and just use 2\tau as the feedback. The cutoff exponential distribution has bounded support and thus satisfies the R-sub-Gaussian property. We regard an edge as blocked if its latency is larger than threshold \tau (say as an application requirement). An action is a routing path from the source to the target. The reward of the action is 1 if no edge on the path is blocked, and 0 if some edge on the path is blocked (ignoring position discount in this example). After an action is played in each round, the observed feedback is the delays of edges up until the first blocked edge (for the first blocked edge, we still give it a chance after \tau up to 2\tau to observe its delay). The mean delay of an edge e with the cutoff exponential distribution is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta_*.

In this example, we can use observed delays and contexts to apply linear regression to estimate \theta_*, as given in the paper. However, the expected reward function as a function of mean delays of edges is a complicated function (even without a closed-form formula): we need to transform the mean delays of the cutoff exponential distribution to the non-cutoff exponential distribution, and then use the latter to derive the blocking probability with threshold \tau. Thus it is not covered by existing cascading bandit studies. Yet we can still argue that this function is monotone and Lipschitz continuous, and thus obtain regret bound from Theorem 4.3. On the other hand, if we treat edge blocked or unblocked as the feedback in order to fit into the existing cascading bandit framework, we cannot apply linear regression to learn the latent vector \theta_*, because the probability of edge blocking or nonblocking is not a linear combination of contexts and \theta_*.

This example is also experimented in Section 5.3 with Figure 3(c).

- On reviewer 1’s concern about 1/p* being arbitrarily large and p* not tied to the reward function.

Our understanding is that p* is always tied to the reward function. If not, consider an extreme example, where a sequence of base arms has a tiny probability p observing the last base arm in the sequence, making p* very small and 1/p* very large. If the outcome of the last base arm is not tied to the reward function, it means that observing the last base arm or not does not make a difference, then we can remove it from the sequence so that p* is not defined based on this observation probability. In general, if observing a base arm is not tied with the reward function, we can remove it in the problem instance so that it does not affect p*. When observing a base arm indeed could make a difference in the final reward and the optimal action selection, then one has to observe this base arm, no matter how small the observation probability is, and in this case a regret with 1/p* is reasonable and inevitable. We will add proper discussions in the paper to clarify this point.

- On reviewer 1’s concern about monotonicity assumption

This assumption implies if the recommended list has higher reward means, then the expected reward of the list should also get higher. We think this is a relatively basic assumption.

- On reviewer 1’s concern about last paragraph in Section 5.3

This experiment is to demonstrate that the knowledge of position discount \gamma could be important in the learning process. For the network routing tests, Fig. 3(d) shows that without considering position discount (\gamma = 1), the regret is much larger than using a position discount close to the true value of (\gamma*= 0.9). The intuition is that a position discount will guide the selection towards selecting paths that are likely to be reliable initially, while no position discount will guide the selection towards globally reliable paths. Essentially, in the network routing case different position discounts lead to different optimal solutions. This is not the case for the disjunctive cascading bandit (selecting top k base arms with the highest probability of one of them returning 1) --- with all position discounts, the top k choices are the same. We just want to illustrate the importance of position discounts in some applications.

- On reviewer 4’s concern about Line 657-663

This part is to justify the additional term in the regret due to accommodating contextual information. Our result is based on the linear bandits (Abbasi-Yadkori et al. 2011), which also introduces an additional term compared to the classical MAB.

- On reviewer 4’s concern about the context in Section 5.3

We generate the contextual information x_{t,a} randomly. CombCascade performs much worse because they do not use the contextual information. Even though the context is random, it still guides C^3-UCB to learn the latent \theta_* much better, so that given a new (and random) context, C^3-UCB knows much better what action to choose. Without the use of contexts, CombCascade can only select the action that performs well for the *average* context, which is certainly much worse than C^3-UCB, which can perform well on *every* context after the learning period.

- On reviewers’ other concerns

The V_t norm in line 376 is defined in line 362-364.

The simple path in Line 812 is a directed path without cycles.

### 2016-03-29 rebuttal_cascadingBandit.txt

@@
-- On reviewers’ concern about experimental results
+- All reviewers: seemingly linear regret/reward curves
 
-When we demonstrate the experimental results, we focus on the comparison aspect to show the advantage of involving contextual information and position discounts over alternative methods.
-Actually the learning curves will show a good concave/convex shape when n, the number of rounds, is small.
-Taking Figure 1(b) for an example, the learning curves show a good concave shape when n <= 2000, during which the cosine similarity between \theta_* and its estimate \hat{\theta} increases to 0.995.
-This means that our algorithm learns quickly, which is because we use a small d=10 as the dimension of the latent vector \theta_*, making the learning task easy.
+The learning curves will show a good concave/convex shape when n, the number of rounds, is small.
+For example, the curve in Fig.1(b) shows a good concave shape when n <= 2000, during which the cosine similarity between \theta_* and its estimate \hat{\theta} increases to 0.995.
+This means that our algorithm learns quickly, because the learning task is relatively easy with a small d=10, the dimention of \theta_*.
 When n>2000, due to the randomness, the accuracy of $\hat{\theta}$ increases very slowly.
-Thus there is a very small probability that $\hat{\theta}$ will lead to a wrong choice of the action.
-Such a small probability is decreasing, but in a very slow rate, which results in the almost linear shape of the curves when n is relatively large.
-We will test harder learning tasks with larger d values to make the learning curves exhibit more obvious concave shape.
+Thus there is a small probability that $\hat{\theta}$ leads to a wrong action choice.
+Such a small probability is decreasing very slowly, resulting in the almost linear shape of the curves when n is large.
+We will test harder learning tasks with larger d to make the curves exhibit more obvious concave shape.
 
-- On reviewer 1’s comment “the authors never give an example of a more general reward function or experiment with it.”, and the request to clarify Sec. 4.3 and Sec. 5.3
+- Reviewer 1: on an example of a more general reward function, and unclear last paragraph of Sec. 4.3
 
-We indeed provide an example in the contextual bandit setting that cannot be covered if we simply extend existing cascading bandit results to involve contextual information.
-The example is given in Section 4.3 and is experimented in Section 5.3 with Figure 3(c).
-Perhaps our original explanation is unclear, so we provide further details here.
+We indeed provided an example of a more general reward function in Sec.
+4.3 (last paragraph) and experimented it in Sec.
+5.3 with Figure 3(c).
+Perhaps our explanation is unclear, so we provide further details here.
 
@@
 The latency of each edge follows an exponential distribution with a cutoff value, say 2\tau.
-That is, after time 2\tau, we do not wait for the actual delay feedback and just use 2\tau as the feedback.
-The cutoff exponential distribution has bounded support and thus satisfies the R-sub-Gaussian property.
+That is, after time 2\tau, we do not wait for the actual delay and just use 2\tau as the feedback.
+The cutoff exponential distribution satisfies the R-sub-Gaussian property.
 We regard an edge as blocked if its latency is larger than threshold \tau (say as an application requirement).
-An action is a routing path from the source to the target.
-The reward of the action is 1 if no edge on the path is blocked, and 0 if some edge on the path is blocked (ignoring position discount in this example).
-After an action is played in each round, the observed feedback is the delays of edges up until the first blocked edge (for the first blocked edge, we still give it a chance after \tau up to 2\tau to observe its delay).
-The mean delay of an edge e with the cutoff exponential distribution is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta_*.
+An action is a routing path.
+The reward of the action is 1 if no edge on the path is blocked, and 0 if some edge on the path is blocked.
+After an action is played, the observed feedback is the delays of edges up to the first blocked edge (this delay of this blocked edge is observed if it is less than 2\tau).
+The mean delay of an edge e is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta_*.
 
-In this example, we can use observed delays and contexts to apply linear regression to estimate \theta_*, as given in the paper.
-However, the expected reward function as a function of mean delays of edges is a complicated function (even without a closed-form formula): we need to transform the mean delays of the cutoff exponential distribution to the non-cutoff exponential distribution, and then use the latter to derive the blocking probability with threshold \tau.
+In this example, we can use observed delays and contexts and apply linear regression to estimate \theta_*, as given in the paper.
+However, the expected reward as a function of mean edge delays is a complicated function without a closed-form: we need to transform the mean delay of a cutoff exponential distribution to the blocking probability with threshold \tau.
 Thus it is not covered by existing cascading bandit studies.
 Yet we can still argue that this function is monotone and Lipschitz continuous, and thus obtain regret bound from Theorem 4.3.
-On the other hand, if we treat edge blocked or unblocked as the feedback in order to fit into the existing cascading bandit framework, we cannot apply linear regression to learn the latent vector \theta_*, because the probability of edge blocking or nonblocking is not a linear combination of contexts and \theta_*.
+In contrast, if we treat edge blocked or unblocked as the feedback in order to fit into the existing cascading bandit framework, we cannot apply linear regression to learn the latent vector \theta_*, because the probability of edge being blocked is not a linear combination of contexts and \theta_*.
 
-This example is also experimented in Section 5.3 with Figure 3(c).
-
-- On reviewer 1’s concern about 1/p* being arbitrarily large and p* not tied to the reward function.
+- Reviewer 1: 1/p* may be arbitrarily large and not tied to the reward function
 
 Our understanding is that p* is always tied to the reward function.
-If not, consider an extreme example, where a sequence of base arms has a tiny probability p observing the last base arm in the sequence, making p* very small and 1/p* very large.
-If the outcome of the last base arm is not tied to the reward function, it means that observing the last base arm or not does not make a difference, then we can remove it from the sequence so that p* is not defined based on this observation probability.
-In general, if observing a base arm is not tied with the reward function, we can remove it in the problem instance so that it does not affect p*.
-When observing a base arm indeed could make a difference in the final reward and the optimal action selection, then one has to observe this base arm, no matter how small the observation probability is, and in this case a regret with 1/p* is reasonable and inevitable.
-We will add proper discussions in the paper to clarify this point.
+In general, if the probability of observing a base arm i is very small causing 1/p* large while observing i is not tied to the reward function, we can ignore arm i so that it does not affect p*.
+In the other extreme, when observing arm i indeed could make a difference in the optimal action selection, one has to observe arm i, no matter how small its observation probability, which means in this case a regret with 1/p* is reasonable.
+In other cases when p* is tied with the reward function but not the optimal reward, one may add some condition similar to the one in Lemma 4.7 to detach p* from the regret.
+We will add discussions in the paper to clarify this point.
 
-- On reviewer 1’s concern about monotonicity assumption
+- Reviewer 1: unclear last paragraph of Sec. 5.3
 
-This assumption implies if the recommended list has higher reward means, then the expected reward of the list should also get higher. We think this is a relatively basic assumption.
+This experiment is to demonstrate that position discount \gamma could significantly affect the learning result.
+The intuition behind is that, for network routing, a position discount will guide the selection towards selecting paths that are likely to be reliable initially, while no position discount will guide the selection towards globally reliable paths.
+Essentially, in network routing different position discounts lead to different optimal solutions.
+This is not the case for the top-k disjunctive/conjunctive cascading bandit --- with all position discounts, the top k choices are the same.
 
-- On reviewer 1’s concern about last paragraph in Section 5.3
+- Reviewer 4: unclear Line 657-663
 
-This experiment is to demonstrate that the knowledge of position discount \gamma could be important in the learning process.
-For the network routing tests, Fig.
-3(d) shows that without considering position discount (\gamma = 1), the regret is much larger than using a position discount close to the true value of (\gamma*= 0.9).
-The intuition is that a position discount will guide the selection towards selecting paths that are likely to be reliable initially, while no position discount will guide the selection towards globally reliable paths.
-Essentially, in the network routing case different position discounts lead to different optimal solutions.
-This is not the case for the disjunctive cascading bandit (selecting top k base arms with the highest probability of one of them returning 1) --- with all position discounts, the top k choices are the same.
-We just want to illustrate the importance of position discounts in some applications.
+We intend to say that, using the same approach as in Abbasi-Yadkori et al. 2011, we can obtain matching regret bound as cascading bandits after removing the contextual information.
 
-- On reviewer 4’s concern about Line 657-663
+- Reviewer 4: unclear context in Sec. 5.3
 
-This part is to justify the additional term in the regret due to accommodating contextual information.
-Our result is based on the linear bandits (Abbasi-Yadkori et al.
-2011), which also introduces an additional term compared to the classical MAB.
-
-- On reviewer 4’s concern about the context in Section 5.3
-
-We generate the contextual information x_{t,a} randomly.
-CombCascade performs much worse because they do not use the contextual information.
-Even though the context is random, it still guides C^3-UCB to learn the latent \theta_* much better, so that given a new (and random) context, C^3-UCB knows much better what action to choose.
-Without the use of contexts, CombCascade can only select the action that performs well for the *average* context, which is certainly much worse than C^3-UCB, which can perform well on *every* context after the learning period.
-
-- On reviewers’ other concerns
-
-The V_t norm in line 376 is defined in line 362-364.
-
-The simple path in Line 812 is a directed path without cycles.
+Context is generated randomly.
+Without context, CombCascade only selects the action that performs well for the *average* context, which is certainly much worse than C^3-UCB, which uses context to learn latent \theta_* and selects much better actions on *every* context after the learning period.

### 2016-03-29 experiment/agent.py
update bleedtest parameters

@@ -56,6 +56,7 @@ def contextual_cascading_sherry(s, T, delta=0.9, lamb=0.1):
     timestamp = time.time()
     for t in range(1, T):
         #print(t)
+        #delta = t ** (-0.5)
         x, params = s.new()
         U = {arm: theta.dot(x[arm]) + beta * x[arm].dot(np.linalg.inv(V)).dot(x[arm]) for arm in x}
         recc = s.oracle(U, *params)

### 2016-03-29 experiment/bleedtest.py

@@ -89,15 +89,14 @@ def flowtest_gisp(T, **kw):
 
 #kw = {'L':20, 'd':5, 'b':0, 'K':4, 'gamma':0.9, 'eps':0.1, 'v':0.35, 'disj':True}
 #kw = {'L':100, 'd':10, 'b':0, 'K':10, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
-#kw = {'L':200, 'd':20, 'b':0, 'K':2, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
-#reward, regret = flowtest_monkey(500000, **kw)
-#plt.plot(regret)
-#plt.show()
+kw = {'L':200, 'd':20, 'b':0, 'K':2, 'gamma':0.95, 'eps':0.1, 'v':0.35, 'disj':False}
+reward, regret = flowtest_monkey(500000, **kw)
+plt.plot(regret)
+plt.show()
 
 
-kw = {'n_movies':200, 'train_portion':0.7, 'd':10, 'K':2, 'baseline':(0.02, 0.04), 'gamma':1.00, 'disj':True}
-reward, regret = flowtest_movielens(7000, **kw)
-#plt.plot(reward)
+#kw = {'n_movies':200, 'train_portion':0.7, 'd':10, 'K':2, 'baseline':(0.02, 0.04), 'gamma':1.00, 'disj':True}
+#reward, regret = flowtest_movielens(7000, **kw)
 plt.show()
 
 #kw = {'isp':6461, 'd':5, 'v':0.35, 'k':10, 'gamma':0.90}

### 2016-03-29 experiment/environment.py

@@ -19,14 +19,16 @@ from utils import sparse_suni
 class c3synthetic_monkey_rng:
 
     # contextual_monkey_rng(self, L=20, d=10, b=0, K=4, gamma=0.95, eps=0.1, v=0.35, disj=False)
-    
+
     def __init__(self, **kwarg):
         logger.info('Initializing random settings "Contextual Monkey"')
         self.__dict__.update(kwarg)
         self.name = 'c3synthetic-monkey'
         self.arms = list(range(self.L))
         self.x = {arm: sparse_suni(self.d, 3) for arm in self.arms}
+        #self.x = {arm: np.append(sparse_suni(self.d-1, 2), [1,]) for arm in self.arms}
         self.theta = suni(self.d)
+        #self.theta = np.append(suni(self.d-1)/2, [0.5,])
         self.oracle = argmax_oracle
         self.regret_avl = True
         logger.info(self)
@@ -35,19 +37,23 @@ class c3synthetic_monkey_rng:
         return serialize(self, 'arms', 'x', 'theta')
 
     def slot(self):
+        #self.xt = self.x
         self.xt = {arm: disturb(self.x[arm], self.v) for arm in self.arms}
         return self.xt
 
     def realize(self, action):
         return [pendulum() < self.theta.dot(self.xt[arm]) + self.b + np.random.normal(0, self.eps) for arm in action]
-    
+        #return [pendulum()/2+0.5 < self.theta.dot(self.xt[arm]) + self.b + np.random.normal(0, self.eps) for arm in action]
+
     def regret(self, action):
         Ew = {arm: self.theta.dot(self.xt[arm]) + self.b for arm in self.arms}
         opt = self.oracle(Ew, *self.params(True))
         p = [(self.theta.dot(self.xt[arm]) + self.b) / 2 + 0.5 for arm in action]
+        #p = [self.theta.dot(self.xt[arm]) + self.b for arm in action]
         popt = [(self.theta.dot(self.xt[arm]) + self.b) / 2 + 0.5 for arm in opt]
+        #popt = [self.theta.dot(self.xt[arm]) + self.b for arm in opt]
         return ereward(popt, self.gamma, self.disj) - ereward(p, self.gamma, self.disj)
-    
+
     def params(self, descend):
         return (self.K, descend)
 

### 2016-03-29 experiment/utils (copy).py

@@ -1,94 +1,0 @@
-from functools import reduce
-import random
-import heapq
-
-from scipy.linalg import sqrtm
-import numpy as np
-import colorama
-colorama.init()
-
-def red(s):
-    return colorama.Fore.RED + s.__str__() + colorama.Fore.WHITE
-
-def pendulum():
-    return np.random.uniform(-1, 1)
-
-def uni(x):
-    return x/np.sqrt(x.dot(x))
-
-def suni(d):
-    x = np.random.normal(0, 1, d)
-    return uni(x)
-
-def sparse_suni(d, z):
-    x = np.random.normal(0, 1, d)
-    i = set(np.random.randint(d, size=z))
-    p = np.array([idx in i for idx in range(d)], dtype=np.int_)
-    x *= p
-    return uni(x)
-
-def scat(d):
-    np.random.dirichlet((1,)*d)
-
-def scat1(d):
-    x = np.random.exponential(1, d)
-    return x / x.sum()
-
-def scat2(d):
-    s = sorted(np.random.uniform(0, 1, d-1))
-    return np.array([s[0], *[s[i+1] - s[i] for i in range(d-2)], 1-s[-1]])
-
-def scat3(d):
-    e = uni(np.ones(d))
-    x = [abs(suni(d)) for _ in range(int(15**(np.sqrt(d))))]
-    x = [v for v in x if np.random.uniform() < v.dot(e)]
-    v = random.sample(x, 1)[0]
-    return v / v.sum()
-
-def squni(d, linear=0.6):
-    Z = np.random.uniform(-1, 1, (d, d))
-    V = Z.dot(np.linalg.inv(sqrtm(Z.T.dot(Z))))
-    theta = suni(d)
-    theta *= linear / np.abs(V.dot(theta)).max()
-    lamb = suni(d)
-    lamb *= (1 - linear) / np.abs(lamb).max()
-    Q = V.dot(np.diagflat(lamb)).dot(V.T)
-    return theta, Q, lamb, V
-
-def disturb(x, h):
-    y = x + h * np.random.normal(0, 1, x.shape)
-    return uni(y)
-
-def argmax_oracle(U, K, descend):
-    return [p[1] for p in heapq.nlargest(K, [(U[arm], arm) for arm in U])][::2*descend-1]
-
-def reward(ctr, gamma, disj):
-    conj = not disj
-    for c, click in enumerate(ctr):
-        if click == disj:
-            return int(conj) + gamma ** c * (int(disj) - int(conj)), c
[…]

### 2016-03-30 rebuttal_cascadingBandit.txt
update rebuttal

@@
-- All reviewers: seemingly linear regret/reward curves
+-Reviewers: seemingly linear regret/reward curves
 
 The learning curves will show a good concave/convex shape when n, the number of rounds, is small.
-For example, the curve in Fig.1(b) shows a good concave shape when n <= 2000, during which the cosine similarity between \theta_* and its estimate \hat{\theta} increases to 0.995.
-This means that our algorithm learns quickly, because the learning task is relatively easy with a small d=10, the dimention of \theta_*.
-When n>2000, due to the randomness, the accuracy of $\hat{\theta}$ increases very slowly.
-Thus there is a small probability that $\hat{\theta}$ leads to a wrong action choice.
+For example, the curve in Fig.1(b) shows a good concave shape when n <= 2000, during which the cosine similarity between \theta* and its estimate \hat{\theta} increases to 0.995.
+This means that our algorithm learns quickly, because the learning task is relatively easy with a small d=10, the dimension of \theta*.
+When n>2000, due to the randomness, the accuracy of \hat{\theta} increases very slowly.
+Thus there is a small probability that \hat{\theta} leads to a wrong action choice.
 Such a small probability is decreasing very slowly, resulting in the almost linear shape of the curves when n is large.
-We will test harder learning tasks with larger d to make the curves exhibit more obvious concave shape.
+We will test harder learning tasks with larger d to make curves exhibit more obvious concave shape.
 
-- Reviewer 1: on an example of a more general reward function, and unclear last paragraph of Sec. 4.3
+-Reviewer 1: examples of a more general reward function, and last paragraph of Sec. 4.3
 
@@
 4.3 (last paragraph) and experimented it in Sec.
-5.3 with Figure 3(c).
+5.3 with Fig.
+3(c).
 Perhaps our explanation is unclear, so we provide further details here.
@@
 After an action is played, the observed feedback is the delays of edges up to the first blocked edge (this delay of this blocked edge is observed if it is less than 2\tau).
-The mean delay of an edge e is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta_*.
+The mean delay of an edge e is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta*.
 
-In this example, we can use observed delays and contexts and apply linear regression to estimate \theta_*, as given in the paper.
+In this example, we can use observed delays and contexts and apply linear regression to estimate \theta*, as given in the paper.
 However, the expected reward as a function of mean edge delays is a complicated function without a closed-form: we need to transform the mean delay of a cutoff exponential distribution to the blocking probability with threshold \tau.
@@
 Yet we can still argue that this function is monotone and Lipschitz continuous, and thus obtain regret bound from Theorem 4.3.
-In contrast, if we treat edge blocked or unblocked as the feedback in order to fit into the existing cascading bandit framework, we cannot apply linear regression to learn the latent vector \theta_*, because the probability of edge being blocked is not a linear combination of contexts and \theta_*.
+In contrast, if we treat edge blocked or unblocked as the feedback in order to fit into the existing cascading bandit framework, we cannot apply linear regression to learn the latent vector \theta*, because the probability of edge being blocked is not a linear combination of contexts and \theta*.
 
-- Reviewer 1: 1/p* may be arbitrarily large and not tied to the reward function
+-Reviewer 1: 1/p* may be arbitrarily large and not tied to the reward function
 
@@
 
-- Reviewer 1: unclear last paragraph of Sec. 5.3
+-Reviewer 1: last paragraph of Sec. 5.3
 
@@
 
-- Reviewer 4: unclear Line 657-663
+-Reviewer 1: monotonicity
 
-We intend to say that, using the same approach as in Abbasi-Yadkori et al. 2011, we can obtain matching regret bound as cascading bandits after removing the contextual information.
+This assumption can be removed if the problem can easily find A_t = argmax_{A, w in confidence ellipsoid} f(A,w).
 
-- Reviewer 4: unclear context in Sec. 5.3
+-Reviewer 4: Line 657-663
+
+We intend to say that, using the same approach as in Abbasi-Yadkori 2011, we can obtain matching regret bound as cascading bandits after removing the contextual information.
+
+-Reviewer 4: context in Sec. 5.3
 
 Context is generated randomly.
-Without context, CombCascade only selects the action that performs well for the *average* context, which is certainly much worse than C^3-UCB, which uses context to learn latent \theta_* and selects much better actions on *every* context after the learning period.
+Without context, CombCascade only selects the action that performs well for the *average* context, which is certainly much worse than C^3-UCB, which uses context to learn latent \theta* and selects much better actions on *every* context after the learning period.

### 2016-03-30 rebuttal_cascadingBandit.txt
update rebuttal

@@
--Reviewers: seemingly linear regret/reward curves
+-Reviewers: experiments
 
@@
 This means that our algorithm learns quickly, because the learning task is relatively easy with a small d=10, the dimension of \theta*.
-When n>2000, due to the randomness, the accuracy of \hat{\theta} increases very slowly.
-Thus there is a small probability that \hat{\theta} leads to a wrong action choice.
-Such a small probability is decreasing very slowly, resulting in the almost linear shape of the curves when n is large.
+When n>2000, the small probability of \hat{\theta} leading to a wrong action choice is decreasing very slowly, resulting in the almost linear shape of the curves when n is large.
 We will test harder learning tasks with larger d to make curves exhibit more obvious concave shape.
@@
 
-This assumption can be removed if the problem can easily find A_t = argmax_{A, w in confidence ellipsoid} f(A,w).
+This assumption (together with the offline oracle assumption) can be removed if the problem can easily find A_t = argmax_{A, w in confidence ellipsoid} f(A,w).
 

### 2016-03-30 experiment/flowtest.py
remove deprecated flowtest; update comments

@@ -1,98 +1,0 @@
-import logging
-logfile = logging.FileHandler('log')
-logfile.setLevel(logging.INFO)
-logconsole = logging.StreamHandler()
-logconsole.setLevel(logging.DEBUG)
-logging.basicConfig(format='%(name)s-%(levelname)s: %(message)s', level=logging.DEBUG, handlers=[logfile, logconsole])
-logger = logging.getLogger('Main')
-
-import time
-seed = int(time.time() * 100) % 339
-import numpy as np
-np.random.seed(seed)
-import random
-random.seed(seed)
-logger.info('===== Numpy/Python random seed = {0}'.format(seed))
-
-import matplotlib.pyplot as plt
-
-from agent import contextual_cascading_sherry
-from agent import contextual_cascading_gsherry
-from agent import contextual_cascading_monkey
-from agent import contextual_full_monkey
-from agent import contextual_full_lijing
-from agent import absolute_cascading_ucb
-from environment import contextual
-from environment import c3synthetic_monkey_rng
-from movielens import c3_movielens_rng
-from isp import c3synthetic_isp_rng
-from isp import c3synthetic_Zisp_rng
-from isp import c3synthetic_Cisp_rng
-
-def flowtest_monkey(T, **kw):
-    logger.info('Monkey flowtest')
-    logger.info('Require rng initialization')
-    logger.info('\n    '.join(str(k) + ' ' + str(v) for k, v in kw.items()))
-    s = c3synthetic_monkey_rng(**kw)
-    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
-    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=False, descend=False), T=T)
-    reward, regret, similarity = contextual_cascading_sherry(contextual(s, cascade=True, rgamma=False, descend=True), T=T)
-    reward, regret, similarity = contextual_full_lijing(contextual(s, cascade=False, rgamma=False, descend=False), T=T)
-    reward, regret, similarity = absolute_cascading_ucb(contextual(s, cascade=True, rgamma=True, descend=False), T=T)
[…]

### 2016-03-30 rebuttal_cascadingBandit.txt

@@
 The reward of the action is 1 if no edge on the path is blocked, and 0 if some edge on the path is blocked.
-After an action is played, the observed feedback is the delays of edges up to the first blocked edge (this delay of this blocked edge is observed if it is less than 2\tau).
+After an action is played, the observed feedback is the delays of edges up to the first blocked edge (the delay of this blocked edge is observed if it is less than 2\tau).
 The mean delay of an edge e is determined by the linear combination of the context of the round x_{t,e} and the latent vector \theta*.
